### 2023-06-05 visual/dorsal/latex/neuro/response/ResponseLetter.tex
init

\documentclass[12pt,journal,onecolumn]{IEEEtran}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\usepackage[table,xcdraw]{xcolor}
\usepackage[TABBOTCAP]{subfigure}
\usepackage{bm}
\usepackage{upgreek} 
\usepackage{amsmath}
\usepackage{breqn}
\usepackage{color}
\usepackage{cite}
\usepackage[none]{hyphenat}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{caption2}
\usepackage{setspace}

\usepackage{tikz}
\newcommand*{\circled}[1]{\lower.7ex\hbox{\tikz\draw (0pt, 0pt)%
		circle (.4em) node {\makebox[1em][c]{\small #1}};}}

\linespread{1.5}

\begin{document}

\begin{center}
	\textbf{\LARGE Response to Comments} 
\end{center}
\vspace{8pt}

\noindent NEUCOM-Manuscript: NEUCOM-D-21-03628R1 \\

\noindent Title: BTN: Neuroanatomical Aligning between Visual Object Tracking in Deep Neural Network and Smooth Pursuit in Brain \\

\noindent Dear Editor and Reviewers:

\textcolor{blue}{
We want to thank you and the review team for the detailed comments on our submission, and for the opportunity to revise and reconsider the paper to NEUROCOMPUTING.  
Those comments are all valuable and very helpful for revising and improving our paper, as well as the important guiding significance to our researches. 
We have studied these comments carefully and have made correction to meet with your approval. 
The responds to the reviewer's comments are labeled in blue, 
and the main corrections in the paper are marked in red to facilitate your reading. 
}

\vspace{8pt}

\newpage

\textbf{To Reviewer \#1:}

\textcolor{blue}{Thanks for the comments for our paper, we have revised the manuscript according to your recommendations as follows:}

\textbf{Comment (1).} In this paper, The author raises a viewpoint that in the visual object tracking problem, humans present behavioral modes (eye movement) that differ from the bounding box of single object tracking. 
Therefore, the main purpose is to evaluate the behavioral output mode, not only the tracking performance. 
This part needs to adds more content to explain why the evaluation of the behavioral output mode is more important which means why we need to consider brain-like score. 
Because in visual object tracking problem, the problem is the accuracy of object tracking. 
The reason for considering the result of behavioral output mode is not adequate for the reviewer.
% 为什么用行为输出模式
% 更接近于人。使模型的输出更加接近于人的响应。

\textbf{Response:} \textcolor{blue}{Thank you for your valuable comment.
%Maybe we did not explain it clearly in the previous manuscript. 
In the revised version, we have reorganized the introduction of Brain-like Tracking Score, especially the behavioral metrics. 
The purpose of behavioral benchmarks it to compute the similarity between source (e.g., a DNN model) and target (e.g., human) behavioral responses. 
% 第二段
Even within the visual behavioral domain of core object recognition, there are many similar behavioral metrics.
They use the metric of image-by-image patterns of human behavior [1]. 
For core eye object tracking tasks, human exhibits behavioral patterns that differ from ground truth labels. 
For example, in pedestrians tracking, humans may pay more attention to the head or even the face, while the visual tracking task focuses on the body or even torso.
One consequence of this is that DNNs can achieve 100\% accuracy but will not gain a perfect behavioral and cortical similarity score.
Thus, we use both the behavioral response pattern metric and cortical metric, not an overall accuracy metric, and higher scores are obtained by DNNs that produce and predict the human patterns.
Finally, we have emphasized it in Section 5.1 as follows: 
}

% 5.1章 第一段
\textcolor{red}{
``The aim of behavioral metrics is to calculate the
similarity between the DNN outputs and the human behavioral outputs in a specific problem [9]. 
In the human eye object tracking, the subjects’s attention is a circle scope and related to human pupil.
Thus, the behavioral modes (the position of eye gaze and the size of pupil) is modeled as a circle and differs from the bounding box in visual object tracking. 
Meanwhile, the main purpose is to realize human-like intelligence, not only the tracking accuracy [36]; and BTN obtains better behavioral similarity and can predict the position and scope of eye gaze well. 
Otherwise, the result is that DNNs gain perfect bounding box fitting but can not obtain a good eye gaze prediction performance. "
} \\
% APA：名字全部列出来，没有省略
%\textcolor{blue}{
%	[1] Schrimpf, M., Kubilius, J., Lee, M. J., Murty, N. A. R., Ajemian, R., \& DiCarlo, J. J. (2020). Integrative benchmarking to advance neurally mechanistic models of human intelligence. Neuron.
%} \\
\textcolor{blue}{
	[1] Rajalingham, R., Issa, E. B., Bashivan, P., Kar, K., Schmidt, K., \& DiCarlo, J. J. (2018). Large-scale, high-resolution comparison of the core visual object recognition behavior of humans, monkeys, and state-of-the-art deep artificial neural networks. Journal of Neuroscience, 38(33), 7255-7269.
} \\

%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/inconsistency.png}
%\end{figure}
%
%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/framework.png}
%\end{figure}
%\vspace{8pt}

\textbf{(2).} The paper says that the BTS may vary when the BTN is retrained. 
So only the given trained BTN is optimal. 
Does it means that the application of BTN is very limited according to its training dataset. 
How to improve the BTN so it could applied to the most conditions.

% 更好的架构对泛化能力的影响大于特定数据集上学习到的特征（权重）
% 即使权重信息并不能在任务间很好地迁移，但是网络架构可以很好地被迁移。
% 最佳的 ImageNet 模型没有给出最佳的图像特征。在 ImageNet 上训练的 ResNet 模型的特征始终优于那些在 ImageNet 上取得更高准确率的网络。
% 优化过的超参数训练的 inception v4 模型
\textbf{Response:} \textcolor{blue}{Thank you for your comment. 
The old version elaborates unclearly in explaining the training of the BTN. 
In the revised manuscript, we have rewritten our description about the discussion to make it more understandable.
Since BTN is a transferable problem, architectures transfer well across tasks.
However, it cannot be precluded that the BTS may vary when using same network architectures and different training settings. 
It is useful to improve the transfer by retraining the DNN with optimized training configurations. 
Therefore, we believe that only the given trained BTN is optimal and not all types of network structure.
In the application of BTN, we can perform grid search to select the optimal training settings, such as learning rate and weight decay, based on a validation set.
We have emphasized it in Section 7.2 as follows:
}

% 7.2章 第二段
% 只是特定训练好的模型是效果最好的，而不是网络结构就行(重新训练就可能不是最好的了)
% 具体地应用中怎么训练模型（寻找最优的训练配置）
\textcolor{red}{
``Nevertheless, the independent training configuration may be the essential characteristic that trains the DNN [68]. In addition, an auxiliary task does not have a very large impact on the score but notably improves the transfer effect [68]. 
Because the BTN is a transferable problem, it cannot be precluded that the BTS may vary when using different training settings. 
They claim that it is useful to tremendously improve the transfer effect by retraining the DNN with optimized configurations [68].
Therefore, we believe that only the given trained
BTN is optimal and not all model of network architecture. 
Practically speaking, we can perform grid search to select the optimal training settings based on a validation set."
} \\

%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/inconsistency.png}
%\end{figure}

\vspace{8pt}

\textbf{(3).} The paper has raised a brain-like tracking network model to solve object tracking problem. 
But it appears that it contributes most to establish a neuroscience-like model rather than solving the object tracking problem. 
So is it necessary to use brain-like model to solve the object tracking problem than just using DNN?
% 不是主要解决SOT的问题：可解释的问题
% DNN的必要性，为什么不用其他 类脑模型。（复杂场景）

\textbf{Response:} \textcolor{blue}{Thanks for your professional suggestions. 
The goal of our work is mainly to solve the interpretability problem of visual tracking model and implement a brain-like architecture with both high accuracy and excellent brain similarity. 
In the revised manuscript, we have analysed the motivation of our work and the reason for using the brain-like model in our introduction as follows:
}

% TODO
% 第1章 第1段
\textcolor{red}{
``Amazingly, in
trained deep neural networks (DNNs) used to classify images [2], the middle layer in DNNs can partially explain why the nerve cell in the middle layer of the visual cortex has specific activations to an image [3, 4, 5, 6, 7, 8]. 
Furthermore, these models also partly predict primate image classification behavior and evaluations [9, 10].
Excellent models of the brain provide extraordinary opportunities for brain-computer interfaces, and these methods can be utilized to produce the expected activations in the cortical pathway [11]." 
} \\
% 第1章 第2段
\textcolor{red}{
``To capture cortical processing even more strictly
in these models, continued architectural search on
traditional visual datasets alone no longer seems
to be a feasible solution. 
Even though the great tracking performance in deeper DNNs has truly increased [12, 13], it is hopeless to raise the brain-like score [9, 14]. 
In addition, at the beginning, only partial modules can be obviously mapped to corresponding regions of the visual pathway, and the relations between the small number of visual regions and the numerous and complex modules in GoogleNet [15] or Inception-v4 [16] are inconspicuous. 
Finally, the network with high accuracy in the visual task becomes increasingly deeper except for several brain-like architectures for image classification [17, 18]." 
} \\

%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/online_tracking.png}
%\end{figure}
%\vspace{8pt}

\textbf{(4).} Another suggestion is that it will be better to introduce the structure of the paper in the introduction part.
This paper has very good potential. 
The reviewer believes it could be an outstanding paper after revision.

\textbf{Response:} \textcolor{blue}{Thanks for your valuable suggestions.
In the revised manuscript, we have introduced the structure of the paper in the tail of our introduction part as follows:
}

% 第1章 第3段
\textcolor{red}{
``To address the interpretability problem of visual tracking model, in this study, we propose that aligning DNNs to anatomy will result in shallower, more interpretable, and more brain-like tracking models, named brain-like tracking network (BTN). 
The BTN is a shallow recurrent brain-like architecture of the brain pathway; hence, it has a much more brain-like structure. In section 4, we introduce the method utilized to analyse human behavioral and cortical data during object tracking. In section 5, we build a fancy measurement method for predicting eye movement behavior and neural activations on the brain-like tracking score (BTS).
In our experiments, we introduce a new benchmark dataset composed of behavioral and cortical recordings, and present an outstanding tracking result of 36.5\% at evaluating the model similarity of the visual pathway while obtaining a good tracking effect in the Tracking-Gump dataset [19]. 
We find that these results are mainly due to the brain-like architecture, in accordance with prior knowledge of the human cortical pathway processing stimuli input [17, 20, 18]. 
Finally, to compare the model activations between the RNN MT/MST in the BTN and the responses in the human middle temporal and medial superior temporal areas (MT/MST), we discover that the BTN predicts these cortical activations well, and it is also the first visual tracking model to do so on the neural recordings." 
}

%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/result_MOT_one_two_stage.png}
%\end{figure}
\vspace{8pt}

\vspace{8pt}

\newpage

\textbf{To Reviewer \#3:}

\textcolor{blue}{Thanks for the comments for our paper, we have revised the manuscript according to your recommendations as follows:}

\textbf{(1).}  The literature review is not thorough about the application and the contributions. 
To highlight the contributions, it suggests reorganizing the section of the related work. 
At least, for each contribution, it should be novel and meaningful according to a thorough literature review. 
In the literature analysis, it is recommended to read the following works and consider to discuss their similar application scenarios in the introduction and discussion, 
Improved recurrent neural network-based manipulator control with remote center of motion constraints: Experimental results; 
A teleoperation framework for mobile robots based on shared control.
% 重新组织introduction和realted work，突出重点，并引用文章。

\textbf{Response:}  \textcolor{blue}{Thank you for your kind suggestion.
The goal of our work is mainly to solve the interpretability problem of visual tracking model.
In the revised manuscript, we have reorganized the corresponding description of recurrent neural networks and related applications in the section of related work, and emphasized it as follows:} \\
% 2.1第二段
\textcolor{red}{
``To track a target, it seems to be very suitable to use recurrences and glimpses, but they have only been employed successfully in monochromatic videos with simple backgrounds [23]. 
Some [27] obtained prominent results through representations of the target detector that is the input of a recurrent neural network (RNN) [28].
However, it needs to process each full frame. 
A recent study [29] utilized an RNN cropping explicitly to build attention in humans. 
Our study is similar to [23, 30], and utilizes human attention which is implemented with a long short memory network (LSTM) to extract the movement features well in multiple frames. 
In addition, we seek to design a brain-like network that will gain a superior BTS and exceed the existing tracking models on the Tracking-Gump dataset [19]."
} \\
\textcolor{red}{
[28] Su, H., Hu, Y., Karimi, H. R., Knoll, A., Ferrigno, G., \& De Momi, E. (2020). Improved recurrent neural network-based manipulator control with remote center of motion constraints: Experimental results. Neural Networks, 131, 291-299.
} \\
\textcolor{red}{[30] 
Luo, J., Lin, Z., Li, Y., \& Yang, C. (2019). A teleoperation framework for mobile robots based on shared control. IEEE Robotics and Automation Letters, 5(2), 377-384.
} \\
\vspace{8pt}

\textbf{(2).} It is recommended to present in the first section so that it can highlight the specific scope of this article. 
The meaning of the assessment experiment should be highlighted.
% 指定文章的研究范围
% 强调评估实验的意义（作用），为什么这么设计实验

\textbf{Response:} \textcolor{blue}{Thank you very much for your helpful comment. 
In the new manuscript, we have first present in our introduction so that it can highlight the specific scope of this article as follows: \\
% 第一章第二段
\textcolor{red}{
``To capture cortical processing even more strictly in these models, continued architectural search on traditional visual datasets alone no longer seems to be a feasible solution. 
Even though the great tracking performance in deeper DNNs has truly increased [12, 13], it is hopeless to raise the brain-like score [9, 14]. 
In addition, at the beginning, only partial modules can be obviously mapped to corresponding regions of the visual pathway, and the relations between the small number of visual regions and the numerous and complex modules in GoogleNet [15] or Inception-v4 [16] are inconspicuous. 
Finally, the network with high accuracy in the
visual task becomes increasingly deeper except for
several brain-like architectures for image classification [17, 18]."
} \\
Second, we have highlighted the meaning of the assessment experiment in our introduction and Section 6.3 as follows: \\
% 第一张第三段We find that开始
\textcolor{red}{
``We find that these results are mainly due to the brain-like architecture, in accordance with prior knowledge of the human cortical pathway processing stimuli input [17, 20, 18]. 
Finally, to compare the model activations between the RNN MT/MST in the BTN and the responses in the human middle temporal and medial superior temporal areas (MT/MST), we discover that the BTN predicts these cortical activations well, and it is also the first visual tracking model to do so on the neural recordings."
} \\
% 6.3 章第一段
\textcolor{red}{
``We compared various experimental results to explain why the proposed BTN is a brain-like tracking model. 
It is easy to see that the model architecture and training procedure are slightly different from other implementations of the visual tracking model."
} \\
% 6.3.1 第一段
\textcolor{red}{
``We design a brain-like BTN that follows neuroanatomical aligning more closely than classic DNNs.
Besides, the BTN achieves good tracking performance as measured by the BTS on Tracking Gump dataset. 
Therefore, the BTN satisfies both neuroanatomical limitations in neuroscience and engineering requirements in computer vision."
} \\
% 6.3.2 第一段 前两句
\textcolor{red}{
``A feedforward neural network can not predict the trend of time series, and thus cannot capture a brain-like response of the tracking model [18, 17]. 
By using recurrent connections, the BTN is able to predict time-varying activation in the corresponding cortex."
} \\
% 6.3.3 第一段
\textcolor{red}{
``Although the tracking performance is truly improved in the later training when improving the cortical similarity, we select the epoch with maximum BTS."
} \\
}
\\

\vspace{8pt}

\textbf{(3).} Maybe it is better to discuss the possibility to improve the scope using deep learning to learn and control robot behavior in the introduction, for example, 
An Incremental Learning Framework for Human-like Redundancy Optimization of Anthropomorphic Manipulators; 
Trajectory Online Adaption Based on Human Motion Prediction for Teleoperation.

\textbf{Response:} \textcolor{blue}{Thank you very much for your valuable comment. 
In the revised version, we have improved the scope using deep learning to learn and deploy in related application in our introduction as follows:
} 
% 第1章第2段
\textcolor{red}{
``To capture cortical processing even more strictly in these models, continued architectural search on traditional visual datasets alone no longer seems to be a feasible solution. 
Even though the great tracking performance in deeper DNNs has truly increased [12, 13], it is hopeless to raise the brain-like score [9, 14]. 
In addition, at the beginning, only partial modules can be obviously mapped to corresponding regions of the visual pathway, and the relations between the small number of visual regions and the numerous and complex modules in GoogleNet [15] or Inception-v4 [16] are inconspicuous. 
Finally, the network with high accuracy in the visual task becomes increasingly deeper except for several brain-like architectures for image classification [17, 18]. "
} \\
\textcolor{red}{[13] Luo, J., Huang, D., Li, Y., \& Yang, C. (2021). Trajectory Online Adaption Based on Human Motion Prediction for Teleoperation. IEEE Transactions on Automation Science and Engineering.
} \\
\textcolor{red}{[14] Su, H., Qi, W., Hu, Y., Karimi, H. R., Ferrigno, G., \& De Momi, E. (2020). An incremental learning framework for human-like redundancy optimization of anthropomorphic manipulators. IEEE Transactions on Industrial Informatics.
} \\
\\
\vspace{8pt}

\textbf{(4).} Figure 5 is not clear and we would suggest adding more details and labels to make it clear.

\textbf{Response:} \textcolor{blue}{Thank you for your kind suggestion.
Maybe we did not explain it clearly in the previous manuscript. 
We have emphasized it in Figure 5 as follows:
}
\begin{figure}[H]
	\centering 
	\includegraphics[width=0.5\textwidth]{imgs/tracking.png}
\end{figure}
\vspace{8pt}

\textbf{(5).} There should be a further discussion about the limitation of the current works, in particular, what could be the challenge for its related applications.
% 当前工作的局限性，并提出以后可能的应用（脑机接口、机械手）

\textbf{Response:} \textcolor{blue}{Thank you for your kind suggestion. 
We discuss the limitation of the current works and the challenge for its related applications in Section 7.2 as follows: 
} \\
% 7.2 第二段
\textcolor{red}{
``Nevertheless, the independent training configuration may be the essential characteristic that trains the DNN [68]. In addition, an auxiliary task does not have a very large impact on the score but notably improves the transfer effect [68]. Because the BTN is a transferable problem, it cannot be precluded that the BTS may vary when using different training settings. They claim that it is useful to tremendously improve the transfer effect by retraining the DNN with optimized configurations [68].
Therefore, we believe that only the given trained BTN is optimal and not all model of network architecture. Practically speaking, we can perform grid search to select the optimal training settings based on a validation set."
} \\
% 7.2第一段
\textcolor{red}{
``The proposed BTN can be utilized in the traditional visual object tracking task. Besides, it is a more interpretable brain-like tracking model and can be utilized to predict the position of eye gaze and the expected activations in cortical pathway."
} \\
% 第一章第一段 最后一句
\textcolor{red}{
``Excellent models of
the brain provide extraordinary opportunities for brain-computer interfaces, and these methods can be utilized to produce the expected activations in the cortical pathway [11]."
} \\
%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/result_MOT_one_two_stage.png}
%\end{figure}
\vspace{8pt}

%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/result_MOT_one_two_stage.png}
%\end{figure}

\textbf{(6).} To let readers better understand future work, please give specific research directions.

\textbf{Response:} \textcolor{blue}{Thank you for your kind suggestion. 
In the revised manuscript, we have fixed it in Section 7.3 and 8 as follows: \\
}
% 7.3最后一段
\textcolor{red}{
``In general, we indicate that the brain-like model is a prospective opportunity to cooperate for deep learning and neuroscience. We compare these DNNs through similarity quantification using the BTS and assess the metrics of various behavioral and neural datasets on BTS. 
For the BTN, we demonstrate that an anatomical model of the cortex according to alignment and recurrent structure can learn cortical mechanisms well through cortical activation prediction and frame-by-frame behavior. 
In this way, we can simultaneously obtain high tracking performance and the prominent brain-like model."
} \\
% 8，最后两句
\textcolor{red}{
``Furthermore, the model with neuroanatomical alignment can better predict the neural response of human brain. 
We believe the proposed BTN could encourage novel inspirations in the interpretability of DNN 
and even motivate the development of brain-computer interfaces."
}

%\textbf{[1]} Gu, X. , et al. "Temporal Knowledge Propagation for Image-to-Video Person Re-Identification." International Conference on Computer Vision.
\vspace{8pt}

\vspace{8pt}

\newpage

\textbf{To Reviewer \#5:}

\textcolor{blue}{Thanks for the comments for our paper, we have revised the manuscript according to your recommendations as follows:}

\textbf{(1).} In Equation (14), the description of the formula symbol is missing.

\textbf{Response:} \textcolor{blue}{Thank you for your kind suggestion. 
We have fixed it in the revised version as follows: \\
}
% 5.2 最后一段
\textcolor{red}{
The Pearson correlation coefficient $s_r$ constitutes the final neural similarity score for visual motion cortex as follows:
}
\begin{figure}[H]
	\centering 
	\includegraphics[width=0.4\textwidth]{imgs/pearson.png}
\end{figure}
\textcolor{red}{
where $y^\prime$ is the model activation, $y$ is the actual activation. $\bar{y}$ and $\bar{y}^\prime$ are the corresponding median over all individual neural response values.
}
\\
\vspace{8pt}

\textbf{(2).} Please add some figure descriptions to Fig 3 and proofread the manuscript.

\textbf{Response:} \textcolor{blue}{Thank you for your valuable suggestion. 
First, we have added detailed figure descriptions to Fig 3 and proofread the manuscript as follows: 
}

\begin{figure}[H]
	\centering 
	\includegraphics[width=0.6\textwidth]{imgs/structure_analysis.png}
\end{figure}

\vspace{8pt}

\textbf{(3).} It would be interesting to discuss the limitations of the proposed approach.

\textbf{Response:} \textcolor{blue}{Thank you for your professional suggestion. 
In the revised manuscript, we have discussed the limitations of the proposed approach in Section 7.2 as follows: \\
}
% 7.2 第二段
\textcolor{red}{
``Nevertheless, the independent training configuration may be the essential characteristic that trains the DNN [68]. 
In addition, an auxiliary task does not have a very large impact on the score but notably improves the transfer effect [68]. 
Because the BTN is a transferable problem, it cannot be precluded that the BTS may vary when using different training settings. 
They claim that it is useful to tremendously improve the transfer effect by retraining the DNN with optimized configurations [68].
Therefore, we believe that only the given trained BTN is optimal and not all model of network architecture. Practically speaking, we can perform grid search to select the optimal training settings based on a validation set."
}
%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/result_MOT_one_two_stage.png}
%\end{figure}
\vspace{8pt}

\vspace{8pt}

\vspace{8pt}

\bibliographystyle{ACM-Reference-Format}
%\bibliography{test1}

\end{document}

### 2023-06-05 auditory/latex/ban.tex
init

%!TEX program = pdflatex 
% !BIB program = bibtex
%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\usepackage[table,xcdraw]{xcolor}
\usepackage[TABBOTCAP]{subfigure}
\usepackage{bm}
\usepackage{upgreek} 
\usepackage{amsmath}
\usepackage{breqn}
\usepackage{color}
\usepackage{cite}
\usepackage[none]{hyphenat}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amssymb}

\usepackage{multirow}

% Neurocomputing
\usepackage{float}
\usepackage{caption}
\usepackage{array}
\usepackage{booktabs}
% 设置超链接跳转
\usepackage[colorlinks,
linkcolor=blue,
anchorcolor=blue,
citecolor=blue]{hyperref} 
\usepackage{amsmath}

% 改变字体颜色
\usepackage{color,xcolor}
\usepackage{makecell}

% 智能引用
%\usepackage{hyperref}
%\usepackage{cleveref}
%
%% 跨文件引用
\usepackage{xr}
\externaldocument{figs/prediction_accuracies}

% include文件不分页
%\usepackage{newclude}

% 给表格添加注脚
\usepackage{threeparttable}
\usepackage{footnote}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{BAN: Neuroanatomical Aligning in Auditory Recognition between Deep Neural Network and Human Brain}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Haidong~Wang,~Jianhua~Zhang,~and Ke Nai,% <-this % stops a space
	\thanks{H. Wang and J. Zhang are with the School of Computer Science and Electronic Engineering of Hunan University, Key Laboratory for Embedded and Network Computing of Hunan Province, Changsha 410082, China (e-mail: wanghaidong@hutb.edu.cn; zhangjianhua@hutb.edu.cn;
		naike@hnu.edu.cn).}
	\thanks{M. Wen is with State Grid Hunan Electric Power Company Limited Economical \& Technical Research Institute, Hunan Key Laboratory of Energy Internet Supply-demand and Operation, Changsha 410000, China (e-mail: hnjyy1903wen@126.com).}
% % <-this % stops a space
}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Inspired by neuroanatomy, deep neural networks (DNNs) have recently developed from shallow network to exceedingly deep structures, providing excellent auditory recognition performance.
However, conventional DNNs usually do not easily connect with brain areas on account of their excessive network depth and absent biological constraints, such as recurrent connections. 
We propose a brain-like auditory network (BAN) with four neuroanatomically mapped regions and recurrence, guided by the brain-like auditory score (BAS), 
a novel benchmark to measure the model similarity of the human auditory recognition pathway. 
In addition, we propose that the middle temporal and medial superior temporal (T2/T3) areas in the cerebral cortex are equivalent to the designed network structure on the basis of auditory perception pathway, 
and indicate that the metrics between the neuroanatomical similarity in cerebral cortex and auditory recognition of the DNN are compatible. 
Despite having excellent recognition performance on the Music genres dataset, the BAN has achieved a high BAS. 
In summary, this research builds a BAN, a brain-like and recurrent DNN, as the first model of the cortical pathway of auditory recognition.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords} 
Auditory Recognition, Deep Neural Network, Brain-like Model, Neuroanatomical Similarity. 
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\begin{figure*}
	\centering
	\includegraphics[width=6.7in]{figs/introduction.pdf}
	\caption{
		\textbf{
		Collaborative design between a DNN and neuroanatomy with a BAS.} 
		Through the quantitative brain-like score, we refer to the human brain and utilize acquired knowledge to enlighten the design of the BAN. 
		The BAN includes four regions that are mapped into the primary auditory cortex (A1), the belt or peripheral area (Belt), parabelt cortex (PB) and the areas of middle and superior temporal cortex (T2/T3). 
		CONV\textsubscript{V1} is the classical convolutional layer and performs preprocessing to reduce the data size.
		The RNN\textsubscript{Belt} and RNN\textsubscript{PB} and RNN\textsubscript{T2/T3} is recurrent neural network, as depicted in Section~\ref{sec:cornet_s_def} for details.
		The the upper-right image corresponds to the auditory recognition activation and predicted generes labels in the brain-aligned models, 
		while lower-right image represents the cortical activation and human choice with the same stimulus in the far left,
		which demonstrates the relationship between computer prediction performance and brain auditory recognition response with the BAS, as depicted in Section~\ref{sec:experiments}.
	}
	\label{fig:introduction}
\end{figure*}

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.+

% problem: time, optimization joint
% the development of object detection
% joint detection and embeding, -> problem
% joint detection and association
% contribution: end-to-end, data preparation, training

% /data3/dong/data/brain/auditory/Music_Genre_Classification_Pytorch-master/report.pdf, 1. Music
% 一定要在路径中添加latex/bin/win32/bibtex.exe，否则参考文献为问号，且不会报错
\IEEEPARstart{H}{earing} is crucial for identifying sound for humans, it is particularly important because of its role in the understanding and production of music.
Genre classification is a task that aims to predict music genre using audio signal.
Music genres are a set of descriptive keywords that convey high-level information about a music clip (jazz, classical and rock .etc).
According to Tzanetakis and Cook~\cite{tzanetakis2002musical}, the genre of music is a categorical label created by humans to characterize musical works.
The genre of music is characterized by a common characteristic shared by members.
These characteristics are typically associated with musical instruments, rhythmic structures and harmonized content.
Automatic music genre classification can help or replace human users in the process and will be a valuable addition to the music information retrieval system.
According to Nam~\cite{nam2018deep}, music genre classification has a significant impact on auditory recognition and recommendation of music streaming services.
In the above mentioned musical classification and tagging task solving methodology, it is very important to make the computer aware of the pattern of music and identify them.
The characteristics of this traditional framework are critical to the design of pipeline through feature engineering and classifier production.

When humans distinguish music, it is important to tell machines the feature inside music, just they distinguish genres through the sound of musical instruments or through rhythm.
This is commonly called hand engineering using domain knowledge.
But as we move on to the era of deep learning after 2015, a variety of attempts and high performance begin to emerge.
The deep learning methodology leverages less domain knowledge and allows feature learning.
In general, the deep learning methodology builds pipeline through linear part, line transformation, nonlinear part activation function, and optional pooling operation.
As you pass through these layers, the model learns feature and enables end-to-end learning.

Deep learning has made great progress in building the candidate model of the neuromechanism in the neurological community~\cite{kubilius2019brain-like}. 
Amazingly, in trained deep neural networks (DNNs) used to classify images~\cite{Deng2009ImageNet}, the middle layer in DNNs can partially explain why the nerve cell in the middle layer of the visual cortex has specific activations to an image~\cite{yamins2014performance,khaligh2014deep,gucclu2015deep,murugesan2017brain,cichy2016deep,yamins2016using}. 
Furthermore, these models also partly predict primate image recognition behavior and cortical activation~\cite{rajalingham2018large,kubilius2016deep}.
Excellent models of the brain provide extraordinary opportunities for brain-computer interfaces,
and these methods can be utilized to predict the expected activations in the cortical pathway~\cite{bashivan2019neural}.

To capture cortical processing even more strictly in these models, continued architectural search on traditional visual datasets alone no longer seems to be a feasible solution. 
Even though the great performance in deeper DNNs has truly increased~\cite{ILSVRC15,luo2021trajectory}, it is hopeless to raise the brain-like score~\cite{rajalingham2018large,su2020incremental}. 
In addition, at the beginning, only partial modules can be obviously mapped to corresponding regions of the visual pathway, 
and the relations between the small number of visual regions and the numerous and complex modules in GoogleNet~\cite{szegedy2015going} or Inception-v4~\cite{szegedy2017inception} are inconspicuous. 
Finally, the network with high accuracy in the visual task becomes increasingly deeper except for several brain-like architectures for image classification~\cite{TangSchrimpfLotter2018Recurrent, kar2019evidence}.

To address the interpretability problem of auditory recognition model, in this study, we propose that neuroanatomical aligning DNNs will result in more interpretable, more shallower, and more brain-like models, named brain-like auditory recognition network (BAN).
The BAN is a shallow recurrent brain-like architecture of the brain pathway; 
hence, it has a much more brain-like structure. 
In section \ref{sec:data_analysis}, we introduce a method utilized to analyse cortical data and human behavioral during auditory recognition. 
In section \ref{sec:bas}, we build a fancy measurement method for predicting auditory recognition behavior and neural activations on the brain-like auditory recognition score (BAS). 
In our experiments, we introduce a new benchmark dataset composed of behavioral and cortical recordings, 
and present an outstanding recognition result of at evaluating the model similarity of the auditory recognition pathway while obtaining a good prediction effect in the Music genres dataset~\cite{nakai2022music}. 
We find that these results are mainly due to the brain-like architecture, in accordance with prior knowledge of the human cortical pathway processing stimuli input~\cite{TangSchrimpfLotter2018Recurrent, yin2020deep, kar2019evidence}. 
Finally, to compare the model activations between the RNN\textsubscript{T2/T3} in the BAN and the responses in the human middle temporal and superior temporal areas (T2/T3), we discover that the BAN predicts these cortical activations well, 
and it is also the first auditory recognition model to do so on the neural recordings.

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)

\section{Related Works}

% 音频识别相关的神经网络
\subsection{Deep neural network}\par
Many works have recently shown that salient objects are extracted by a series of foveal views~\cite{mnih2014recurrent,draw}.
The object extraction module in the BAN is implemented with a two-dimensional gaussian filter~\cite{RATM} that is neuroanatomically explainable.
Focusing on specific appearance representations may be as important as spatial attention. 
An approach with recurrence can adaptively change the filter of the convolution module, therefore changing it to presentations on a frame and optimizing model performance~\cite{stollenga2014deep}. 
The filters of the dynamic filter network (DFN)~\cite{brabandere2016dynamic} are obtained online based on the input feature, and the DFN implements model compression without degrading the accuracy. 
Input-dependent state transitions can help to learn the markovian decision model~\cite{karl2017deep}. 
We do not follow the results, and use the idea to predict the salient feature.

To track a target, it seems to be very suitable to use recurrences and glimpses, but they have only been employed successfully in monochromatic videos with simple backgrounds~\cite{RATM}. 
Some~\cite{ning2017spatially} obtained prominent results through representations of the target detector that is the input of a recurrent neural network (RNN)~\cite{su2020improved}.
However, it needs to process each full frame. 
A recent study~\cite{gordon2017re3} utilized an RNN cropping explicitly to build attention in humans. 
Our study is similar to~\cite{RATM,luo2019teleoperation}, and utilizes human attention which is implemented with a long short memory network (LSTM) to extract the movement features well in multiple frames. 
In addition, we seek to design a brain-like network that will gain a superior BAS and exceed the existing tracking models on the Tracking-Gump dataset~\cite{gaze_forrest}.
\par

% 人类的音频识别 
\subsection{Auditory Recognition}
There have been many successful auditory recognition researches. 
Some eye movement detection methods are proposed according to the existing plentiful datasets that have annotated eye movement data~\cite{dorr2010variability,mathe2012dynamic,hooge2017is,blstm_class}. 
Many of the existing classification methods, which are designed using motionless input, only process saccades and fixations. 
Therefore, these methods cannot detect smooth pursuit and prevent the detection of brain-like correlations with smooth pursuit. 
In order to address this issue, a multi-observer smooth pursuit method (MOSP)~\cite{mosp} that can differentiate three primary eye movements, including saccade, fixation and smooth pursuit, 
and acquire good performance evaluation is designed~\cite{blstm_class}.
In addition, to accurately explain the domain of  intelligence as a brain-like model in the human brain and cognitive sciences, 
the brain-score has been proposed in the research of an integrated benchmark in the field of computer vision~\cite{schrimpf2020integrative}.

In this work, we take full advantage of the latest achievements. 
By utilizing these excellent eye movement classification and computer vision methods, 
we can process functional magnetic resonance imaging (fMRI) and gaze data in the studyforrest dataset~\cite{gaze_forrest} 
and detect corresponding cortical regions associated with saccadic and smooth pursuit in Tracking-Gump.
In addition, based on model activation and cortical activation, we designed the BAS to measure their similarity.

\section{BAN: Brain-like Auditory Network}
In this section, we introduce the proposed BAN with three steps. 
First, we indicate the motivation and design criteria in our methods.
Second, we detail each component in the BAN pipeline. 
Finally, we introduce the loss function to train the BAN. \par

\subsection{Design criteria}
Our aim is to obtain a high auditory recognition brain-likeness between DNN and human brain.
Additionally, auditory recognition in our brain shows through human choices. 
In the pathway of auditory recognition, primary auditory cortex (A1) is the first stage to preprocess the input signals, 
Belt and PB integrate sound signal across space,
and T2/T3 generates predictive auditory labels~\cite{b11,b13,b14}.
\par
% todo

Inspired by the pathway of auditory recognition in brain, we build neuroanatomical mapping from cortical regions to DNN layers, as depicted in Figure~\ref{fig:introduction}.
For model comparison, we build the mapping by examining the layer in DNN that understands activations well in a specific cortical region.
Ideally, such activations will already be predicted by the model with no superfluous parameters. 
Therefore, the BAN consists of four neural network modules including a convolution layer and three recurrent layer.
And they are the analogy to auditory recognition pathway A1, Belt, PB, T2/T3.
And recognition predictor that converts the output of T2/T3 to corresponding action selection responses, as depicted in Figure~\ref{fig:pipeline}. 
This plain idea of explicit brain areas segmentation is an important step to design a brain-like auditory recognition model, 
and we are committed to finding more universal structures. 
Examples include an entire model as a neural network with no difference in cortical areas
and various connections that may improve BAS in future work.
In addition, we follow these two criteria to design the BAN~\cite{kubilius2018predict}:

(1) \textbf{Architecture}: In models with similar recognition performance, we prefer a brain-like network because it is easier to understand and can meet the anatomical constraints.
And we use DNNs because their neurons are the basic unit of data processing, 
and all neural activations in DNNs can be clearly mapped to cortical activation~\cite{yamins2016using}.
In addition, recurrent connections are naturally considered for auditory recognition on account of the temporal attributes in the audio sequence.
Activations in the auditory ventral pathway also have a temporal attribute; 
therefore, the BAN is assumed to generate activations in time series.

(2) \textbf{Predictivity}: 
There is more correct behavior output in intermediate layers and final outputs that meet neuroanatomical constraints (neural responses). 
This make our model have an ability to predict cortical activation and human category choice behavior.

We now introduce the pipeline for BAN.

\subsection{BAN pipeline} \label{sec:cornet_s_def}

Given the input audio sequence $A$ and attention parameters $a_t$, the fovea (imitating spatial attention) selects a foveal view $f_t$. 
Moreover, we use an appearance selector, parameterized with appearance $\alpha _t$ including V1 and this dorsal pathway and ventral pathway, to obtain the tracked target representations $m_t$ 
and update hidden state $h_t$ in LSTM.
Then, we decode the output of LSTM and use it to infer the eye movement $\Delta p_t$, spatial attention $a_{t+1}$ and the appearance attention $\alpha _{t+1}$ in the next frame.  
Appearance attention is driven by top-down information $\alpha _t$ and bottom-up (the foveal view $f_t$) information. 
However, spatial attention only relies on top-down information $a_t$.
In this case, bottom-up information only has localized impacts and relies on salience input at a position, 
but top-down information combines global features into localized analysis. 
The attention mechanism, which intensified with recurrence, imitates the visual cortex~\cite{attention}.
Then, we detail each component of the brain-like tracking architecture.

%\begin{figure*}
%	\centering
%	\includegraphics[width=5.7in]{figs/pipeline.pdf}
%	\caption{
	%		\textbf{
		%			The designed architecture in visual object tracking in humans.} 
	%		The believable cortical areas implementing particular roles in smooth pursuit are indicated with rectangular modules.
	%		The foveal view $f_t$ is obtained in the input frame $F_t$ with the spatial selector in the fovea. 
	%		V1 and the ventral pathway learn the appearance representations $v_t$, 
	%		and neurons in the dorsal pathway (including V1 and MT/MST) segment the salient object $d_t$ and background on the foveal view.
	%		The refined representations $m_t$ are utilized to compute the working memory $h_t$.
	%		Specifically, the FEF may be more important for initiating pursuit learning based on the target velocity,
	%		and we combine FEF output $o_t$ and dorsal stream output $d_t$ into the next module. 
	%		The cerebellum and brainstem together (including pontine nuclei (PN), flocculus, vermis and vestibular nuclei (VN)) are modeled by fully connected layers (FCs) to generate attention $a_{t+1}$, appearance $\alpha_{t+1}$, and eye position correction signals $\Delta p$,
	%		even the final eye movement ($\Delta p_t$) via the oculomotor.
	%		All black arrows indicate that information flows within one time-step, 
	%		while the gray colored arrows represent the temporal connections.  
	%	}
%	\label{fig:pipeline}
%\end{figure*}

\subsubsection{Cochlear and MFCC features}
For the mel-frequency cepstral coefficient (MFCC) model, the MIR toolbox was used to extract multiple music-related features from the dataset (Lartillot et al., 2008).
Consistent with a previous neuroimaging study on music (Alluri et al., 2012), we extracted the following 24 features: 
RMS energy as the loudness feature; 
zero-crossing rate, 
high energy–low energy ratio, 
spectral centroid, 
spectral roll-off, 
spectral entropy, 
spectral flatness, 
roughness, 
spectral spread, 
spectral flux, 
and sub-band flux (with nine sub-bands) as timbral features; 
pulse clarity, 
fluctuation centroid, 
and fluctuation entropy as rhythm features; 
and mode and key clarity as tonal features. 
For loudness and timbral features, the frame duration was set to 25 ms, with a 50\% overlap between the two adjacent frames. 
For rhythm and tonal features, the frame duration was set to 3 s, with a 33\% overlap. 
Each feature was averaged across 1.5 s. 
In addition, we used the MIR toolbox to extract MFCC features with 12 channels (Lartillot et al., 2008). 
Feature extraction of the MIRT and MFCC models was also restricted within 100–8,000 Hz. 
The number of features used in the MIRT and MFCC models was 24 and 12, respectively.

\subsubsection{Primary Auditory Cortex}
Typical, input is a data matrix represented by a time-frequency representation. 
Typically there is a Mel-spectrogram.

The spatial selector selects the foveal view $f_t$ for the current frame $F_t$,
and its output is transmitted to two interconnected cortical pathways.
The ventral pathway recognizes the tracked targets 
and the dorsal pathway learns motion features in the field of view. 
We present the dorsal pathway with the MT/MST that analyses motion features, as depicted in Figure~\ref{fig:pipeline};
and computes a foreground segmentation $d_t$ of the foveal view.

(1) \textbf{Retina}: 
The spatial attention mechanism in our model pipeline is modeled according to~\cite{RATM}. 
An input frame $F_t \in R^{W \times H}$ forms matrices $M_t^x \in R^{w \times W}$ and $M_t^y \in R^{h \times H}$.
A row of the matrix contains a gaussian distribution. 
The position and width of the gaussian distribution determine which parts of the input frame are selected as the foveal view $f_t$ in the retina.
Therefore, the foveal view $f_t \in R^{h \times w}$ can be denoted as
\begin{equation}
	f_t = M_t^y F_t (M_t^x)^T.
\end{equation}
We represent attention with the distributive center, the variance and the stride of the distributive center of continuous matrix rows.
Unlike the study~\cite{hart}, only the stride and center are predicted through LSTM;
however, variance only relies on stride.
The operation avoids extravagant bias when estimating a smaller variance, contributing to a faster learning speed. 
In addition, the utilized size of $f_t$ relies on the experimental analysis.

(2) \textbf{Ventral Pathway}: 
The ventral pathway converts the foveal view $f_t$ into a fixed dimension vector $v_t$ including spatial and appearance features of the tracked object. 
The network structure architecture relies on the specific experimental analysis. 
In the architecture of the ventral pathway, we implement V1 using a CNN, which is a mutual module in the ventral pathway and dorsal pathway.
Generally, however, we implement V1 using several convolutional layers and max pooling layers. 
These layers, which imitate V1 in humans~\cite{theoretical_neuroscience}, are shared with the dorsal pathway.
In addition, the pipeline is split into dorsal and ventral pathways. 
Finally, we implement the ventral pathway by CNN that extracts object representations $v_t$.

(3) \textbf{Dorsal Pathway}: 
The dorsal pathway (MT/MST) is implemented as a DFN~\cite{brabandere2016dynamic} 
and is used to address spatial relations between the foreground and background. 
Let FC$(\cdot)$ indicate a fully connected layer.
MT/MST utilizes appearance representation $\alpha_t$ to dynamically predict the convolutional filter $\phi_t$
\begin{equation}
	\left\{ \phi _t ^i \right\}_{i=1}^N = \text{FC}(\alpha_t).
\end{equation}
The filters with corresponding nonlinearities in $N$ convolutional layers are applied to the feature in V1. 
Then, we apply a $1 \times 1$ convolution and a sigmoid function to convert the representation into a two-dimensional mask $d_t$.
Every point in $d_t$ indicates how likely the pursued target is occupied.

The position map of the dorsal pathway is integrated over the object representations learned by the ventral pathway, which simulate the noise restraining mechanism in the visual system. 
This can handle occlusion and avoid drift, because the target representation is not overwritten in LSTM when the current frame has no representations of the pursued target. 
Therefore, the output of ventral and dorsal pathways are integrated as
\begin{equation}
	m_t = \text{FC}(conc(v_t \odot d_t)),
\end{equation}
where $\odot$ indicates the Hadamard product that performs salient object extraction through the representation mask, 
and $conc$ means a concatenation operator that concatenates all rows of a matrix into a vector.

\subsubsection{Belt and PB}

The proposed method depends on the ability to estimate the object appearance and position in the next frame; 
and therefore, it heavily relies on state prediction. 
The LSTM can utilize spatial-temporal and appearance features, 
and enables the proposed model to handle occlusion and drifting target representations, such as a tracked target obscured by other distractors.

The LSTM module, presented in Figure~\ref{fig:pipeline} and named the FEF, utilizes the output error to predict eye movement. 
Similar predictive actions exist when smooth pursuit is demonstrated in the FEF area that accepts the output of the dorsal stream~\cite{b11,b13,b14}. 
The output error goes to zero when the delay between object and eye movement is decreased in model training; 
thus, LSTM requires inferring eye motion without image input.
The refined representations $m_t$ are used to update the hidden state $h_t$ in the FEF. 
\begin{equation} \label{LSTM}
	h_t, o_t = \text{LSTM}(h_{t-1}, m_t).
\end{equation}

\subsubsection{Middle and Superior Temporal Cortex}

Then we utilize the output $d_t$ and $o_t$ to estimate eye movement $\Delta p_t$, attention $a_{t+1}$ and appearance $\alpha_{t+1}$.
\begin{equation} \label{FC}
	\Delta p_t, \Delta a_{t+1}, \alpha_{t+1} = \text{FC}(conc(d_t), o_t),
\end{equation}
\begin{equation} \label{attention}
	a_{t+1} = a_t + tanh(c) \Delta a_{t+1},
\end{equation}
where $c$ is a trainable coefficient initialized with a low parameter to restrict the update size during learning. 
Equations (\ref{LSTM}) to (\ref{attention}) describe the information update. 
We calculate the gaze position with an accumulation of attention variations. 
Because spatial attention is learned to estimate the position of the tracked object in the next frame, as depicted in Section~\ref{sec:loss}, a gaze position $p_t$ relative to the attention at time $t$ is predicted.
\begin{equation}
	p_t = a_t + \Delta p_t.
\end{equation}

In addition, we refer to the discoveries and the idea~\cite{b9} that the brainstem and the cerebellum both instantiate an inverse dynamics controller (IDC)~\cite{purkinje_IDC}. 
Like~\cite{b9}, we suppose that the IDC is perfect, and thus we can denote 
\begin{equation}
	\Delta p_t = \Delta p,
\end{equation}
where $\Delta p$ is the low pass filter of eye motion.
Based on this hypothesis, we will not implement IDC in our study.

\subsection{Loss} \label{sec:loss}

We train the proposed BAN by optimizing an assembly of losses: a tracking loss, a series of attention losses and an auxiliary loss. 
The BAN loss $L_{b}$ is given by
\begin{equation}
	L_{b} = L_t + L_a + L_u.
\end{equation}
Detailed information on the BAN loss is described below.

\subsubsection{Tracking Loss}
To locate the tracked target, we design the tracking loss between the output of the BAN and the true label. 
We refer to the study~\cite{UnitBox} and denote the tracking loss as the negative logarithm of their intersection over union (IoU) between predicted bounding box $p_t$ and ground truth $\hat{p}_t$:
\begin{equation}
	L_t = -\log(\mbox{IoU} ( \frac{p_t \cap \hat{p}_t}{p_t \cup \hat{p}_t} )).
\end{equation}

\subsubsection{Attention Loss}
The attention mechanism selects the tracked object from the input frame $F_t$.
To train the BAN better, we utilize three attention loss terms.
The first item makes the intersection area between the predicted attention $a_t$ and the bounding box $p_t$ as large as possible. 
The second item prevents obtaining a very large width, and the log functions are applied to maintain stability in the calculation. 
The third item restrains background noise while focusing entirely on the tracked target, e.g., gazing at a particular object moving in a crowd. 
To achieve this, we elaborately design a loss that selects only the tracked target.
For the attention $a_t$ and bounding box $p_t$, $r(a_t, p_t)$ indicates a binary mask that has the same size as the output of V1. 
$r(a_t, p_t)$ is one where the bounding box and the foveal view intersect.
Finally, the third item is denoted as the cross entropy between $r(a_t, p_t)$ and $d_t$.
\begin{equation}
	L_a = -\log (\frac{a_t \cap p_t}{p_t}) - \log (1 - \frac{a_t \cap F_t}{a_t \cup F_t})
	- r(a_t, p_t) \log(d_t).
\end{equation}

\subsubsection{Auxiliary Loss}
We use L2 regularization to regularize the dynamic filter parameter $\phi_t(\alpha_t)$ and the model parameter $\theta$.
\begin{equation}
	L_u = \frac{1}{2} \left\vert \left\vert \phi_t \right\vert \right\vert _2 ^2 
	+ \frac{1}{2} \left\vert \left\vert \theta \right\vert \right\vert _2 ^2.
	%- \sum_{i} \log (\lambda_i^{-1})
\end{equation}

\section{Data Analysis} \label{sec:data_analysis}
To compare the similarity between DNN tracking and human smooth pursuit, we first extract the smooth pursuit from various eye movements 
and then select the corresponding brain areas and activations.

\subsection{Feature assignment}
To examine the representational basis of music, the following features are assigned to the stimulus sounds.

\subsubsection{Genre-label features}
The genre-label features consisted of 10 features corresponding to the 10 music genres.
Values of either 1 or 0 are assigned to the entire time duration of a 15s music clip (consisting 0f 10 TRs) to denote the music genre of the target music clip.

\subsection{fMRI analysis}

\subsubsection{fMRI data processing}
% Correspondence, 2.5.1
% 头动矫正
Motion correction is performed for each run using the Statictical Parameter Mapping toolbox (SPM 12).
% EPI: epipolar plane image 核极线平面
% 两个平面的参数化，分别为相机平面和图像平面
All volumes are aligned to the first EPI image for each participant.
Low-frequency drift is removed using a median filter with a 240 s windows.
To augment model fitting accuracy, the response for each voxel is normalized by subtracting the mean response and then scaling it to the unit variance.
We use FreeSurfer~\cite{dale1999cortical,fischl1999cortical} to identify the cortical surfaces from the anatomical data and register them with the voxels of the functional data.
We use only cortical voxels as targets of the analysis for each participant.
For each participant, we use the voxels identified in the cerebral cortex in the analysis (53,421-64,700 voxels per participant).

% Correspondence, 2.5.1
\subsubsection{Voxel-wise encoding model fitting}
For each of the above models, cortical activation for each voxel is fitted using a set of linear temporal filters that captured the slow hemodynamic response and its coupling with brain activaty~\cite{nishimoto2011reconstructing}.
% 样本数即为音乐片段的数目
A feature matrix $ F_E \ [T \times 5N] $ is modeled using concatenated sets of $ [T \times N] $ feature matrices with five temporal delays of 1.5, 3, 4.5, 6, and 7.5 s ($ T $ is the number of samples; $ N $ is the number of features). 
The cortical response $ R_E \ [T \times V] $ is modeled using the feature matrix $ F_E $ times the weight matrix $ W_E \ [5N \times V] $ (V is the number of voxels):
% 特征 经过权重变换转变为 皮层响应
\begin{equation}\label{cortical_response}
	\hat{R}_E = F_E W_E
\end{equation}

% Correspondence, 2.5.1， We
We conducted an L2-regularized linear regression using the training dataset (4,800 samples, 7,200 s) to obtain the weight matrix $ W_E $.
% 使用随机重采样 10次 划分训练集和测试集 进行训练和测试
The optimal regularization parameter was evaluated via random resampling of the training dataset into two subsets, with 80\% of the dataset being used for model fitting and the remaining 20\% being used for model validation.
This random resampling procedure is repeated 10 times.

% \include* 配合 \usepackage{newclude} 实现include文件不分页（但是参考文献引用都变成0了！！！
\begingroup  % 使用\include时，包在中间的文件都不会分页
\let\clearpage\relax 
\endgroup

\begin{table*}
	%\begin{threeparttable}

	\centering  % 使表格整体居中
	\caption{Prediction accuracy in each anatomical region}
	\label{tab:prediction_accuracies} % label需要在caption后面，否则引用时是问号

	% \linewidth: 这指得是目前环境的宽度，是依赖于上下文的一个宽度值
	\resizebox{\linewidth}{!}{ %此处！表示根据根据宽高比进行自适应缩放
		\begin{tabular}{llllllll} 
			\toprule
			&    	    Genere-Label &		  Regressor &   		 Cochlear &  		  MTF &   	 			MIRT & 			  		MFCC &    				Voice 			    \\
			\midrule
			L.LSTG &  	0.079 $\pm$ 0.009 &   0.069 $\pm$ 0.017 &    0.070$\pm$0.022 &    0.095 $\pm$ 0.017 &   0.074 $ \pm $ 0.016 &   0.034 $ \pm $ 0.007 &	 0.078 $ \pm $ 0.015 \\
			L.HG &  	0.153 $\pm$ 0.027 &   0.144 $\pm$ 0.023 &    0.159$\pm$0.017 &    0.194 $\pm$ 0.040 &   0.159 $ \pm $ 0.023 &   0.095 $ \pm $ 0.027 &	 0.098 $ \pm $ 0.030 \\
			L.HS &  	0.222 $\pm$ 0.085 &   0.199 $\pm$ 0.076 &    0.200$\pm$0.043 &    0.261 $\pm$ 0.050 &   0.223 $ \pm $ 0.075 &   0.104 $ \pm $ 0.038 &	 0.169 $ \pm $ 0.065 \\
			L.PT &  	0.121 $\pm$ 0.027 &   0.111 $\pm$ 0.028 &    0.104$\pm$0.033 &    0.130 $\pm$ 0.027 &   0.114 $ \pm $ 0.027 &   0.058 $ \pm $ 0.017 &	 0.114 $ \pm $ 0.044 \\
			R.LSTG &  	0.100 $\pm$ 0.023 &   0.081 $\pm$ 0.026 &    0.102$\pm$0.016 &    0.131 $\pm$ 0.029 &   0.100 $ \pm $ 0.015 &   0.053 $ \pm $ 0.009 &	 0.103 $ \pm $ 0.023 \\
			R.HG &  	0.152 $\pm$ 0.022 &   0.136 $\pm$ 0.034 &    0.163$\pm$0.029 &    0.213 $\pm$ 0.045 &   0.161 $ \pm $ 0.011 &   0.099 $ \pm $ 0.018 &	 0.125 $ \pm $ 0.030 \\
			R.HS &  	0.198 $\pm$ 0.035 &   0.178 $\pm$ 0.026 &    0.188$\pm$0.037 &    0.248 $\pm$ 0.040 &   0.205 $ \pm $ 0.045 &   0.102 $ \pm $ 0.048 &	 0.145 $ \pm $ 0.031 \\
			R.PT &  	0.116 $\pm$ 0.040 &   0.108 $\pm$ 0.041 &    0.131$\pm$0.017 &    0.140 $\pm$ 0.069 &   0.118 $ \pm $ 0.018 &   0.059 $ \pm $ 0.023 &	 0.090 $ \pm $ 0.046 \\
			\bottomrule
		\end{tabular}
		%		\input{figs/prediction_accuracies}				
	}

	%\end{threeparttable}
\end{table*}

% Correspondence, 2.5.1, The test
The test dataset comprised 600 samples (900 s).
The signal-to-noise ratio is increased by averaging four repetitions of the test datasets.
We calculated prediction accuracy by means of the Pearson's correlation coefficient between the predicted signal and the measured signal in the test dataset.
The resulting $ p $ values are corrected for multiple comparisons within each participant using the false discovery rate (FDR) procedure~\cite{benjamini1995controlling}.
Mean prediction accuracy of each encoding model is calculated by averaging the prediction accuracy of all voxels within the participant-specific region-of-interest mask.
% \include 跨文件引用表格是问号，而\include正常（不会创建新的页面）
The prediction accuracies of all models are summarized in Table~\ref{tab:prediction_accuracies}.
% Table 1 note
Note: Average prediction accuracies of six models across all participants (mean $ \pm $ SD) calculated in the eight anatomical regions of interest.
The prediction accuracy of the genre-label model is also calculated by regressing out the voice effect.
% 颞上回的41区、42区和颞横回为听觉皮层区
LSTG, lateral superior temporal gyrus; 
% 赫氏回、颞横回（隐在外侧裂内）：在外侧沟下壁上，几条颞横沟之间的短而斜行的脑回
HG, Heschl's gyrus;
% 赫氏沟、颞横沟：位于颞叶上面，大脑外侧沟下壁上 的几条短沟。
HS, Heschl's sulcus;
% 颞平回
PT, planum temporale;
MTF, modulation-transfer function;
MIRT, music information retrieval toolbox;
MFCC, mel-frequency cepstral coefficient.
All model fitting and analyses are performed using custom software written on Matlab.
For data visualization on the cortical maps, pycortex is used~\cite{gao2015pycortex}.

\subsubsection{Genre-representation ROI mask}
% Correspondence, 2.5.3, To obtain
To obtain robust estimates of the genre-related cortical regions, we use the following resampling procedure:
First, the training dataset is divided randomly into training samples (80\%) and validation samples (20\%). 
Using the optimal regularization parameter estimated in the analysis of the genre-label model, we then perform encoding model fitting using the genre-label features with the training samples and calculated the prediction accuracy with the validation samples.
Model fitting is performed using L2-regularized linear regression.
The random resampling procedure is repeated 50 times, 
and the voxels showing significant prediction accuracy (FDR corrected) for more than 80\% of the repetitions are selected for the ROI mask.
We induce 468 voxels in the ROI mask for participant ID01,
453 for participant ID02,
1,686 for participant ID03,
576 for participant ID04, 
and 530 for participant ID05.
Unless otherwise indicated, the following analyses are performed using the extracted ROI mask.

\subsubsection{Decoding of genre labels}
In the decoding model, the cortical response matrix $ R_D \ [T \times 5V] $ was obtained by concatenating the set of $ [T \times V] $ response matrices with five temporal delays of 1.5, 3, 4.5, 6, and 7.5s.
The genre-label matrix $ G \ [T \times 10] $ was modeled using the cortical response matrix $ R_D $ times the weight matrix $ W_D \ [5V \times 10] $:
\begin{equation}\label{equ:genre_label_matrix}
	\hat{G} = R_D W_D.
\end{equation}
The weight matrix $ W_D $ was estimated using an L2-regularized linear regression with the training dataset following the sample procedure used for the encoding model fitting.
We use linear regression rather than a categorical classifier, such as logistic regression, to maintain the similarity between the encoding and decoding analyses.
To calculate the classification accuracy, we first assigned genre-label indices (1 to 10) to each time point by taking the argmax of the decoded genre-label matrix.
Then, we estimated the representative genre-label index for each music clip by the majority voting method~\cite{jang2008music}.
Specifically, the genre-label that was most frequently assigned for all time points during a single music clip was regarded as a representative genre of that clip.

In the activity-based approach, we obtained a response matrix $ R_D $ for each participant, whereas we used the feature matrix $ F_D \ [T \times N]$ in the feature-based approach.

\subsection{Behavioral analysis}
To confirm that brain activation in response to music genres was related to the behavioral performance of genre classification, we performed additional behavioral experiments.
These experiments were conducted in a soundproof room by the same participants who participated in the MRI experiments, as well as an additional 21 participants who had not taken part in the MRI experiments.
Participants were first asked to listen to three original music clips (30s) per genre as a reference;
these clips were selected at random from the 460 clips not used in the MRI experiment.
In this training session, correct music genres were informed to the participants.
Participants then listened to the 60 music clips used as the test dataset in the MRI experiment and judged the music genre to which the target music clip belonged by filling in 1 of 10 cells on the answer sheet provided.
Participants listened to each music clip only once and in the same order of presentation as in the fMRI experiment.
Of the 21 non-MRI participants, data from one participant were excluded because the average accuracy (30.0\%) was outside the mean $ \pm \ 3*SD $ range (and also outside the median 3*interquartile range) for all participants.

\section{BAS: Brain-like Auditory Score} \label{sec:bas}
In this part, we present the BAS metrics, which measure the similarity between DNN model and the human cortex. 
The BAS is a metric tested on specific experimental datasets, which can be both cortical and behavioral measurements.

In order to obtain the quantitative metrics about brain similarity, we refer to the open-sourced platform brain-score~\cite{SchrimpfKubilius2018BrainScore} and propose the BAS, a well-designed metric that evaluates a model's ability to predict 
(a) the average behavior choice when listening an target music clip of the Music Genre dataset~\cite{nakai2022music}, 
and (b) the average activation of each cortical position to each input music clip in human visual areas ST on the Music genre neuroimaging dataset~\cite{nakai2022music}.
To evaluate BAN on a unified metric, we compute the average of behavioral and cortical metrics.

\subsection{Cortical metrics}
\label{sec:neural-pred}

We utilize the cortical metrics, which infer activations of the human cortex, such as responses in motion cortical MT/MST, to measure how fine the model predicts the specific input frame in the DNN~\cite{yamins2014performance}. 
This metric requires two groups of inputs with the form of $\text{input} \times \text{neuroids}$, where neuroids are either model interlayer activations or neural recordings.

In total, 149 frames including a tracked object that appeared randomly on a natural scene are presented to 13 subjects,
and the neural responses are collected from 2177 MT/MST voxels. 
In addition, we report the most predictive layer or specific model regions in the BAN.

In our experiment, the relations are fitted to map from a DNN to a cortex, and these relations are utilized to predict the responses in the provided frames. 
To accelerate the process, we reduce the activation dimensionality to specified components using principal component analysis (PCA)~\cite{2002Principal}. 
We utilize the activations from MT/MST to learn the fits. 
The Pearson correlation coefficient $s_r$ constitutes the final neural similarity score for visual motion cortex as follows:
\begin{equation}
	s_r=\frac{\sum_{i=1}^{n} (y_i-\bar{y}) (y_i^\prime - \bar{y}^\prime) }{\sqrt{\sum_{i=1}^{n} (y_i - \bar{y})^2 (y_i^\prime - \bar{y}^\prime)^2 }},
\end{equation}
where $y^\prime$ is the model activation, $y$ is the actual activation and $n$ is the corresponding feature dimension in DNN. $\bar{y}$ and $\bar{y}^\prime$ are the corresponding median over all individual neural response values.

\subsection{Behavioral metrics}
The aim of behavioral metrics is to calculate the similarity between the DNN outputs and the human behavioral outputs in a specific problem~\cite{rajalingham2018large}. 
In the human eye object tracking, the subjects's attention is a circle scope and related to human pupil.
Thus, the behavioral modes (the position of eye gaze and the size of pupil) is modeled as a circle and differs from the bounding box in visual object tracking. 
Meanwhile, the main purpose is to realize human-like intelligence, not only the tracking accuracy~\cite{schrimpf2020integrative}; 
and BAN obtains better behavioral similarity and can predict the position and scope of eye gaze well. 
Otherwise, the result is that DNNs gain perfect bounding box fitting but can not obtain a good eye gaze prediction performance.

The utilized 12 video sequences including a salient object moving against a natural background are shown to humans for approximately 20s 
and their gaze scopes are recorded to track the salient object, and depicted in Section~\ref{sec:datasets}. 
To analyse and evaluate the proposed model, we used the subject eye movement and model responses of 149 images in 12 image sequences.
A total of 149 of those frames, where each frame is the input of DNN, are used to predict the eye gaze scope.
Then, this behavioral predictivity is measured through the scope of eye attention in each frame.

The resulting output of the DNN is the bounding box of the tracked target, 
and the subject's attention is a circular scope (center coordinates $x$, $y$ and the radius).
Therefore, the eye movement predictivity or behavioral score can be modeled as the IoU between the actual eye attention circular scope of gaze $S_{roi}^a$ and the bounding box of the DNN's predictions $S_{roi}^b$. 
We compute the overall behavioral metrics~$s_b$ among all frame sequences as the eye movement predictivity score as follows: 
\begin{equation}
	s_b=\frac{area(S_{roi}^a \cap S_{roi}^b) }  { area(S_{roi}^a \cup S_{roi}^b) }.
\end{equation}

\subsection{Overall score}
In order to measure how well the BAN performs integrally, we use the BAS as a combination of the IoU behavioral metric and MT/MST cortical metrics.
The BAS $s_{t}$ presented below is the mean of the two scores. 
\begin{equation} \label{equ:score_btn}
	s_{t} = \frac{s_b + s_r}{2}.
\end{equation}
The design of the BAS is not normalized in various score magnitude because this possibly penalizes scores with small variances.
So we treat each score for significance fairly for the BAS.

\section{Experiments} \label{sec:experiments}
Here we indicate the experiments and validity of our proposed BAN with three steps. 
First, we introduce the datasets and detailed implementation in our method.
Second, we demonstrate that the BAN is a valid and brain-like pursuit model.
Finally, we discuss the model design mechanism and the relationship between DNN and neuroscience.

\subsection{Datasets} \label{sec:datasets}
We use the GTZAN dataset which has been the most widely used in the music genre classification task.
The dataset contains 30-second audio file including 10 different genres including reggae, classical, country, jazz, metal, pop, disco, hiphop, rock and blues.

% \makecell [c]
\begin{table}[h]
	\centering
	\footnotesize
	\caption{The segmentation and mergence of raw film.
		Raw segments of Forrest Gump that constitute the true input. 
		The 7 segments are merged~\cite{2014A}, and then, they are segmented into 8 segments, each corresponding to an fMRI recording. 
		TRs indicates the number of repetition times.
		The unit of duration is seconds.
		In these experiments, we utilize the 2002 movie release.}

	\label{tab:movie_seg}

	\begin{tabular}{p{0.9cm}<{\centering}p{1.2cm}<{\centering}p{1.45cm}<{\centering}p{1.15cm}<{\centering}p{0.95cm}<{\centering}}
		\toprule[1.5pt]
		{Video ID} & {Begin Frame} & {Frame Number} & {Duration}  & {TRs}   \\ \midrule[1pt]
		1       & 0           & 22,550      & 902.00 & 451.00 \\ 
		2       & 22,150      & 22,050      & 882.00 & 441.00 \\ 
		3       & 43,802      & 21,900      & 876.00 & 438.00 \\ 
		4       & 65,304      & 24,400     & 976.00 & 488.00 \\ 
		5       & 89,305     & 23,100     & 924.00 & 462.00 \\ 
		6       & 112,007     & 21,950     & 878.00 & 439.00 \\ 
		7       & 133,559     & 27,100     & 1,084.00 & 542.00 \\
		8       & 160,261     & 16,876     & 575.04 & 337.52 \\ 
		\bottomrule[1.5pt]
	\end{tabular}

\end{table}

\begin{table}[h]
	\centering
	\footnotesize
	\caption{Frame sequences 1-12 to construct our Tracking-Gump dataset.
		These 12 short videos in which only one salient object appears in the video sequence are selected. 
		This ensures that most of subjects will gaze at the object constantly.}

	\label{tab:track_seg}

	\begin{tabular}{p{1.0cm}<{\centering}p{0.9cm}<{\centering}p{1.6cm}<{\centering}p{1.5cm}<{\centering}p{0.7cm}<{\centering}}
		\toprule[1.5pt]
		Segment ID & Video ID  & Start Frame    & End Frame  & TRs   \\ \midrule[1pt]
		1     		  & 3 			   & 02:30.00 	   & 02:48.00  & 10  		  \\
		2  	 		  & 4 			   & 14:50.00 	   & 15:14.00  & 13   		  \\
		3   		  & 5 			   & 01:32.00 	   & 01:48.00  & 9   		  \\
		4   		  & 5 			   & 05:02.00  	   & 05:20.00  & 10   		  \\
		5   		  & 6 			   & 00:08.00 	   & 00:24.00  & 9   		  \\
		6   		  & 6 			   & 06:56.00 	   & 07:10.02  & 8   		  \\
		7   		  & 6 			   & 09:42.00  	   & 09:56.01  & 8   		  \\
		8   		  & 6 			   & 12:26.00 	   & 12:44.00  & 12		      \\
		9   		  & 7  			   & 06:44.00 	   & 07:06.00  & 12		      \\
		10  		  & 7 			   & 07:26.00 	   & 08:28.00  & 32		      \\
		11  		  & 7 			   & 08:30.00 	   & 08:52.00  & 12		      \\
		12 			  & 7 			   & 10:40.00 	   & 11:10.00  & 16		      \\
		\bottomrule[1.5pt]
	\end{tabular}

\end{table}

\subsection{Implementation details}
% 数据增强
However, we thought that the absolute amount of data was insufficient to learn the parameters of CNN.
Therefore, we conducted the data augmentation using the given data.

Data augmentation is the process by which we create new synthetic training samples by adding small perturbations on our initial training set.
The objective is to make our model invariant to those perturbations and enhance it ability to generalize.
In order to this to work adding the perturbations must conserve the same label as the original training sample.

\begin{itemize}
	\item Add noise. 
	Add the data sampled from the Gaussian distribution at the same position by 0.005 times as much as the length of the data, scale normalize to a smaller number and then apply element wise add to the data.

	\item Shift. We slightly shift the starting point of the audio, then pad it to original length.
	Roll array elements along a given axis.
	Elements that roll beyond the last position are re-introduced at the first.

	\item Speed change. 
	Time stretching is the process of changing the speed or duration of an audio signal without affecting it pitch.
	Time stretch an audio series by a fixed rate.
	Slightly change the speed of the audio, then pad or slice it.
	We conducted two augmentations by dividing the standard of the speed change by one second and a standard of variation of 0.9-1.1.

	\item  Pitch shift.
	Pitch shift is the adjustment of the frequency part while preserving the structural characteristics of the music.
	Bins per octave is held at 12 and pitch change is 2.
	This was reflected in the characteristics of Western music structure.

	\item Pitch and speed.
	% 同时产生音高和速度的变化
	Simultaneously engenders pitch and speed variants.

	\item Multiply value.
	Value change is similar to add noise.
	Bug multiply the data sampled from the uniform distribution at the same position.
	This uniform distribution value is contain low 1.5, high 3.

	\item Percussive.
	Using harmonic-percussive sound separation (HPSS), separation factor parameter into the decomposition process that allows for tightening separation results.
	The percussive part is expected to reflect the musical characteristics of particular genre.

	\item After feature engineering, divide data.
	In 3D CNN, we have feature length of 1024 in the 128 mel frequency region.
	30 seconds of data will be compressed in 1024 area.
	However, learning 30 seconds of data at once is not very effective.
	It is hypothesized that human beings are able to grasp only about 3 to 4 seconds of information in order to reflect their musical characteristics.
	For sample CNN, this is done by dividing the waveform.
\end{itemize}

Each visual cortical region is implemented by a certain DNN performing some classical operations, such as convolutional operation and nonlinear activation. 
These network modules are equivalent to visual regions, but we change the number of neurons in each cortical region.
Considering the computational costs, we utilize Python with the TensorFlow package~\cite{abadi2015tensorflow} 
and model the V1 with the headmost 3 convolutional module from the revised AlexNet~\cite{imagenet}. 
The input size of raw AlexNet is $227 \times 227$ and is downsized to $14 \times 14$ after 3 convolutional modules. 
Because low-resolution features will lead to poor tracking results, 
we convert the preliminary step size of 4 to 1 
and remove a pooling module to retain spatial features, as depicted in Figure~\ref{fig:structure_analysis}. 
In this way, the size of the obtained feature is $14 \times 14 \times 384$, and the size of the input foveal view is $56 \times 56$.
In addition, at the tail of V1, there is a 20$\%$ probability of randomly omitting the feature. 
The ventral pathway includes a convolutional module in which the kernel size is $1 \times 1$. 
The filters of the DFN are $3 \times 3$ and $1 \times 1$.
We used 100 LSTM units with the zoneout operation~\cite{zoneout} that have a probability of 0.05.
We train BAN~\cite{curriculum}, and utilize a similar learning configuration except for the learning rate, which is $2 \times 10 ^{-6}$.
The starting sequence length is five and increases every twelve iterations.

% 流派分类
\subsection{Genre classification accuracy based on brain activity, behavior, and acoustic models}
In the MRI experiments in this study, participants listened passively to music stimuli and did not carry out any genre classification tasks during scanning.
To confirm that participant's brain activity captured sufficient information to distinguish different music genres in the current experimental setting, we conducted a genre classification based on brain activity using a decoding model approach.
We evaluated the confusion matrix, along with the classification accuracy (the diagonal elements of the confusion matrix), using cortical activation within the genre-representing ROI masks.
The results of classification varied across genres, in that classical music was always classified accurately (average classification accuracy, 100\%), whereas classification performance for rock music was poor across all participants (13.3\% $\pm$ 18.3\%).
We also found that participants tended to classify reggae music as hip-hop music (confusion from reggae to hip-hop, 43.3\% $\pm$ 14.9 \%), whereas they tended to classify rock music as country music (confusion from rock to country, 33.3\% $\pm$ 11.8\%).
The activity-based confusion matrices were highly consistent across all participants (Spearman's correlation coefficient, $ \rho = 0.553 \pm 0.062$; $ p < 0.001 $ for all combinations of participants).

% 行为测试
To investigate how brain activation associated with music genre is related to behavioral performance during genre classification, we conducted an additional behavioral test for each participant (MRI participants) after the MRI scanning.
The confusion matrix revealed that participants' genre classification performance varied for each genre, in that classical music was always accurately recognized (average classification accuracy, 100\%), while rock music was less accurately recognized across all participants (36.7\% $\pm$ 13.9 \%).
Behavioral confusion matrices identified brain activity-like error tendencies, such that rock music tended to be classified as country music (confusion from rock to country, 20.0\% $\pm$ 13.9\%).
The behavior-based confusion matrices were highly consistent across all participants (Spearman's correlation coefficient, $ \rho = 0.669 \pm 0.038 $; $ p < 0.001 $ for all combinations of participants).
The confusion matrices of behavior and brain activity were significantly correlated for all participants (Spearman's correlation coefficient, $ \rho = 0.438 \pm 0.081 $, $ p < 0.001 $), suggesting that the genre representational specificity of human behavior mimicked of brain activity.

Further, because the MRI participants listened to the music twice (once in the MRI scanner and again in the behavioral test), there may have been a learning effect.
Moreover, it is necessary to test whether the five MRI participants have similar perceptual properties for music genres as those of the general population.
To confirm the generalizability of the behavioral results of these participants, we recruited an additional 21 participants for the behavioral tests only (non-MRI participants).
The non-MRI participants exhibited variable genre classification accuracy (mean $\pm SD $, 56.3\% $ \pm 6.1\% $; max, 68.3\%; min, 43.3\% ), with performance similar to those of the MRI participants, in that they always recognized classical music accurately (100\%) whereas they did not always do so with rock music (17.5\%). 
Accordingly, the average behavioral confusion matrices of the MRI participants and the non-MRI participants were significantly correlated ($ \rho = 0.826, p < 0.001 $).

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{figs/confusion_matrix}
	\caption{
		\textbf{
			Classification precision of the proposed method on Music Genres dataset. 
		}
		For different audio sequences, the predicted classification results are identified by genres.
		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
	}
	\label{fig:confusion_matrix}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{figs/predicted_results}
	\caption{
		\textbf{
			Classification precision of the proposed method on Music Genres dataset. 
		}
		For different audio sequences, the predicted classification results are identified by genres.
		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
	}
	\label{fig:predicted_results}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{figs/specific_class}
	\caption{
		\textbf{
			Classification precision of the proposed method on Music Genres dataset. 
		}
		For different audio sequences, the predicted classification results are identified by genres.
		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
	}
	\label{fig:specific_class}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{figs/investigate_misclassifications}
	\caption{
		\textbf{
			Classification precision of the proposed method on Music Genres dataset. 
		}
		For different audio sequences, the predicted classification results are identified by genres.
		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
	}
	\label{fig:investigate_misclassifications}
\end{figure}

% 皮层组织
\subsection{Genre-representing cortical organization} \label{sec:cortical_organization}
Genre-representing cortical areas were assessed using the genre-label model.
For all participants, significant prediction accuracy was observed in the bilateral STG ($ p < 0.05 $, with FDR correction).
% 使用重采样 对每一个受试者都确定一个ROI
To identify cortical areas that robustly represented music genres independent of sample selection, we determined the genre-representing functional ROI for each participant.
We performed this using a resampling procedure.
This analysis revealed significant prediction accuracies in the bilateral STG,
and functional ROI was used as an inclusive mask in subsequent analyses.

% 用经过压缩维度的 流派标签权重 来映射到 皮层表面
To examine the relative contribution of each cortical voxel to the 10 music genres, we mapped the representation of the music genres on the cortical surface using PCA with genre-label weights.
For each voxel within the ROI mask, we extracted the estimated weighted matrix of the genre-label encoding models.
By averaging five temporal delays, we obtains matrices of $ [10 \times V_i] $ ($ V_i $ is the number of voxels for participant $ i, i=1,...,5 $).
To obtain a general result across participants, we concatenated the weight matrix of the five participants.
Then, we used PCA to perform dimensionality reduction on the aggregated weight matrix $ [10 \times \sum_{i=1}^{5} V_i] $. 
% 10 个主成分分量
PCA produced a score matrix $ \sum_{i=1}^{5} V_i \times 10 $ and loading matrix $ [10 \times 10] $.
The score matrix indicates how 10 PCs are represented in each cortical voxel.
The loading matrix indicates the contribution of each PC to the representation of 10 music genres.
To demonstrate the representational relationship between the music genres, the 10 genres were mapped onto the 2-D space using the loading of PC1 and PC2 (i.e., the first and second columns of the loading matrix) as the x-axis and the y-axis, respectively.
Genres were colored further in red, green, and blue based on the relative PCA loadings in PC1, PC2, and PC3 (i.e., the first to third columns of loading matrix), respectively.
The top 3 PC components explain 70.9\% of the total variance. 
To represent the cortical organization of music genres for each participant, we extracted and normalized the PCA scores from each participant's voxels (i.e., for each row of the score matrix).
The resultant cortical map indicates the relative contribution of each cortical voxel to the target PC.
By combining the PCA scores of the top three PCs (i.e., the first to the third rows of the normalized score matrix) of each participant, we visualized how each cortical voxel is represented by the 10 music genres.
Each cortical voxel was colored based on the relative PCA scores of PC1, PC2, and PC3, corresponding to the color of the genre in the 2-dimensional space.
This analysis revealed various genre-specific representations within the bilateral STG.
Among the multiple subregions of STG, music genres were represented more clearly in Heschl's sulcus (HS) and the lateral STG (LSTG) than in Heschl's gyrus, the planum temporal (PT), or the lateral sulcus (LS) (except participant ID03, who displayed gene-specific activations in large brain regions including PT).
Although we observed considerable individual variability, there was a marked consistency in that the contribution to pop, disco, country, and hip-hop music was larger in the LSTG than in either the HS or the HG, whereas the contribution to blues music was large around HS.

To illustrate the relative relationships between the cortical activation patterns for different music genres, we visualized the weight values of 10 music genres in each voxel using 2-D coordinates derived from the top two principal components.
Using PCA, we embedded genre-specific representation based on multiple cortical voxels (i.e.,high-dimensional data) into the 2-D space, maintaining their representational similarity.
These findings indicated that the activation patterns induced by classical and jazz music were relatively similar, as were those induced by rock and mental music, whereas blues and hip-hop music seemed to have distinct activation patterns.
Using the weight values of the genre-label model, we further visualized how the 10 music genres were represented differently in each cortical voxel based on the same 2-D coordinates.

\subsection{Genre-specific representation independent from voice stimuli}
% 嗓音刺激
Most of the hip-hop and pop music clips contained voice stimuli,  whereas the classical and jazz music clips did not.
To test whether the genre-specific cortical representation was not explained by the inclusion of voice stimuli, we performed additional encoding model analysis.
We concatenated the voice features with the original genre-label features in the encoding model fitting.
Model testing excluded the voice features from the concatenated feature matrix and the corresponding weight matrix.
In this process, the voice features indicate whether certain music clip contains voice stimuli.
As this regressor was excluded in model testing, we regressed out the effect of voice stimuli.
This model predicted activations in most of the bilateral STG ROI that were used in the original genre-label model (77.8\% $ \pm $ 19.2\% of voxels were significant across all participants; prediction accuracy, $ r=0.246 \pm 0.027 $; original genre-label model, $ r=0.284 \pm 0.025 $).
% 回归去除语音刺激后
To examine how the cortical representation of 10 music genres is affected by regressing out the voice effect, we mapped the weight values of 10 music genres in each voxel using PCA.
We also visualize the relative relationships of 10 music genres derived from the top two PCs and their representation in each cortical voxel.
Similar to the results in Sec.~\ref{sec:cortical_organization}, the activation patterns induced by classical and jazz music were relatively similar, as were those induced by rock and metal music, whereas blues and hip-hop music had distinct activation patterns.
These findings suggest that the genre-specific activation patterns were not explained merely by the inclusion of the voice stimuli.

% 可解释
\subsection{Genre-specific brain activity was explained by the spectro-temporal modulation of music genres}
Next, we tested how well acoustic feature-based genre specificity corresponds to brain-based feature specificity.
To achieve this, we extracted the acoustic features of each music stimulus using the five acoustic models (Cochlear, MTF, MIRT, MFCC, and voice).
In this study, we only show the MTF model results for the purpose of visualization;
however, the following analyses were performed similarly for all acoustic models.
Spectro-temporal modulation of each music genre was evaluated according to the feature matrix used for encoding model fitting.
Interpretable spectro-temporal information was obtained for each MTF feature by restoring the MTF feature matrix to the original size through multiplying it by the transposed PCA coefficient matrix.
Moreover, we transformed the MTF weight matrix by multiplying it by the PCA loading matrix.
In order to visualize the MTF model, we further averaged the feature values obtained at the 20 central frequencies for each of the 10 $ \times $ 10 combinations of spectral modulation $ \Omega $ (cyc/oct) and temporal modulation $ \omega $ (Hz).
Genre-specific feature vectors were calculated for the other models using the same procedure.
By averaging the MTF features for the 48 clips of the same music genre in the training dataset, we obtained reference MTF features for the 10 music genres.
When then obtained the MTF features of each cortical voxel using the weight matrix of the MTF model.
The response of each cortical voxel to spectro-temporal modulation was assessed using the transformed weight matrix.
Voxel-specific weight vectors were calculated by averaging the MTF weight values of the 48 training clips for each genre.
Voxel-specific weight vectors were calculated for the other models using the same procedure.
In order to visualize the MTF model, we further averaged the weight values obtained at the 20 central frequencies for each of the 10 $\times$ 10 combinations of spectral modulation $\Omega$ (cyc/oct) and temporal modulation $\omega$ (Hz).

To examine whether genre-representing activation patterns were explained by the extracted features, we calculated the Person's correlation coefficients between the reference genre-specific feature vector and the voxel-specific weight vector in each cortical voxel.
Through this analysis, we obtained an FBS cortical map of each music genre based on its MTF features.
The FBS map based on the MTF model was very similar to the cortical map obtained for genre-label weight, 
and they were significantly correlated for all music genres (Pearson's correlation coefficient, $ p < 0.001 $ with Bonferroni correction).
A significant correlation was observed consistently across all participants ($ r = 0.729 \pm 0.111 $), indicating that the different spectro-temporal modulations of the 10 music genres explained genre-specific activity patterns.
The FBS map also obtained for the other acoustic models, and we found that MTF model outperformed the other models (cochlear, MIRT, MFCC, and voice models) in terms of the mean correlation between the FBS maps and the genre-weight maps (Wilcoxon signed-rank test, $ p < 0.020 $ for participants except for ID02).
Although we used earphones that attenuate scanning noise, the remaining noise could have degraded the stimulus quality and modulated activity patterns in the auditory cortex.
To evaluate the effects of scanning noise on our result, we therefore performed additional analyses.
Specifically, we recorded the MRI noise inside the scanner using an MRI-compatible microphone and added this noise to the original auditory stimuli.
Since the relative intensity of noise depends on the depth of insertion, we added the noise with three different relative intensities (0.2, 0.5, and 1.0 to the mean RMS of the original stimuli).
% 当数据符合正态分布、方差齐性时，常用参数检验，如u检验、t检验等，但当数据不符合正态分布或方差不齐时，则需要利用非参数检验。
% https://www.cnblogs.com/djx571/p/10216940.html
For participants ID01, ID04, and ID05, we found that the MTF model exhibited the largest correlation coefficients between the FBS maps and genre-weight maps independent of relative noise intensities (Wilcoxon signed-rank test, $ p < 0.050 $; except for the comparison between the MTF and cochlear models for participant ID01 with noise intensities of 1.0 and 0.5, for which $ p = 0.065 $, and between the MTF and MIRT models for participant ID04 with a noise intensity of 0.5, for which $ p=0.084 $).
For participants ID02 and ID02, a relative noise intensity of 0.2 more clearly demonstrated the advantage of the MTF model (Wilcoxon signed-rank test, $ p < 0.010 $).
These results suggest that the MTF model accurately captured genre-specific cortical organization in the bilateral STG.

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{figs/investigate_predictions}
	\caption{
		\textbf{
			Classification precision of the proposed method on Music Genres dataset. 
		}
		For different audio sequences, the predicted classification results are identified by genres.
		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
	}
	\label{fig:investigate_predictions}
\end{figure}

%\begin{figure}
%	\centering
%	\includegraphics[width=.9\linewidth]{figs/structure_analysis.pdf}
%	\caption{\textbf{
		%		BTN architecture analysis.} 
	%		\textcolor{red}{
		%		We analyse four main factors including the initial step size in $\rm{CONV_{V1}}$ and the number of dynamic filter layers in $\rm{DFN_{MT/MST}}$, the number of hidden units in $\rm{LSTM_{FEF}}$ and the number of hidden units in $\rm{FC}$.
		%		Each row indicates how cortical and behavioral score change based on the trained BTN when a certain hyperparameter changes. 
		%		}
	%	}
%	\label{fig:structure_analysis}
%\end{figure}

\section{Discussion}
\label{sec:discussion}

Using fMRI, the current study revealed the cortical organization underlying different music genres.
As the genre-label model did not assume any acoustic properties, we used genre-weight maps to reflect music genre information in general.
% FBS (Feature-Brain Similarity)
Thus, it was important to obtain similar weight patterns between the genre-label model and the FBS map based on the MTF model.
The FBS map shows how the spectro-temporal modulation of each cortical voxel corresponds to the reference spectro-temporal modulation profile for each music genre.
Thus, it is likely that the weight values in the bilateral STG for the genre-label model were determined by the degree to which each STG voxel's spectro-temporal modulation property resembles that of the music stimuli.

Among the multiple subregions in STG, music genres were represented more clearly in both HS and LSTG than in the other subregions.
% 音区定位
Previous studies on frequency-selective (i.e., tonotopic) maps of the human STG have indicated that the primary auditory cortex (A1) is located around the posterior part of HG and HS accompanied by a gradient of low- to high-frequency selectivity from the anterior to posterior direction~\cite{ahveninen2016intracortical,leaver2016functional}.
While cochlear features correspond to positions in the frequency axis and may therefore reflect tonotopic properties, the MTF model further captures the modulation property around each position on the frequency axis.
% MTF 优于 耳蜗模型
Santoro et al.~\cite{santoro2014encoding} showed that the MTF model outperformed the cochlear model in terms of predicting STG activation in response to natural sound stimuli~\cite{santoro2014encoding}, which is consistent with the current results.
% norman2015distinct 音乐和说话的不同皮层通路
LSTG has been reported to represent different sound categories such as the sound of guitar versus. voice of a cat~\cite{staeren2009sound}, and it exhibits human speech-selective activation~\cite{norman2015distinct}.
The MTF model captures detailed spectro-temporal modulation properties both in human speech~\cite{elliott2009the} and in musical instruments~\cite{patil2012music}, which may explain the more general acoustic features that can encompass the feature space of simple categorical models such as genre-label or voice models.
To summarize, the spectro-temporal modulations obtained in our study seem to reflect the general processing of auditory stimuli in the bilateral STG.

Several studies have reported that perceived music genres can be decoded from brain activity.
Ghaemmaghami and Sebe~\cite{ghaemmaghami2016brain} used magnetoencephalogram and electroencephalogram datasets to classify musical stimuli as either pop or rock using SVM.
Further, Casey~\cite{casey2017music} and Sengupta et al.~\cite{sengupta2018spatial} used fMRI data with five distinct music genres, followed by activity-based multi-class classification using SVM.
However, these studies did not provide answers to how cortical representations of music genres contribute to genre classification.
Collectively, the present findings demonstrate the underlying mechanisms of such activity-based genre classification.

We investigated classification accuracy using five models (cochlear, MTF, MIRT, MFCC, and voice).
% Mel-Frequency Cepstral Coefficient / MIRtoolbox
Both the MFCC and the MIRT models were developed in the field of computational science and have been employed previously in studies of music-induced brain activity~\cite{alluri2012large,gucclu2016brains,toiviainen2014capturing}.
The cochlear model has been employed to test cortical activation in the spectral domain~\cite{de2017hierarchical};
however, it cannot capture the dynamic temporal modulation of spectra.
The MTF model was constructed based on the physiological properties of neurons in the auditory cortex~\cite{chi2005multiresolution} and is used widely in neuroscience research into auditory perception~\cite{norman2015distinct,patil2012music,santoro2014encoding,santoro2017reconstructing}.
Therefore, it is likely that the MTF model is more biologically plausible for addressing the auditory processing of music genres.
Our current findings are consistent with this view, because, of all the models, the MTF model showed the highest correlation coefficients between the FBS maps and genre-weight maps.

% 能捕获快节奏
One might argue that the fMRI signal change is too slow to capture the rapid acoustic features of music stimuli and that this could affect the model performance with up-tempo (e.g.,metal) and slow-tempo (e.g., classical) music genres.
However, the MTF model includes temporal modulations of frequency (from 2.8 to 64.0 Hz) and the estimated model weights show signals in high temporal modulation rates suggesting that this model can capture the fine-scale musical information necessary to distinguish relatively up-tempo music genres (e.g., metal and hip-hop).
Indeed, the difference in decoding accuracy in not explained by the difference in tempo, given that both classical and hip-hop music showed higher decoding accuracies.

% 使用行为实验补充 没有主动听的问题
In the MRI experiments in this study, participants listened passively to music stimuli and did not carry out any genre classification tasks during scanning.
It could be argued that we did not confirm that the participants listened attentively to the stimuli and that we overlooked the brain regions activated for top-down decision-making on music genre classification.
To address this, we conducted behavioral experiments of genre classification for MRI participants and confirmed that there were significant correlations between the confusion matrices based on brain activation and behavior.
These findings suggested that passive listening to music stimuli captured enough brain information for use in behavioral music genre classification.

In this study, we adopted a small-N design (five participants).
The small number of subjects is compensated for by the large number of samples for each participant (i.e., three hours).
The small-N design has attracted substantial attention in recent studies combining fMRI data and machine learning~\cite{smith2018small}.
Instead, of group-level statistical analyses, as are often used in conventional neuroimaging, we performed subject-wise analyses.
The correspondence of genre representation among participants was confirmed using Person's correlation of confusion matrices for both activity-based decoding and behavior-based analyses.
In contrast, cortical organization differed across participants.
% SD 标准差
In contrast, cortical organization much larger $ SD $ of prediction accuracy than the other anatomical ROI (genre-label model: left HS, $ SD = 0.085 $; mean $ SD $ across other ROIs = 0.026), indicating that the left HS is the most sensitive region to the individual variability of music genre representation.

% 语言的影响
It is worth considering whether linguistic factors could explain genre-specific organization because most classical and jazz pieces employed in the current study were instrumental (i.e., without human voice), whereas other genres included the human voice.
Previous studies have reported voice-selective and non-voice-selective cortical areas around STG~\cite{kell2018task,leaver2010cortical,norman2015distinct}.
However, our study demonstrated that such linguistic factors do not explain genre-specific patterns.
The genre-label model in our study predicted brain activity even after regressing out voice-related features.
In addition, we also showed that classical and jazz music were not confused with each other and that some music genres containing voice stimuli were not confused with each other (e.g., hip-hop and country music).
Thus, it is likely that genre-specific activation patterns in the bilateral STG reflected detailed spectro-temporal modulation even within nonvoice music pieces.

% 结果不完美的原因
Although we have shown that FBS maps and genre-weight maps largely corresponded, the correspondence is not perfect.
There are several possible reasons for such imperfection.
% 1. 容易受噪声影响
First, the FBS maps and genre-weight maps were susceptible to the noise of brain activity.
The upper limit of prediction accuracy also affects the accuracy of both FBS maps and genre-weight maps.
% 2. MTF模型本身不是最好->深度网络
Second, the MTF might not be the best model.
Indeed, an acoustic model might exist that captures more detailed characteristics of music genres.
% 3. 其他非声音特征
Third, some nonacoustic features (such as the participants' preference, knowledge, and experience related to music) may play important roles in producing the genre-specific cortical organization.
% 音乐类别的神经基础 
Further research is therefore required to clarify the detailed neural basis of music categorization.

\section{CONCLUSION}
Inspired by the visual processing mechanisms found in the human brain, our study presents a brain-like tracking model suited to the problem of visual object tracking. 
Based on the neuroanatomical limitation, the designed model has appropriate tracking performance and improved interpretability. 
In addition, we illustrate the cortical model specifically connected with the human smooth pursuit in a complicated real environment 
and develop a new way to compute the similarity between model activation and cortical activation data. 
Furthermore, the model with neuroanatomical alignment can better predict the neural response of human brain. 
We believe the proposed BAN could encourage novel inspirations in the interpretability of DNN 
and even motivate the development of brain-computer interfaces.
% artificial motion consciousness
% artificial motion intelligence

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\section*{Acknowledgment}
This work was partially supported by the National Key R$\&$D Program of China (No. 2018YFB1308604), Hunan Science and Technology Innovation Project (No. 2017XK2102) and National Natural Science Foundation of China (No.61976086, No.61672215, U1613209). Haidong Wang and Zhiyong Li are co-first authors, they contributed equally to this work. Haidong Wang and Zhiyong Li are the corresponding authors.

\bibliographystyle{IEEEtran}
\bibliography{reference}

%\appendices
%\section{Proof of the First Zonklar Equation}
%Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank

%\section{}
%Appendix two text goes here.

% use section* for acknowledgment

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

%\begin{IEEEbiography}{Michael Shell}
%Biography text here.
%\end{IEEEbiography}

% if you will not have a photo at all:
%\begin{IEEEbiographynophoto}{John Doe}
%Biography text here.
%\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage
%
%\begin{IEEEbiographynophoto}{Jane Doe}
%Biography text here.
%\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Authors/HaidongWang.eps}}]{Haidong Wang}
	 received the B.E. degree in Computer Science and Technology from Hunan University Of Technology and Business, Changsha, China, in 2014, and the M.Sc. degree in Computer Technology from the University of Chinese Academy of Sciences (UCAS), Beijing, 	China, in 2017. At present, he is currently pursuing the Ph.D. degree in Hunan University, Changsha, China. His current research interests include machine learning,  multi-object tracking and reinforcement learning.
\end{IEEEbiography}

%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Authors/ZhiyongLi.eps}}]{Zhiyong Li}
%	received the MSc degree in System Engineering from National University of Defense Technology, Changsha, China, in 1996 and PhD degree in Control Theory and Control Engineering from Hunan University, Changsha, China, in 2004.
%	Since 2004, he joined the College of Computer Science and Electronic Engineering of Hunan University. 
%	Now, he is a Full Professor with Hunan University, member of IEEE, China Computer Federation (CCF) and Chinese Association for Artificial Intelligence (CAAI). 
%	His research interests include Intelligent Perception and Autonomous Moving Body, Machine Learning and Industrial Big Data, Intelligent Optimization Algorithms with Applications. He has published more than 100 papers in international journals and conferences.
%\end{IEEEbiography}
%
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Authors/XuanHe.eps}}]{Xuan He}
%	received her B.S. and M.S. degree from Hunan Normal University (HNU), China, in 2016 and 2020. She is currently pursuing the Ph.D. degree in Computer science and technology with Hunan  University. Her research interests include object detection and recognition, machine learning.
%\end{IEEEbiography}
%
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Authors/KeNai.eps}}]{Ke Nai}
%	received the Ph.D. degree in Computer Science and Technology from Hunan University, Changsha, China, in 2019. Currently, he is working as a Postdoctoral Researcher at Hunan University. His current research interests include visual tracking, face recognition, computer vision, pattern recognition and machine learning. He has published several papers in IEEE-TIP, Information Sciences, Knowledge Based Systems, Neural Computing and Applications, ICIP2019 and so on.
%\end{IEEEbiography}
%
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Authors/MingWen.eps}}]{Ming Wen}
%	 received his M.S. degree and Ph.D. degree from Hunan University in 2006 and 2010, respectively. He has been a senior engineer at State Grid Hunan Electric Power Company Limited Economical \& Technical Research Institute. His research interests include energy internet demand forecasting, electricity price, smart grid, renewable energy accommodation and power system planning.
%\end{IEEEbiography}

% that's all folks
\end{document}

% C#:  https://www.monodevelop.com/download/#fndtn-download-lin-ubuntu

### 2023-06-05 consciousness/latex/philosophy.tex
init

\documentclass[10.5pt,compsoc]{CjC}
\usepackage{CJKutf8}
% 使用Ctex的pdflatex进行编译
% 使用完整版的安装包就没有问题：CTeX_2.9.2.164_Full.exe，解决“模”字显示成'g'的问题
% 缺失安装包的解决办法：https://blog.csdn.net/qq_44009107/article/details/125582211
%\usepackage[UTF8]{ctex}
% 设置-Editor的默认编码 和 文件的编码都是为GBK，编译器为pdflatex
%\usepackage{CJK}
\usepackage{graphicx}
\usepackage{footmisc}
\usepackage{subfigure}
\usepackage{url}
\usepackage{multirow}
\usepackage[noadjust]{cite}
\usepackage{amsmath,amsthm}
\usepackage{amssymb,amsfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{ccaption}
\usepackage{booktabs}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{caption}
\usepackage{xcolor,stfloats}
\usepackage{comment}
\setcounter{page}{1}
\graphicspath{{figures/}}
\usepackage{cuted}%flushend,
\usepackage{captionhack}
\usepackage{epstopdf}
%\usepackage{ccmap}
%\CJKtilde
%\usepackage{CJKpunct} 
%\usepackage[lite,subscriptcorrection,slantedGreek,nofontinfo]{mtpro2}

%===============================%

%\firstfootname{ \quad \quad }
\headevenname{\mbox{\quad} \hfill  \mbox{\zihao{-5}{\begin{CJK*}{GBK}{song}计\quad \quad 算\quad \quad 机\quad \quad 学\quad \quad 报\end{CJK*}} \hspace {50mm} \mbox{\begin{CJK*}{GBK}{song}2019 年\end{CJK*}}}}%
\headoddname{\begin{CJK*}{GBK}{song}? 期 \hfill
		作者姓名等：论文题目\end{CJK*}}%

%footnote use of *
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\setcounter{footnote}{0}
\renewcommand\footnotelayout{\zihao{5-}}

\newtheoremstyle{mystyle}{0pt}{0pt}{\normalfont}{1em}{\bf}{}{1em}{}
\theoremstyle{mystyle}
\renewcommand\figurename{figure~}
\renewcommand{\thesubfigure}{(\alph{subfigure})}
\newcommand{\upcite}[1]{\textsuperscript{\cite{#1}}}
\renewcommand{\labelenumi}{(\arabic{enumi})}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
\newcommand{\abc}{\color{white}\vrule width 2pt}
\makeatletter
\renewcommand{\@biblabel}[1]{[#1]\hfill}
\makeatother
\setlength\parindent{2em}
%\renewcommand{\hth}{\begin{CJK*}{GBK}{hei}}
	%\renewcommand{\htss}{\begin{CJK*}{GBK}{song}}

\begin{document}
	\hyphenpenalty=50000
	\makeatletter
	\newcommand\mysmall{\@setfontsize\mysmall{7}{9.5}}
	\newenvironment{tablehere}
	{\def\@captype{table}}

	\let\temp\footnote
	\renewcommand \footnote[1]{\temp{\zihao{-5}#1}}

	\thispagestyle{plain}%
	\thispagestyle{empty}%
	\pagestyle{CjCheadings}

	\begin{table*}[!t]
		\vspace {-13mm}
		\begin{tabular}{p{168mm}}
			\zihao{5-}\begin{CJK*}{GBK}{song}
				第??卷\quad 第?期 \hfill 计\quad 算\quad 机\quad 学\quad 报\hfill Vol. ??  No. ?\end{CJK*}\\
			\zihao{5-}\begin{CJK*}{GBK}{song}
				20??年?月 \hfill CHINESE JOURNAL OF COMPUTERS \hfill ???. 20??\end{CJK*}\\
			\hline\\[-4.5mm]
			\hline\end{tabular}

		\centering
		\vspace {11mm}
		\begin{CJK}{GBK}{hei}
			{\zihao{2} 基于深度学习的类脑模型综述 }
		\end{CJK}
		\vskip 5mm

		{\zihao{3}\begin{CJK*}{GBK}{fs}
				作者名$^{1)}$\quad  作者名$^{2),3)}$ \quad 作者名$^{3) }$($^*$字体为3号仿宋*作者)\end{CJK*}}

		\vspace {5mm}
		\zihao{6}{\begin{CJK*}{GBK}{song}
				$^{1)}$(单位全名 部门(系)全名, 市(或直辖市) 国家名 邮政编码)
				*字体为6号宋体*单位
		\end{CJK*}}

		\zihao{6}{\begin{CJK*}{GBK}{song}
				$^{2)}$(单位全名 部门(系)全名, 市(或直辖市) 国家名
				邮政编码)*中英文单位名称、作者姓名须一致*
		\end{CJK*}}

		\zihao{6}{\begin{CJK*}{GBK}{song}
				$^{3)}$(单位全名 部门(系)全名, 市(或直辖市) 国家名 邮政编码)
		\end{CJK*}}

		\zihao{6}{\begin{CJK*}{GBK}{hei}
				论文定稿后，作者署名、单位无特殊情况不能变更。若变更，须提交签章申请，国家名为中国可以不写，省会城市不写省的名称，其他国家必须写国家名。
		\end{CJK*}}

		\vskip 5mm
		{\centering
			\begin{tabular}{p{160mm}}
				\zihao{5-}{
					\setlength{\baselineskip}{16pt}\selectfont{
						\noindent\begin{CJK*}{GBK}{hei}摘\quad 要\quad \end{CJK*} \begin{CJK*}{GBK}{song}
							在大数据时代下，深度学习理论和技术取得的突破性进展，为人工智能提供了数据和算法层面的强有力支撑，同时促进了深度学习的规模化和产业化发展。
							然而，尽管深度学习模型在现实应用中有着出色的表现，但其本身仍然面临着诸多的安全威胁。
							为了构建安全可靠的深度学习系统，消除深度学习模型在实际部署应用中的潜在安全风险，深度学习模型鲁棒性分析问题吸引了学术界和工业界的广泛关注，一大批学者分别从精确和近似的角度对深度学习模型鲁棒性问题进行了深入的研究，并且提出了一系列的模型鲁棒性量化分析方法。					在
							本综述中，我们回顾了深度学习模型鲁棒性分析问题当前所面临的挑战，并对现有的研究工作进行了系统的总结和科学的归纳，同时明确了当前研究的优势和不足，最后探讨了深度学习模型鲁棒性研究以及未来潜在的研究方向。
						\end{CJK*}\par}}\\[2mm]

				\zihao{5-}{\noindent
					\begin{CJK*}{GBK}{hei}关键词\end{CJK*} \quad \begin{CJK*}{GBK}{song}{*关键词（中文关键字与英文关键字对应且一致，应有5-7个关键词)；关键词；关键词；关键词*  }
					\end{CJK*}
				}\\[2mm]
				\zihao{5-}{\begin{CJK*}{GBK}{hei}中图法分类号\end{CJK*}	\begin{CJK*}{GBK}{song}
						TP\end{CJK*}\rm{\quad \quad \quad     }
					\begin{CJK*}{GBK}{hei}DOI号:\end{CJK*}\begin{CJK*}{GBK}{song}
						*投稿时不提供DOI号\end{CJK*}}
		\end{tabular}}

		\vskip 7mm

		\begin{center}
			\zihao{3}{ {\begin{CJK*}{GBK}{hei}A Survey of Brain-inspired Models Based on Deep Learning\end{CJK*}}}\\
			\vspace {5mm}
			\zihao{5}{ {\begin{CJK*}{GBK}{hei}NAME Name-Name$^{1)}$ NAME Name$^{2)}$ NAME Name-Name$^{3)}$ *字体为5号Times
						new Roman*Name\end{CJK*}
			}}\\
			\vspace {2mm}
			\zihao{6}{\begin{CJK*}{GBK}{hei}{$^{1)}$(Department of ****, University, City ZipCode, China) *字体为6号Times
						new Roman* Depart.Correspond}\end{CJK*}}

			\zihao{6}{\begin{CJK*}{GBK}{hei}{$^{2)}$(Department of ****, University, City ZipCode)*中国不写国家名*}\end{CJK*}}

			\zihao{6}{\begin{CJK*}{GBK}{hei}{$^{3)}$(Department of ****, University, City ZipCode, country)*外国写国家名*}\end{CJK*}}

		\end{center}

		\begin{tabular}{p{160mm}}
			\zihao{5}{
				\setlength{\baselineskip}{18pt}\selectfont{
					{\bf Abstract}\quad \begin{CJK*}{GBK}{hei}(\textbf{500英文单词，内容包含中文摘要的内容}).
						字体为Times new Roman,字号5号* Abstract\end{CJK*}
					\par}}\\

			\setlength{\baselineskip}{18pt}\selectfont{
				\zihao{5}{\noindent Do not modify the amount of space before and after the artworks. One- or two-column format artworks are preferred. and Tables, create a new break line and paste the resized artworks where desired. Do not modify the amount of space before and after the artworks. One- or two-column format artworks are preferred. All Schemes, Equations, Figures, and Tables should be mentioned in the text consecutively and numbered with Arabic numerals, and appear below where they are mentioned for the first time in the main text. To insert Schemes, Equations, Figures, and Tables, create a new break line and paste the resized artworks where desired. Do not modify the amount of space before and after the artworks. One- or two-column format artworks are preferred.Do not modify the amount of space before and after the artworks. One- or two-column format artworks are preferred. and Tables, create a new break line and paste the resized artworks where desired. Do not modify the amount of space before and after the artworks. One- or two-column format artworks are preferred. All Schemes, Equations, Figures, and Tables should be mentioned in the text consecutively and numbered with Arabic numerals, and appear below where they are mentioned for the first time in the main text.

					\vspace {5mm}
					{\bf Keywords}\quad \begin{CJK*}{GBK}{hei}中文关键字与英文关键字对应且一致，\textbf{不要用英文缩写});
						key word; key word; key word* *字体为5号Times new Roman * Key words\end{CJK*}}\par}
		\end{tabular}

		\setlength{\tabcolsep}{2pt}
		\begin{tabular}{p{0.05cm}p{16.15cm}}
			\multicolumn{2}{l}{\rule[4mm]{40mm}{0.1mm}}\\[-3mm]
			&\begin{CJK*}{GBK}{gbsn}
				收稿日期：\quad \quad -\quad -\quad ；最终修改稿收到日期：\quad \quad -\quad -\quad .*投稿时不填写此项*. 本课题得到… …基金中文完整名称(No.项目号)、… …基金中文完整名称(No.项目号)、… … 基金中文完整名称(No.项目号)资助.作者名1(通信作者)，性别，xxxx年生，学位(或目前学历)，职称，是/否计算机学会(CCF)会员（提供会员号),主要研究领域为*****、****.E-mail: **************.作者名2（通信作者)，性别，xxxx年生，学位(或目前学历)，职称，是/否计算机学会(CCF)会员（提供会员号),主要研究领域为*****、****.E-mail: **************. 作者名3（通信作者)，性别，xxxx年生，学位(或目前学历)，职称，是/否计算机学会(CCF)会员（提供会员号),主要研究领域为*****、****.E-mail: **************.(给出的电子邮件地址应不会因出国、毕业、更换工作单位等原因而变动。请给出所有作者的电子邮件)
				第1作者手机号码(投稿时必须提供，以便紧急联系，发表时会删除): … …, E-mail: … …*此部分6号宋体*
			\end{CJK*}
	\end{tabular}\end{table*}
	\clearpage\clearpage
	\begin{strip}
		\vspace {-13mm}
	\end{strip}
	\linespread{1.15}
	\begin{CJK*}{GBK}{hei}
		\zihao{5}
		\vskip 1mm
		\section{一级标题*字体为4号黑体*标题1}
		\textbf{对投稿的基本要求}：
	\end{CJK*}

	\begin{CJK*}{GBK}{song}
		(1) 研究性论文主体应包括引言(重点论述研究的科学问题、意义、解决思路、价值、贡献等)、相关工作(为与引言部分独立的一个章节)、主要成果论述、关键实现技术、验证(对比实验或理论证明)、结论(结束语)等内容；系统实现或实验应有关键点的详细论述，以便读者能够重复实现论文所述成果。实验应有具体的实验环境设置、全面细致的数据对比分析。

		(2) 综述应包括引言、问题与挑战、研究现状分析、未来研究方向、结论等内容。以分析、对比为主，避免堆砌文献或一般性介绍、叙述。

		(3) 定理证明、公式推导、大篇幅的数学论述、原始数据，放到论文最后的附录中。

		{\bf 稿件提交时的基本要求：}

		(1) 本模板中要求的各项内容正确齐全，无遗漏；

		(2) 语句通顺，无中文、英文语法错误，易于阅读理解，符号使用正确，图、表清晰无误；

		(3) 在学术、技术上，论文内容正确无误，各项内容确定。

		{\begin{CJK*}{GBK}{hei}\subsection{二级标题 *字体为5号黑体*标题2}\end{CJK*}}
		\subsubsection{三级标题 *字体为5号宋体*标题3}
		*正文部分, 字体为5号宋体* 正文文字

		\textbf{正文文字要求语句通顺，无语法错误，结构合理，条理清楚，不影响审稿人、读者阅读理解全文内容。以下几类问题请作者们特别注意}：

		1) 文章题目应明确反映文章的思想和方法；文字流畅，表述清楚；

		2) 中文文字、英文表达无语法错误；

		3) 公式中无符号、表达式的疏漏，没有同一个符号表示两种意思的情况；

		4) 数学中使用的符号、函数名用斜体；

		5) 使用的量符合法定计量单位标准；

		6) 矢量为黑体，标量为白体；

		7) 变量或表示变化的量用斜体；

		8) 图表规范，量、线、序无误，位置正确(图表必须在正文中有所表述后出现，即{\ldots}如图1所示)(注意纵、横坐标应有坐标名称和刻度值)。

		9) 列出的参考文献必须在文中按顺序引用，即参考文献顺序与引用顺序一致，各项信息齐全(格式见参考文献部分)；

		10) 首次出现的缩写需写明全称，首次出现的符号需作出解释。

		11) 图的图例说明、坐标说明全部用中文或量符号。

		\textbf{12) 图应为矢量图。}

		13) 表中表头文字采用中文。

		14) 公式尺寸：

		标准：10.5磅

		下标/上标：5.8磅

		次下标/上标：4.5磅

		符号：16磅

		次符号：10.5磅

		15) 组合单位采用标准格式，如：``pJ/bit/m$^{4}$''应为 ``pJ/(bit$\cdot
		$m$^{4})$''

		{\begin{CJK*}{GBK}{hei}\textbf{定理1}.\end{CJK*}}\quad ******. *定理内容.*

		[``定义''、``假设''、``公理''、``引理''等的排版格式与此相同，详细定理证明、公式可放在附录中]

		{\begin{CJK*}{GBK}{fs}证明\end{CJK*}}.\quad  *证明过程.* [``例 x''等的排版格式相同]

		\rightline {证毕.}

		\begin{figure}[htbp]
			\centerline{\includegraphics[width=3.15in,height=1.98in]{CJC1.pdf}}
			图X\quad  图片说明 *字体为小5号，图片应为黑白图，图中的子图要有子图说明*
			\label{fig1}
		\end{figure}

		\begin{table}[htbp]
			\centering {\begin{CJK*}{GBK}{hei}表X\quad 表说明 *表说明采用黑体*\end{CJK*}}
			\vspace {-2.5mm}
			\begin{center}
				\begin{tabular}{ll}
					\toprule
					*示例表格*&*第1行为表头,表头要有内容* \\
					\hline
					&
					\\
					&
					\\
					&
					\\
					&
					\\
					\bottomrule
				\end{tabular}
				\label{tab1}
			\end{center}
		\end{table}

		\begin{CJK*}{GBK}{hei}过程X.\end{CJK*}\quad 过程名称

		{\zihao{5-}*《计算机学报》的方法过程描述字体为小5号宋体，IF、THEN等伪代码关键词全部用大写字母，变量和函数名称用斜体*}

		\begin{CJK*}{GBK}{hei}算法\textbf{Y}\end{CJK*}.\quad 算法名称.
		\zihao{5-}{

			\noindent 输入：{\ldots} {\ldots}

			\noindent 输出：{\ldots} {\ldots}

			*《计算机学报》的算法描述字体为小5号宋体, IF、THEN等伪代码关键词全部用大写字母，变量和函数名称用斜体*}

		\vspace {3mm}
		\zihao{5}{
			\noindent \begin{CJK*}{GBK}{hei}致\quad 谢\end{CJK*}\quad \begin{CJK*}{GBK}{kai} *致谢内容.* 致谢\end{CJK*}}

		\vspace {5mm}
		\centerline
		{\zihao{5}
			\begin{CJK*}{GBK}{hei}参~考~文~献\end{CJK*}}

		\begin{thebibliography}{99}
			\zihao{5-} \addtolength{\itemsep}{-1em}
			\vspace {1.5mm}

			\bibitem[1]{1}
			网上的文献(举例：The Cooperative
			Association for Internet Data Analysis(CAIDA),http://www.caida.org/data
			2010,7,18) \textbf{*请采用脚注放于正文出现处，每页的脚注从1开始编序号*}\footnote{The Cooperative Association for Internet Data
				Analysis (CAIDA), http://www.caida.org/data 2010, 7, 18}

			\bibitem[2]{2} 中文的参考文献需给出中英文对照。形式如[3]。

			\bibitem[3]{3} Zhou Yong-Bin, Feng Deng-Guo. Design and analysis of cryptographic
			protocols for RFID. Chinese Journal of Computers, 2006, 29(4): 581-589 (in
			Chinese) \newline
			(周永彬, 冯登国. RFID安全协议的设计与分析. 计算机学报, 2006, 29(4): 581-589)

			\bibitem[4]{4} 期刊、会议、书籍名称不能用缩写。

			\bibitem[5]{5} 作者(外国人姓在前，名在后可缩写, 后同).
			题目(英文题目第一字母大写，其它均小写)：副标题(如果有). 刊名(全称), 年,
			卷(期): 页码 \textbf{*期刊论文格式*}

			\bibitem[6]{6}作者.
			文章题目(英文题目第1字母大写，其它均小写)：副标题(如果有)//Proceedings of
			the {\ldots} (会议名称). 会议召开城市, 会议召开城市所在国家, 年: 页码
			\textbf{*会议论文集论文格式*}

			\bibitem[7]{7}作者. 文章题目(英文题目第一字母大写, 其它均小写):
			副标题(如果有)//编者. 文集标题. 出版地: 出版社, 出版年: 页码
			\textbf{*文集格式*}

			\bibitem[8]{8}作者. 书名: 副标题(如果有). 版次(初版不写). 出版社地点: 出版社,
			出版年 \textbf{*书籍格式*}

			\bibitem[9]{9}作者. 文章题目[博士学位论文/硕士学位论文]. 单位名称,单位地点, 年
			\textbf{*学位论文格式*}

			\bibitem[10]{10}作者. 文章题目(英文题目第一字母大写，其它均小写). 单位地点: 单位,
			技术报告: 报告编号, 年 \textbf{*技术报告*}

			\bibitem[11]{11}专利拥有人. 专利名称，专利授权国家，专利授权日期
			\textbf{*技术专利*}
		\end{thebibliography}

		\begin{strip}
		\end{strip}

		\noindent {\zihao{5}\bf{附录X}.}

		{\zihao{5-}\setlength\parindent{2em}
			*\textbf{附录内容}置于此处，字体为小5号宋体。附录内容包括：\textbf{详细的定理证明、公式推导、原始数据}等*}

		\begin{strip}
		\end{strip}

		\begin{biography}[yourphotofilename.jpg]
			\noindent
			\textbf{First A. Author}\ \ *计算机学报第1作者提供照片电子图片，尺寸为1寸。英文作者介绍内容包括：出生年,学位(或目前学历),职称,主要研究领域(\textbf{与中文作者介绍中的研究方向一致}).*
			*字体为小5号Times New Roman*

		\end{biography}

		\begin{biography}[yourphotofilename.jpg]
			\noindent
			\textbf{Second B. Author} *英文作者介绍内容包括：出生年,学位(或目前学历),职称,主要研究领域(\textbf{与中文作者介绍中的研究方向一致})。*
			*字体为小5号Times New Roman*
		\end{biography}
		\begin{strip}
		\end{strip}
		\zihao{5}
		\noindent \textbf{Background}

		\zihao{5-}{
			\setlength\parindent{2em}
			*论文背景介绍为\textbf{英文}，字体为小5号Times New Roman体*

			论文后面为400单词左右的英文背景介绍。介绍的内容包括：

			本文研究的问题属于哪一个领域的什么问题。该类问题目前国际上解决到什么程度。

			本文将问题解决到什么程度。

			课题所属的项目。

			项目的意义。

			本研究群体以往在这个方向上的研究成果。

			本文的成果是解决大课题中的哪一部分，如果涉及863$\backslash
			$973以及其项目、基金、研究计划，注意这些项目的英文名称应书写正确。}

	\end{CJK*}
\end{document}

### 2023-06-05 nsfc/brain.tex
init

%!TEX program = xelatex 
% 告诉 texstudio， 无论默认编译器什么设置， 本 tex 文档都采用 xelatex 编译
% "C:/software/texlive/2016/bin/win32/xelatex.exe" -synctex=1 -interaction=nonstopmode %.tex
% 参考：https://github.com/YimianDai/iNSFC
\documentclass[a4paper,zihao=-4]{article}
\usepackage[UTF8,punct,linespread=1.56]{ctex}
% \documentclass[a4paper,cs4size,UTF8,punct,linespread=1.56]{ctexart}
\pagestyle{empty} % 第二页以后页码空白
\usepackage[a4paper, left = 3.2cm, right = 3.2cm, top = 2.54cm, bottom = 2.54cm]{geometry}
\usepackage{xcolor}
% \usepackage[citebordercolor = white]{hyperref}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{times}
\usepackage[subrefformat=parens,labelformat=parens]{subfig} %
\usepackage{booktabs} % for \toprule \midrule \bottomrule \cmidrule
\usepackage{cleveref}
\crefformat{table}{表~#2#1#3}
\crefformat{figure}{图~#2#1#3}
\crefformat{equation}{式~（#2#1#3）}
\usepackage{enumitem}
% \setenumerate[1]{itemsep = 0pt, parsep = 0pt, topsep = 2bp}
\setlist[enumerate]{itemsep = 0pt, parsep = 0pt, topsep = 2bp}
% \setitemize[1]{itemsep = 0pt, parsep = 0pt, topsep = 2bp}
\setlist[itemize]{itemsep = 0pt, parsep = 0pt, topsep = 2bp}
\usepackage{fontspec}
\setmainfont{Times New Roman}
% \usepackage{minted}   % For syntax highlighting
% \usemintedstyle{friendly}
\usepackage{setspace} 
\usepackage{caption}
\DeclareCaptionFont{capfont}{\kaishu\zihao{-4}\selectfont} % Caption font
\DeclareCaptionFont{subfont}{\kaishu\zihao{5}\selectfont} % Sub-caption font
\captionsetup{font = capfont}
\captionsetup[subfigure]{font = subfont}
\captionsetup[figure]{labelsep=space} % 空格 space；点 period；冒号 colon
\captionsetup[table]{labelsep=space}  % 空格 space；点 period；冒号 colon
\usepackage[square,numbers,sort&compress]{natbib}   % For Reference
\newcommand{\citess}[1]{\textsuperscript{\cite{#1}}}
\setlength{\bibsep}{1pt plus 0.3ex}
\usepackage{titlesec}
\titleformat{\subsubsection}[block]{\hspace{3em}}{\thesubsubsection}{1em}{}
\usepackage{insfc}

\graphicspath{{images/}}   % 设置图片所存放的目录

\begin{document}

\kaishu

% Decrease space above and below equations
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}

%%%%%%%%% TITLE %%%%%%%%%
% \title{报告正文 \vspace{-3.4ex}}
% \title{报告正文}
% \maketitle
\begin{center}
	{\kaishu \zihao{2} \textbf{报告正文} \vspace{-3ex}}
\end{center}

\thispagestyle{empty} 　　　% 首页页码空白

%%%%%%%%% Your Content %%%%%%%%%
%{\kaishu \zihao{4}参照以下提纲撰写，要求内容翔实、清晰，层次分明，标题突出。}\alert{请勿删除或改动下述提纲标题及括号中的文字。\vspace{9bp}}

\NsfcChapter{（一）立项依据与研究内容}{（4000-8000字）：}

\NsfcSection{1}{项目的立项依据}{（研究意义、国内外研究现状及发展动态分析，需结合科学研究发展趋势来论述科学意义；或结合国民经济和社会发展中迫切需要解决的关键科技问题来论述其应用前景。附主要参考文献目录）；}

\subsection{研究意义}
近年来，人工智能经历了迅猛的发展并且深刻地改变着人类社会和生活的方方面面。世界上的众多发达国家都将发展人工智能作为增强国家综合实力、提高先进科技竞争力和维护国家安全与稳定的重大战略方案[1]。2016年10月，美国国家科学技术委员会（NSTC）先后公布了《Preparing for the Future of Artificial Intelligence》（为人工智能的未来做好准备）和《National Artificial Intelligence Research and Development Strategic Plan》（国家人工智能研究与发展战略计划）两份重要报告，阐述了美国政府重点发展人工智能的战略决策与相关建议[2]。2017年7月，中国国务院也颁布了《新一代人工智能发展规划》，重点介绍了我国政府发展新一代人工智能的战略目标和主要任务，指明了构建世界一流科技强国的重要方向[3]。此外，中国科技部也在2018年10月开始启动“科技创新2030—‘新一代人工智能’”重大项目，意在鼓励国内各大科研院所、高等院校和企业对人工智能进行深入研究与探索。伴随着人工智能的蓬勃发展，以视觉目标跟踪、图像分类、目标检测等任务为代表的计算机视觉领域也获得了广泛的关注并在理论研究和实际应用方面取得了巨大的进展。
作为人工智能与计算机视觉领域最重要的问题之一，目标跟踪在无人驾驶系统、服务机器人和无人机等方面有着十分重要的应用。随着深度学习和传统机器学习相关理论的发展与完善，封闭固定环境下的目标跟踪已经达到了实际应用所需的性能要求。一些面向封闭环境的目标跟踪系统已经被用于现实生活中以保证人们的生命财产安全，比如家庭智能监控系统等。与封闭环境下的目标跟踪相比，开放环境下的目标跟踪具有更为重要的应用价值和社会需求。例如，对于无人驾驶系统来说，目标跟踪功能是其完成智能感知与决策所必不可少的组成部分。一个稳定且可靠的无人驾驶系统必须在开放环境中准确地跟踪到无人车周边的不同目标（如车辆、行人等）以便做出合理的决策来规避潜在的交通风险，进而保证无人车的行车安全。然而，开放环境下的目标跟踪是一个非常具有挑战性的任务并且依然存在着诸多技术难点和挑战，这极大地限制了各类目标跟踪方法的跟踪性能和在实际工程中的推广与使用[4]。因此，深入研究面向开放环境的鲁棒目标跟踪方法具有非常重要的理论研究意义和实际应用价值。
针对开放环境下的目标跟踪任务，已有许多机器学习方法[5]和深度网络模型[6]被研究以进一步提高跟踪性能。但是由于某些技术困难与挑战，这些方法无法获得理想的跟踪精度来完成从封闭环境到开放环境的有效跨越，也不能被真正地用于解决各种实际问题。具体来说，开放环境下的目标跟踪主要存在以下几个方面的难点和挑战：

1）复杂多变场景下的跟踪适应性问题。一个完整的目标跟踪系统主要包括跟踪模型和特征表达两个组成部分，其中跟踪模型主要负责在视频序列中确定目标位置，特征表达则选择合理的视觉特征对目标进行表示。在开放环境下，目标跟踪系统需要在复杂多变的跟踪场景中成功地跟踪到目标。因此，为了追求更好的跟踪性能，主流的目标跟踪方法往往会学习到高度复杂的跟踪模型。以目前十分流行的相关滤波方法[7][8]为例，当利用高维深度特征进行特征表达时，该类方法的跟踪模型（岭回归模型）的参数数目能够达到109。高度复杂的跟踪模型极有可能导致机器学习中的过拟合问题，从而降低跟踪方法适应复杂跟踪场景的能力。也就是说，尽管这些方法可以在一些特定场景下准确地跟踪到目标，但是却无法在复杂多变的跟踪场景下成功地完成跟踪任务。例如，在无人驾驶系统中，高度复杂的跟踪模型将极大地降低跟踪方法的适应性，从而造成跟踪方法不能在复杂的交通场景中准确地跟踪到无人车周围的重要目标以规避交通风险。机器学习中的奥卡姆剃刀原则（Occam’s Razor）指出[9]：在所有可以选择的模型当中，能够很好地解释已知数据并且十分简单才是最好的模型。因此，如何降低跟踪模型复杂度以提高复杂场景下的跟踪适应性是开放环境下目标跟踪的一个重大挑战。
2）目标复杂的外观变化。在开放环境下，目标自身会发生十分复杂的外观变化，这极大地增加了跟踪方法取得理想性能的难度。目前主流的OTB数据集[10]和每年举办的VOT（Visual Object Tracking）[11]目标跟踪竞赛都把目标的外观变化分为多种类型，如：运动模糊、目标形变、光照变化、平面旋转等。值得一提的是，目标在某个时刻可能同时发生多种类型的外观变化，这将直接导致目标出现非常复杂的外观变化，进而限制跟踪方法在开放环境下的跟踪准确性。能否成功地应对目标复杂的外观变化将决定跟踪方法的跟踪性能和在实际问题中的应用前景。以刑事侦查中所依靠的天眼系统为例，如果目标在跟踪过程中所出现的复杂外观变化能够被有效地捕获，那么天眼系统将顺利地完成跟踪任务以确保社会安全，反之则系统可能在某一时刻跟丢目标，后果将十分严重。综上所述，如何捕获目标所出现的复杂外观变化以提高跟踪准确性是开放环境下目标跟踪的又一个重大挑战。
3）模型漂移问题。在跟踪过程中，目标不仅会经历复杂的外观变化，而且还会受到严重遮挡、嘈杂背景等外界干扰。由于目标跟踪方法中的跟踪模型需要被更新以考虑目标最新的外观变化[12]，所以目标所遇到的外界干扰可能会导致模型漂移问题。一旦模型漂移问题在跟踪过程中发生，跟踪方法将再也无法在复杂多变的场景中成功地跟踪到目标，这极大地降低了跟踪方法的跟踪性能。因此，理想的目标跟踪方法必须具有良好的鲁棒性以应对跟踪过程中的模型漂移问题。然而，目前主流的跟踪方法依然不具备良好的跟踪鲁棒性，比如在OTB和VOT数据集上达到顶级跟踪性能的SiamRPN++方法[13]经常在出现嘈杂背景和严重遮挡时发生模型漂移，进而导致跟踪失败的结果。对于ADAS系统（Advanced Driving Assistance System，高级驾驶辅助系统）和天眼系统等应用系统来说，能否抑制跟踪过程中的模型漂移问题也在很大程度上决定着这些系统的性能和应用前景。因此，如何抑制模型漂移问题以保证跟踪鲁棒性也开放环境下目标跟踪的一个重大挑战
针对上述挑战，本项目从模型精简与压缩、特征融合和跟踪框架设计等方面展开研究，解决开放环境下目标跟踪所面临的多个关键性科学问题，实现开放场景下的鲁棒目标跟踪。具体的研究工作包括：（1）拟提出基于稀疏约束的判别性跟踪模型，主要解决由于跟踪模型复杂度过高所引起的跟踪适应性问题；（2）拟提出基于时空上下文信息的动态多特征融合策略，重点解决目标所出现的复杂外观变化以提高开放场景下的跟踪准确性；（3）拟提出基于集成学习的跟踪方法，主要解决跟踪过程中的模型漂移问题以提高开放场景下的跟踪鲁棒性。值得一提的是，由于上述三个工作分别从跟踪模型、特征表达和跟踪框架角度出发以解决关键科学问题，因此工作（1）和（2）可以直接嵌入到工作（3）中以保证研究的整体性和统一性。
项目基于前期关于稀疏表达[14][15]、相关滤波[16][17]等方法的研究基础，结合集成学习、判别性跟踪模型、多特征融合和深度学习等相关方法和理论，拟提出基于稀疏约束的判别性跟踪模型、基于时空上下文信息的动态多特征融合策略和基于集成学习的跟踪方法，解决开放场景下目标跟踪任务中的跟踪适应性、目标复杂的外观变化和模型漂移等重要问题，提高跟踪方法的跟踪性能，实现开放环境下的鲁棒目标跟踪。本课题具有十分重要的理论研究意义和实际应用价值，相关研究成果将为目标跟踪的发展提供重要参考，并促进目标跟踪方法在不同领域中的现实应用。

\subsection{国内外研究现状及发展动态分析}
\subsubsection{类脑目标识别研究现状}
视觉目标跟踪是计算机视觉领域最重要和最有挑战性的任务之一，具备十分重要的应用价值。近年来，许多目标跟踪算法被提出以便在开放环境下取得理想的跟踪性能。总的来说，存在的目标跟踪方法可以被分为三大类：生成式跟踪方法、判别性跟踪方法和深度学习跟踪方法。
生成式方法将跟踪任务定义为一个相似性匹配问题，该类方法在跟踪过程中构建一个目标模型来表示目标所具有的特征，然后比较候选区域和目标模型的相似性来确定跟踪结果。最具代表性的生成式方法主要包括子空间方法[18][19]和稀疏表达方法[20][21]。其中子空间方法通过维度规约以获得一个低维子空间对目标进行表示，并且通过在子空间中比较所有候选目标的匹配度以完成对目标的跟踪。Ross等[18]提出了一种增量主成分分析方法（Incremental Principal Component Analysis）以准确地进行跟踪，该方法使用经典的PCA方法学习到一个关于目标的子空间，并在跟踪过程中对子空间进行增量地更新来考虑目标的外观变化。Sui等[19]首先利用跟踪过程中的跟踪结果学习一个全局子空间模型，然后学习一个基于像素级别的局部子空间模型，最后结合两个子空间模型以准确地跟踪目标。该方法可以利用全局模型和局部模型的优点以提升跟踪性能。与子空间方法有所不同，稀疏表达方法通过求解L1正则化模型完成对每个候选目标的稀疏编码，然后计算并比较所有候选的重构误差以选取最终的目标。Mei等[20]首次应用稀疏表达方法来解决目标跟踪问题，提出了流行的L1跟踪方法。L1方法利用粒子滤波采样多个候选目标，进而对每个候选进行稀疏编码以选取合适的候选作为跟踪结果。Qi等[21]提出了一种结构感知的局部稀疏编码算法来准确地跟踪目标。该方法考虑全局和局部稀疏限制对候选目标进行稀疏编码，采用快速迭代收缩阈值算法（Fast Iterative Shrinkage-thresholding Algorithm）来对模型进行求解。生成式跟踪方法在简单封闭环境下能够取得不错的跟踪精度和鲁棒性，但是该类方法在开放环境下的跟踪性能和速度都不太理想。
判别性方法把目标跟踪看作一个二分类问题（目标为正类，背景为负类），并且在线学习一个分类器来区分目标和背景。经典的判别性跟踪方法包括多实例学习[22]、P-N学习[23]、结构化支持向量机[24][25]和相关滤波[26][27][28]等。Babenko等[22]将训练样本以包的形式进行划分来训练分类器，进而提出了多实例学习方法（Multiple Instance Learning）以完成目标跟踪任务。Kalal等[23]将目标跟踪分为检测、跟踪和学习，并且设计了一个TLD（Tracking-Learning-Detection）框架以迭代地执行三种操作。为消除分类器训练过程中的样本标签问题，Hare等[24]基于机器学习中的结构化学习理论提出了一种结构化支持向量机（Structured Output SVM）跟踪方法。该方法能够准确地将目标和背景区分开来，具有更好的判别性。相关滤波方法[26][27][28]是近些年最成功和最有效的判别性跟踪方法。该类方法一方面利用信号处理领域的卷积操作以获取大量虚拟样本来训练高性能的滤波器，另一方面通过执行离散傅里叶变换（Discrete Fourier Transform，DFT）将空域内复杂的卷积操作转换为频域内简单的点击操作以进行高速的跟踪。 Bolme等[26]首先利用相关滤波方法来解决目标跟踪问题，并提出了MOSSE跟踪方法。MOSSE跟踪方法的跟踪速度达到每秒几百帧，满足了实时跟踪的要求。为了获得更好的跟踪性能，Henriques等[27]将高维HOG （Histogram of Oriented Gradient）特征嵌入到相关滤波框架，提出了十分流行的核相关滤波（Kernelized Correlation Filters）跟踪方法。判别性跟踪方法在开放环境下能够取得比生成式方法更好的跟踪性能和速度，也不存在深度学习方法那样的训练困难。然而，在追求更高的跟踪性能时，该类方法可能学习到高度复杂的跟踪模型，这限制了方法的对于复杂场景的适应能力。
显然，深度学习跟踪方法是目标跟踪领域最受关注的方法，并且达到了顶级的跟踪结果。主流的深度学习方法包括卷积神经网络[29][30][31]、孪生网络[32][33]、深度残差网络[34]等。卷积神经网络（Convolutional Neural Network）是传统神经网络的一种改进形式，它极大地减少了网络的参数数量。Nam等[29]利用大量带标注的视频训练一种多域网络（Multi-Domain Network）以准确地跟踪目标。该网络能够学习到关于目标的共享表示形式。Li等[30]设计了一个回归损失和一个排序损失来选择最有表示能力和最有效的卷积滤波器，进而获得目标感知的深度特征以表示目标。孪生网络（Siamese Network）方法的主要思想是将相似性度量学习应用到卷积神经网络来完成目标跟踪。Bertinetto等[32]首先提出了一种全卷积孪生网络来跟踪以完成跟踪任务。该网络在更大的范围内搜索目标，并且通过比较目标模板和候选的特征相似性来确定目标位置。为了处理目标剧烈的形变，Yu等[33]利用自注意力机制和跨越注意力机制以设计一个可形变孪生注意力网络。尽管基于深度网络的方法获得了理想的跟踪性能，但是大规模网络的训练不仅需要大量带标注的视频序列，而且存在着过拟合、难以收敛和容易陷入局部极小等问题。因此，许多研究工作[35][36][37]将深度特征引入到判别性跟踪方法（如支持向量机、相关滤波等）中以提高跟踪性能和规避训练问题。Hong等[35]从卷积网络中提取出深度特征以表示目标，并且学习支持向量机来进行目标跟踪。Danelljan等[36]学习一个连续卷积滤波器（Continuous Convolution Filters）以融合多个分辨率的视觉特征来获得更好的跟踪结果。通过利用深度特征，判别性跟踪方法可以取得理想的跟踪结果并且不存在训练方面的问题。但由于学习得到的跟踪模型具有很高的复杂度（例如：连续卷积滤波器[36]的模型参数可以达到109），这些方法的跟踪适应性会受到很大的影响。
由上可知，判别性方法和深度学习方法可以取得比生成式方法更优的跟踪性能，具有更好地应用前景。然而，在寻求更好的跟踪结果的同时，这些方法往往学习到高度复杂的跟踪模型。以判别性方法为例，当使用深度特征时，该类方法的模型复杂度将变得不可接受。高度复杂的跟踪模型严重降低了跟踪方法对复杂场景的适应性。因此，提出有效方法降低跟踪模型复杂度以提高开放场景下的跟踪适应性具有重要意义。

\subsubsection{多模态融合研究现状}
在开放环境下，目标在跟踪过程中会经历光照变化、剧烈形变和旋转等挑战，进而产生非常复杂的外观变化。复杂的外观变化极大地增加了跟踪方法准确跟踪到目标的难度，也降低了跟踪方法的准确性。怎样应对目标复杂的外观变化直接决定了跟踪方法的性能。研究表明，单一的视觉特征无法在复杂的跟踪场景下有效地建模目标外观。因此，融合多种视觉特来捕获目标复杂的外观变化以提高跟踪的准确性便成为一种可行的方案。
事实上，特征融合被广泛地应用于计算机视觉领域的多个任务，并且能够获得比单个特征更好的性能。对目标跟踪而言，前期的特征融合方法通常仅仅融合梯度（如：HOG特征）、颜色（如：ColorNames特征和RGB特征）和纹理（如：LBP特征）等传统手工特征。Hong等[38]利用稀疏表达和多任务学习设计了一种用以融合梯度、颜色和灰度等传统特征的联合稀疏跟踪方法。该方法将不同特征的稀疏编码作为不同的任务，利用混合范数约束多个特征具有类似的稀疏编码以联合地学习多个任务。Zhang等[39]通过梯度、纹理和颜色等特征训练多个支持向量机来从不同的角度对目标进行建模与跟踪。为有效地融合多个支持向量机的跟踪结果以确定目标位置，所提出的方法利用了一种基于信息熵的融合策略。基于流行的相关滤波框架，Li等[40]提出了一种SAMF 跟踪算法以融合对于目标跟踪任务十分有效的HOG特征和ColorNames特征以进行目标跟踪。通过融合上述两种视觉特征，SAMF方法可以取得更好的跟踪结果。通过分析颜色直方图和梯度特征之间具有互补性，Bertinetto等[41]设计了一种Staple跟踪算法融合颜色直方图特征和HOG特征以表示目标。Staple方法在跟踪精度与跟踪速度两方面都达到了不错的结果。由于不同的视觉特征能从不同的角度对目标外观进行表示，因此特征融合方法可以更好地捕获目标在跟踪过程中所发生的复杂外观变化，进而获得更优的跟踪性能。
考虑到深度特征具有很强的目标表示能力，许多特征融合方法尝试融合该类特征以进一步提高跟踪准确性。Ma等[42]将由卷积神经网络提取出来的深度特征融入到相关滤波框架以准确地跟踪目标。所提出的方法利用不同层次的特征学习多个相关滤波器，并且融合所有滤波器的相关响应以获得最终的跟踪结果。Zhang等[43]设计了一个多任务相关粒子滤波方法（Multi-task Correlation Particle Filter）以融合深度特征和传统特征来提升目标跟踪性能。该方法考虑多任务学习以挖掘多种视觉特征之间的潜在联系，进而实现有效的特征融合。为了融合具有不同分辨率的视觉特征, Danelljan等[44]提出了一种高效卷积跟踪器（Efficient Convolution Operators）。该跟踪方法基于相关滤波框架，融合梯度特征（HOG特征）、（ColorNames特征）和深度特征以准确地跟踪目标。Xu等[45]利用深度残差网络（ResNet-50网络）获得深度特征，并且结合梯度特征和颜色特征以完成跟踪任务。为准确地定位目标，所提出的方法首先利用能够捕获高层语义信息的深度特征以排除不可靠的候选目标，然后利用能够捕获目标细节的梯度和颜色特征来确定最终的目标。通过融合传统特征和深度特征以表示目标，特征融合方法可以获得不错的跟踪性能。然而当前的特征融合方法通常采用简单地串联或者由粗到精的策略融合多种特征，因此并不能充分利用不同特征的特性与优点以应对目标出现所的复杂外观变化。
事实上，传统特征（例如颜色、梯度等）和深度特征从不同的角度对目标进行表示并且具有不同的特点和优势，例如：前者可以表示目标的底层细节信息，而后者能够捕获目标的高层语义信息。因此，面对不同的跟踪场景，传统特征和深度特征应该被赋予不同的重要性来进行特征融合操作以捕获目标出现的复杂外观变化。提出高效的动态多特征融合方法以应对目标复杂的外观变化是提高跟踪准确性的关键。

\subsubsection{多专家机制与集成学习方法}
由于目标跟踪是一个在线学习任务，跟踪模型在跟踪过程中需要被更新以适应目标所出现的外观变化。但是当出现目标遮挡或嘈杂背景等外界干扰时，更新操作会严重地腐蚀跟踪模型，进而导致模型漂移问题。一旦模型漂移问题发生，跟踪方法将再也无法成功地跟踪到目标。为了确保跟踪方法的鲁棒性，必须设计有效的方法消除模型漂移问题。目前，用于应对模型漂移问题的跟踪方法主要有两类：多专家方法和集成学习方法。
基于多专家的跟踪方法通常构造多个专家抑制模型漂移问题，并且设计有效的选择机制以便从多个专家中选择出最好的一个来准确地确定目标。考虑到目标在跟踪过程中会出现多种外观模式，Nai等[16]学习多个相关滤波器以表示这些不同的外观模式。所提出的方法利用了一个两阶段选择策略来选择出一个合适的滤波器以定位目标，进而消除模型漂移问题和捕获目标复杂的外观变化。 Zhang等[46]设计了一种MEEM（Multi-Expert Entropy Minimization）跟踪算法提高跟踪的鲁棒性。MEEM算法通过保存跟踪过程中的跟踪器快照（Tracker Snapshot）以构成一个专家集合，然后通过最小熵准则从专家集合中挑选出一个用于确定目标状态的专家。Li等[47]利用多个跟踪器快照提出了一种HSME（Historical Snapshots Multi-Expert）跟踪方法以抑制模型漂移。该方法使用离散图建模多个专家之间的相互关联，并通过动态规划算法求解目标模型来得到一个精确解。Wang等[48]提出了一种多线索相关跟踪器（Multi-Cue Correlation Tracker）以利用多种视觉特征来有效地建模目标外观。MCCT方法首先通过不同的特征组合学习多个相关滤波器，然而计算单个滤波器的自相关分数和多个滤波器在跟踪过程中的互相关分数选择出一个最好的滤波器来准确地跟踪目标。基于多专家的跟踪方法在应对模型漂移问题上具有一定的优势，但是该类方法的稳定性却不足。此外，由于在跟踪过程中所利用的专家集合经常保留多个相似的专家，所以多专家跟踪方法存在专家选择方面的困难。
由于集成学习能够达到很好的泛化能力和鲁棒性，该类方法也被用于解决目标跟踪问题。和多专家方法相比，集成学习方法没有专家选择方面的问题，并且具备更好的稳定性。基于经典的Adaboost算法框架，Adrian等[49]在线学习多个弱分类器以构成一个强分类器来有效地区分背景和目标。所提出的跟踪方法可以在一定程度上消除模型漂移问题以提升跟踪鲁棒性。Bai等[51]将贝叶斯理论融入到集成学习框架当中，设计了一种随机集成跟踪器（Randomized Ensemble Tracker）来应对跟踪过程中的模型漂移和目标所出现的复杂外观变化。该算法把所有弱分类器的权值当成一个随机向量，然后通过求解该随机向量的后验分布来完成最后的跟踪任务。Gundogdu等[52]提出了一种基于树结构的集成学习算法以准确地跟踪目标。该方法首先学习多个相关滤波器并利用二叉树结构进行存储，然后将目标所出现的外观划分为多个类别且保证二叉树的每一个分支表示一种特定的外观，最后通过在二叉树中选取与目标当前外观最为相似的分支以确定最后的跟踪结果。为了获得满意的跟踪性能，基于集成学习的跟踪方法需要满足两个基本要求：首先，集成跟踪方法必须学习具有多样性的基分类器以确保最终的集成跟踪器能够应对复杂多变的跟踪场景；其次，所有基分类器必须被分配合理的权重以保证集成跟踪器能够消除跟踪过程中的模型漂移问题。然而，存在的基于集成学习的跟踪方法无法满足上述两个基本要求，这严重地限制了目标跟踪的鲁棒性和准确性。
由上可知，多样的基分类器和合理的权值是集成跟踪方法取得理想跟踪性能的关键，前者保证跟踪方法可以成功应对跟踪过程中多变的跟踪场景，后者则能确保跟踪方法有效抑制模型漂移问题。设计高效的基于集成学习的跟踪方法来消除模型漂移问题和对提高开放环境下目标跟踪的鲁棒性具有重要意义。

% 参考文献放这里
\begin{spacing}{1.3} % 行距
	\zihao{5} \songti   
	\bibliographystyle{gbt7714-nsfc}
	\bibliography{ref}  
	\vspace{11bp}
\end{spacing}

\NsfcSection{2}{项目的研究内容、研究目标，以及拟解决的关键科学问题}{（此部分为重点阐述内容）；}

\subsection{研究目标}
本项目以开放环境下的目标跟踪所面临的跟踪适应性、目标复杂的外观变化和模型漂移问题等挑战出发，从模型精简与压缩、特征融合和跟踪框架设计等方面展开研究，聚焦稀疏表达、判别性跟踪模型、动态多特征融合、集成学习和深度学习等相关理论与方法，重点突破基于稀疏约束的判别性跟踪模型、基于时空上下文信息的动态多特征融合策略、基于集成学习的跟踪方法等关键技术，研发面向开放环境的鲁棒目标跟踪算法，并利用标准视频数据集、ADAS高级智能驾驶辅助系统和真实无人车平台相结合的实验手段进行算法验证与测试，提高开放环境下的跟踪适应性、准确性和鲁棒性，设计具有良好性能的目标跟踪系统，推动目标跟踪在实际问题中的具体应用，为实现开放环境下的鲁棒目标跟踪提供新技术和新方法。图1展示了本项目的技术挑战、研究内容和关键科学问题。

\subsection{研究内容}

\subsubsection{基于多模态融合的类脑感知模型}
本项目针对开放环境下目标跟踪所存在的跟踪适应性问题，从模型精简与压缩的角度出发，拟提出基于稀疏约束的判别性跟踪模型以限制跟踪模型复杂度，提升跟踪方法在开放环境下的适应性。

\begin{itemize}
	\item 掌握模型精简与压缩方面的理论与方法，深入研究判别性跟踪方法（例如：支持向量机和相关滤波等）的跟踪模型复杂度对跟踪适应性的影响，了解稀疏表达方法在各类计算机视觉任务中的具体应用；
	\item 将稀疏表达思想引入到判别性跟踪模型当中，设计基于稀疏约束的判别性跟踪模型，研究高效的凸优化算法以正确地求解目标模型；
	\item 研究主流深度神经网络（例如：卷积神经网络、深度残差网络和孪生网络等）的特点与优势，选择合适的网络模型进行特征提取来有效地表示目标；
\end{itemize}

\subsubsection{基于全局工作空间理论的类脑规划决策模型}
本项目针对目标在开放环境下所出现的复杂外观变化，从特征融合的角度出发，拟提出基于时空上下文信息的动态多特征融合策略以有效地捕获目标所出现的复杂外观变化，提高跟踪方法的跟踪准确性。

\begin{itemize}
	\item 研究传统手工特征（例如：颜色特征、纹理特征和梯度特征）和深度特征在不同跟踪场景下的跟踪性能，分析各类特征在目标表示方面的优点和不足，调研主流特征融合方法的跟踪性能；
	\item 利用跟踪过程中的时空上下文信息评价不同特征的稳定性和判别性，动态地融合多种视觉特征来应对目标复杂的外观变化；
	\item 在上述基础之上，研究多模态信息融合方法以融合目标的多源信息（如深度信息，热红外信息），提高跟踪的准确性；
\end{itemize}

\subsubsection{基于运动皮层的类脑控制策略}
本项目针对跟踪过程中所出现的模型漂移问题，从跟踪框架的角度出发，拟提出基于集成学习的跟踪方法以消除模型漂移问题，提高跟踪方法在开放环境下的鲁棒性。

\begin{itemize}
	\item 分析模型漂移问题对跟踪性能的影响，研究各类跟踪算法（例如：生成式方法、判别性方法和深度学习方法）应对模型漂移问题的鲁棒性；
	\item 将集成学习框架作为跟踪框架，研究在线聚类算法和权值分配算法来获得具有多样性的弱分类器和合理的权值；
	\item 研究深度森林，深度boosting、深度梯度boosting等深度集成学习方法，进一步提高跟踪方法在复杂场景下的鲁棒性；
\end{itemize}

综上所述，本项目旨在从模型精简与压缩、特征融合和跟踪框架设计等角度展开研究以设计具有鲁棒性的目标跟踪方法。考虑到目标跟踪系统通常包括跟踪模型和特征表达两个组成模块，所以研究内容的前两点可以被嵌入到研究内容的第三点以保证项目研究的整体性。因此，本项目的研究工作具有系统性和整体性。

\subsection{拟解决的关键科学问题}

本项目以开放环境下的目标跟踪为研究对象，旨在设计鲁棒的目标跟踪方法以获得更好的跟踪精度，拟解决如下关键科学问题：

\subsubsection{基于多模态融合的类脑感知模型}
面向开放环境的目标跟踪方法需要具有良好的跟踪适应性以应对复杂多变的跟踪场景。然而，为了获得更好的跟踪性能，主流的跟踪方法（如：判别性跟踪方法和深度学习方法）往往会学习到高度复杂的跟踪模型。高度复杂的跟踪模型不仅计算代价大，而且容易导致过拟合问题。因此，如何对高度复杂的跟踪模型进行精简与压缩以提高模型的跟踪适应性是提高本项目拟解决的关键科学问题之一，也是提升开放环境下的跟踪性能所必须要解决的困难。

\subsubsection{基于全局工作空间理论的类脑规划决策模型}
目标在开放环境下不可避免地会出现光照变化、平面旋转、剧烈形变和运动模糊等多种外观变化，进而产生十分复杂的外观变化。复杂的外观变化大大地增加了跟踪方法成功跟踪目标的难度，降低了跟踪方法开放环境下的跟踪准确性。研究表明，单个视觉特征往往不能有效地捕获目标所出现的复杂外观变化。考虑到不同的视觉能够从不同的角度对目标进行表示，融合多种视觉特征便成为应对目标复杂外观变化的一种可行方案。因此，如何设计具有强表示能力的多特征融合以捕获目标复杂的外观变化也是本项目拟解决的关键科学问题。

\subsubsection{基于运动皮层的类脑控制策略}
目标在跟踪过程中会受到严重遮挡、嘈杂背景等外界干扰，进而引发模型漂移问题。模型漂移问题会导致跟踪失败，使得跟踪方法无法再准确地跟踪到目标。一个鲁棒的目标跟踪系统必须具有良好的鲁棒性以抑制模型漂移问题。事实上，仅仅研究目标跟踪系统中的跟踪模型或特征表达部分无法有效地消除模型漂移问题。因此，本项目从跟踪框架的角度出发以考虑跟踪的鲁棒性问题。如何设计具有强鲁棒性的跟踪框架以消除模型漂移问题是本项目拟解决的又一关键科学问题。

\NsfcSection{3}{拟采取的研究方案及可行性分析}{（包括研究方法、技术路线、实验手段、关键技术等说明）；}

\subsection{研究方法与技术路线}
该课题主要包括三个阶段：类脑图像识别的设计分析和建模、类脑跟踪的机理研究和仿真、类脑感知融合探索和研究。
本项目结合理论研究与实际应用，针对开放环境下的目标跟踪所面临的跟踪适应性问题、目标复杂的外观变化和模型漂移等挑战，采用计算机视觉、机器学习、深度学习、稀疏表达、判别性跟踪模型、集成学习、多特征融合等方法、技术与理论，考虑公开视频数据集、ADAS智能驾驶辅助系统和真实无人车平台相结合的验证与测试方法，研究基于稀疏约束的判别性跟踪模型、基于时空上下文信息的动态多特征融合策略和基于集成学习的跟踪方法，提高开放环境下的跟踪性能。
以开放环境下的目标跟踪为研究对象，本项目的研究工作分为相关问题分析、模型算法设计和方法验证测试三个层面（图2为技术路线）：
（1）相关问题分析：利用当前主流的目标跟踪系统和公开视频数据集，深入分析跟踪适应性问题、目标复杂的外观变化与模型漂移等挑战对目标跟踪算法性能和鲁棒性的影响。此外，结合计算机视觉、机器学习等相关理论方法与申请人前期关于目标跟踪课题所做的研究工作，从跟踪模型精简与压缩、特征融合和跟踪框架设计等方面展开具体的研究工作。具体来说，从跟踪模型精简与压缩的角度研究跟踪适应性问题的解决方法、从特征融合的角度研究目标复杂的外观变化的解决方法、从跟踪框架设计的角度研究模型漂移问题的解决方法。
（2）模型算法设计：基于对关键性科学问题的详细分析与申请人在目标跟踪、深度学习、判别性模型、稀疏表达、集成学习、多特征融合等方面的相关工作，设计鲁棒跟踪方法解决（1）中的科学问题以获得更好的跟踪效果。其中，提出基于稀疏约束的判别性跟踪模型解决跟踪适应性问题，提出基于时空上下文信息的动态多特征融合策略捕获目标复杂的外观变化，提出基于集成学习的跟踪方法应对跟踪过程中的模型漂移问题。
（3）方法验证测试：为有效地评估（2）中所设计的目标跟踪方法，采用开放环境下的标准视频数据集、项目申请人参加研发的ADAS高级智能驾驶辅助系统与真实无人车平台进行测试和验证，分析跟踪算法的跟踪性能、优势和不足，增强跟踪算法在实际应用中的可行性。
综上所述，本项目重点研究开放环境下的目标跟踪，以跟踪适应性、目标复杂的外观变化、模型漂移问题等科学问题为驱动，采用“相关问题分析模型算法设计方法验证测试”的技术路线，研究“基于稀疏约束的判别性跟踪模型、基于时空上下文信息的动态多特征融合策略、基于集成学习的跟踪方法”三个方面的相关理论与关键技术。

\subsection{关键技术}

\subsubsection{基于多模态融合的类脑感知模型}
第一阶段，根据大脑皮层视觉中腹侧流通路的研究，如图1所示，涉及目标识别的通路主要包括初级视觉皮层V1、纹外皮层V2和V4、颞枕皮层TEO、下颞皮层IT，其中下颞皮层时目标识别的主要区域。参照腹侧流通路的解剖结构，利用卷积和循环结构，构建大脑对齐的深度模型，可以设计相对应的类脑图像识别网络，并获得输入图像在深度网络中的激活响应，研究图像识别功能在大脑皮层和深度神经网络中表现的激活相似性，同时进行进行神经度量和行为度量，利用类脑识别分数进行深度神经网络和大脑的对比，并利用设计并训练好的类脑模型，确定识别的图像模式分别在深度网络和大脑皮层中的位置，寻找图像识别的类别信息在深度网络中的表征模式与大脑中的激活特征之间的映射关系。

\subsubsection{基于全局工作空间理论的类脑规划决策模型}
第二阶段，参照人类大脑皮层中背侧流通路进行类脑跟踪的机理研究和仿真，通过量化的大脑相似性分数，并利用所获得的皮层解剖知识来启发类脑跟踪模型的设计。如图2所示，类脑跟踪模型包括映射到人脑的四个区域：初级视觉皮层，中颞和上颞内侧区、额叶视区和脑干/小脑 。初级视觉皮层使用经典的卷积层进行建模，执行预处理以减少数据大小。中颞区和上颞内侧区使用动态滤波器网络进行建模，额叶视区使用循环神经网络进行建模。对于最开始的输入刺激，神经网络的输出表示大脑对齐模型中的深度神经网络的激活响应和边界框，而大脑皮层在跟踪时的表示是大脑皮层的激活和眼睛注视的位置，同时类脑跟踪模型显示了计算机视觉跟踪性能与大脑跟踪响应之间的相似性关系。为了比较模型，通过检查深度神经网络中各层的激活来构建到皮层的映射，以便能够很好地理解特定大脑皮层区域中的激活，理想情况下，这种大脑皮层激活不需要多余参数的类脑模型所预测得到，将会降低传统深度跟踪模型的冗余度。因此类脑跟踪模型由卷积层、动态滤波网络、长短时记忆网络和全连接层四个神经网络模块组成，它们类比于大脑平滑跟踪皮层通路中的初级视觉皮层、中颞区和上颞内侧区、额叶视区、脑干/小脑，其中脑干/小脑是运动预测器，将额叶视区的输出转换为相应的运动响应。这种明确的大脑分区思想是设计类脑跟踪模型重要的一步，并且致力于寻找更通用的网络结构。整个模型包括在皮层区域没有差异的神经网络，以及各种改进类脑跟踪模型的连接。并在此基础上对比激活和行为之间的相似性。
同时时在类脑跟踪模型的基础之上分析模型的动态响应和大脑皮层对运动的响应之间的相似性或相关性。并加入第一阶段类脑图像识别模型，类比于大脑皮层中腹侧流和背侧流之间的相互连接和影响，进一步提高视觉皮层的建模精度，以便更好地适应真实和复杂的动态场景，提高类脑模型的跟踪精度和类脑的真实性。

\subsubsection{基于运动皮层的类脑控制策略}
在之前工作的基础之上，考虑大脑中其他模态的信息和视觉信息的相互作用，类比于人类感知中的“通感”。考虑在人所接收的所有感知信息中，听觉信息是仅次于视觉信息的第二大感知源，两者占人所有感知信息的百分之九十以上，所以在建模类脑的多模态感知时主要考虑人类的听觉。听觉识别通路主要包括初级听觉皮层A1、带状区Belt、伞状区PB、中颞/下颞区，并利用卷积神经网络和循环网络为基本结构，模拟人脑处理模式，构建大脑对齐的类脑模型，进行激活和行为之间的对比，包括大脑激活和神经网络激活之间的相似性、网络预测的音频类别和人类动作选择之间的相似性。
同时由于听觉识别的核心区域中颞/下颞区和第一阶段中的目标识别的下颞核心区有重叠部位，为视觉和听觉的融合处理提供了神经解剖基础，可以进一步在图像识别模型和音频识别模型的基础之上设计视觉/听觉融合模块，进行高层特征级别融合，有望进一步提高处理复杂环境输入的能力和提升类脑模型的预测能力。
在进行类脑模型的研究过程中，期待逐步建立一套科学合理的类脑评价指标用于评价所设计的类脑深度神经网络模型和人脑大脑处理信息的相似程度，在类脑图像识别中表现为图像分类和人进行图片识别时选择的相似性，在类脑跟踪中表现为深度神经网络输出的定位框和以人眼中央凹为中心的注意力范围，在感知融合中表现为在融合其他类型信息的复杂条件下模型的预测输出和人行为的相似性。该指标不仅衡量和模型的预测输出和人类行为之间的相似性，而且还衡量模型面对相同的输入刺激，各个中间层的激活响应和人类大脑皮层各个区域的激活（血液动力学响应或者脑电信号等）之间的相似性或相关性，实现从模型结构、皮层激活响应、人类行为等方面进行综合的类脑相似性解释。

\subsection{实验手段}
本项目主要采用标准数据集、ADAS高级智能驾驶辅助系统和真实无人车平台相结合的实验方法，分析拟提出的跟踪方法在开放环境下的跟踪性能。实验主要包括基于标准数据集的验证、基于ADAS系统的测试和基于真实无人车平台的测试等三个方面。

\subsubsection{基于标准数据集的验证}
当前已有许多具有大规模的标准数据集被发布以推动目标跟踪的发展，例如OTB、VOT、UAV123、TC-128和LaSOT等。这些数据集都是在复杂多变的场景下所采集到的，十分具有挑战性。以权威的OTB和VOT为例，OTB数据集由100个视频所组成，包含了58000多帧图片，视频集捕获了复杂场景下的行人、车辆、动物等多种目标，VOT数据主要用于一年一度的视觉目标跟踪竞赛，该数据集每年都会被重新标注和更新来提高数据集的准确性和竞赛难度，目前主要包括60个具有高难度的视频。本项目申请人所在的实验室拥有由多台服务器和PC机所组成的计算平台，该计算平台上安装了Caffe、Keras和Tensflow等深度学习框架，下载了OTB、VOT、UAV123、TC-128和LaSOT等视频数据集，并配置了不同数据集的测试程序。值得一提的是，由于不同数据集采用不同的性能指标以评估跟踪算法的结果，因此测试程序可以有效地验证跟踪算法在不同数据集上的跟踪精度。通过在大规模的标准数据集进行综合性实验能够可靠地验证拟提出的跟踪算法在开放环境下的跟踪性能。

\subsubsection{基于ADAS高级智能驾驶辅助系统的测试}
项目申请人在攻读博士学位期间作为团队的骨干成员参与了ADAS高级智能驾驶辅助系统的研发工作，主要负责环境感知模块的主要功能与相关算法的设计。具体来说，ADAS系统中的环境感知模块主要包括行人与车辆检测与跟踪、交通标志检测与跟踪和车道线检测等任务。图15展示了与本项目研究相关的行人与车辆检测与跟踪和交通标志检测与跟踪的定性结果。因此，可以将本项目拟提出的目标跟踪算法移植到ADAS系统中，通过利用ADAS系统平台测试跟踪方法的性能。

\subsubsection{基于真实无人车平台的测试}
本项目申请人所在的团队与长沙智能驾驶研究院存在合作关系，具有无人车一台。无人车平台上装有摄像头、激光雷达、毫米波雷达和组合导航等多个传感设备。图16展示了无人车平台和团队成员进行实车测试的情况。因此，本项目具有在真实无人车平台上进行实车测试的条件，将来有可能利用该无人车平台验证本项目拟提出的跟踪算法在开放环境下的跟踪性能。

\subsection{可行性分析}
（1）研究目标明确，技术路线清晰。本项目主要研究面向开放环境的鲁棒目标跟踪方法。具体来说，以目标跟踪所存在的跟踪适应性、目标复杂的外观变化和模型漂移等问题为驱动，基于“相关问题分析——模型算法设计——方法验证测试”的技术路线，利用深度学习、机器学习、稀疏表达、判别性模型、多特征融合和集成学习等方法与理论，拟提出基于稀疏约束的判别性跟踪模型、基于时空上下文信息的动态多特征融合策略和基于集成学习的跟踪方法以提高开放环境下的跟踪适应性、准确性和鲁棒性，进而提高开放环境下的跟踪性能。
（2）项目申请人具有一定的研究基础。如上所述，关于该课题三个阶段已有一定的研究基础，包括基本的类脑图像识别模型和评价指标，可以要在此基础上基于已有的人脸识别刺激数据和对应的多模型神经成像数据，利用人脸识别任务分析类脑模型和深度神经网络对相同图像刺激所产生的激活之间的相似性或关联关系，以及进一步分析负责人脸识别区的梭状回和负责目标识别区的下颞回之间的联系和区别。
本课题组已设计和测试类脑跟踪中背侧通路的建模和仿真，建立初步的运动感知模型，定量化验证中颞区和上颞内侧区和动态滤波网络激活的相似性，并在公开数据集上进行了仿真和验证，可以在此基础上加入图像识别的腹侧流模型，进一步研究背侧流和腹侧流共同作用下动态环境的建模和仿真。
类脑感知融合研究中已对类脑听觉皮层模型进行了初步建模，在音乐流派分类数据集合对应的核磁共振数据集上进行了响应分析，需要在此基础上分析深度模型激活和大脑皮层激活之间的相似性，并加入第一阶段腹侧流通路的建模，以进一步提高类脑模型的鲁棒性，提升模型的激活和行为的预测精度。

\NsfcSection{4}{本项目的特色与创新之处；}{}

该类脑研究是可解释深度神经网络的一个很好地解决方案，设计大脑皮层对齐的类脑模型不仅可以设计出符合生物学解剖规律的深度神经网络，利用神经科学的原理来解释所设计的深度网络模型，有望解决深度神经网络“黑盒”的问题，还可以精简模型的层数，减少模型冗余，有利于工程化部署，加快计算机视觉算法的产业化落地。      同时利用设计并训练好的类脑深度神经网络探索脑机接口的应用和人产生视觉概念乃至意识的神经相关物，利用已经比较成熟的高性能计算机和深度学习算法，解决神经科学实验条件受限的不足，解决深度学习领域模型的复杂度越来越高、可解释性越来越差的问题。

\NsfcSection{5}{年度研究计划及预期研究结果}{（包括拟组织的重要学术交流活动、国际合作与交流计划等）。}

本项目以开放环境下的目标跟踪为研究对象，旨在设计鲁棒的目标跟踪方法以获得更好的跟踪精度，拟解决如下关键科学问题：

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\NsfcChapter{（二）研究基础与工作条件}{}

\NsfcSection{1}{研究基础}{（与本项目相关的研究工作积累和已取得的研究工作成绩）；}

无

\NsfcSection{2}{工作条件}{（包括已具备的实验条件，尚缺少的实验条件和拟解决的途径，包括利用国家实验室、国家重点实验室和部门重点实验室等研究基地的计划与落实情况）；}

无

\NsfcSection{3}{正在承担的与本项目相关的科研项目情况}{（申请人和项目组主要参与者正在承担的与本项目相关的科研项目情况，包括国家自然科学基金的项目和国家其他科技计划项目，要注明项目的名称和编号、经费来源、起止年月、与本项目的关系及负责的内容等）；}

无

\NsfcSection{4}{完成国家自然科学基金项目情况}{（对申请人负责的前一个已结题科学基金项目（项目名称及批准号）完成情况、后续研究进展及与本申请项目的关系加以详细说明。另附该已结题项目研究工作总结摘要（限500字）和相关成果的详细目录）。}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

无

\NsfcChapter{（三）其他需要说明的问题}{}

\NsfcSection{1}{}{申请人同年申请不同类型的国家自然科学基金项目情况（列明同年申请的其他项目的项目类型、项目名称信息，并说明与本项目之间的区别与联系）。}

无

\NsfcSection{2}{}{具有高级专业技术职务（职称）的申请人或者主要参与者是否存在同年申请或者参与申请国家自然科学基金项目的单位不一致的情况；如存在上述情况，列明所涉及人员的姓名，申请或参与申请的其他项目的项目类型、项目名称、单位名称、上述人员在该项目中是申请人还是参与者，并说明单位不一致原因。}

无

\NsfcSection{3}{}{具有高级专业技术职务（职称）的申请人或者主要参与者是否存在与正在承担的国家自然科学基金项目的单位不一致的情况；如存在上述情况，列明所涉及人员的姓名，正在承担项目的批准号、项目类型、项目名称、单位名称、起止年月，并说明单位不一致原因。}

无

\NsfcSection{4}{}{其他。}

\end{document}

### 2023-06-05 prediction/foreshadow/Code/Models.Rmd
init

---
output:
  pdf_document: default
  html_document: default
---

---
title: "Brain activity foreshadows stock price dynamics"
output:
  html_notebook: default
  html_document: default

## Load libraries
```{r, include=F}
library(reshape2)
library(dplyr)
library(ggplot2)
library(lmerTest)
require(MuMIn)
source('../rsquaredglmm.R') 
source('../Functions.R')
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#D55E00", "#F0E442", "#0072B2", "#CC79A7", "#999999")

# Read df with data per stock for forecasting analyses
gdf <- read.csv('../../voi_csv/data.csv')
```

#Experiment 1
```{r}
# Choice model (Behavioral model)
ans <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ Choice"), type='glm', split.method ='average', days_train=9)
print(ans)

# Market model
ans <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ slope + volatility + Previous_Trial"), type='glm', split.method ='average', days_train=9)

# Neural model 
ans <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4"), type='glm', split.method ='average', days_train=9)
print(ans)

# Combined model
ans <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', split.method ='average', days_train=9)
print(ans)

# Compare models Experiment 1
model_Choice <- glm("Result ~ Choice", data = filter(gdf, Experiment==1), family = binomial(link = logit))

model_Market <- glm("Result ~ slope + volatility + Previous_Trial", data = filter(gdf, Experiment==1), family = binomial(link = logit))

model_Neural <- glm("Result ~ nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4", data = filter(gdf, Experiment==1), family = binomial(link = logit))

model_Combined <- glm("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility", data = filter(gdf, Experiment==1), family = binomial(link = logit))

lrtest(model_Market, model_Combined)
anova(model_Market, model_Combined, test = "LRT")

lrtest(model_Choice, model_Combined)
anova(model_Choice, model_Combined, test = "LRT")

lrtest(model_Neural, model_Combined)
anova(model_Neural, model_Combined, test = "LRT")
```

# Experiment 2
```{r}
# Choice model (Behavioral model)
ans <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ Choice"), type='glm', split.method ='average', days_train=9)
print(ans)

# Market model
ans <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ slope + volatility + Previous_Trial"), type='glm', split.method ='average', days_train=9)

# Neural model
ans <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4"), type='glm', split.method ='average', days_train=9)
print(ans)

# Combined model
ans <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', split.method ='average', days_train=9)
print(ans)

# Compare models Experiment 2
model_Choice <- glm("Result ~ Choice", data = filter(gdf, Experiment==2), family = binomial(link = logit))

model_Market <- glm("Result ~ slope + volatility + Previous_Trial", data = filter(gdf, Experiment==2), family = binomial(link = logit))

model_Neural <- glm("Result ~ nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4", data = filter(gdf, Experiment==2), family = binomial(link = logit))

model_Combined <- glm("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility", data = filter(gdf, Experiment==2), family = binomial(link = logit))

lrtest(model_Market, model_Combined)
anova(model_Market, model_Combined, test = "LRT")

lrtest(model_Choice, model_Combined)
anova(model_Choice, model_Combined, test = "LRT")

lrtest(model_Neural, model_Combined)
anova(model_Neural, model_Combined, test = "LRT")
```

# Reduced model with only AIns * Previous_Trial 
```{r}
summary(glm('Result ~ desai_insb_TR_4*Previous_Trial', data = filter(gdf, Experiment==1), family = binomial(link = logit)))

summary(glm('Result ~ desai_insb_TR_4*Previous_Trial', data = filter(gdf, Experiment==2), family = binomial(link = logit)))
```

# Interaction AIns*Previous_Trial; Post-hoc T-tests, Exp 1 and Exp 2
```{r}
# Post-hoc t-tests to compare AIns activity in inflection vs no inflection trials
gdf_E1_inflection <- filter(gdf, (Experiment =='1' & Is_Inflection == 1))
gdf_E1_noinflection <- filter(gdf, (Experiment =='1' & Is_Inflection == 0))

gdf_E2_inflection <- filter(gdf, (Experiment =='2' & Is_Inflection == 1))
gdf_E2_noinflection <- filter(gdf, (Experiment =='2' & Is_Inflection == 0))

t.test(gdf_E1_inflection$desai_insb_TR_4, gdf_E1_noinflection$desai_insb_TR_4, paired=F)
t.test(gdf_E2_inflection$desai_insb_TR_4, gdf_E2_noinflection$desai_insb_TR_4, paired=F)

sd(gdf_E1_inflection$desai_insb_TR_4)
sd(gdf_E1_noinflection$desai_insb_TR_4)
sd(gdf_E2_inflection$desai_insb_TR_4)
sd(gdf_E2_noinflection$desai_insb_TR_4)

# Post-hoc t-tests for AIns activation for Result - Goes Down after previous Up or Down day
# Exp1
gdf_E1 <- filter(gdf, Experiment =='1')
up_rd <- filter(gdf_E1, (Result=='Result - Goes Down' & Previous_Trial=="Went Up"))
down_rd <- filter(gdf_E1, (Result=='Result - Goes Down' & Previous_Trial=="Went Down"))
sd(up_rd$desai_insb_TR_4)
sd(down_rd$desai_insb_TR_4)

t.test(up_rd$desai_insb_TR_4, down_rd$desai_insb_TR_4, paired=F)

# Exp2
gdf_E2 <- filter(gdf, Experiment =='2')
up_rd <- filter(gdf_E2, (Result=='Result - Goes Down' & Previous_Trial=="Went Up"))
down_rd <- filter(gdf_E2, (Result=='Result - Goes Down' & Previous_Trial=="Went Down"))
sd(up_rd$desai_insb_TR_4)
sd(down_rd$desai_insb_TR_4)

t.test(up_rd$desai_insb_TR_4, down_rd$desai_insb_TR_4, paired=F)
```

# Classification analyses: Forecasting stock prices out of sample
```{r}
# Specify downsample.var in order for results to be downsampled (e.g. downsample.var = 'Result')

# Train on Combined model of Experiment 1 and test on data of Experiment 2
set.seed(0)
ans1 <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', downsample.var = 'Result', split.method ='average', d.test=filter(gdf, Experiment==2))
kable(ans1)

# Train on Combined model of Experiment 2 and test on data of Experiment 1
set.seed(0)
ans2 <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', split.method ='average', downsample.var = 'Result', d.test=filter(gdf, Experiment==1))
kable(ans2)

# Train on reduced model with interaction between AIns and PreviousTrial in Experiment 1 [2] and test on data of Experiment 2 [1]
set.seed(0)
ans1 <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ desai_insb_TR_4*Previous_Trial"), type='glm', split.method ='average', downsample.var = 'Result', d.test=filter(gdf, Experiment==2))
kable(ans1)

set.seed(0)
ans2 <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ desai_insb_TR_4*Previous_Trial"), type='glm', split.method ='average', downsample.var = 'Result', d.test=filter(gdf, Experiment==1))
kable(ans2)
```

# Forecasting stock prices using randomized stock data
```{r, error=F, warning=F, message=false}
# Combined model
gdf_rdm1 <- filter(gdf, Experiment ==1)
gdf_rdm2 <- filter(gdf, Experiment ==2)

NUM_ITERATIONS <- 500
results_train_1_test_2= t(matrix(NA, NUM_ITERATIONS, 9))
results_train_2_test_1= t(matrix(NA, NUM_ITERATIONS, 9))

set.seed(0)
for(i in 1: NUM_ITERATIONS){
  gdf_rdm1$Result <- sample(gdf_rdm1$Result, replace = F)
  gdf_rdm2$Result <- sample(gdf_rdm2$Result, replace = F)
  ans1 <- checkClassifier(gdf_rdm1, as.formula("Result  ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', split.method ='average', d.test=filter(gdf, Experiment==2), complete_result=T, verbose=F)

  ans2 <- checkClassifier(gdf_rdm2, as.formula("Result  ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', split.method ='average', d.test=filter(gdf, Experiment==1), complete_result=T, verbose=F)

  results_train_1_test_2[, i] <- unlist(ans1)
  results_train_2_test_1[, i] <- unlist(ans2)
}
print("---------------------------------------------------")

train1.test2.result.df <- data.frame(t(results_train_1_test_2))
colnames(train1.test2.result.df) <- names(ans1)
print("Train 1 Test 2 Results")
meanResults12 <- colMeans(train1.test2.result.df)
print(meanResults12)
t.test(train1.test2.result.df$test_accuracy, mu=.5)

print("---------------------------------------------------")

train2.test1.result.df <- data.frame(t(results_train_2_test_1))
colnames(train2.test1.result.df) <- names(ans2)
print("Train 2 Test 1 Results")
meanResults21 <- colMeans(train2.test1.result.df)

print(meanResults21)
t.test(train2.test1.result.df$test_accuracy, mu=.5)

print("---------------------------------------------------")

# Reduced model: AIns interaction with Previous Trial
gdf_rdm1 <- filter(gdf, Experiment ==1)
gdf_rdm2 <- filter(gdf, Experiment ==2)

NUM_ITERATIONS <- 500
results_train_1_test_2= t(matrix(NA, NUM_ITERATIONS, 9))
results_train_2_test_1= t(matrix(NA, NUM_ITERATIONS, 9))

set.seed(0)
for(i in 1: NUM_ITERATIONS){
  gdf_rdm1$Result <- sample(gdf_rdm1$Result, replace = F)
  gdf_rdm2$Result <- sample(gdf_rdm2$Result, replace = F)
  ans1 <- checkClassifier(gdf_rdm1, as.formula("Result  ~  desai_insb_TR_4 *Previous_Trial"), type='glm', split.method ='average', d.test=filter(gdf, Experiment==2), complete_result=T, verbose=F)

  ans2 <- checkClassifier(gdf_rdm2, as.formula("Result  ~  desai_insb_TR_4 *Previous_Trial"), type='glm', split.method ='average', d.test=filter(gdf, Experiment==1), complete_result=T, verbose=F)

  results_train_1_test_2[, i] <- unlist(ans1)
  results_train_2_test_1[, i] <- unlist(ans2)
}
print("---------------------------------------------------")

train1.test2.result.df <- data.frame(t(results_train_1_test_2))
colnames(train1.test2.result.df) <- names(ans1)
print("Train 1 Test 2 Results")
meanResults12 <- colMeans(train1.test2.result.df)
print(meanResults12)
t.test(train1.test2.result.df$test_accuracy, mu=.5)

print("---------------------------------------------------")

train2.test1.result.df <- data.frame(t(results_train_2_test_1))
colnames(train2.test1.result.df) <- names(ans2)
print("Train 2 Test 1 Results")
meanResults21 <- colMeans(train2.test1.result.df)

print(meanResults21)
t.test(train2.test1.result.df$test_accuracy, mu=.5)

print("---------------------------------------------------")
```

### 2023-06-05 visual/dorsal/latex/neuro/Manuscript.tex
init

%% 
%% Copyright 2007-2019 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%% 
%%
%% $Id: elsarticle-template-num.tex 168 2019-02-25 07:15:41Z apu.v $
%%
%%
%\documentclass[preprint,12pt]{elsarticle}
%\documentclass[final,1p,times,twocolumn]{elsarticle} 
\documentclass[final,3p,times,twocolumn]{elsarticle}
%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\graphicspath{{image/}}
\usepackage{float}
\usepackage{caption}
\usepackage{array}
\usepackage{booktabs}
 % 设置超链接跳转
\usepackage[colorlinks,
            linkcolor=blue,
            anchorcolor=blue,
            citecolor=blue]{hyperref} 
\usepackage{amsmath}

% 改变字体颜色
\usepackage{color,xcolor}
\usepackage{makecell}

\journal{Neurocomputing}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{BTN: Neuroanatomical Aligning between Visual Object Tracking \\in Deep Neural Network and Smooth Pursuit in Brain}

%% use optional labels to link authors explicitly to addresses:
 \author[label1]{Haidong Wang}
 \ead{haidong@hnu.edu.cn}
 \author[label1]{Zhiyong Li\corref{cor1}}
 \ead{zhiyong.li@hnu.edu.cn}
 \author[label1]{Ke Nai}
 \ead{naike\_hnu@hnu.edu.cn}
 \author[label1]{Jin Yuan}
 \ead{yuanjin@hnu.edu.cn}
 \author[label2]{Shutao Li}
 \ead{shutao\_li@hnu.edu.cn}
 \author[label3]{Xianghua Li}
 \ead{493630379@qq.com}
 \address[label1]{College of Computer Science and Electronic Engineering, Hunan University, Changsha, China}
 \address[label2]{College of Electrical and Information Engineering, Hunan University, Changsha, China}
 \address[label3]{State Grid Hunan Electric Power Company Limited Economical and Technical Research Institute, Changsha, China}
\cortext[cor1]{Corresponding authors.}

%\author{}
%
%\address{}

\begin{abstract}
Inspired by neuroanatomy, deep neural networks (DNNs) have recently developed from shallow network structures to exceedingly deep structures, providing excellent visual tracking results.
However, standard DNNs usually do not easily connect with brain areas on account of their excessive network depth and absent biological constraints, such as recurrent connections. 
We propose a brain-like tracking network (BTN) with four neuroanatomically mapped regions and recurrence, guided by the brain-like tracking score (BTS), 
a novel benchmark to measure the model similarity of the human smooth pursuit pathway. 
In addition, we propose that the middle temporal (MT) and medial superior temporal (MST) areas in the cerebral cortex are equivalent to the designed network structure on the basis of the continuous motion perception of the tracking pathway, 
and indicate that the metrics between the neuroanatomical similarity in the cerebral cortex and visual tracking of the DNN are compatible. 
Despite having significant tracking performance on the Tracking-Gump dataset, the BTN has achieved a high BTS. 
In summary, this research builds a BTN, a brain-like and recurrent DNN, as the first model of the cortical pathway of smooth pursuit.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
Visual object tracking \sep deep neural network \sep neuroscience \sep smooth pursuit

\end{keyword}

\end{frontmatter}

%% \linenumbers

\begin{figure*}
	\centering
	\includegraphics[width=6.7in]{imgs/introduction.pdf}
	\caption{
		\textbf{
		Collaborative design between a DNN and neuroanatomy with a BTS.} 
		Through the quantitative brain-like score, we refer to the human brain and utilize acquired knowledge to enlighten the design of the BTN. 
		The BTN includes four regions that are mapped into the 		primary visual cortex (V1), 
		the middle temporal and medial superior temporal areas (MT/MST), the frontal eye field (FEF) and the brainstem/cerebellum. 
		CONV\textsubscript{V1} is the classical convolutional layer and performs preprocessing to reduce the data size.
		The DFN\textsubscript{MT/MST} is dynamic filter network, and the RNN\textsubscript{FEF} is recurrent, as depicted in Section~\ref{sec:cornet_s_def} for details.
		The the upper-right image corresponds to the tracking activation and bounding box in the brain-aligned models, 
		while lower-right image represents the cortical activation and eye gaze position with the stimulus in the far left,
		which demonstrates the relationship between computer vision tracking performance and brain tracking response with the BTS, as depicted in Section~\ref{sec:results1}.
	}
	\label{fig:introduction}
\end{figure*}

\section{Introduction}{D}{eep} learning has made great progress in building the candidate model of the neuromechanism in the neurological community~\cite{kubilius2019brain-like}. 
Amazingly, in trained deep neural networks (DNNs) used to classify images~\cite{Deng2009ImageNet}, the middle layer in DNNs can partially explain why the nerve cell in the middle layer of the visual cortex has specific activations to an image~\cite{yamins2014performance,khaligh2014deep,gucclu2015deep,murugesan2017brain,cichy2016deep,yamins2016using}. 
\textcolor{red}{
Furthermore, these models also partly predict primate image recognition behavior and cortical activation~\cite{rajalingham2018large,kubilius2016deep}.
Excellent models of the brain provide extraordinary opportunities for brain-computer interfaces,
and these methods can be utilized to predict the expected activations in the cortical pathway~\cite{bashivan2019neural}.}

\textcolor{red}{
To capture cortical processing even more strictly in these models, continued architectural search on traditional visual datasets alone no longer seems to be a feasible solution. 
Even though the great tracking performance in deeper DNNs has truly increased~\cite{ILSVRC15,luo2021trajectory}, it is hopeless to raise the brain-like score~\cite{rajalingham2018large,su2020incremental}. 
In addition, at the beginning, only partial modules can be obviously mapped to corresponding regions of the visual pathway, 
and the relations between the small number of visual regions and the numerous and complex modules in GoogleNet~\cite{szegedy2015going} or Inception-v4~\cite{szegedy2017inception} are inconspicuous. 
Finally, the network with high accuracy in the visual task becomes increasingly deeper except for several brain-like architectures for image classification~\cite{TangSchrimpfLotter2018Recurrent, kar2019evidence}. 
}

\textcolor{red}{
To address the interpretability problem of visual tracking model, in this study, we propose that aligning DNNs to anatomy will result in shallower, more interpretable, and more brain-like tracking models, named brain-like tracking network (BTN).
The BTN is a shallow recurrent brain-like architecture of the brain pathway; 
hence, it has a much more brain-like structure. 
In section 4, we introduce the method utilized to analyse human behavioral and cortical data during object tracking. 
In section 5, we build a fancy measurement method for predicting eye movement behavior and neural activations on the brain-like tracking score (BTS). 
In our experiments, we introduce a new benchmark dataset composed of behavioral and cortical recordings, 
and present an outstanding tracking result of 36.5\% at evaluating the model similarity of the visual pathway while obtaining a good tracking effect in the Tracking-Gump dataset~\cite{gaze_forrest}. 
We find that these results are mainly due to the brain-like architecture, in accordance with prior knowledge of the human cortical pathway processing stimuli input~\cite{TangSchrimpfLotter2018Recurrent, yin2020deep, kar2019evidence}. 
Finally, to compare the model activations between the RNN\textsubscript{MT/MST} in the BTN and the responses in the human middle temporal and medial superior temporal areas (MT/MST), we discover that the BTN predicts these cortical activations well, 
and it is also the first visual tracking model to do so on the neural recordings. 
} 
%\par

\section{Related Works}

\subsection{Deep neural network}\par
Many works have recently shown that salient objects are extracted by a series of foveal views~\cite{mnih2014recurrent,draw}.
The object extraction module in the BTN is implemented with a two-dimensional gaussian filter~\cite{RATM} that is neuroanatomically explainable.
Focusing on specific appearance representations may be as important as spatial attention. 
An approach with recurrence can adaptively change the filter of the convolution module, therefore changing it to presentations on a frame and optimizing model performance~\cite{stollenga2014deep}. 
The filters of the dynamic filter network (DFN)~\cite{brabandere2016dynamic} are obtained online based on the input feature, and the DFN implements model compression without degrading the accuracy. 
Input-dependent state transitions can help to learn the markovian decision model~\cite{karl2017deep}. 
\textcolor{red}{
We do not follow the results, and use the idea to predict the salient feature.}

\textcolor{red}{
To track a target, it seems to be very suitable to use recurrences and glimpses, but they have only been employed successfully in monochromatic videos with simple backgrounds~\cite{RATM}. 
Some~\cite{ning2017spatially} obtained prominent results through representations of the target detector that is the input of a recurrent neural network (RNN)~\cite{su2020improved}.
However, it needs to process each full frame. 
A recent study~\cite{gordon2017re3} utilized an RNN cropping explicitly to build attention in humans. 
Our study is similar to~\cite{RATM,luo2019teleoperation}, and utilizes human attention which is implemented with a long short memory network (LSTM) to extract the movement features well in multiple frames. 
In addition, we seek to design a brain-like network that will gain a superior BTS and exceed the existing tracking models on the Tracking-Gump dataset~\cite{gaze_forrest}.
}\par

\subsection{Smooth pursuit}
There have been many successful eye movement experiments. 
Some eye movement detection methods are proposed according to the existing plentiful datasets that have annotated eye movement data~\cite{dorr2010variability,mathe2012dynamic,hooge2017is,blstm_class}. 
Many of the existing classification methods, which are designed using motionless input, only process saccades and fixations. 
Therefore, these methods cannot detect smooth pursuit and prevent the detection of brain-like correlations with smooth pursuit. 
In order to address this issue, a multi-observer smooth pursuit method (MOSP)~\cite{mosp} that can differentiate three primary eye movements, including saccade, fixation and smooth pursuit, 
and acquire good performance evaluation is designed~\cite{blstm_class}.
In addition, to accurately explain the domain of  intelligence as a brain-like model in the human brain and cognitive sciences, 
the brain-score has been proposed in the research of an integrated benchmark in the field of computer vision~\cite{schrimpf2020integrative}.

In this work, we take full advantage of the latest achievements. 
By utilizing these excellent eye movement classification and computer vision methods, 
we can process functional magnetic resonance imaging (fMRI) and gaze data in the studyforrest dataset~\cite{gaze_forrest} 
and detect corresponding cortical regions associated with saccadic and smooth pursuit in Tracking-Gump.
In addition, based on model activation and cortical activation, we designed the BTS to measure their similarity.

\section{BTN: Brain-like Tracking Network} 
In this section, we introduce the proposed BTN with three steps. 
First, we indicate the motivation and design criteria in our methods.
Second, we detail each component in the BTN pipeline. 
Finally, we introduce the loss function to train the BTN. \par

\subsection{Design criteria}
Our aim is to obtain a high brain-likeness between visual object tracking in DNN and the smooth pursuit in brain.
Additionally, smooth-pursuit movements in our brain keep the image of a moving target on the fovea. 
\textcolor{red}{
In the pathway of smooth pursuit,
primary visual cortex (V1) is the first stage to preprocess the input signals, 
MT/MST \textcolor{red}{integrate} motion signal across space,
and frontal eye field (FEF) generates predictive eye movement signals~\cite{b11,b13,b14}.
}\par

\textcolor{red}{
Inspired by the pathway of smooth pursuit in brain, we build neuroanatomical mapping from cortical regions to DNN layers, as depicted in Figure~\ref{fig:introduction}.}
For model comparison, we build the mapping by examining the layer in the DNN that understands activations well in a specific cortical region, 
ideally such activations will already be predicted by the model with no superfluous parameters. 
Therefore, the BTN consists of four neural network modules including convolution layer, DFN, LSTM and FC.
And they are the analogy to the smooth pursuit pathway V1, MT/MST, FEF, 
and motion predictor that converts the output of FEF to corresponding motion responses, as depicted in Figure~\ref{fig:pipeline}. 
This plain idea of explicit brain areas segmentation is an important step to design a brain-like tracking model, 
and we are committed to finding more universal structures. 
Examples include an entire model as a neural network with no difference in cortical areas
and various connections that may improve BTS in future work.
In addition, we follow these two criteria to design the BTN~\cite{kubilius2018predict}:

(1) \textbf{Architecture}: In models with similar tracking performance, we prefer a brain-like network because it is easier to understand and can meet the anatomical constraints.
And we use DNNs because their neurons are the basic unit of data processing, 
and all neural activations in DNNs can be clearly mapped to cortical activation~\cite{yamins2016using}.
\textcolor{red}{
In addition, recurrent connections are naturally considered for visual object tracking on account of the temporal attributes in the video sequence.}
Activations in the dorsal pathway also have a temporal attribute; 
therefore, the BTN is assumed to generate activations in time series.

(2) \textbf{Predictivity}: 
There is more correct behavior output in intermediate layers and final outputs that meet neuroanatomical constraints (neural responses). 
This make our model have an ability to predict cortical activation and human eye movement behavior.

We now introduce the pipeline for BTN.

\subsection{BTN pipeline} \label{sec:cornet_s_def}

Given the input frame $F_t$ and attention parameters $a_t$, the fovea (imitating spatial attention) selects a foveal view $f_t$. 
\textcolor{red}{Moreover, we use an appearance selector, parameterized with appearance $\alpha _t$ including V1 and this dorsal pathway and ventral pathway, to obtain the tracked target representations $m_t$ 
and update hidden state $h_t$ in LSTM.}
Then, we decode the output of LSTM and use it to infer the eye movement $\Delta p_t$, spatial attention $a_{t+1}$ and the appearance attention $\alpha _{t+1}$ in the next frame.  
Appearance attention is driven by top-down information $\alpha _t$ and bottom-up (the foveal view $f_t$) information. 
However, spatial attention only relies on top-down information $a_t$.
In this case, bottom-up information only has localized impacts and relies on salience input at a position, 
but top-down information combines global features into localized analysis. 
The attention mechanism, which intensified with recurrence, imitates the visual cortex~\cite{attention}.
Then, we detail each component of the brain-like tracking architecture.

\begin{figure*}
	\centering
	\includegraphics[width=5.7in]{imgs/pipeline.pdf}
	\caption{
		\textbf{
			The designed architecture in visual object tracking in humans.} 
		The believable cortical areas implementing particular roles in smooth pursuit are indicated with rectangular modules.
		The foveal view $f_t$ is obtained in the input frame $F_t$ with the spatial selector in the fovea. 
		V1 and the ventral pathway learn the appearance representations $v_t$, 
		and neurons in the dorsal pathway (including V1 and MT/MST) segment the salient object $d_t$ and background on the foveal view.
		The refined representations $m_t$ are utilized to compute the working memory $h_t$.
		Specifically, the FEF may be more important for initiating pursuit learning based on the target velocity,
		and we combine FEF output $o_t$ and dorsal stream output $d_t$ into the next module. 
		The cerebellum and brainstem together (including pontine nuclei (PN), flocculus, vermis and vestibular nuclei (VN)) are modeled by fully connected layers (FCs) to generate attention $a_{t+1}$, appearance $\alpha_{t+1}$, and eye position correction signals $\Delta p$,
		even the final eye movement ($\Delta p_t$) via the oculomotor.
		All black arrows indicate that information flows within one time-step, 
		while the gray colored arrows represent the temporal connections.  
	}
	\label{fig:pipeline}
\end{figure*}

\subsubsection{Retina and Dorsal/Ventral \textcolor{red}{Pathway}}
The spatial selector selects the foveal view $f_t$ for the current frame $F_t$,
and its output is transmitted to two interconnected cortical pathways.
The ventral pathway recognizes the tracked targets 
and the dorsal pathway learns motion features in the field of view. 
\textcolor{red}{
We present the dorsal pathway with the MT/MST that analyses motion features, as depicted in Figure~\ref{fig:pipeline};
and computes a foreground segmentation $d_t$ of the foveal view.}

(1) \textbf{Retina}: 
The spatial attention mechanism in our model pipeline is modeled according to~\cite{RATM}. 
An input frame $F_t \in R^{W \times H}$ forms matrices $M_t^x \in R^{w \times W}$ and $M_t^y \in R^{h \times H}$.
A row of the matrix contains a gaussian distribution. 
The position and width of the gaussian distribution determine which parts of the input frame are selected as the foveal view $f_t$ in the retina.
Therefore, the foveal view $f_t \in R^{h \times w}$ can be denoted as
\begin{equation}
f_t = M_t^y F_t (M_t^x)^T.
\end{equation}
We represent attention with the distributive center, the variance and the stride of the distributive center of continuous matrix rows.
Unlike the study~\cite{hart}, only the stride and center are predicted through LSTM;
however, variance only relies on stride.
The operation avoids extravagant bias when estimating a smaller variance, contributing to a faster learning speed. 
In addition, the utilized size of $f_t$ relies on the experimental analysis.

(2) \textbf{Ventral Pathway}: 
The ventral pathway converts the foveal view $f_t$ into a fixed dimension vector $v_t$ including spatial and appearance features of the tracked object. 
The network structure architecture relies on the specific experimental analysis. 
In the architecture of the ventral pathway, we implement V1 using a CNN, which is a mutual module in the ventral pathway and dorsal pathway.
Generally, however, we implement V1 using several convolutional layers and max pooling layers. 
\textcolor{red}{
These layers, which imitate V1 in humans~\cite{theoretical_neuroscience}, are shared with the dorsal pathway.}
In addition, the pipeline is split into dorsal and ventral pathways. 
Finally, we implement the ventral pathway by CNN that extracts object representations $v_t$.

(3) \textbf{Dorsal Pathway}: 
The dorsal pathway (MT/MST) is implemented as a DFN~\cite{brabandere2016dynamic} 
and is used to address spatial relations between the foreground and background. 
Let FC$(\cdot)$ indicate a fully connected layer.
MT/MST utilizes appearance representation $\alpha_t$ to dynamically predict the convolutional filter $\phi_t$
\begin{equation}
\left\{ \phi _t ^i \right\}_{i=1}^N = \text{FC}(\alpha_t).
\end{equation}
The filters with corresponding nonlinearities in $N$ convolutional layers are applied to the feature in V1. 
Then, we apply a $1 \times 1$ convolution and a sigmoid function to convert the representation into a two-dimensional mask $d_t$.
\textcolor{red}{
Every point in $d_t$ indicates how likely the pursued target is occupied.}

The position map of the dorsal pathway is integrated over the object representations learned by the ventral pathway, which simulate the noise restraining mechanism in the visual system. 
This can handle occlusion and avoid drift, because the target representation is not overwritten in LSTM when the current frame has no representations of the pursued target. 
Therefore, the output of ventral and dorsal pathways are integrated as
\begin{equation}
m_t = \text{FC}(conc(v_t \odot d_t)),
\end{equation}
where $\odot$ indicates the Hadamard product that performs salient object extraction through the representation mask, 
and $conc$ means a concatenation operator that concatenates all rows of a matrix into a vector.

\subsubsection{FEF}

The proposed method depends on the ability to estimate the object appearance and position in the next frame; 
and therefore, it heavily relies on state prediction. 
The LSTM can utilize spatial-temporal and appearance features, 
and enables the proposed model to handle occlusion and drifting target representations, such as a tracked \textcolor{red}{target} obscured by other distractors.

The LSTM module, presented in Figure~\ref{fig:pipeline} and named the FEF, utilizes \textcolor{red}{the} output error to predict eye movement. 
Similar predictive actions exist when smooth pursuit is demonstrated in the FEF area that accepts the output of the dorsal stream~\cite{b11,b13,b14}. 
The output error goes to zero when the delay between object and eye movement is decreased in model training; 
thus, LSTM requires inferring eye motion without image input.
The refined representations $m_t$ are used to update the hidden state $h_t$ in the FEF. 
\begin{equation} \label{LSTM}
h_t, o_t = \text{LSTM}(h_{t-1}, m_t).
\end{equation}

\subsubsection{Brainstem/Cerebellum}

Then we utilize the output $d_t$ and $o_t$ to estimate eye movement $\Delta p_t$, attention $a_{t+1}$ and appearance $\alpha_{t+1}$.
\begin{equation} \label{FC}
\Delta p_t, \Delta a_{t+1}, \alpha_{t+1} = \text{FC}(conc(d_t), o_t),
\end{equation}
\begin{equation} \label{attention}
a_{t+1} = a_t + tanh(c) \Delta a_{t+1},
\end{equation}
where $c$ is a trainable coefficient initialized with a low parameter to restrict the update size during learning. 
Equations (\ref{LSTM}) to (\ref{attention}) describe the information update. 
We calculate the gaze position with an accumulation of attention variations. 
Because spatial attention is learned to estimate the position of the tracked object in the next frame, as depicted in Section~\ref{sec:loss}, a gaze position $p_t$ relative to the attention at time $t$ is predicted.
\begin{equation}
p_t = a_t + \Delta p_t.
\end{equation}

In addition, we refer to the discoveries and the idea~\cite{b9} that the brainstem and the cerebellum both instantiate an inverse dynamics controller (IDC)~\cite{purkinje_IDC}. 
Like~\cite{b9}, we suppose that the IDC is perfect, and thus we can denote 
\begin{equation}
\Delta p_t = \Delta p,
\end{equation}
where $\Delta p$ is the low pass filter of eye motion.
Based on this hypothesis, we will not implement IDC in our study.

\subsection{Loss} \label{sec:loss}

We train the proposed BTN by optimizing an assembly of losses: a tracking loss, a series of attention losses and an auxiliary loss. 
The BTN loss $L_{b}$ is given by
\begin{equation}
L_{b} = L_t + L_a + L_u.
\end{equation}
Detailed information on the BTN loss is described below.

\subsubsection{Tracking Loss}
To locate the tracked target, we design the tracking loss between the output of the BTN and the true label. 
We refer to the study~\cite{UnitBox} and denote the tracking loss as the negative logarithm of their intersection over union (IoU) between predicted bounding box $p_t$ and ground truth $\hat{p}_t$:
\begin{equation}
L_t = -\log(\mbox{IoU} ( \frac{p_t \cap \hat{p}_t}{p_t \cup \hat{p}_t} )).
\end{equation}

\subsubsection{Attention Loss}
\textcolor{red}{
The attention mechanism selects the tracked object from the input frame $F_t$.}
To train the BTN better, we utilize three attention loss terms.
The first item makes the intersection area between the predicted attention $a_t$ and the bounding box $p_t$ as large as possible. 
The second item prevents obtaining a very large width, and the log functions are applied to maintain stability in the calculation. 
The third item restrains background noise while focusing entirely on the tracked target, e.g., gazing at a particular object moving in a crowd. 
To achieve this, we elaborately design a loss that selects only the tracked target.
For the attention $a_t$ and bounding box $p_t$, $r(a_t, p_t)$ indicates a binary mask that has the same size as the output of V1. 
$r(a_t, p_t)$ is one where \textcolor{red}{the} bounding box and the foveal view intersect.
Finally, the third item is denoted as the cross entropy between $r(a_t, p_t)$ and $d_t$.
\begin{equation}
L_a = -\log (\frac{a_t \cap p_t}{p_t}) - \log (1 - \frac{a_t \cap F_t}{a_t \cup F_t})
- r(a_t, p_t) \log(d_t).
\end{equation}

\subsubsection{Auxiliary Loss}
We use L2 regularization to regularize the dynamic filter parameter $\phi_t(\alpha_t)$ and the model parameter $\theta$.
\begin{equation}
L_u = \frac{1}{2} \left\vert \left\vert \phi_t \right\vert \right\vert _2 ^2 
+ \frac{1}{2} \left\vert \left\vert \theta \right\vert \right\vert _2 ^2.
%- \sum_{i} \log (\lambda_i^{-1})
\end{equation}

\section{Brain Data Analysis}
To compare the similarity between DNN tracking and human smooth pursuit, we first extract the smooth pursuit from various eye movements 
and then select the corresponding brain areas and activations.

\subsection{Eye movement analysis}
% follow gump 2.3, From the 
Based on the existing studyforrest dataset~\cite{gaze_forrest}, we obtain the display coordinates and the data assessment for every eye movement recording. 
A data assessment of 1 means perfect eye movement tracking 
and a value of 0 means lost. 
After examining the dataset, we find that subjects 5 and 20 have a conspicuous anomaly. 
Their lost tracking is 86\% and 39\%, respectively. 
Therefore, we remove them from our eye movement analysis.

The remaining eye gaze samples are classified into various types of eye movements by the MOSP method~\cite{mosp},
which is implemented by~\cite{mosp_imp}.
The method achieves prominent performance compared to several latest eye movement detection methods on a benchmark dataset~\cite{fix_sp_detection, eye_move_det}. 
Another feature of the MOSP method that is appropriate for our research is that it utilizes comprehensible parameters that are easy to tune.
In particular, MOSP achieves remarkable smooth pursuit detection performance which is significant for further experiments.

The MOSP method has two steps.
The first step detects saccades, 
and the second step classifies fixations and smooth pursuits. 
The method in the first step is detailed in~\cite{dorr2010variability} and utilizes both low-and-high speed threshold values. 
A larger value is utilized to initialize saccade detection.
Then, the thresholds are stretched in two directions until the speed is less than the small value. 
This next step initially assigns a sample with fixation because it is certainly eye fixation. 
Then the remaining data are labeled as smooth pursuit. 
Next, we use the DBSCAN method~\cite{1996A} to generate clusters when the density of samples exceeds some value. 
The smooth pursuit detection method based on density clustering is reliable due to two important characteristics. 
First, smooth pursuit can exist only if a movement occurs at a given frame, 
and the number of motion objects in each frame is usually low. 
Second, motion objects usually attract attention and are tracked by most of subjects. 
The two characteristics allow the method to robustly detect actual smooth pursuit from similar motion and drift, 
which is very significant for the latter fMRI analysis.
For instance, even though we erroneously label certain recordings as smooth pursuit, we label them correctly when the remaining subjects do not have the same feature at the same time and region. 
However, there are some potential defects of losing smooth pursuit samples as long as a small number of people track the object, and the increased robustness is very significant in our research seeking to identify cortical regions correlated with smooth pursuit.

Because the raw MOSP is conceived and tested on other datasets~\cite{dorr2010variability}, several hyperparameters are fine tuned. 
In addition, we improve the smooth pursuit detection performance by utilizing both in-scanner and in-lab samples together because the smooth pursuit detection performance is improved with data augmentation.

\subsection{fMRI analysis}
We use SPM12 software to analyse the fMRI data. 
First, we utilize a typical analytic flow, including realigning, coregistering, normalizing and smoothing, for all data~\cite{fMRI_handbook}. 
In the first-level analysis, we integrate eight segmentation recordings into a design matrix to build the entire video. 
In every session, we fit a saccade, a smooth pursuit and a video motion regressor. 
Except for preceding regressors, we utilize 6 head movement elements, which are obtained from the realignment in data pre-processing as disgusting regressors.

The motion and eye movement regressors are built according to the sequence of events with 2 s intervals, which coincide with \textcolor{red}{repetition} time in fMRI. 
Thus, every event indicates the variance of the regressor between recordings. 
The event intensity is tuned through the number of motions in 2 s.
The event intensity is zero when it is equal to the average value 
and increases to one linearly. 
In the regressor construction step, we consider video motion, 
which is implemented using the average video motion in 2 s intervals as before. 
In particular, the intensity evaluation of the modulating factor of eye movement consider three primary factors: 
(1) The first factor is based on the recording;
the number of eye movements varies with different subjects 
and it may be involved in the differences in cortical connectivity~\cite{individual_variability}. 
\textcolor{red}{
In studyforrest dataset~\cite{gaze_forrest}, saccades vary from 6\% to 12\%, and smooth pursuits vary from 12\% to 19\% among different subjects.}
Therefore, if the average is utilized, the relevant responses in some subjects will be magnified, and some will be suppressed. 
(2) The second factor captures the variations in eye movement for different inputs 
and indicates the average percent of every eye movement for a subject. 
This is equal to the average eye movement. 
(3) The last captures prevalent differences and variances in the different types of eye movement, 
and the modulating parameters are proportional to the variances. 
This factor is selected in the dataset to cause approximately 90\% of the modulating values to be less than one. 
Hence, we set a smaller modulation factor for saccades because they have lower variance with different stimuli. 
For smooth pursuit, we set a bigger modulation factor to indicate a larger variance in smooth pursuit, 
which will not appear without an object in motion.

For the intensity of the modulation values of movement estimation, we follow the same steps as the building of the motion factors. 
Therefore, we capture the stable condition using the average motion in every input separately. 
This result is regularized by 90 percent of the movement parameters among all crops and is a limit to one to reduce the impact of abnormal value.

As it becomes obvious from how the regressors are built, it is impossible to build both smooth pursuits and fixations with these steps without making strong associations in the different eye movements. 
In order to reinforce the interrelation, we think that the subjects track an object from the beginning. 
Therefore, the intensity regressor of smooth pursuit will be increased as the fixation intensity decreases.

When the generalized linear model is fit on the dataset for every subject individually, we utilize the intensity module of the hemodynamic response function of a regressor that crossed all sessions to obtain the contrast of region of interest (ROI). 
The contrasts contain the primary effect on eye movement and motion, the contrast between saccade and smooth pursuit, and the contrast between motion and eye movement. 
Finally, in the between-subject analysis, we perform the one sample $t$-test in every preceding contrast of all subjects. 
The clustering results ($p<0.05$) are mapped to the three-dimensional cortical regions 
and are selected with specific cortical regions MT/MST to compute BTS in the next section.

\section{BTS: Brain-like Tracking Score} \label{sec:bts}
In this part, we present the BTS metrics, which measure the similarity between the DNN model and the human cortex. 
The BTS is a metric tested on specific experimental datasets, which can be both behavioral and cortical measurements.

In order to obtain the quantitative metrics about brain similarity, we refer to the open-sourced platform brain-score~\cite{SchrimpfKubilius2018BrainScore} and propose the BTS, a well-designed metric that evaluates a model's ability to predict 
\textcolor{red}{
(a) the average pooled human eye movements when tracking an object in each input video frame of the studyforrest dataset~\cite{gaze_forrest}, 
and (b) the average activation of each cortical position to each input video frame in human visual areas MT/MST on the studyforrest dataset~\cite{gaze_forrest}.
To evaluate BTN on a unified metric, we compute the average of behavioral and cortical metrics.}

\subsection{Behavioral metrics}
\textcolor{red}{
The aim of behavioral metrics is to calculate the similarity between the DNN outputs and the human behavioral outputs in a specific problem~\cite{rajalingham2018large}. 
In the human eye object tracking, the subjects's attention is a circle scope and related to human pupil.
Thus, the behavioral modes (the position of eye gaze and the size of pupil) is modeled as a circle and differs from the bounding box in visual object tracking. 
Meanwhile, the main purpose is to realize human-like intelligence, not only the tracking accuracy~\cite{schrimpf2020integrative}; 
and BTN obtains better behavioral similarity and can predict the position and scope of eye gaze well. 
Otherwise, the result is that DNNs gain perfect bounding box fitting but can not obtain a good eye gaze prediction performance. 
}

The utilized 12 video sequences including a salient object moving against a natural background are shown to humans for approximately 20s 
and their gaze scopes are recorded to track the salient object, and depicted in Section~\ref{sec:datasets}. 
To analyse and evaluate the proposed model, we used the subject eye movement and model responses of 149 images in 12 image sequences.
A total of 149 of those frames, where each frame is the input of DNN, are used to predict the eye gaze scope.
Then, this behavioral predictivity is measured through the scope of eye attention in each frame.

The resulting output of the DNN is the bounding box of the tracked target, 
and the subject's attention is a circular scope (center coordinates $x$, $y$ and the radius).
Therefore, the eye movement predictivity or behavioral score can be modeled as the IoU between the actual eye attention circular scope of gaze $S_{roi}^a$ and the bounding box of the DNN's predictions $S_{roi}^b$. 
We compute the overall behavioral metrics~$s_b$ among all frame sequences as the eye movement predictivity \textcolor{red}{score as follows:} 
\begin{equation}
s_b=\frac{area(S_{roi}^a \cap S_{roi}^b) }  { area(S_{roi}^a \cup S_{roi}^b) }.
\end{equation}

\subsection{Cortical metrics}
\label{sec:neural-pred}

We utilize the cortical metrics, which infer activations of the human cortex, such as responses in motion cortical MT/MST, to measure how fine the model predicts the specific input frame in the DNN~\cite{yamins2014performance}. 
This metric requires two groups of inputs with the form of $\text{input} \times \text{neuroids}$, where neuroids are either model interlayer activations or neural recordings.

In total, 149 frames including a tracked object that appeared randomly on a natural scene are presented to 13 subjects,
and the neural responses are collected from 2177 MT/MST voxels. 
In addition, we report the most predictive layer or specific model regions in the BTN.

In our experiment, the relations are fitted to map from a DNN to a cortex, and these relations are utilized to predict the responses in the provided frames. 
To accelerate the process, we reduce the activation dimensionality to specified components using principal component analysis (PCA)~\cite{2002Principal}. 
We utilize the activations from MT/MST to learn the fits. 
\textcolor{red}{
The Pearson correlation coefficient $s_r$ constitutes the final neural similarity score for visual motion cortex as follows:
}
\begin{equation}
s_r=\frac{\sum_{i=1}^{n} (y_i-\bar{y}) (y_i^\prime - \bar{y}^\prime) }{\sqrt{\sum_{i=1}^{n} (y_i - \bar{y})^2 (y_i^\prime - \bar{y}^\prime)^2 }},
\end{equation}
\textcolor{red}{
where $y^\prime$ is the model activation, $y$ is the actual activation and $n$ is the corresponding feature dimension in DNN. $\bar{y}$ and $\bar{y}^\prime$ are the corresponding median over all individual neural response values.
}

\subsection{Overall score}
In order to measure how well the BTN performs integrally, we use the BTS as a combination of the IoU behavioral metric and MT/MST cortical metrics.
The BTS $s_{t}$ presented below is the mean of the two scores. 
\begin{equation} \label{equ:score_btn}
s_{t} = \frac{s_b + s_r}{2}.
\end{equation}
The design of the BTS is not normalized in various score magnitude because this possibly penalizes scores with small variances.
So we treat each score for significance fairly for the BTS.

\section{Experiments}
Here we indicate the experiments and validity of our proposed BTN with three steps. 
First, we introduce the datasets and detailed implementation in our \textcolor{red}{method}.
Second, we demonstrate that the BTN is a valid and brain-like pursuit model.
Finally, we discuss the model design mechanism and the relationship between DNN and neuroscience.

\subsection{Datasets} \label{sec:datasets}
We train the proposed BTN in a challenging natural environment on the KITTI dataset~\cite{kitti}. 
This dataset includes 21 frame sequences including various probable distracters. 
In addition, 80$\%$ of these sequences are divided into a training dataset and 20$\%$ are divided into a validation dataset.

To test and analyse our proposed model, the public studyforrest dataset~\cite{gaze_forrest} is utilized as the agent for the real scenario. 
In the detailed dataset, we use this work describing the initial dataset~\cite{gaze_forrest}. 
In the studyforrest dataset, the video stimulus is divided into eight segments 
and played through scanner, as described in Table~\ref{tab:movie_seg}. 
In brief, the utilized dataset has 15 subjects who watch the movie.
Meanwhile, the eye tracking is recorded in the scanner. 
An additional 15 subjects had only their eye tracking recorded in the lab, 
and these data are utilized to increase the detection performance in smooth pursuit. 
The movie is played to the in-scanner subject on a projector with a front-reflective mirror 
and to the in-lab subject through a display directly. 
The eye tracking data were collected by the 1000Hz eye tracker. 
These fMRI data were obtained through a 3T scanner with a repetition time of 2 s with a $3 \times 3 \times 3 $ mm$^3$ voxel. 
Based on these videos and corresponding fMRI recordings, we select 12 segments to test our proposed method, as depicted in Table~\ref{tab:track_seg}.

% \makecell [c]
\begin{table}[h]
	\centering
	\footnotesize
	\caption{The segmentation and mergence of raw film.
	Raw segments of Forrest Gump that constitute the true input. 
	The 7 segments are merged~\cite{2014A}, and then, they are segmented into 8 segments, each corresponding to an fMRI recording. 
	TRs indicates the number of repetition times.
	The unit of duration is seconds.
	In these experiments, we utilize the 2002 movie release.}

	\label{tab:movie_seg}

	\begin{tabular}{p{0.9cm}<{\centering}p{1.2cm}<{\centering}p{1.45cm}<{\centering}p{1.15cm}<{\centering}p{0.95cm}<{\centering}}
		\toprule[1.5pt]
		{Video ID} & {Begin Frame} & {Frame Number} & {Duration}  & {TRs}   \\ \midrule[1pt]
		1       & 0           & 22,550      & 902.00 & 451.00 \\ 
		2       & 22,150      & 22,050      & 882.00 & 441.00 \\ 
		3       & 43,802      & 21,900      & 876.00 & 438.00 \\ 
		4       & 65,304      & 24,400     & 976.00 & 488.00 \\ 
		5       & 89,305     & 23,100     & 924.00 & 462.00 \\ 
		6       & 112,007     & 21,950     & 878.00 & 439.00 \\ 
		7       & 133,559     & 27,100     & 1,084.00 & 542.00 \\
		8       & 160,261     & 16,876     & 575.04 & 337.52 \\ 
		\bottomrule[1.5pt]
	\end{tabular}

\end{table}

\begin{table}[h]
	\centering
	\footnotesize
	\caption{Frame sequences 1-12 to construct our Tracking-Gump dataset.
	These 12 short videos in which only one salient object appears in the video sequence are selected. 
	This ensures that most of subjects will gaze at the object constantly.}

	\label{tab:track_seg}

	\begin{tabular}{p{1.0cm}<{\centering}p{0.9cm}<{\centering}p{1.6cm}<{\centering}p{1.5cm}<{\centering}p{0.7cm}<{\centering}}
		\toprule[1.5pt]
		Segment ID & Video ID  & Start Frame    & End Frame  & TRs   \\ \midrule[1pt]
		1     		  & 3 			   & 02:30.00 	   & 02:48.00  & 10  		  \\
		2  	 		  & 4 			   & 14:50.00 	   & 15:14.00  & 13   		  \\
		3   		  & 5 			   & 01:32.00 	   & 01:48.00  & 9   		  \\
		4   		  & 5 			   & 05:02.00  	   & 05:20.00  & 10   		  \\
		5   		  & 6 			   & 00:08.00 	   & 00:24.00  & 9   		  \\
		6   		  & 6 			   & 06:56.00 	   & 07:10.02  & 8   		  \\
		7   		  & 6 			   & 09:42.00  	   & 09:56.01  & 8   		  \\
		8   		  & 6 			   & 12:26.00 	   & 12:44.00  & 12		      \\
		9   		  & 7  			   & 06:44.00 	   & 07:06.00  & 12		      \\
		10  		  & 7 			   & 07:26.00 	   & 08:28.00  & 32		      \\
		11  		  & 7 			   & 08:30.00 	   & 08:52.00  & 12		      \\
		12 			  & 7 			   & 10:40.00 	   & 11:10.00  & 16		      \\
		\bottomrule[1.5pt]
	\end{tabular}

\end{table}

\subsection{Implementation details}
Each visual cortical region is implemented by a certain DNN performing some classical operations, such as convolutional operation and nonlinear activation. 
\textcolor{red}{
These network modules are equivalent to visual regions, but we change the number of neurons in each cortical region.}
Considering the \textcolor{red}{computational} costs, we utilize Python with the TensorFlow package~\cite{abadi2015tensorflow} 
and model the V1 with the headmost 3 convolutional module from the revised AlexNet~\cite{imagenet}. 
The input size of raw AlexNet is $227 \times 227$ and is downsized to $14 \times 14$ after 3 convolutional modules. 
Because low-resolution features will lead to poor tracking results, 
we convert the preliminary step size of 4 to 1 
and remove a pooling module to retain spatial features, as depicted in Figure~\ref{fig:structure_analysis}. 
In this way, the size of the obtained feature is $14 \times 14 \times 384$, and the size of the input foveal view is $56 \times 56$.
In addition, at the tail of V1, there is a 20$\%$ probability of randomly omitting the feature. 
The ventral pathway includes a convolutional module in which the kernel size is $1 \times 1$. 
The filters of the DFN are $3 \times 3$ and $1 \times 1$.
We used 100 LSTM units with the zoneout operation~\cite{zoneout} that have a probability of 0.05.
We train BTN~\cite{curriculum}, and utilize a similar learning configuration except for the learning rate, which is $2 \times 10 ^{-6}$.
The starting sequence length is five and increases every twelve iterations.

\subsection{The BTN is a brain-like pursuit model}
\label{sec:results1}

\textcolor{red}{
We compared various experimental results to explain why the proposed BTN is a brain-like tracking model. 
It is easy to see that the model architecture and training procedure are slightly different from other implementations of the visual tracking model.}

Figure~\ref{fig:neural_predictivity} shows how the BTN performs with the BTS on Tracking-Gump dataset. 
It \textcolor{red}{performs} well with a BTS of 0.365. 
Interestingly, models that attain the highest tracking scores also have an excellent BTS on Tracking-Gump dataset, 
indicating a possible relation between the tracking effect and cortical activation pattern on Tracking-Gump dataset. 
Models with good Tracking-Gump tracking performance show a strong correlation with a BTS of 0.365 and there is a significant correlation ($p \textless 0.05$) in the Tracking-Gump dataset, as depicted in Figure~\ref{fig:neural_predictivity}.

\subsubsection{The BTN maintains the architectural similarity with the cerebral cortex}

\textcolor{red}{
We design a brain-like BTN that follows neuroanatomical aligning more closely than classic DNNs.
Besides, the BTN achieves good tracking performance as measured by the BTS on Tracking-Gump dataset.  
Therefore, the BTN satisfies both neuroanatomical limitations in neuroscience and engineering requirements in computer vision.}

We find that the BTN is a closer approximation of neuroanatomy than current excellent DNNs 
since it especially limits the number of regions and uses a recurrent structure. 
In neuroscience, because there are no neurologically credible training methods, 
a brain-like DNN for smooth pursuit will use better neuroanatomical and connectional mechanisms.
For example, the skip connection~\cite{he2016deep} is not inspired by brain mechanisms and is used to solve the vanishing gradient issue during DNN training.
Considering various architectures, we tested various architectural configurations before finding the appropriate brain-like architecture BTN as depicted in Figure~\ref{fig:structure_analysis}.

\begin{figure}
	\centering
	\includegraphics[width=.9\linewidth]{imgs/structure_analysis.pdf}
	\caption{\textbf{
		BTN architecture analysis.} 
		\textcolor{red}{
		We analyse four main factors including the initial step size in $\rm{CONV_{V1}}$ and the number of dynamic filter layers in $\rm{DFN_{MT/MST}}$, the number of hidden units in $\rm{LSTM_{FEF}}$ and the number of hidden units in $\rm{FC}$.
		Each row indicates how cortical and behavioral score change based on the trained BTN when a certain hyperparameter changes. 
		}
	}
	\label{fig:structure_analysis}
\end{figure}

\subsubsection{The BTN captures neural responses in MT/MST}
\label{sec:capture_neural}

\textcolor{red}{
A feedforward neural network can not predict the trend of time series, 
and thus cannot capture a brain-like response of the tracking model~\cite{kar2019evidence, TangSchrimpfLotter2018Recurrent}.
By using recurrent connections, the BTN is able to predict time-varying activation in the corresponding cortex.}
The latest research work~\cite{kar2019evidence} finds that the decodable results in image classification are not generated in inferior temporal cortical neurons, 
and these inputs are very difficult for DNNs to spend more time decoding in the inferior temporal region. 
The time property inspires an assumption for the brain-like network: 
Does it predict frame-by-frame motion information in MT/MST cortical activations over time? 
Therefore, the BTN predicts the movement in a video frame when obvious target motion features are available,
and compared it with the responses recorded in the human MT/MST cortex.
Significantly, the BTN never learns to predict the human cortical response intensity.
However, a feature comparison that can decode the object motion similarity between neural responses and the model's responses is learned. 
When using the PCA method for data compression, more components will retain more neural information.
Finally, we evaluate how well the BTN captures the fine-grained motion responses in human MT/MST and present a BTS of 0.365 ($p < 0.05$) as depicted in Figure~\ref{fig:neural_predictivity}.

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{imgs/comp_sim.pdf}
	\caption{
		\textbf{
		The BTN captures neural responses in MT/MST.
		}
		This indicates the normalized neural similarity and p value according to different PCA component. 
		When the number of PCA components reaches 90, the neural predictivity for the BTN obtains the best results of 0.365. 
	}
	\label{fig:neural_predictivity}
\end{figure}

\subsubsection{The BTN is the valid brain-like tracking model on Tracking-Gump dataset}
\textcolor{red}{
Although the tracking performance is truly improved in the later training when improving the cortical similarity, we select the epoch with maximum BTS.}
In addition, the bounding box of the model prediction is roughly consistent with the position of the eye gaze. 
Finally, we use both behavioral and MT/MST metrics in our experiments to analyse the motion information in BTN. 
The BTN also achieves excellent tracking performance on the Tracking-Gump dataset, as depicted in Figure~\ref{fig:tracking}, demonstrating the validity and robustness of this proposed BTN in complex environments.

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{imgs/tracking.pdf}
	\caption{
		\textbf{
		Tracking examples of the proposed method on Tracking-Gump dataset. 
		}
		\textcolor{red}{
		For different video sequences, the predicted track results are identified by bounding boxes.
		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
		}
	}
	\label{fig:tracking}
\end{figure}

\section{Discussion}
\label{sec:discussion}

In our work, we design the BTN for predicting \textcolor{red}{eye movement and cortical activation in smooth pursuit.
The BTN implements predictive mechanisms and tracks voluntary objects online.}
As far as we can see, the BTN allows the DNN to implement the introduced tracking behavioral prediction and neuroanatomical aligning, 
and the results indicate that the BTN can produce continuous predictive tracking signals. 
Although smooth pursuit studies demonstrate that the cortical representation of object movement is possibly utilized to tracking inference~\cite{b21,b4,b3}, the cortical theory to build and hold the cortical representation is unknown. 
This study indicates that the online learning and updating of the cortical representation through the BTN decreases tracking lag, 
adjusts eye movement and produces continuous tracking when facing drift or occlusion.

An interesting characteristic of smooth pursuit is that when occlusion occurs, pursuit movement continues. 
There is a motion action at the retina when track a moving object without delay by BTN. 
After learning the object motion feature, the retinal slip is small. 
However, the small retinal slip cannot enable occluded object tracking. 
LSTM can produce self-sustained eye movement prediction~\cite{kashyap2018a}. 
The small retinal slip components are persistently utilized to adjust the pursuit prediction. 
When occlusion occurs, this adjustable retinal slip information is absent.
Thus, tracking is lost step by step, as in the research results~\cite{b4}. 
Furthermore, in the BTN, every neuron in LSTM has basal voluntary activation. 
When the tracked target is occluded, the trained activation mode generates tracking signals continuously.

\subsection{The role of MT/MST and the FEF in object tracking}
Many works have found a function in the FEF to predict  object tracking. 
The ablations or lesions of the FEF impair monkeys tracking moving objects when the object is occluded or appears~\cite{b11}. 
The neuron activations in the FEF show that continuous activation exists intensively after a moving target has vanished~\cite{b14}. 
In addition, some fMRI works have found the motion indicator of eye  pursuit prediction in the FEF~\cite{b33}. 
Our works demonstrate that the FEF extracts a cortical representation of the object movement mode to indicate predictive tracking.

The FEF receives abundant mappings from MT/MST, which are the areas in the dorsal stream that process moving targets. 
In the latter part, the outputs of the FEF are delivered to dorsal PN in brainstem areas, as depicted in Figure~\ref{fig:introduction}. 
In addition, these brainstem areas transfer signals from the FEF to PN that conduct oculogyric adjustment~\cite{b36}.

The results of neuroanatomical ablation indicate that the FEF follows the parietal regions and outputs to PN to control eye movement~\cite{b11}. 
These results \textcolor{red}{demonstrate} that the FEF has a credible cortical correlation with LSTM, which is based on the object tracking prediction abilities. 
In addition, FEF (LSTM) uses an image stimulus to infer eye motion signals for oculogyric adjustment.

\subsection{The applications and limitations of BTN}
\textcolor{red}{
The proposed BTN can be utilized in the traditional visual object tracking task.
Besides, it is a more interpretable brain-like tracking model and can be utilized to predict the position of eye gaze and the expected activations in cortical pathway.
}

\textcolor{red}{
Nevertheless, the independent training configuration may be the essential characteristic that trains the DNN~\cite{Kornblith2018a}. 
In addition, an auxiliary task does not have a very large impact on the score but notably improves the transfer effect~\cite{Kornblith2018a}.
Because the BTN is a transferable problem, it cannot be precluded that the BTS may vary when using different training settings.  
They claim that it is useful to tremendously improve the transfer effect by retraining the DNN with optimized configurations~\cite{Kornblith2018a}. 
Therefore, we believe that only the given trained BTN is optimal and not all model of network architecture. 
Practically speaking, we can perform grid search to select the optimal training settings based on a validation set.
}

\subsection{The relationship between DNNs and neuroscience}
A significant element to building a BTN that is an important potential architecture for the cortex is the BTS, which is a quantitative metric used to compare a DNN with the cortex in object tracking. 
Although there are no cortical tracking metrics thus far, the proposed framework proposes a meaningful idea. 
First, the proposed framework extends previous studies indicating that tracking performance is correlated with cortical similarity.
Nevertheless, the use of recurrent structures changes this tendency and has excellent neuroanatomical similarity with the cerebral cortex. 
In addition, a possible conflict is discovered between the Tracking-Gump tracking score and the BTS in the BTN.
There are many excellent models for visual object tracking, 
that achieve poor results in the BTS.
However, these DNNs with poor Tracking-Gump tracking results may \textcolor{red}{acquire} better BTSs. 
Besides, we find that these DNNs have excellent BTS performance and may easily acquire good tracking results, which supports the assumption that the BTS is a comprehensive metric, and these results are not solely based on the utilized behavioral and neural datasets.

\textcolor{red}{
In general, we indicate that the brain-like model is a prospective opportunity to cooperate for deep learning and neuroscience. 
We compare these DNNs through similarity quantification using the BTS 
and assess the metrics of various behavioral and neural datasets on BTS. 
For the BTN, we demonstrate that an anatomical model of the cortex according to alignment and recurrent structure can learn cortical mechanisms well through cortical activation prediction and frame-by-frame behavior. 
In this way, we can simultaneously obtain high tracking performance and the prominent brain-like model.}

\section{CONCLUSION}
Inspired by the visual processing mechanisms found in the human brain, our study presents a brain-like tracking model suited to the problem of visual object tracking. 
Based on the neuroanatomical limitation, the designed model has appropriate tracking performance and improved interpretability. 
In addition, we illustrate the cortical model specifically connected with the human smooth pursuit in a complicated real environment 
and develop a new way to compute the similarity between model activation and cortical activation data. 
\textcolor{red}{
Furthermore, the model with neuroanatomical alignment can better predict the neural response of human brain. 
We believe the proposed BTN could encourage novel inspirations in the interpretability of DNN 
and even motivate the development of brain-computer interfaces.}
% artificial motion consciousness
% artificial motion intelligence

\section*{Acknowledgements}This work was partially supported by National Key Research and Development Program of China (No.2018YFB1308604), National Natural Science Foundation of China (No.61976086,62106071), Hunan Innovation Technology Investment Project (No.2019GK5061), and Special Project of Foshan Science and Technology Innovation Team (No. FS0AA-KJ919-4402-0069).
\label{}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\bibliographystyle{elsarticle-num} 
\bibliography{references}
%
%\begin{thebibliography}{00}
%
%%% \bibitem{label}
%%% Text of bibliographic item
%
%\bibitem{}
%
%\end{thebibliography}
\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2023-06-05 visual/face/brain_like/latex/bfn.tex
init

--- 2023-06-05 auditory/latex/ban.tex
@@
-%!TEX program = pdflatex 
-% !BIB program = bibtex
 %% bare_jrnl.tex
@@
 
-\author{Haidong~Wang,~Jianhua~Zhang,~and Ke Nai,% <-this % stops a space
-	\thanks{H.
-Wang and J.
-Zhang are with the School of Computer Science and Electronic Engineering of Hunan University, Key Laboratory for Embedded and Network Computing of Hunan Province, Changsha 410082, China (e-mail: wanghaidong@hutb.edu.cn; zhangjianhua@hutb.edu.cn;
+\author{Haidong~Wang, Zhiyong Li, \emph{Member, IEEE},~Xuan He,~Ke Nai,~and Ming Wen% <-this % stops a space
+	\thanks{H. Wang, Z. Li, K. Nai, S. Wang and J. Lv are with the School
+		of Computer Science and Electronic Engineering of Hunan University, Key Laboratory for Embedded and Network Computing of Hunan Province, Changsha 410082,
+		China (e-mail: haidong\_hnu@hnu.edu.cn; zhiyong.li@hnu.edu.cn;
 		naike@hnu.edu.cn).}
@@
 \begin{abstract}
-Inspired by neuroanatomy, deep neural networks (DNNs) have recently developed from shallow network to exceedingly deep structures, providing excellent auditory recognition performance.
-However, conventional DNNs usually do not easily connect with brain areas on account of their excessive network depth and absent biological constraints, such as recurrent connections. 
+Inspired by neuroanatomy, deep neural networks (DNNs) have recently developed from shallow network structures to exceedingly deep structures, providing excellent recognition performance.
+However, standard DNNs usually do not easily connect with brain areas on account of their excessive network depth and absent biological constraints, such as recurrent connections. 
 We propose a brain-like auditory network (BAN) with four neuroanatomically mapped regions and recurrence, guided by the brain-like auditory score (BAS), 
-a novel benchmark to measure the model similarity of the human auditory recognition pathway. 
-In addition, we propose that the middle temporal and medial superior temporal (T2/T3) areas in the cerebral cortex are equivalent to the designed network structure on the basis of auditory perception pathway,
-and indicate that the metrics between the neuroanatomical similarity in cerebral cortex and auditory recognition of the DNN are compatible. 
-Despite having excellent recognition performance on the Music genres dataset, the BAN has achieved a high BAS. 
-In summary, this research builds a BAN, a brain-like and recurrent DNN, as the first model of the cortical pathway of auditory recognition.
+a novel benchmark to measure the model similarity of the human smooth pursuit pathway. 
+In addition, we propose that the middle temporal (MT) and medial superior temporal (MST) areas in the cerebral cortex are equivalent to the designed network structure on the basis of the continuous motion perception of the tracking pathway,
+and indicate that the metrics between the neuroanatomical similarity in the cerebral cortex and visual tracking of the DNN are compatible. 
+Despite having significant tracking performance on the Tracking-Gump dataset, the BTN has achieved a high BTS. 
+In summary, this research builds a BTN, a brain-like and recurrent DNN, as the first model of the cortical pathway of smooth pursuit.
 \end{abstract}
@@
 \begin{IEEEkeywords} 
-Auditory Recognition, Deep Neural Network, Brain-like Model, Neuroanatomical Similarity. 
+Online Multi-object Tracking, End-to-end Model, Joint Detection and Data Association. 
 \end{IEEEkeywords}
@@
 		Collaborative design between a DNN and neuroanatomy with a BAS.} 
-		Through the quantitative brain-like score, we refer to the human brain and utilize acquired knowledge to enlighten the design of the BAN. 
-		The BAN includes four regions that are mapped into the primary auditory cortex (A1), the belt or peripheral area (Belt), parabelt cortex (PB) and the areas of middle and superior temporal cortex (T2/T3).
+		Through the quantitative brain-like score, we refer to the human brain and utilize acquired knowledge to enlighten the design of the BTN. 
+		The BAN includes four regions that are mapped into the primary auditory cortex (A1), 		the belt or peripheral area, parabelt cortex (PB) and the areas of temporal cortex (T2/T3). 
 		CONV\textsubscript{V1} is the classical convolutional layer and performs preprocessing to reduce the data size.
-		The RNN\textsubscript{Belt} and RNN\textsubscript{PB} and RNN\textsubscript{T2/T3} is recurrent neural network, as depicted in Section~\ref{sec:cornet_s_def} for details.
-		The the upper-right image corresponds to the auditory recognition activation and predicted generes labels in the brain-aligned models, 
-		while lower-right image represents the cortical activation and human choice with the same stimulus in the far left,
-		which demonstrates the relationship between computer prediction performance and brain auditory recognition response with the BAS, as depicted in Section~\ref{sec:experiments}.
+		The DFN\textsubscript{MT/MST} is dynamic filter network, and the RNN\textsubscript{FEF} is recurrent, as depicted in Section~\ref{sec:cornet_s_def} for details.
+		The the upper-right image corresponds to the tracking activation and bounding box in the brain-aligned models, 
+		while lower-right image represents the cortical activation and eye gaze position with the stimulus in the far left,
+		which demonstrates the relationship between computer vision tracking performance and brain tracking response with the BTS, as depicted in Section~\ref{sec:experiments}.
 	}
@@
 % /data3/dong/data/brain/auditory/Music_Genre_Classification_Pytorch-master/report.pdf, 1. Music
-% 一定要在路径中添加latex/bin/win32/bibtex.exe，否则参考文献为问号，且不会报错
-\IEEEPARstart{H}{earing} is crucial for identifying sound for humans, it is particularly important because of its role in the understanding and production of music.
+\IEEEPARstart{M}{usic} genres are a set of descriptive keywords that convey high-level information about a music clip (jazz, classical and rock .etc).
 Genre classification is a task that aims to predict music genre using audio signal.
-Music genres are a set of descriptive keywords that convey high-level information about a music clip (jazz, classical and rock .etc).
 According to Tzanetakis and Cook~\cite{tzanetakis2002musical}, the genre of music is a categorical label created by humans to characterize musical works.
@@
 Automatic music genre classification can help or replace human users in the process and will be a valuable addition to the music information retrieval system.
-According to Nam~\cite{nam2018deep}, music genre classification has a significant impact on auditory recognition and recommendation of music streaming services.
+According to Nam~\cite{nam2018deep}, music genre classification has a significant impact on music search and recommendation of music streaming services.
 In the above mentioned musical classification and tagging task solving methodology, it is very important to make the computer aware of the pattern of music and identify them.
@@
 
-When humans distinguish music, it is important to tell machines the feature inside music, just they distinguish genres through the sound of musical instruments or through rhythm.
+When humans distinguish music, it is important to tell machines the feature inside the music, just they distinguish genres through the sound of musical instruments or through rhythm.
 This is commonly called hand engineering using domain knowledge.
@@
 To capture cortical processing even more strictly in these models, continued architectural search on traditional visual datasets alone no longer seems to be a feasible solution. 
-Even though the great performance in deeper DNNs has truly increased~\cite{ILSVRC15,luo2021trajectory}, it is hopeless to raise the brain-like score~\cite{rajalingham2018large,su2020incremental}. 
+Even though the great tracking performance in deeper DNNs has truly increased~\cite{ILSVRC15,luo2021trajectory}, it is hopeless to raise the brain-like score~\cite{rajalingham2018large,su2020incremental}.
 In addition, at the beginning, only partial modules can be obviously mapped to corresponding regions of the visual pathway, 
@@
 
-To address the interpretability problem of auditory recognition model, in this study, we propose that neuroanatomical aligning DNNs will result in more interpretable, more shallower, and more brain-like models, named brain-like auditory recognition network (BAN).
-The BAN is a shallow recurrent brain-like architecture of the brain pathway; 
+To address the interpretability problem of visual tracking model, in this study, we propose that aligning DNNs to anatomy will result in shallower, more interpretable, and more brain-like tracking models, named brain-like tracking network (BTN).
+The BTN is a shallow recurrent brain-like architecture of the brain pathway; 
 hence, it has a much more brain-like structure. 
-In section \ref{sec:data_analysis}, we introduce a method utilized to analyse cortical data and human behavioral during auditory recognition. 
-In section \ref{sec:bas}, we build a fancy measurement method for predicting auditory recognition behavior and neural activations on the brain-like auditory recognition score (BAS). 
+In section 4, we introduce the method utilized to analyse human behavioral and cortical data during object tracking. 
+In section 5, we build a fancy measurement method for predicting eye movement behavior and neural activations on the brain-like tracking score (BTS). 
 In our experiments, we introduce a new benchmark dataset composed of behavioral and cortical recordings, 
-and present an outstanding recognition result of at evaluating the model similarity of the auditory recognition pathway while obtaining a good prediction effect in the Music genres dataset~\cite{nakai2022music}.
+and present an outstanding tracking result of 36.5\% at evaluating the model similarity of the visual pathway while obtaining a good tracking effect in the Tracking-Gump dataset~\cite{gaze_forrest}. 
 We find that these results are mainly due to the brain-like architecture, in accordance with prior knowledge of the human cortical pathway processing stimuli input~\cite{TangSchrimpfLotter2018Recurrent, yin2020deep, kar2019evidence}.
-Finally, to compare the model activations between the RNN\textsubscript{T2/T3} in the BAN and the responses in the human middle temporal and superior temporal areas (T2/T3), we discover that the BAN predicts these cortical activations well,
-and it is also the first auditory recognition model to do so on the neural recordings.
+Finally, to compare the model activations between the RNN\textsubscript{MT/MST} in the BTN and the responses in the human middle temporal and medial superior temporal areas (MT/MST), we discover that the BTN predicts these cortical activations well,
+and it is also the first visual tracking model to do so on the neural recordings.
 
@@
 
-% 音频识别相关的神经网络
 \subsection{Deep neural network}\par
 Many works have recently shown that salient objects are extracted by a series of foveal views~\cite{mnih2014recurrent,draw}.
-The object extraction module in the BAN is implemented with a two-dimensional gaussian filter~\cite{RATM} that is neuroanatomically explainable.
+The object extraction module in the BTN is implemented with a two-dimensional gaussian filter~\cite{RATM} that is neuroanatomically explainable.
 Focusing on specific appearance representations may be as important as spatial attention. 
@@
 Input-dependent state transitions can help to learn the markovian decision model~\cite{karl2017deep}. 
-We do not follow the results, and use the idea to predict the salient feature.
-
+\textcolor{red}{
+	We do not follow the results, and use the idea to predict the salient feature.}
+
+\textcolor{red}{
 	To track a target, it seems to be very suitable to use recurrences and glimpses, but they have only been employed successfully in monochromatic videos with simple backgrounds~\cite{RATM}. 
@@
 	Our study is similar to~\cite{RATM,luo2019teleoperation}, and utilizes human attention which is implemented with a long short memory network (LSTM) to extract the movement features well in multiple frames.
-In addition, we seek to design a brain-like network that will gain a superior BAS and exceed the existing tracking models on the Tracking-Gump dataset~\cite{gaze_forrest}.
-\par
-
-% 人类的音频识别 
-\subsection{Auditory Recognition}
-There have been many successful auditory recognition researches. 
+	In addition, we seek to design a brain-like network that will gain a superior BTS and exceed the existing tracking models on the Tracking-Gump dataset~\cite{gaze_forrest}.
+}\par
+
+\subsection{Smooth pursuit}
+There have been many successful eye movement experiments. 
 Some eye movement detection methods are proposed according to the existing plentiful datasets that have annotated eye movement data~\cite{dorr2010variability,mathe2012dynamic,hooge2017is,blstm_class}.
@@
 and detect corresponding cortical regions associated with saccadic and smooth pursuit in Tracking-Gump.
-In addition, based on model activation and cortical activation, we designed the BAS to measure their similarity.
+In addition, based on model activation and cortical activation, we designed the BTS to measure their similarity.
 
 \section{BAN: Brain-like Auditory Network} 
-In this section, we introduce the proposed BAN with three steps. 
+In this section, we introduce the proposed BTN with three steps. 
 First, we indicate the motivation and design criteria in our methods.
-Second, we detail each component in the BAN pipeline. 
-Finally, we introduce the loss function to train the BAN. \par
+Second, we detail each component in the BTN pipeline. 
+Finally, we introduce the loss function to train the BTN. \par
 
 \subsection{Design criteria}
-Our aim is to obtain a high auditory recognition brain-likeness between DNN and human brain.
-Additionally, auditory recognition in our brain shows through human choices. 
-In the pathway of auditory recognition, primary auditory cortex (A1) is the first stage to preprocess the input signals, 
-Belt and PB integrate sound signal across space,
-and T2/T3 generates predictive auditory labels~\cite{b11,b13,b14}.
-\par
-% todo
-
-Inspired by the pathway of auditory recognition in brain, we build neuroanatomical mapping from cortical regions to DNN layers, as depicted in Figure~\ref{fig:introduction}.
-For model comparison, we build the mapping by examining the layer in DNN that understands activations well in a specific cortical region.
-Ideally, such activations will already be predicted by the model with no superfluous parameters. 
-Therefore, the BAN consists of four neural network modules including a convolution layer and three recurrent layer.
-And they are the analogy to auditory recognition pathway A1, Belt, PB, T2/T3.
-And recognition predictor that converts the output of T2/T3 to corresponding action selection responses, as depicted in Figure~\ref{fig:pipeline}. 
-This plain idea of explicit brain areas segmentation is an important step to design a brain-like auditory recognition model, 
+Our aim is to obtain a high brain-likeness between visual object tracking in DNN and the smooth pursuit in brain.
+Additionally, smooth-pursuit movements in our brain keep the image of a moving target on the fovea. 
+\textcolor{red}{
+	In the pathway of smooth pursuit,
+	primary visual cortex (V1) is the first stage to preprocess the input signals, 
+	MT/MST \textcolor{red}{integrate} motion signal across space,
+	and frontal eye field (FEF) generates predictive eye movement signals~\cite{b11,b13,b14}.
+}\par
+
+\textcolor{red}{
+	Inspired by the pathway of smooth pursuit in brain, we build neuroanatomical mapping from cortical regions to DNN layers, as depicted in Figure~\ref{fig:introduction}.}
+For model comparison, we build the mapping by examining the layer in the DNN that understands activations well in a specific cortical region, 
+ideally such activations will already be predicted by the model with no superfluous parameters. 
+Therefore, the BTN consists of four neural network modules including convolution layer, DFN, LSTM and FC.
+And they are the analogy to the smooth pursuit pathway V1, MT/MST, FEF, 
+and motion predictor that converts the output of FEF to corresponding motion responses, as depicted in Figure~\ref{fig:pipeline}. 
+This plain idea of explicit brain areas segmentation is an important step to design a brain-like tracking model, 
 and we are committed to finding more universal structures. 
 Examples include an entire model as a neural network with no difference in cortical areas
-and various connections that may improve BAS in future work.
-In addition, we follow these two criteria to design the BAN~\cite{kubilius2018predict}:
-
-(1) \textbf{Architecture}: In models with similar recognition performance, we prefer a brain-like network because it is easier to understand and can meet the anatomical constraints.
+and various connections that may improve BTS in future work.
+In addition, we follow these two criteria to design the BTN~\cite{kubilius2018predict}:
+
+(1) \textbf{Architecture}: In models with similar tracking performance, we prefer a brain-like network because it is easier to understand and can meet the anatomical constraints.
 And we use DNNs because their neurons are the basic unit of data processing, 
 and all neural activations in DNNs can be clearly mapped to cortical activation~\cite{yamins2016using}.
-In addition, recurrent connections are naturally considered for auditory recognition on account of the temporal attributes in the audio sequence.
-Activations in the auditory ventral pathway also have a temporal attribute; 
-therefore, the BAN is assumed to generate activations in time series.
+\textcolor{red}{
+	In addition, recurrent connections are naturally considered for visual object tracking on account of the temporal attributes in the video sequence.}
+Activations in the dorsal pathway also have a temporal attribute; 
+therefore, the BTN is assumed to generate activations in time series.
 
@@
 There is more correct behavior output in intermediate layers and final outputs that meet neuroanatomical constraints (neural responses). 
-This make our model have an ability to predict cortical activation and human category choice behavior.
-
-We now introduce the pipeline for BAN.
-
-\subsection{BAN pipeline} \label{sec:cornet_s_def}
-
-Given the input audio sequence $A$ and attention parameters $a_t$, the fovea (imitating spatial attention) selects a foveal view $f_t$. 
-Moreover, we use an appearance selector, parameterized with appearance $\alpha _t$ including V1 and this dorsal pathway and ventral pathway, to obtain the tracked target representations $m_t$ 
-and update hidden state $h_t$ in LSTM.
+This make our model have an ability to predict cortical activation and human eye movement behavior.
+
+We now introduce the pipeline for BTN.
+
+\subsection{BTN pipeline} \label{sec:cornet_s_def}
+
+Given the input frame $F_t$ and attention parameters $a_t$, the fovea (imitating spatial attention) selects a foveal view $f_t$. 
+\textcolor{red}{Moreover, we use an appearance selector, parameterized with appearance $\alpha _t$ including V1 and this dorsal pathway and ventral pathway, to obtain the tracked target representations $m_t$
+	and update hidden state $h_t$ in LSTM.}
 Then, we decode the output of LSTM and use it to infer the eye movement $\Delta p_t$, spatial attention $a_{t+1}$ and the appearance attention $\alpha _{t+1}$ in the next frame.  
@@
 
-\subsubsection{Cochlear and MFCC features}
-For the mel-frequency cepstral coefficient (MFCC) model, the MIR toolbox was used to extract multiple music-related features from the dataset (Lartillot et al., 2008).
-Consistent with a previous neuroimaging study on music (Alluri et al., 2012), we extracted the following 24 features: 
-RMS energy as the loudness feature; 
-zero-crossing rate, 
-high energy–low energy ratio, 
-spectral centroid, 
-spectral roll-off, 
-spectral entropy, 
-spectral flatness, 
-roughness, 
-spectral spread, 
-spectral flux, 
-and sub-band flux (with nine sub-bands) as timbral features; 
-pulse clarity, 
-fluctuation centroid, 
-and fluctuation entropy as rhythm features; 
-and mode and key clarity as tonal features. 
-For loudness and timbral features, the frame duration was set to 25 ms, with a 50\% overlap between the two adjacent frames. 
-For rhythm and tonal features, the frame duration was set to 3 s, with a 33\% overlap. 
-Each feature was averaged across 1.5 s. 
-In addition, we used the MIR toolbox to extract MFCC features with 12 channels (Lartillot et al., 2008). 
-Feature extraction of the MIRT and MFCC models was also restricted within 100–8,000 Hz. 
-The number of features used in the MIRT and MFCC models was 24 and 12, respectively.
-
-\subsubsection{Primary Auditory Cortex}
+\subsubsection{Retina and Dorsal/Ventral \textcolor{red}{Pathway}}
 Typical, input is a data matrix represented by a time-frequency representation. 
@@
 and the dorsal pathway learns motion features in the field of view. 
+\textcolor{red}{
 	We present the dorsal pathway with the MT/MST that analyses motion features, as depicted in Figure~\ref{fig:pipeline};
-and computes a foreground segmentation $d_t$ of the foveal view.
+	and computes a foreground segmentation $d_t$ of the foveal view.}
 
@@
 Generally, however, we implement V1 using several convolutional layers and max pooling layers. 
-These layers, which imitate V1 in humans~\cite{theoretical_neuroscience}, are shared with the dorsal pathway.
+\textcolor{red}{
+	These layers, which imitate V1 in humans~\cite{theoretical_neuroscience}, are shared with the dorsal pathway.}
 In addition, the pipeline is split into dorsal and ventral pathways. 
@@
 Then, we apply a $1 \times 1$ convolution and a sigmoid function to convert the representation into a two-dimensional mask $d_t$.
-Every point in $d_t$ indicates how likely the pursued target is occupied.
+\textcolor{red}{
+	Every point in $d_t$ indicates how likely the pursued target is occupied.}
 
@@
 
-\subsubsection{Belt and PB}
+\subsubsection{FEF}
 
@@
 The LSTM can utilize spatial-temporal and appearance features, 
-and enables the proposed model to handle occlusion and drifting target representations, such as a tracked target obscured by other distractors.
-
-The LSTM module, presented in Figure~\ref{fig:pipeline} and named the FEF, utilizes the output error to predict eye movement. 
+and enables the proposed model to handle occlusion and drifting target representations, such as a tracked \textcolor{red}{target} obscured by other distractors.
+
+The LSTM module, presented in Figure~\ref{fig:pipeline} and named the FEF, utilizes \textcolor{red}{the} output error to predict eye movement. 
 Similar predictive actions exist when smooth pursuit is demonstrated in the FEF area that accepts the output of the dorsal stream~\cite{b11,b13,b14}. 
@@
 
-\subsubsection{Middle and Superior Temporal Cortex}
+\subsubsection{Brainstem/Cerebellum}
 
@@
 
-We train the proposed BAN by optimizing an assembly of losses: a tracking loss, a series of attention losses and an auxiliary loss. 
-The BAN loss $L_{b}$ is given by
+We train the proposed BTN by optimizing an assembly of losses: a tracking loss, a series of attention losses and an auxiliary loss. 
+The BTN loss $L_{b}$ is given by
 \begin{equation}
@@
 \end{equation}
-Detailed information on the BAN loss is described below.
+Detailed information on the BTN loss is described below.
 
 \subsubsection{Tracking Loss}
-To locate the tracked target, we design the tracking loss between the output of the BAN and the true label. 
+To locate the tracked target, we design the tracking loss between the output of the BTN and the true label. 
 We refer to the study~\cite{UnitBox} and denote the tracking loss as the negative logarithm of their intersection over union (IoU) between predicted bounding box $p_t$ and ground truth $\hat{p}_t$:
@@
 \subsubsection{Attention Loss}
-The attention mechanism selects the tracked object from the input frame $F_t$.
-To train the BAN better, we utilize three attention loss terms.
+\textcolor{red}{
+	The attention mechanism selects the tracked object from the input frame $F_t$.}
+To train the BTN better, we utilize three attention loss terms.
 The first item makes the intersection area between the predicted attention $a_t$ and the bounding box $p_t$ as large as possible. 
@@
 For the attention $a_t$ and bounding box $p_t$, $r(a_t, p_t)$ indicates a binary mask that has the same size as the output of V1. 
-$r(a_t, p_t)$ is one where the bounding box and the foveal view intersect.
+$r(a_t, p_t)$ is one where \textcolor{red}{the} bounding box and the foveal view intersect.
 Finally, the third item is denoted as the cross entropy between $r(a_t, p_t)$ and $d_t$.
@@
 
-\section{Data Analysis} \label{sec:data_analysis}
+\section{Data Analysis}
 To compare the similarity between DNN tracking and human smooth pursuit, we first extract the smooth pursuit from various eye movements 
@@
 % Correspondence, 2.5.1
-% 头动矫正
 Motion correction is performed for each run using the Statictical Parameter Mapping toolbox (SPM 12).
@@
 
-\subsection{Behavioral analysis}
+\subsection{Behavioral experiment}
 To confirm that brain activation in response to music genres was related to the behavioral performance of genre classification, we performed additional behavioral experiments.
@@
 
-\section{BAS: Brain-like Auditory Score} \label{sec:bas}
-In this part, we present the BAS metrics, which measure the similarity between DNN model and the human cortex. 
-The BAS is a metric tested on specific experimental datasets, which can be both cortical and behavioral measurements.
-
-In order to obtain the quantitative metrics about brain similarity, we refer to the open-sourced platform brain-score~\cite{SchrimpfKubilius2018BrainScore} and propose the BAS, a well-designed metric that evaluates a model's ability to predict
-(a) the average behavior choice when listening an target music clip of the Music Genre dataset~\cite{nakai2022music}, 
-and (b) the average activation of each cortical position to each input music clip in human visual areas ST on the Music genre neuroimaging dataset~\cite{nakai2022music}.
-To evaluate BAN on a unified metric, we compute the average of behavioral and cortical metrics.
-
-\subsection{Cortical metrics}
-\label{sec:neural-pred}
-
-We utilize the cortical metrics, which infer activations of the human cortex, such as responses in motion cortical MT/MST, to measure how fine the model predicts the specific input frame in the DNN~\cite{yamins2014performance}.
-This metric requires two groups of inputs with the form of $\text{input} \times \text{neuroids}$, where neuroids are either model interlayer activations or neural recordings.
-
-In total, 149 frames including a tracked object that appeared randomly on a natural scene are presented to 13 subjects,
-and the neural responses are collected from 2177 MT/MST voxels. 
-In addition, we report the most predictive layer or specific model regions in the BAN.
-
-In our experiment, the relations are fitted to map from a DNN to a cortex, and these relations are utilized to predict the responses in the provided frames. 
-To accelerate the process, we reduce the activation dimensionality to specified components using principal component analysis (PCA)~\cite{2002Principal}. 
-We utilize the activations from MT/MST to learn the fits. 
-The Pearson correlation coefficient $s_r$ constitutes the final neural similarity score for visual motion cortex as follows:
-\begin{equation}
-	s_r=\frac{\sum_{i=1}^{n} (y_i-\bar{y}) (y_i^\prime - \bar{y}^\prime) }{\sqrt{\sum_{i=1}^{n} (y_i - \bar{y})^2 (y_i^\prime - \bar{y}^\prime)^2 }},
-\end{equation}
-where $y^\prime$ is the model activation, $y$ is the actual activation and $n$ is the corresponding feature dimension in DNN.
-$\bar{y}$ and $\bar{y}^\prime$ are the corresponding median over all individual neural response values.
+\section{BAS: Brain-like Auditory Score} \label{sec:bts}
+In this part, we present the BTS metrics, which measure the similarity between the DNN model and the human cortex. 
+The BTS is a metric tested on specific experimental datasets, which can be both behavioral and cortical measurements.
+
+In order to obtain the quantitative metrics about brain similarity, we refer to the open-sourced platform brain-score~\cite{SchrimpfKubilius2018BrainScore} and propose the BTS, a well-designed metric that evaluates a model's ability to predict
+\textcolor{red}{
+	(a) the average pooled human eye movements when tracking an object in each input video frame of the studyforrest dataset~\cite{gaze_forrest}, 
+	and (b) the average activation of each cortical position to each input video frame in human visual areas MT/MST on the studyforrest dataset~\cite{gaze_forrest}.
+	To evaluate BTN on a unified metric, we compute the average of behavioral and cortical metrics.}
 
 \subsection{Behavioral metrics}
+\textcolor{red}{
 	The aim of behavioral metrics is to calculate the similarity between the DNN outputs and the human behavioral outputs in a specific problem~\cite{rajalingham2018large}. 
@@
 	Meanwhile, the main purpose is to realize human-like intelligence, not only the tracking accuracy~\cite{schrimpf2020integrative}; 
-and BAN obtains better behavioral similarity and can predict the position and scope of eye gaze well. 
+	and BTN obtains better behavioral similarity and can predict the position and scope of eye gaze well. 
 	Otherwise, the result is that DNNs gain perfect bounding box fitting but can not obtain a good eye gaze prediction performance. 
+}
 
@@
 Therefore, the eye movement predictivity or behavioral score can be modeled as the IoU between the actual eye attention circular scope of gaze $S_{roi}^a$ and the bounding box of the DNN's predictions $S_{roi}^b$.
-We compute the overall behavioral metrics~$s_b$ among all frame sequences as the eye movement predictivity score as follows: 
+We compute the overall behavioral metrics~$s_b$ among all frame sequences as the eye movement predictivity \textcolor{red}{score as follows:} 
 \begin{equation}
@@
 
+\subsection{Cortical metrics}
+\label{sec:neural-pred}
+
+We utilize the cortical metrics, which infer activations of the human cortex, such as responses in motion cortical MT/MST, to measure how fine the model predicts the specific input frame in the DNN~\cite{yamins2014performance}.
+This metric requires two groups of inputs with the form of $\text{input} \times \text{neuroids}$, where neuroids are either model interlayer activations or neural recordings.
+
+In total, 149 frames including a tracked object that appeared randomly on a natural scene are presented to 13 subjects,
+and the neural responses are collected from 2177 MT/MST voxels. 
+In addition, we report the most predictive layer or specific model regions in the BTN.
+
+In our experiment, the relations are fitted to map from a DNN to a cortex, and these relations are utilized to predict the responses in the provided frames. 
+To accelerate the process, we reduce the activation dimensionality to specified components using principal component analysis (PCA)~\cite{2002Principal}. 
+We utilize the activations from MT/MST to learn the fits. 
+\textcolor{red}{
+	The Pearson correlation coefficient $s_r$ constitutes the final neural similarity score for visual motion cortex as follows:
+}
+\begin{equation}
+	s_r=\frac{\sum_{i=1}^{n} (y_i-\bar{y}) (y_i^\prime - \bar{y}^\prime) }{\sqrt{\sum_{i=1}^{n} (y_i - \bar{y})^2 (y_i^\prime - \bar{y}^\prime)^2 }},
+\end{equation}
+\textcolor{red}{
+	where $y^\prime$ is the model activation, $y$ is the actual activation and $n$ is the corresponding feature dimension in DNN.
+$\bar{y}$ and $\bar{y}^\prime$ are the corresponding median over all individual neural response values.
+}
+
 \subsection{Overall score}
-In order to measure how well the BAN performs integrally, we use the BAS as a combination of the IoU behavioral metric and MT/MST cortical metrics.
-The BAS $s_{t}$ presented below is the mean of the two scores. 
+In order to measure how well the BTN performs integrally, we use the BTS as a combination of the IoU behavioral metric and MT/MST cortical metrics.
+The BTS $s_{t}$ presented below is the mean of the two scores. 
 \begin{equation} \label{equ:score_btn}
@@
 \end{equation}
-The design of the BAS is not normalized in various score magnitude because this possibly penalizes scores with small variances.
-So we treat each score for significance fairly for the BAS.
+The design of the BTS is not normalized in various score magnitude because this possibly penalizes scores with small variances.
+So we treat each score for significance fairly for the BTS.
 
 \section{Experiments} \label{sec:experiments}
-Here we indicate the experiments and validity of our proposed BAN with three steps. 
-First, we introduce the datasets and detailed implementation in our method.
-Second, we demonstrate that the BAN is a valid and brain-like pursuit model.
+Here we indicate the experiments and validity of our proposed BTN with three steps. 
+First, we introduce the datasets and detailed implementation in our \textcolor{red}{method}.
+Second, we demonstrate that the BTN is a valid and brain-like pursuit model.
 Finally, we discuss the model design mechanism and the relationship between DNN and neuroscience.
@@
 Each visual cortical region is implemented by a certain DNN performing some classical operations, such as convolutional operation and nonlinear activation. 
-These network modules are equivalent to visual regions, but we change the number of neurons in each cortical region.
-Considering the computational costs, we utilize Python with the TensorFlow package~\cite{abadi2015tensorflow} 
+\textcolor{red}{
+	These network modules are equivalent to visual regions, but we change the number of neurons in each cortical region.}
+Considering the \textcolor{red}{computational} costs, we utilize Python with the TensorFlow package~\cite{abadi2015tensorflow} 
 and model the V1 with the headmost 3 convolutional module from the revised AlexNet~\cite{imagenet}. 
@@
 We used 100 LSTM units with the zoneout operation~\cite{zoneout} that have a probability of 0.05.
-We train BAN~\cite{curriculum}, and utilize a similar learning configuration except for the learning rate, which is $2 \times 10 ^{-6}$.
+We train BTN~\cite{curriculum}, and utilize a similar learning configuration except for the learning rate, which is $2 \times 10 ^{-6}$.
 The starting sequence length is five and increases every twelve iterations.
 
-% 流派分类
-\subsection{Genre classification accuracy based on brain activity, behavior, and acoustic models}
-In the MRI experiments in this study, participants listened passively to music stimuli and did not carry out any genre classification tasks during scanning.
-To confirm that participant's brain activity captured sufficient information to distinguish different music genres in the current experimental setting, we conducted a genre classification based on brain activity using a decoding model approach.
-We evaluated the confusion matrix, along with the classification accuracy (the diagonal elements of the confusion matrix), using cortical activation within the genre-representing ROI masks.
-The results of classification varied across genres, in that classical music was always classified accurately (average classification accuracy, 100\%), whereas classification performance for rock music was poor across all participants (13.3\% $\pm$ 18.3\%).
-We also found that participants tended to classify reggae music as hip-hop music (confusion from reggae to hip-hop, 43.3\% $\pm$ 14.9 \%), whereas they tended to classify rock music as country music (confusion from rock to country, 33.3\% $\pm$ 11.8\%).
-The activity-based confusion matrices were highly consistent across all participants (Spearman's correlation coefficient, $ \rho = 0.553 \pm 0.062$; $ p < 0.001 $ for all combinations of participants).
-
-% 行为测试
-To investigate how brain activation associated with music genre is related to behavioral performance during genre classification, we conducted an additional behavioral test for each participant (MRI participants) after the MRI scanning.
-The confusion matrix revealed that participants' genre classification performance varied for each genre, in that classical music was always accurately recognized (average classification accuracy, 100\%), while rock music was less accurately recognized across all participants (36.7\% $\pm$ 13.9 \%).
-Behavioral confusion matrices identified brain activity-like error tendencies, such that rock music tended to be classified as country music (confusion from rock to country, 20.0\% $\pm$ 13.9\%).
-The behavior-based confusion matrices were highly consistent across all participants (Spearman's correlation coefficient, $ \rho = 0.669 \pm 0.038 $; $ p < 0.001 $ for all combinations of participants).
-The confusion matrices of behavior and brain activity were significantly correlated for all participants (Spearman's correlation coefficient, $ \rho = 0.438 \pm 0.081 $, $ p < 0.001 $), suggesting that the genre representational specificity of human behavior mimicked of brain activity.
-
-Further, because the MRI participants listened to the music twice (once in the MRI scanner and again in the behavioral test), there may have been a learning effect.
-Moreover, it is necessary to test whether the five MRI participants have similar perceptual properties for music genres as those of the general population.
-To confirm the generalizability of the behavioral results of these participants, we recruited an additional 21 participants for the behavioral tests only (non-MRI participants).
-The non-MRI participants exhibited variable genre classification accuracy (mean $\pm SD $, 56.3\% $ \pm 6.1\% $; max, 68.3\%; min, 43.3\% ), with performance similar to those of the MRI participants, in that they always recognized classical music accurately (100\%) whereas they did not always do so with rock music (17.5\%).
-Accordingly, the average behavioral confusion matrices of the MRI participants and the non-MRI participants were significantly correlated ($ \rho = 0.826, p < 0.001 $).
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\linewidth]{figs/confusion_matrix}
-	\caption{
-		\textbf{
-			Classification precision of the proposed method on Music Genres dataset. 
-		}
-		For different audio sequences, the predicted classification results are identified by genres.
-		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
-	}
-	\label{fig:confusion_matrix}
-\end{figure}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\linewidth]{figs/predicted_results}
-	\caption{
-		\textbf{
-			Classification precision of the proposed method on Music Genres dataset. 
-		}
-		For different audio sequences, the predicted classification results are identified by genres.
-		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
-	}
-	\label{fig:predicted_results}
-\end{figure}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\linewidth]{figs/specific_class}
-	\caption{
-		\textbf{
-			Classification precision of the proposed method on Music Genres dataset. 
-		}
-		For different audio sequences, the predicted classification results are identified by genres.
-		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
-	}
-	\label{fig:specific_class}
-\end{figure}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\linewidth]{figs/investigate_misclassifications}
-	\caption{
-		\textbf{
-			Classification precision of the proposed method on Music Genres dataset. 
-		}
-		For different audio sequences, the predicted classification results are identified by genres.
-		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
-	}
-	\label{fig:investigate_misclassifications}
-\end{figure}
-
-% 皮层组织
 \subsection{Genre-representing cortical organization} \label{sec:cortical_organization}
@@
 
-% 可解释
 \subsection{Genre-specific brain activity was explained by the spectro-temporal modulation of music genres}
@@
 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\linewidth]{figs/investigate_predictions}
-	\caption{
-		\textbf{
-			Classification precision of the proposed method on Music Genres dataset. 
-		}
-		For different audio sequences, the predicted classification results are identified by genres.
-		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
-	}
-	\label{fig:investigate_predictions}
-\end{figure}
+\subsection{Genre classification accuracy based on brain activity, behavior, and acoustic models}
+In the MRI experiments in this study, participants listened passively to music stimuli and did not carry out any genre classification tasks during scanning.
+To confirm that participant's brain activity captured sufficient information to distinguish different music genres in the current experimental setting, we conducted a genre classification based on brain activity using a decoding model approach.
+We evaluated the confusion matrix, along with the classification accuracy (the diagonal elements of the confusion matrix), using cortical activation within the genre-representing ROI masks.
+The results of classification varied across genres, in that classical music was always classified accurately (average classification accuracy, 100\%), whereas classification performance for rock music was poor across all participants (13.3\% $\pm$ 18.3\%).
+We also found that participants tended to classify reggae music as hip-hop music (confusion from reggae to hip-hop, 43.3\% $\pm$ 14.9 \%), whereas they tended to classify rock music as country music (confusion from rock to country, 33.3\% $\pm$ 11.8\%).
+The activity-based confusion matrices were highly consistent across all participants (Spearman's correlation coefficient, $ \rho = 0.553 \pm 0.062$; $ p < 0.001 $ for all combinations of participants).
+
+% 行为测试
+To investigate how brain activation associated with music genre is related to behavioral performance during genre classification, we conducted an additional behavioral test for each participant (MRI participants) after the MRI scanning.
+The confusion matrix revealed that participants' genre classification performance varied for each genre, in that classical music was always accurately recognized (average classification accuracy, 100\%), while rock music was less accurately recognized across all participants (36.7\% $\pm$ 13.9 \%).
+Behavioral confusion matrices identified brain activity-like error tendencies, such that rock music tended to be classified as country music (confusion from rock to country, 20.0\% $\pm$ 13.9\%).
+The behavior-based confusion matrices were highly consistent across all participants (Spearman's correlation coefficient, $ \rho = 0.669 \pm 0.038 $; $ p < 0.001 $ for all combinations of participants).
+The confusion matrices of behavior and brain activity were significantly correlated for all participants (Spearman's correlation coefficient, $ \rho = 0.438 \pm 0.081 $, $ p < 0.001 $), suggesting that the genre representational specificity of human behavior mimicked of brain activity.
+
+Further, because the MRI participants listened to the music twice (once in the MRI scanner and again in the behavioral test), there may have been a learning effect.
+Moreover, it is necessary to test whether the five MRI participants have similar perceptual properties for music genres as those of the general population.
+To confirm the generalizability of the behavioral results of these participants, we recruited an additional 21 participants for the behavioral tests only (non-MRI participants).
+The non-MRI participants exhibited variable genre classification accuracy (mean $\pm SD $, 56.3\% $ \pm 6.1\% $; max, 68.3\%; min, 43.3\% ), with performance similar to those of the MRI participants, in that they always recognized classical music accurately (100\%) whereas they did not always do so with rock music (17.5\%).
+Accordingly, the average behavioral confusion matrices of the MRI participants and the non-MRI participants were significantly correlated ($ \rho = 0.826, p < 0.001 $).
 
@@
 %	\label{fig:structure_analysis}
+%\end{figure}
+
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=\linewidth]{figs/tracking.pdf}
+%	\caption{
+	%		\textbf{
+		%		Tracking examples of the proposed method on Tracking-Gump dataset. 
+		%		}
+	%		\textcolor{red}{
+		%		For different video sequences, the predicted track results are identified by bounding boxes.
+		%		In addition, the average eye gaze position of these subjects is identified by the center of a circle, and its area is proportional to the size of pupil.
+		%		}
+	%	}
+%	\label{fig:tracking}
 %\end{figure}
@@
 and develop a new way to compute the similarity between model activation and cortical activation data. 
+\textcolor{red}{
 	Furthermore, the model with neuroanatomical alignment can better predict the neural response of human brain. 
-We believe the proposed BAN could encourage novel inspirations in the interpretability of DNN 
-and even motivate the development of brain-computer interfaces.
+	We believe the proposed BTN could encourage novel inspirations in the interpretability of DNN 
+	and even motivate the development of brain-computer interfaces.}
 % artificial motion consciousness

### 2023-06-05 visual/face/latex/sn-article.tex
init

--- 2023-06-05 visual/face/brain_like/latex/bfn.tex
@@
-%% bare_jrnl.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[journal]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-\usepackage{graphicx}
-\usepackage[table,xcdraw]{xcolor}
-\usepackage[TABBOTCAP]{subfigure}
-\usepackage{bm}
-\usepackage{upgreek} 
-\usepackage{amsmath}
-\usepackage{breqn}
-\usepackage{color}
-\usepackage{cite}
-\usepackage[none]{hyphenat}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{amssymb}
-
-\usepackage{multirow}
-
-% Neurocomputing
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing
+
+%%=======================================================%%
+%% to print line numbers in the margin use lineno option %%
+%%=======================================================%%
+
+%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+
+%%======================================================%%
+%% to compile with pdflatex/xelatex use pdflatex option %%
+%%======================================================%%
+
+%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+
+%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+\documentclass[sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
+%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
+%%\documentclass[sn-vancouver]{sn-jnl}% Vancouver Reference Style
+%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style
+%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
+%%\documentclass[sn-standardnature]{sn-jnl}% Standard Nature Portfolio Reference Style
+%%\documentclass[default]{sn-jnl}% Default
+%%\documentclass[default,iicol]{sn-jnl}% Default with double column layout
+
+%%%% Standard Packages
+%%<additional latex packages if required can be included here>
+%%%%
+
+%%%%%=============================================================================%%%%
+%%%%  Remarks: This template is provided to aid authors with the preparation
+%%%%  of original research articles intended for submission to journals published 
+%%%%  by Springer Nature. The guidance has been prepared in partnership with 
+%%%%  production teams to conform to Springer Nature technical requirements. 
+%%%%  Editorial and presentation requirements differ among journal portfolios and 
+%%%%  research disciplines. You may find sections in this template are irrelevant 
+%%%%  to your work and are empowered to omit any such section if allowed by the 
+%%%%  journal you intend to submit to. The submission guidelines and policies 
+%%%%  of the journal take precedence. A detailed User Manual is available in the 
+%%%%  template package for technical guidance.
+%%%%%=============================================================================%%%%
+
+\jyear{2021}%
+
+%% as per the requirement new theorem styles can be included as shown below
+\theoremstyle{thmstyleone}%
+\newtheorem{theorem}{Theorem}%  meant for continuous numbers
+%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
+%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
+\newtheorem{proposition}[theorem]{Proposition}% 
+%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+
+\theoremstyle{thmstyletwo}%
+\newtheorem{example}{Example}%
+\newtheorem{remark}{Remark}%
+
+\theoremstyle{thmstylethree}%
+\newtheorem{definition}{Definition}%
+
+\raggedbottom
+%%\unnumbered% uncomment this for unnumbered level heads
+
 \usepackage{float}
@@
 % 设置超链接跳转
-\usepackage[colorlinks,
-linkcolor=blue,
-anchorcolor=blue,
-citecolor=blue]{hyperref} 
+%\usepackage[colorlinks,
+%linkcolor=blue,
+%anchorcolor=blue,
+%citecolor=blue]{hyperref} 
 \usepackage{amsmath}
@@
 % 智能引用
-%\usepackage{hyperref}
-%\usepackage{cleveref}
+\usepackage{hyperref}
+\usepackage{cleveref}
 %
@@
 
+% plot subfigure
+\usepackage{graphicx}
+\usepackage{subfigure}
+
+% degree
+\usepackage{gensymb}
+
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{BAN: Neuroanatomical Aligning in Auditory Recognition between Deep Neural Network and Human Brain}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-
-\author{Haidong~Wang, Zhiyong Li, \emph{Member, IEEE},~Xuan He,~Ke Nai,~and Ming Wen% <-this % stops a space
-	\thanks{H. Wang, Z. Li, K. Nai, S. Wang and J. Lv are with the School
-		of Computer Science and Electronic Engineering of Hunan University, Key Laboratory for Embedded and Network Computing of Hunan Province, Changsha 410082,
-		China (e-mail: haidong\_hnu@hnu.edu.cn; zhiyong.li@hnu.edu.cn;
-		naike@hnu.edu.cn).}
-	\thanks{M.
-Wen is with State Grid Hunan Electric Power Company Limited Economical \& Technical Research Institute, Hunan Key Laboratory of Energy Internet Supply-demand and Operation, Changsha 410000, China (e-mail: hnjyy1903wen@126.com).}
-% % <-this % stops a space
-}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-\begin{abstract}
-Inspired by neuroanatomy, deep neural networks (DNNs) have recently developed from shallow network structures to exceedingly deep structures, providing excellent recognition performance.
+
+\title[Article Title]{Article Title}
+
+%%=============================================================%%
+%% Prefix	-> \pfx{Dr}
+%% GivenName	-> \fnm{Joergen W.}
+%% Particle	-> \spfx{van der} -> surname prefix
+%% FamilyName	-> \sur{Ploeg}
+%% Suffix	-> \sfx{IV}
+%% NatureName	-> \tanm{Poet Laureate} -> Title after name
+%% Degrees	-> \dgr{MSc, PhD}
+%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate} 
+%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
+%%=============================================================%%
+
+\author*[1,2]{\fnm{Haidong} \sur{Wang}}\email{wanghaidong@hutb.edu.cn}
+
+\author[2,3]{\fnm{Second} \sur{Author}}\email{iiauthor@gmail.com}
+\equalcont{These authors contributed equally to this work.}
+
+\author[1,2]{\fnm{Third} \sur{Author}}\email{iiiauthor@gmail.com}
+\equalcont{These authors contributed equally to this work.}
+
+\affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}
+
+\affil[2]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{10587}, \state{State}, \country{Country}}}
+
+\affil[3]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{610101}, \state{State}, \country{Country}}}
+
+%%==================================%%
+%% sample for unstructured abstract %%
+%%==================================%%
+
+\abstract{Inspired by neuroanatomy, deep neural networks (DNNs) have recently developed from shallow network structures to exceedingly deep structures, providing excellent recognition performance.
 	However, standard DNNs usually do not easily connect with brain areas on account of their excessive network depth and absent biological constraints, such as recurrent connections. 
@@
 	In summary, this research builds a BTN, a brain-like and recurrent DNN, as the first model of the cortical pathway of smooth pursuit.
-\end{abstract}
-
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords} 
-Online Multi-object Tracking, End-to-end Model, Joint Detection and Data Association. 
-\end{IEEEkeywords}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
+}
+
+%%================================%%
+%% Sample for structured abstract %%
+%%================================%%
+
+% \abstract{\textbf{Purpose:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
 % 
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=6.7in]{figs/introduction.pdf}
-	\caption{
-		\textbf{
-		Collaborative design between a DNN and neuroanatomy with a BAS.} 
-		Through the quantitative brain-like score, we refer to the human brain and utilize acquired knowledge to enlighten the design of the BTN. 
-		The BAN includes four regions that are mapped into the primary auditory cortex (A1), 		the belt or peripheral area, parabelt cortex (PB) and the areas of temporal cortex (T2/T3). 
-		CONV\textsubscript{V1} is the classical convolutional layer and performs preprocessing to reduce the data size.
-		The DFN\textsubscript{MT/MST} is dynamic filter network, and the RNN\textsubscript{FEF} is recurrent, as depicted in Section~\ref{sec:cornet_s_def} for details.
-		The the upper-right image corresponds to the tracking activation and bounding box in the brain-aligned models, 
-		while lower-right image represents the cortical activation and eye gaze position with the stimulus in the far left,
-		which demonstrates the relationship between computer vision tracking performance and brain tracking response with the BTS, as depicted in Section~\ref{sec:experiments}.
-	}
-	\label{fig:introduction}
-\end{figure*}
-
-\section{Introduction}
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps.
+% \textbf{Methods:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
 % 
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
+% \textbf{Results:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
 % 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by the IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-% 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.+
-
-% problem: time, optimization joint
-% the development of object detection
-% joint detection and embeding, -> problem
-% joint detection and association
-% contribution: end-to-end, data preparation, training
+% \textbf{Conclusion:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.}
+
+\keywords{keyword1, Keyword2, Keyword3, Keyword4}
+
+%%\pacs[JEL Classification]{D8, H51}
+
+%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}
+
+\maketitle
+
+\section{Introduction}\label{sec1}
 
 % /data3/dong/data/brain/auditory/Music_Genre_Classification_Pytorch-master/report.pdf, 1. Music
-\IEEEPARstart{M}{usic} genres are a set of descriptive keywords that convey high-level information about a music clip (jazz, classical and rock .etc).
+Music genres are a set of descriptive keywords that convey high-level information about a music clip (jazz, classical and rock .etc).
 Genre classification is a task that aims to predict music genre using audio signal.
@@
 
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-
-\section{Related Works}
-
-\subsection{Deep neural network}\par
-Many works have recently shown that salient objects are extracted by a series of foveal views~\cite{mnih2014recurrent,draw}.
-The object extraction module in the BTN is implemented with a two-dimensional gaussian filter~\cite{RATM} that is neuroanatomically explainable.
-Focusing on specific appearance representations may be as important as spatial attention. 
-An approach with recurrence can adaptively change the filter of the convolution module, therefore changing it to presentations on a frame and optimizing model performance~\cite{stollenga2014deep}. 
-The filters of the dynamic filter network (DFN)~\cite{brabandere2016dynamic} are obtained online based on the input feature, and the DFN implements model compression without degrading the accuracy. 
-Input-dependent state transitions can help to learn the markovian decision model~\cite{karl2017deep}. 
-\textcolor{red}{
-	We do not follow the results, and use the idea to predict the salient feature.}
-
-\textcolor{red}{
-	To track a target, it seems to be very suitable to use recurrences and glimpses, but they have only been employed successfully in monochromatic videos with simple backgrounds~\cite{RATM}. 
-	Some~\cite{ning2017spatially} obtained prominent results through representations of the target detector that is the input of a recurrent neural network (RNN)~\cite{su2020improved}.
-	However, it needs to process each full frame. 
-	A recent study~\cite{gordon2017re3} utilized an RNN cropping explicitly to build attention in humans. 
-	Our study is similar to~\cite{RATM,luo2019teleoperation}, and utilizes human attention which is implemented with a long short memory network (LSTM) to extract the movement features well in multiple frames.
-	In addition, we seek to design a brain-like network that will gain a superior BTS and exceed the existing tracking models on the Tracking-Gump dataset~\cite{gaze_forrest}.
-}\par
-
-\subsection{Smooth pursuit}
-There have been many successful eye movement experiments. 
-Some eye movement detection methods are proposed according to the existing plentiful datasets that have annotated eye movement data~\cite{dorr2010variability,mathe2012dynamic,hooge2017is,blstm_class}.
-Many of the existing classification methods, which are designed using motionless input, only process saccades and fixations. 
-Therefore, these methods cannot detect smooth pursuit and prevent the detection of brain-like correlations with smooth pursuit. 
-In order to address this issue, a multi-observer smooth pursuit method (MOSP)~\cite{mosp} that can differentiate three primary eye movements, including saccade, fixation and smooth pursuit, 
-and acquire good performance evaluation is designed~\cite{blstm_class}.
-In addition, to accurately explain the domain of  intelligence as a brain-like model in the human brain and cognitive sciences, 
-the brain-score has been proposed in the research of an integrated benchmark in the field of computer vision~\cite{schrimpf2020integrative}.
-
-In this work, we take full advantage of the latest achievements. 
-By utilizing these excellent eye movement classification and computer vision methods, 
-we can process functional magnetic resonance imaging (fMRI) and gaze data in the studyforrest dataset~\cite{gaze_forrest} 
-and detect corresponding cortical regions associated with saccadic and smooth pursuit in Tracking-Gump.
-In addition, based on model activation and cortical activation, we designed the BTS to measure their similarity.
+%\par
+
+\begin{figure*}[htbp]
+	\centering
+
+	\subfigure%[Without STURE]
+	{
+		\begin{minipage}[t]{1.0\linewidth}
+			\centering
+			\includegraphics[width=1.0\textwidth]{figs/fig_1_c.pdf}
+		\end{minipage}%
+	}%
+	%	\subfigure[With STURE]{
+		%		\begin{minipage}[t]{0.48\linewidth}
+			%			\centering
+			%			\includegraphics[width=1\textwidth]{tsne_best.eps}
+			%		\end{minipage}%
+		%	}%
+	%\n is important,(or \quad)
+
+	\subfigure%[Tracking results without STURE]
+	{
+		\begin{minipage}[t]{1.0\linewidth}
+			\centering
+			\includegraphics[width=1.0\textwidth]{figs/fig_1_d.pdf}
+		\end{minipage}
+	}%
+	%	\subfigure[Tracking results with STURE]{
+		%		\begin{minipage}[t]{0.48\linewidth}
+			%			\centering
+			%			\includegraphics[width=1\textwidth]{tsne_tracking_result_with_STURE.eps}
+			%		\end{minipage}
+		%	}%
+
+	\subfigure%[Tracking results without STURE]
+	{
+		\begin{minipage}[t]{1.0\linewidth}
+			\centering
+			\includegraphics[width=1.0\textwidth]{figs/fig_1_f_g.pdf}
+		\end{minipage}
+	}
+
+	\centering
+	\caption{
+		\textbf{Spontaneous emergence of face-selectivity in untrained networks.
+		}
+		\textbf{(a)} Face-select neurons and their response observed in monkey experiments.
+		The response was normalized to the maximum value as 1.
+		The face image shown is not the original stimulus set due to copyright.
+		The image shown is available at \url{https://www.shutterstock.com} (see Methods for details).
+		\textbf{(b)} the architecture of the untrained AlexNet~\cite{krizhevsky2012imagenet}.
+		The untrained AlexNet was devised using a random initialization method~\cite{lecun2012efficient}, for which the values in each weight kernel were randomly sampled from a Gaussian distribution.
+		\textbf{(c)} A stimulus set was designed to control the degree of intra-class image similarity.
+		Stimulus images were selected and modified from a publicly available dataset that has been used in human fMRI study~\cite{stigliani2015temporal}.
+		The original images are available at [\url{http://vpnl.stanford.edu/fLoc/}].
+		\textbf{(d)} Responses of individual face-selective units in the untrained AlexNet ($ P < 0.001 $, two-sided rank-sum test, uncorrected).
+		\textbf{(e)} The number of face-selective units in each convolutional layer in untrained networks ($ n=100 $).
+		% 面部选择单元的面部选择指数
+		\textbf{(f)} Face-selectivity index (FSI) of face-selective neurons in the primate IT~\cite{freiwald2010functional} ($ n=158 $), and face units in each convolutional layer in the untrained AlexNet.
+		The control FSI was measured according to the shuffled responses of face-selective units in the untrained network.
+		% 和打乱的人脸响应进行对比
+		\textbf{(g)} (Left) Examples of texform and scrambled face images.
+		(Right) Responses of face-selective units to the original face ($ n = 200 $), the scrambled face ($ n=200 $) and texform face images ($ n = 100 $).
+		\textbf{(h)} Responses of face-selective units to four different sets of novel face images: 
+		(1) 50 face images from our original dataset (images not used for finding face-selective units),
+		(2) 16 images used in Tsao et al.~\cite{tsao2006cortical,freiwald2010functional},
+		(3) 50 images used in Cao et al.~\cite{cao2018vggface2} in color and gray scale,
+		and (4) 50 face images artificially generated by the FaceGen simulator (singular inversions) in color and gray scale. % Singular Inversions (软件公司)
+		\textbf{(i)} The number of face-selective units, where the weight variation was changed from 5 to 200\% of the original value using two different initialization methods with Gaussian (red) and a uniform distribution (blue).
+		\textbf{(j)} FSI of face-selective units across changes in the weight.
+		Dashed lines indicate the mean and shaded areas indicate the standard deviation of 30 random networks.
+		% 针对所有图进行说明
+		All box plots indicate the inter-quartile range (IQR between Q1 and Q3) of the dataset,
+		% 第三四分位数与第一四分位数的差距又称四分位距（InterQuartile Range, IQR）
+		the horizontal line depicts the median and the whiskers correspond to the rest of the distribution (Q1-1.5*IQR, Q3+1.5*IQR).
+	}
+	\label{fig:emergence}
+\end{figure*}
+
+\section{Results}\label{sec2}
+
+\subsection{The emergence of face-selectivity in untrained DNNs}\par
+To simulate the emergence of face-selective neurons (\Cref{fig:emergence}a), we measured the responses of a biologically inspired DNN model, AlexNet~\cite{krizhevsky2012imagenet} (\Cref{fig:emergence}b), to similarity-controlled face stimulus set (\Cref{fig:emergence}c).
+A standard AlexNet model is composed of five convolutional layers (feature extraction network) and three fully connected layers (classification network), which together reproduce the structure of the ventral stream of the visual pathway (\Cref{sec:nn}).
+To investigate the selective response of individual units rather than the performance of a trained system, 
+we discard the classification layers and examined activity in the final layer (\Cref{fig:emergence}b,top,Conv5) of the feature extraction network.
+To examine whether face tuning of units can arise even in completely untrained DNNs, 
+we devised an untrained AlexNet by randomly initializing the weights of filters in each convolutional layer (\Cref{fig:emergence}b, bottom).
+% 控制输入信号的长度？
+For this, we used a standardized network initialization method~\cite{lecun2012efficient}, by which the weights of kernels in each convolutional layer were randomly drawn from a Gaussian distribution with parameters set to control the strength of the input signals across layers.
+The stimulus set consisted of grayscale images in six different categories (\Cref{fig:emergence}c), specifically the face, a scrambled face, and four non-face objects, as previously done in monkey experiments~\cite{stigliani2015temporal}.
+The images in each class were designed to control the low-level features of the luminance, contrast, object size, and object location, and they have statistically comparable intra- and inter-class image levels of similarity.
+
+% 观察到的现象
+Surprisingly, we observed a group of face-selective units ($ n = 250 \pm 63 $ in 100 random networks, mean $ \pm $ s.d.) that show significantly higher response to face images than to non-face images emerging in the untrained networks (\Cref{fig:emergence}d, $ P<0.001 $, two-sided rank-sum test).
+Here, a unit is defined as a unit component at each position of the channel in an activation map of the network.
+For example, there are 43,264 units (=13$\times$13$\times$256, $ N_{x-position} \times N_{y-position} \times N_{channel} $) in Conv5.
+We considered each unit (of the same filter) at different spatial locations as different ones, as the selectivity of units at different locations appears to be distinct despite the fact that they share the same filter.
+We also investigated the layer-specific emergence of face-selective units in untrained networks.
+We found that face-selective units are also observed in earlier layers, Conv3 to 5 but are scarcely found in Conv1 and 2 (\Cref{fig:emergence}e, 
+Conv1: $ n=0.008 \pm0.002\% $, 
+Conv2: $ n=0.047 \pm 0.009\% $, 
+Conv3: $ n=0.491 \pm 0.089\% $, 
+Conv4: $ n=0.534 \pm 0.103\% $,
+Conv5: $ n=0.579 \pm 0.146\% $).
+We found that the number of face-selective units and the face-selectivity index (FSI) of each unit increased through the layer hierarchy (\Cref{fig:emergence}e,f).
+Notably, the number of face-selective units did not show significant differences across the convolutional group or filters within each layer.
+This suggests that face-selective units are not dominantly generated by a particular filter.
+The number of observed face-selective units was highest in the mid- and high-level layers, similar to observations in the ventral visual pathway of monkeys~\cite{tsao2006cortical,livingstone2017development}.
+These results suggest that the development of face-selectivity requires a hierarchical structure of the network along with random feedforward weights, which enables multiple linear-nonlinear computations.
+We also found that the observed face-selective units in the untrained networks (Conv5) show a value of the averaged FSI~\cite{tsao2006cortical,freiwald2010functional} comparable to the index associated with monkey IT neurons (\Cref{fig:emergence}f, $ n_{untrained} = 465 $, $ n_{monkey} = 158 $, NS, two-sided rank-sum test, $ P=7.69 \times 10 ^{-2} $, $ r_{rbc} = 9.25 \times 10^{-2} $, two-sided Kolmogorov-Smirnov test, $ P=2.49 \times 10^{-4}, d=2.32 \times 10^{-2} $)
+and a significantly higher value that those measured from a shuffled response (\Cref{fig:emergence}f, $ n_{untrained} = 465 $, $ n_{shuffled} = 465 $, two-sided rank-sum test, $ P=1.49 \times 10^{-25}, r_{rbc} = 5.09 \times 10^{-1} $) for various definitions of the FSI~\cite{tsao2006cortical,aparicio2016neurophysiological,duyck2021color}.
+These results suggest that face-selective units, highly tuned to the face as observed in the brain, can emerge in DNNs even in the complete absence of learning.
+
+One possible scenario for the emergence of such face-selectivity in random networks is that the observed face-selective units are simply sensitive for local face parts common to facial images.
+To investigate this possibility, we measured the responses of the face-selective units to a local feature of the face using two types of control images in which global face features are disrupted but local face features are preserved.
+These were (1) scrambled faces, in which small patches of the local face components were spatially scrambled, and (2) texform face~\cite{long2018mid}, in which global face features are disrupted but the statistics of the local face texture is preserved (\Cref{fig:emergence}g,left).
+We confirmed that face-selective units show significantly higher responses to the original face images compared to the corresponding control images (\Cref{fig:emergence}g, right; 
+Face vs. Scrambled face, $ n=200 $, one-side rank-sum test, $ P=1.71 \times 10^{-52} $, $ r_{rbc}=7.69 \times 10^{-1} $;
+Face vs. Texform face, $ n=100 $, one-sided rank-sum test, $ P=4.12\times10^{-30} $, $ r_{rbc}=6.56\times 10^{-1} $).
+In addition, the responses of face units to these control images were not greater than those to other non-face images, implying that face-selective units are selective to the global context of faces instead of the local components (\Cref{fig:emergence}g, right; Scrambled face vs.
+Non-face, $ n=200 $, one-sided Kolmogorov-Smirnov test, $ P=8.31 \times 10^{-1} $, $ d=3.00 \times 10^{-3} $;
+Texform face vs. Non-face, $ n=100 $, one-sided rank-sum test, NS, $ P=9.40 \times 10^{-1} $, $ r_{rbc}=4.51 \times 10^{-2} $, $ d=1.84 \times 10^{-2} $).
+These results suggest that the observed face units in the untrained network are not particularly selective to local face parts, but are instead selective to a whole face.
+
+% h
+Next, we investigated the responses of face-selective units to four different novel stimulus sets that were not used to find face-selective units.
+These were
+(1) 50 face images from our original data set, not used for finding the face-selective units;
+(2) 15 face image used in Tsao et al.~\cite{tsao2006cortical,freiwald2010functional};
+(3) 50 face images used in Cao et al.~\cite{cao2018vggface2};
+and (4) 50 face images artificially generated by the FaceGen simulator (singular inversions) in color and grayscale (\Cref{fig:emergence}h).
+We found that face-selective units in the untrained network show significantly higher responses to novel face images compared to the responses to non-face under all conditions (\Cref{fig:emergence}h, Novel face vs.
+Non-face images, one-sided rank-sum test, $ P \leq 1.47 \times 10^{-11} $, $ r_{rbc} \geq 4.54 \times 10^{-1}$).
+These results suggests that the observed face-selectivity in an untrained network defined by one specific dataset can be generalized to other novel sets of faces.
+
+% figure i, j
+To confirm that the emergence of face-selective units is not due to the specific initial parameter set but is rather generally observed in an untrained network,
+we varied the width of the weight distribution for random network initialization (Gaussian and uniform) from 5 to 200\% of the original standard deviation of the standardized random initialization and examined if face-selective units consistently emerge (\Cref{fig:emergence}i,j).
+We found that face-selective units consistently arise in the untrained networks across the variation of the parameter.
+The number (\Cref{fig:emergence}i) and selectivity index (\Cref{fig:emergence}j) of observed face units were largely unchanged across a wide range of weight variations and across the wide variation in the width of the weight distribution.
+This implies that the emergence of face-selective units in untrained networks is highly robust to variations of the wiring strength.
+
+\begin{figure*}[htbp]
+	\centering
+
+	\subfigure%[Without STURE]
+	{
+		\begin{minipage}[t]{0.8\linewidth}
+			\centering
+			\includegraphics[width=1.0\textwidth]{figs/fig_2_c.pdf}
+		\end{minipage}%
+	}%
+
+	\centering
+	\caption{
+		\textbf{Preferred feature images of face-selective units in untrained networks.
+		}
+		\textbf{(a)} Measurements of preferred feature images (PFI) of target units in Conv5 from the reverse-correlation analysis~\cite{bonin2011local}.
+		Bright and dark 2D Gaussian filters were generated at a random position as an input stimulus set.
+		The PFI was obtained as the summation of stimuli weighted by the corresponding response.
+		The initial preferred feature image was calculated from the local Gaussian stimulus set by the classical reverse-correlation method~\cite{bonin2011local}.
+		% RNN?
+		Then, a new stimulus set was generated as the summation of the obtained PFI and local Gaussian stimuli, with the second preferred feature image then obtained from a new stimulus set.
+		This procedure was repeated to obtain the preferred feature image.
+		\textbf{(b)} Schematics of the process used to achieve a preferred feature image (PFI) using a generative neural network (GAN) and a genetic algorithm (X-Dream)~\cite{ponce2019evolving}.
+		Synthesized images are generated by the GAN with image codes and are fed into an untrained network as input.
+		The genetic algorithm finds a new image code that maximizes the response of the target unit.
+		The PFI of a target unit is achieved after 100 iterations of this procedure.
+		\textbf{(c)} The obtained preferred feature images, using the reverse-correlation method and X-Dream, of the face-selective unit, selective units to non-face class (flower), and units selective to none of the class.
+		\textbf{(d)} Illustration of the face-configuration index (FCI) of a face unit's PFI.
+		The FCI was defined as pixel-wise correlation between the original face stimuli and the generated PFIs.
+		\textbf{(e)} FCI of PFI, using the reverse correlation method, of units selective to each class ($ n_\textrm{Face} = 465 $, $ n_\textrm{Hand} = 7 $, $ n_\textrm{Horn} = 772 $, $ n_\textrm{Flower} = 107 $, $ n_\textrm{Chair} = 63 $).
+		\textbf{(f)} FCI of PFI, using X-Dream, of the same units as the units used in (\textbf{e}).
+		All box plots indicate the inter-quartile range (IQR between Q1 and Q3) of the dataset,
+		the horizontal line depicts the median and the whiskers correspond to the rest of the distribution (Q1-1.5*IQR, Q3+1.5*IQR).
+		The face images shown in panels (\textbf{d})-(\textbf{f}) are selected examples from the publicly available dataset~\cite{stigliani2015temporal}.
+		The original images are available at [\url{http://vpnl.stanford.edu/fLoc}].
+	}
+	\label{fig:preferred}
+\end{figure*}
+
+\subsection{Preferred feature images of face-selective units in an untrained network}
+
+Next, to characterize the feature-selective responses of these face-selective units qualitatively,
+we reconstructed preferred feature images (PFI) of individual units using a reverse-correlation (RC) method~\cite{bonin2011local} and a generative adversarial network algorithm (X-Dream)~\cite{ponce2019evolving} (see~\Cref{sec:preferred}).
+In the RC analysis, we presented 2500 images of bright and dard 2D Gaussian filters at random positions as input stimuli to an untrained network (\Cref{fig:preferred}).
+By adding stimuli weighted according to the corresponding neural response with 100 repeated iterations, we obtained the preferred feature images of the target units.
+In the X-Dream analysis, a deep generative adversarial neural network~\cite{dosovitskiy2016generating} was trained to ImageNet datasets to synthesize preferred feature images from the image codes scored by a genetic algorithm using the responses of units from repeated iterations.
+(\Cref{fig:preferred}b).
+We found that the response of target units induced by the PFI was increased, being higher that those induced by face stimulus images, as the iteration number of the genetic algorithm exceeds a certain value
+(\Cref{fig:preferred}a, right, $ n=465 $, 
+RC PFI vs. face stimulus, two-sided rank-sum test, $ P=1.51 \times 10^{-6} $, $ r_{rbc} = 1.58 \times 10^{-1} $;
+RC PFI vs. non-face stimulus, two-sided rank-sum test, $ P=3.12 \times 10^{-2} $, $ r_{rbc} = 7.07 \times 10^{-2} $,
+\Cref{fig:preferred}b, right, $ n=465 $, 
+X-Dream PFI vs. face stimulus, two-sided rank-sum test, $ P=1.92 \times 10^{-119} $, $ r_{rbc} = 7.63 \times 10^{-1} $;
+X-Dream PFI vs. non-face stimulus, two-sided rank-sum test, $ P = 2.68 \times 10^{-129} $, $ r_{rbc} = 7.94 \times 10^{-1} $
+).
+These results indicate that our PFI generation methods successfully find the most preferred input feature of face-selective units.
+As a result, using both methods, we obtained the PFI of face-selective units, units selective to non-face classes, and units without selective responses to any image classes (\Cref{fig:preferred}c).
+We found that the PFI of the face-selective units presents distinguishable features from those of other objects.
+We observed that the PFIs of face-selective units represent face-like configurations, whereas the PFIs of units selective to non-face classes show noticeable configurations of each object class (i.e., flowers in an RC and X-Dream).
+
+% d
+To quantify the structural similarity of the PFIs to face images, we defined the face-configuration index as the averaged pixel-wise correlation between a PFI and the 200 face images used for face unit selection (\Cref{fig:preferred}d).
+We estimated the face-configuration index of each PFI of face-selective and non-face-selective units generated by the RC method.
+We found that the estimated PFIs of face-selective units (with a visually observable face-like configuration) have a significantly higher average value of the index than that from the units selective to non-face objects (\Cref{fig:preferred}e,
+Face PFI vs. Non-face PFI, 
+$ n_\textrm{Face}    = 465 $,
+$ n_\textrm{Horn}    = 772 $,
+$ n_\textrm{Hand}    = 7   $,
+$ n_\textrm{Chair}   = 63  $,
+$ n_\textrm{Flower}  = 107 $,
+one-sided rank-sum test,
+$ P \leq 5.63 \times 10^{-4} $,
+$ r_{rbc} \geq 1.56 \times 10^{-1} $;
+\Cref{fig:preferred}f, Face PFI vs. Non-face PFI,
+$ n_\textrm{Face}   = 465 $,
+$ n_\textrm{Chair}  = 63  $,
+$ n_\textrm{Horn}	= 773 $,
+$ n_\textrm{Hand}	= 7	  $,
+$ n_\textrm{Flower}	= 107 $,
+one-sided rank-sum test, 
+$ P \leq 1.93 \times 10^{-5} $,
+$ r_{rbc} \geq 2.35 \times 10^{-1} $
+).
+Notably, the average pairwise correlation estimated between each face stimulus image shows a significantly lower value of nearly zero, 
+implying that the observed index of face-selective units reflects structural similarity to the averaged (or a prototype, abstract) face image rather than similarly to particular face images accidentally observable.
+
+Next, we hypothesized that the observed face-selective units may encode invariant representations of the prototype face images, as some types of intrinsic are a basic property of CNNs.
+A number of previous studies suggested that various types of invariance (e.g., translation, scaling, and rotation) over a wide range of image transformations can be implemented in a CNN~\cite{lecun2004learning,kavukcuoglu2010learning,lecun2012learning,chidester2018rotation,srivastava2018effect}, mostly due to three key components--the convolutional layer, the pooling layer, and the hierarchical structure--in CNN models.
+Thus, to investigate whether the observed face-selective units show invariant representations of face images regardless of corresponding image condition, 
+we measured the response of face-selective units to face and non-face object images with various positions, sizes, and rotation angles.
+First, we observed that single face units show constant face tuning under a fairly wide range of size/potion/rotation variations and that range was comparable with those of face-selective neurons in IT~\cite{zoccolan2007trade}.
+Notably, we found that our model units also show the inversion effect observed in monkeys~\cite{tsao2006cortical,buiatti2019cortical,perrett1985visual}.
+We found that the response of face-selective units to inverted face images are significantly lower that those to upright faces.
+
+Similarly, we found viewpoint-invariant face-selective units and mirror-symmetric viewpoint-specific units in a random network.
+Interestingly, the number of viewpoint-invariant face-selective units increased along the network hierarchy, similar to previous observations in the brain~\cite{freiwald2010functional}.
+These results show that the observed invariances can arise from the hierarchical structure with convolutional filtering without the contribution of structured spatial filters.
+Notably, the current result also suggests a possible scenario through which to understand how viewpoint invariant selectivity can arise in infant animals.
+From the similarities between the CNN and the biological brain models, i.e., that the fundamentals of both CNNs and sensory cortices are based on the hierarchical feedforward structure and that the process of convolution via weight sharing in CNNs can be approximated by a biological model of periodic functional maps with hypercolumns in the visual cortex,
+our result may inspire insight into how innate invariance can arise in infant animals.
+
+\begin{figure*}[htbp]
+	\centering
+
+	\subfigure%[Without STURE]
+	{
+		\begin{minipage}[t]{1.0\linewidth}
+			\centering
+			\includegraphics[width=1.0\textwidth]{figs/fig_3_c_d.pdf}
+		\end{minipage}%
+	}%
+
+	\centering
+	\caption{
+		\textbf{Detection of face images using the response of face units in untrained networks.
+		}
+		(\textbf{a}) Design of the face detection task and SVM classifier using the responses of the untrained AlexNet.
+		During this task, face or non-face images were randomly presented to the networks and the observed response of the final layer was use d to train a support vector machine (SVM) to classify whether the given image was a face or not.
+		Among 60 images from each class (face, hand, horn, flower, chair, and scrambled face) that were not used for face unit selection, 40 images were randomly sampled for the training of the SVM, and the other 20 images were used for testing.
+		The images shown are selected examples from the publicly available dataset~\cite{stigliani2015temporal}.
+		The original images are available at [\url{http://vpnl.standford.edu/fLoc}].
+		(\textbf{b}) Performance on the face detection task using a single unit randomly sampled from face-selective units ($ n = 465 $) and units without selective responses to any image classes ($ n = 7776 $).
+		The channel level was measured by the shuffled responses of face-selective units in the untrained network.
+		The error bar indicates the standard deviation of each unit.
+		Each bar indicates the mean and the error bar indicates the standard deviation of performance of each unit.
+		(\textbf{c}) Performance of the face detection task using face-selective units and non-selective units when varying the number of units from 1 to 456.
+		The dashed line indicates the detection performance using all units in Conv5 ($ n=43,264 $).
+		Each line indicates the mean and the shaded area indicates the standard deviation for 100 repeated trials of the random sampling of units.
+		(\textbf{d}) Performance on the face detection task using face-selective units ($ n=465 $) and then using all units in Conv5 ($ n=43,264 $).
+		Each bar indicates the mean and the error bar indicates the standard deviation for 100 repeated trials of the random sampling of units.
+	}
+	\label{fig:detection}
+\end{figure*}
+
+\subsection{Detection of face images using the responses of face-selective units}
+We tested whether the selective responses of these face units could provide reliable information with which to detect between faces and non-face objects.
+During this task, face ($ n=40 $) or non-face ($ n=40 $) images were randomly presented to the networks, and the observed response of the final layer was used to train a support vector machine (SVM) to classify whether the given image was a face or not (\Cref{fig:detection}a).
+First, we compared the detection performance of the SVM using a single unit randomly sampled from face-selective units and using units without selective responses to any image classes.
+We confirmed that the SVM trained with a single face-selective unit shows noticeably higher performance that those measured from shuffled responses, whereas the SVM trained with units without selectivity does not
+(\Cref{fig:recognition}b,
+Face unit vs. Response shuffled, 
+$ n_\textrm{face} = 465 $,
+two-sided rank-sum test,
+$ P = 2.97 \times 10 ^{-121} $,
+$ r_{rbc} = 7.68 \times 10^{-1} $;
+Response shuffled vs. Non-selective unit, 
+$ n_\textrm{non-selective} = 7,776 $,
+two-sided rank-sum test, NS, 
+$ P = 1.10 \times 10^{-1} $,
+$ r_{rbc} = 4.52 \times 10^{-2} $,
+two-sided Kolmogorov-Smirnov test,
+$ P = 1.93 \times 10^{-1} $,
+$ d = 2.12 \times 10^{-2} $
+).
+Then, extending the test to various numbers of units, we compared the detection performance of this SVM using face-selective units with the performance when using the same number of randomly sampled non-selective units.
+We confirmed that the SVM trained with multiple face-selective units shows noticeably better performance that that trained with the same number of non-selective units, 
+as the number of units used in each condition was varied from $ n=1 $ to 465 (total number of face units in untrained networks)
+(\Cref{fig:recognition}c,
+Face vs. Non-selective units, 
+$ n_\textrm{trial} = 100 $,
+two-sided rank-sum test, 
+$ P \leq 1.45 \times 10^{-33} $,
+$ r_{rbc} \geq 8.74 \times 10^{-1} $
+).
+We also found that the SVM using face units ($ n=465 $) nearly matches the performance of the SVM using all units in the final layer ($ n=43,264 $)
+(\Cref{fig:recognition}d, 
+Face vs. All units, 
+$ n_\textrm{trial} = 100 $,
+two-sided rank-sum test, NS, 
+$ P = 1.90 \times 10^{-1} $,
+$ r_{rbc} = 9.29 \times 10^{-2} $,
+two-sided Kolmogorov-Smirnov test,
+$ P = 1.90 \times 10^{-1} $,
+$ d = 9.20 \times 10^{-3} $
+).
+Furthermore, we found that face units enable the networks to detect faces with various sizes, position, and rotations even when such image conditions were held constant when training the SVM classifier.
+
+Notably, we also found that the SVM can successfully detect faces when it is trained with the responses of units selective to non-face classes, 
+similar to the results in a previous experiment in human~\cite{haxby2001distributed},
+whereas it failed to detect with units not selective to any of the classes.
+To compare our results with the experiment condition of the previous human experiment~\cite{haxby2001distributed},
+we first trained the SVM using the responses of four distinct populations:
+(1) all of the units selective to each class (All-selective),
+(2) units selective to non-face classes (Non-face-selective),
+(3) face-selective units only (Face-selective),
+and (4) units not selective to any of the classes (Non-selective).
+As a result, we found that the SVM trained with non-face-selective units showed a performance comparable with the results of Haxby et al.~\cite{haxby2001distributed}.
+Interestingly, the performance was also comparable with those with all-selective units and those with face-selective units only,
+similar to the results in a previous experiment in human~\cite{haxby2001distributed}.
+This result is understandable considering that there are only five image classes;
+thus, even non-face-selective units can provide information for discriminating face and non-face images by generating different levels of activities for each class.
+Taken together, these results imply that the information provided by selective units that emerge in the untrained networks is sufficient to detect between faces and non-face objects.
+
+\begin{figure*}[htbp]
+	\centering
+
+	\subfigure%[Without STURE]
+	{
+		\begin{minipage}[t]{1.0\linewidth}
+			\centering
+			\includegraphics[width=1.0\textwidth]{figs/fig_4_b_f.pdf}
+		\end{minipage}%
+	}%
+
+	\centering
+	\caption{
+		\textbf{Effect of training on face-selectivity in untrained networks.
+		}
+		(\textbf{a}) Three different datasets modified from publicly available ImageNet~\cite{ILSVRC15} were used for the training of the network for image classification: 
+		(1) face-reduced ImageNet, 
+		(2) original Imagenet, 
+		and (3) ImageNet with added face images.
+		For copyright reasons, the face image shown here is not the actual image used in the experiments.
+		The original images are replaced with images with similar contents for display purposes.
+		The original images are available at [\url{https://www.image-net.org/download}].
+		Images shown are available at [\url{https://www.shutterstock.com},\url{http://vpnl.stanford.edu/fLoc/}~\cite{stigliani2015temporal}].
+		(\textbf{b}) Face-selectivity index of face-selective units in untrained network and in networks trained with the three datasets ($ n_\textrm{Untrained} = 4,267 $, $ n_\textrm{Reduced} = 2,452 $, $ n_\textrm{Original} = 3,561 $, $ n_\textrm{Face} = 3,585 $).
+		(\textbf{c}) The number of face-selective units in untrained networks and in networks trained with three datasets ($ n_\text{net} = 10 $).
+		(\textbf{d}) Face detection performance of untrained networks and of networks trained with three different datasets ($ n_\textrm{trial} = 1,000 $).
+		(\textbf{e}) The obtained preferred feature images (PFI), using reverse-correlation method of the face-selective unit on each network.
+		All box plots indicate the inter-quartile range (IQR between Q1 and Q3) of the dataset,
+		the horizontal line depicts the median and the whiskers correspond to the rest of the distribution (Q1-1.5*IQR, Q3+1.5*IQR).
+	}
+	\label{fig:effect}
+\end{figure*}
+
+\subsection{The emergence of face-selectivity in trained DNNs}
+We tested a scenario in which our current model can corroborate the conflicting observations regarding the role of visual experience for the development of face-selectivity.
+A previous report suggested that visual experience is necessary for the emergence of face-selectivity by showing that monkeys raised without exposure to faces lack face-selective domains~\cite{arcaro2017seeing}.
+On the other hand, another recent study showed that the face-selective area develops robustly in congenitally blind humans, suggesting that visual experience is not necessary for face-selectivity~\cite{arcaro2017seeing}.
+Regarding these conflicting results, we examined how face-selective units in untrained networks can be affected by training with visual inputs.
+
+To investigate the effect of training on a face image set,
+we prepared the following three different stimulus sets:
+(1) face-reduced ImageNet: 500 classes including no recognizable face images were manually curated from the ILSVRC 2010 dataset according to a visual inspection by the authors,
+(2) the original ImageNet, 
+and (3) the original ImageNet with added face images used in the current study~\Cref{fig:effect}a.
+Then, the network was trained with each of these image sets.
+First, we found that the FSI of the face-selective units was significantly decreased after being trained to the face-reduced image set 
+(~\Cref{fig:effect}b,
+Untrained vs. Face-reduced,
+$ n_\textrm{Untrained} = 4,267 $,
+$ n_\textrm{Reduced} = 2,452 $,
+two-sided rank-sum test,
+$ P = 2.99 \times 10^{-28} $,
+$ r_\textrm{rbc} = 6.76 \times 10^{-1} $
+),
+whereas it was increased after being trained to the face-including image sets 
+(Untrained vs. Face-included,
+$ n_\textrm{Face} =3585 $,
+two-sided rank-sum test,
+$ P = 1.21 \times 10^{-3} $,
+$ r_{rbc} = 2.60 \times 10^{-1} $
+).
+Notable, the FSI was significantly decreased after being trained to the original ImageNet dataset that contains images of faces but has no group labeled as face
+(~\Cref{fig:effect}b, Untrained vs. Original, 
+$ n_\textrm{Original} = 3,561 $,
+two-sided rank-sum test,
+$ P = 9.34 \times 10^{-45} $,
+$ r_\textrm{rbc} = 8.15 \times 10^{-1} $
+).
+This suggests that the tuning of face-selective units could either be sharpened or weakened by training with distinct stimulus sets.
+
+% Fig.4 c
+Next, we found that the number of face-selective units observed was greater in the network trained with face-including image set compared to that trained to face-reduced images 
+(~\Cref{fig:effect}c, Untrained vs. Trained,
+$ n_\textrm{Net} = 10 $,
+two-sided rank-sum test,
+$ P \leq 1.40 \times 10 ^{-3} $,
+$ r_\textrm{rbc} \geq 5.72 \times 10^{-1} $
+).
+Interesting, however, we found that the number of face-selective units, when trained to face-including images, appeared to be smaller than that of untrained networks.
+These results imply that the training process of the network to face-including images selectively sharpens the tuning of face units so that the selectivity of strongly tuned units is sharpened while the weakly tuned units are pruned.
+In this condition, the face detection performance of the networks would improve in face-trained networks even if the number of face units decreased compared to the initial, untrained condition.
+To validate this scenario, we trained the SVM using the response of face-selective units for a face detection task in an untrained network and in the three networks trained to each type of data set.
+As predicted, we found that the face detection performance was significantly increased in the networks trained to the face-including image set compared to that of the untrained network
+(~\Cref{fig:effect}d, Untrained vs. Face included, 
+$ n_\textrm{trial} = 1000 $,
+two-sided rank-sum test,
+$ P = 1.04 \times 10^{-3} $,
+$ r_\textrm{rbc} = 2.60 \times 10^{-1} $
+),
+whereas the face detection performance of the network trained to the face-reduced image set was significantly decreased compared to the untrained network
+(~\Cref{fig:effect}, Untrained vs. Face-reduced,
+$ n_\textrm{trial} = 1,000 $,
+two-sided rank-sum test,
+$ P = 1.06 \times 10^{-22} $,
+$ r_\textrm{rbc} = 6.42 \times 10^{-1} $
+).
+Furthermore, we found that the PFI of the face-selective unit shows a clear face configuration in the network trained to face-including natural images,
+whereas the face configuration is disrupted in network trained to face-reduced dataset (~\Cref{fig:effect}e).
+This result is consistent with previous observation of decreased face-selectivity in face-deprived monkeys~\cite{arcaro2017seeing}.
+
+\begin{figure*}[htbp]
+	\centering
+
+	\subfigure%[Without STURE]
+	{
+		\begin{minipage}[t]{1.0\linewidth}
+			\centering
+			\includegraphics[width=1.0\textwidth]{figs/fig_5_a-f_1.pdf}
+		\end{minipage}%
+	}%
+
+	\centering
+	\caption{
+		\textbf{ImageNet category-selective units in untrained networks.
+		}
+		(\textbf{a}) The responses of units in untrained networks to the images of 1,000 ImageNet~\cite{ILSVRC15} classes and to face images (VGGFace2)~\cite{cao2018vggface2}.
+		% 杂色菊
+		(\textbf{b}) Average tuning curve of gazania selective units.
+		(Inset) Responses of gazania-selective units to the original gazania ($ n = 100 $), the scrambled gazania ($ n = 100 $) and texform gazania images ($ n = 100 $).
+		(\textbf{c}) The number of selective units for 39 classes in which selective units are observed.
+		The error bar indicates the standard deviation of 50 random networks.
+		%	
+		(\textbf{d}) Sample preferred feature images achieved by reverse-correlation analysis and stimulus images (inset).
+		% 
+		(\textbf{e}) Visualization of the PCA (principal component analysis)~\cite{wold1987principal} analysis results (only two principal components (PC) are shown) using the Conv5 unit response to each class in untrained networks.
+		The analysis was performed using 3,999 principal components, and the top $140 \pm 32$ components contained $ 75\% $ of the variance.
+		% 轮廓系数(Silhouette Coefficient),是聚类效果好坏的一种评价方式。
+		(\textbf{f}) The silhouette index~\cite{kaufman2009finding} of the Conv5 unit responses was measured using all principal components to estimate the consistency of data clustering.
+		Each dot indicates the mean and the error bar indicates the standard deviation of 50 simulations of randomly initialized networks.
+		% 
+		(\textbf{g}) Correlation between the silhouette index and the number of selective units observed (Pearson correlation).
+		Each dot indicates the mean and the error bar indicates the standard deviation of 50 random networks.
+		%
+		All box plots indicate the inter-quartile range (IQR between Q1 and Q3) of the dataset, the horizontal line depicts the median and the whiskers correspond to the rest of the distribution (Q1-1.5*IQR, Q3+1.5*IQR).
+		For copyright reasons, the images in panels (\textbf{a}) and (\textbf{d}) are not the actual images used in the experiments.
+		The original images are replaced with images with similar contents for display purposes.
+		The original images are available at [\url{https://www.image-net.org/download}, \url{https://arxiv.org/abs/1710.08092}].
+		Images shown are available at [\url{https:/www.shutterstock.com}].
+	}
+	\label{fig:image_net}
+\end{figure*}
+
+\subsection{The emergence of selectivity to various objects in untrained DNNs}
+Lastly, we investigated the possibility that units selective to various objects other than faces also emerge similarly in untrained neural networks.
+For this, we measured the responses of units in random networks to a stimulus dataset of ImageNet containing 1,000 classes of objects (~\Cref{fig:image_net}a).
+As a result, we found that selective units are observed in 39 classes among the 1,000 classes (~\Cref{fig:image_net}b,c).
+From the analysis using scrambled and texform control images, we confirmed that these object-selective units are not particularly selective to local image parts but are selective to a whole object, similar with units selective to faces
+(~\Cref{fig:image_net}b, inset,
+Gazania vs. Scrambled gazania, 
+$ n=100 $,
+one-sided rank-sum test,
+$ P = 2.67 \times 10^{-12} $,
+$ r_\textrm{rbc} = 4.89 \times 10^{-1} $,
+%
+Gazania vs. Texform gazania, 
+$ n = 100 $,
+one-sided rank-sum test, NS,
+$ P = 1.00 $,
+$ r_\textrm{rbc} = 3.17 \times 10^{-1} $,
+one-sided Kolmogorov-Smirnov test,
+$ P = 1.02 \times 10^{-2} $,
+$ d = 2.97 \times 10^{-2} $;
+% 
+Texform gazania vs. other-class,
+$ n = 100 $,
+one-sided Kolmogorov-Smirnov test,
+$ P = 3.45 \times 10^{-2} $,
+$ d = 2.55 \times 10^{-2} $
+).
+This result suggests that units selective innately to various objects such as faces can emerge in untrained neural networks.
+
+Next, to investigate the emergent condition of units selective to each object further, we sorted those 39 classes according to the number of selective units observed and computed the PFI using the RC method (~\Cref{fig:image_net}c,d).
+In general, we observed a tendency in which the PFIs of the large number group showed a relatively simple configuration of each preferred object class that was visually observable (~\Cref{fig:image_net}d, top),
+whereas those of the small number classes represented a more complicated structure of the PFI (~\Cref{fig:image_net}d, bottom).
+From this result, we hypothesized that objects with a simple configuration, such as faces, can induce stronger clustering in the latent space representation than those of other object classes and therefore may have a greater likelihood of generating units selective to them.
+To validate our hypothesis, we used the dimension-reduction method~\cite{wold1987principal} to compare a clustered representation of each object class in terms of the raw pixel values and in the responses of Conv5.
+For quantification of the representational clustering of each class, we measured the silhouette index~\cite{kaufman2009finding} to estimate the consistency of data clustering.
+We found that there is a strong correlation between the silhouette index in the Conv5 latent space and the number of selective units observed
+(~\Cref{fig:image_net}e-g, Pearson correlation coefficient,
+$ n_\textrm{Net} = 50 $,
+$ r = 5.85 \times 10^{-1} $,
+$ P = 7.48 \times 10^{-5} $
+).
+This result demonstrates that objects with a simple profile, readily distinguishable from those of other objects statistically, lead to a strong clustering of abstracted responses in the DNN and are more likely to generate units selective to it.
+Furthermore, the relationship between the silhouette index and the number of units observed shows that the number of units increases as the silhouette index increases,
+with no selective units observed when the silhouette index is below 0.036 (~\Cref{fig:image_net}g, black dashed line).
+This result implies that there may be a threshold of the clustering level in the response embedding space, by which a unit selective to that object class can be defined and observed.
+In neuroscience, this may provide a possible explanation of why face-selective neurons are observed in various experiments while neurons selective to other objects are not observed as readily.
+Thus, the observed face-selectivity may not be a special case of tuning, 
+whereas selectivity to other visual objects can also arise in random networks simply due to the relatively simple configuration of the corresponding geometric components.
+
+\section{Discussion}\label{sec12}
+
+We showed that a biologically inspired DNN develops face-selective units without training, solely from statistical variations of the feedforward projections.
+These results suggest that the statistical complexity embedded in the structure of the hierarchical circuit~\cite{paik2011retinal,jang2017interlayer,sailamul2017synaptic} can initialize primitive cognitive functions such as face-selectivity in untrained neural networks.
+Although the performance of a DNN appears to be similar to that of the brain on certain visual tasks, 
+there are critical differences between biological brains and DNN models, such as convolutional filtering in DNN models, which is not biologically plausible.
+However, although DNNs are not an impeccable model of the visual pathway of the brain, 
+the current results provide a possible scenario for understanding how primitive visual functions such as face detection can initially arise in early brains before learning begins with sensory inputs.
+
+State-of-the-art studies using random networks provide important clues regarding how these selective units can arise spontaneously in untrained model networks.
+Recently, it was reported that a network can classify an untrained image class by combining pre-trained readout units~\cite{socher2013zero}, a process known as zero-shot learning.
+Our results suggest that such zero-shot learning is even possible without any pre-trained readout units.
+It was also reported that an artificial network that learns visual features with random, untrained weights can perform image classification tasks~\cite{jarrett2009best,pinto2009high}.
+Jarrett et al. showed that features from a randomly initialized one-layer convolutional network could classify the Caltech 101 dataset with a performance level similar to that of fine-tuned network, 
+consistent with the mathematical notion that a combined convolutional and pooling architecture could develop spatial frequency selectivity and translation invariance~\cite{saxe2011random}.
+Overall, these results suggest that the initial structure of random networks plays an important role in visual feature extraction before the training process.
+They also imply that complex types of feature selectivity, such as face-selectivity, may arise innately from the structure of the random feedforward circuitry.
+
+Furthermore, recent model studies using the lottery ticket hypothesis~\cite{frankle2019stabilizing,ramanujan2020s} showed that randomly weighted neural networks contain subnetworks that can perform tasks without modifying the initial random weight values,
+implying that functional architectures can emerge from random initial wirings.
+This model and our current model have a common aspect in that functional structures can emerge without any modification to the initial random weights.
+However, the lottery ticket hypothesis showed that a random subnetwork can perform tasks without learning,
+while our model demonstrates that the functional tuning of single units can arise spontaneously.
+Indeed, our model not only suggests a possible mechanism of the origin of the functional tuning of single neurons in the early developmental process in the brain but also provides insight into the mechanism underlying the emergence of functional subnetworks,
+possibly from tuned individual units that emerge in random artificial neural networks.
+
+% 储备池计算
+% RC的好处是特征提取网络，即Reservoir ，是随机生成并在训练和预测阶段是固定的，只有readout部分是要学的
+Similarly, the theory of reservoir computing suggests that the circuits required for higher-order cognitive functions, such as classification, may already exist in untrained, random recurrent neural networks.
+In this scenario, higher-order cognitive functions can be achieved only by training a read-out network, as suggested by the lottery ticket hypothesis~\cite{verstraeten2007experimental,bellec2020solution}.
+Interestingly, our results in the face-detection task performed with the SVM are comparable to the concept of reservoir computing, 
+as the training of the SVM with the responses of untrained networks is consistent with the procedure of training a read-out projection from random networks in reservoir computing.
+It is notable that recent studies suggest that the random network can perform this task if the read-out units are selected via a prior understanding of the system.
+For example, object classification can be performed by a random network if read-outs are chosen by a synaptic rule observed in the brain~\cite{weidel2021unsupervised,tetzlaff2013synaptic}.
+While these models focus on the innate functions of networks in that a high dimensional space generated by a random network can perform various tasks without learning,
+our current results demonstrate that the functional tuning of single units (comparable to neuronal tuning in biological brains) can arise in random networks without any further training of the read-out process,
+which is distinguished from the main idea of the reservoir computing model.
+
+It is important to note that the current results do not necessarily mean that innate face-selectivity is the tuning observed in adult animals.
+There is a wealth of evidence showing that higher areas of the visual cortex are immature in the early development stage and that the corresponding functional circuit is modulated by visual experience~\cite{zhang2005delayed,baldwin2012cortical,bourne2006hierarchical,kiorpes2004neural}.
+There is also strong evidence that the IT region, where face-selective neurons are observed, can be altered by early experience~\cite{srihasam2012behavioral,srihasam2014novel}.
+Considering the anatomical and physiological changes that occur over the first postnatal year, 
+the innate template of face-selective neurons in very early developmental stages must be refined by later visual experience, including both bottom-up and top-down processes~\cite{yan2018bottom,epshtein2008image}.
+This scenario may be supported by recent observations of the existence of the proto-retinotopic organization and rough face-patches in higher regions of the visual cortex~\cite{livingstone2017development,srihasam2014novel,arcaro2017hierarchical}.
+Moreover, observations of the early development of cortical circuits may provide further support to our scenario.
+Retino-thalamic feedforward projections are composed of noisy local samplings that result in unrefined receptive fileds in individual thalamus neurons~\cite{tavazoie2000diverse}.
+This is comparable to randomly initialized convolutional kernels before training.
+Inborn feature-selectivity generated in this early cortex may provide an initial basis for various visual functions.
+
+Importantly, our results imply that innate face-selectivity may arise spontaneously from feedforward wirings, 
+but this requires further evidence and examinations before one can argue whether the mechanism can indeed be considered spontaneous.
+Specifically, our model suggests that the random weights in CNNs (comparable with random feedforward projections in biological networks) can generate selective response of units to face images.
+Then, considering that the development of random weights does not require any training or experience, this could be considered as innate face-selectivity.
+These results imply a possible scenario in which the random feedforward connections that develop in young animals may be sufficient for initializing primitive face-selectivity.
+Arguably, this face-selectivity can be considered to arise spontaneously under the assumption that random feedforward wiring can arise without a complicated process.
+In this scenario, the emergence of face-selectivity may not require genetically programmed innateness but may simply originate from the statistical complexity of random wirings.
+However, it must be noted that an alternative interpretation is also possible:
+the observed face-selectivity is innate but may not be considered spontaneous because the initial development of random feedforward wiring requires a certain mechanism programmed in one's genes.
+Particularly, regarding the question of why face-selective neurons are observed consistently in the same brain regions, the role of programmed genes may be critical--face-selective neurons can simply originate from random feedforward wiring in hierarchical networks,
+but this neuronal selectivity can only be refined and reserved in a particular face-patch region in the brain, 
+most likely controlled by a blueprint of the brain circuitry programmed in genes.
+Detailed arguments pertaining to this issue may become possible when further evidence of the developmental mechanism of random wirings and the corresponding dependence on gene coding becomes available.
+
+Our findings suggest a scenario in which proto-organization for cognitive functions may be spontaneously generated, 
+after which training with data can sharpen and specify the selectivity of networks.
+A recent fMRI study of the inferior temporal cortex in infant and adult monkeys also shows a biological example of this scenario~\cite{livingstone2017development}.
+Livingstone et al. show that neurons broadly tuned to faces are already observed in infant monkeys (~1 month old) 
+and that the region where these neurons are observed is identical to where the face neurons of adult monkeys are observed.
+This result implies that the innate template of face-selective neurons in infant monkeys may develop spontaneously and be later fine-tuned during the early visual experience.
+This is consistent with the model scenario of our study, which shows that face-selective neurons emerge in the early cortex provide a basis for early face detection,
+with this neuronal tuning refined further when learning begins with visual experience with both bottom-up and top-down process~\cite{yan2018bottom,epshtein2008image}.
+
+In summary, our results suggest that face-selectivity can arise in a completely untrained neural network with the random initial wiring of hierarchical feedforward projections.
+These findings may provide insight into the origin of innate cognitive functions in both biological and artificial neural networks.
+
+\section{Method}
+
+\subsection{Neural network model} \label{sec:nn}
+We used AlexNet~\cite{krizhevsky2012imagenet} as a representative model of the convolutional neural network.
+This network consists of feature extraction and classification networks.
+The feature extraction network consists of five convolutional layers with rectified linear unit (ReLU) activation and a pooling layer, while the classification network has three fully connected layers.
+The detailed parameters of the architecture were sourced from Krizhevsky et al.~\cite{krizhevsky2012imagenet}, which provided the models for V4 and IT~\cite{cadieu2014deep}.
+
+To determine the origin of face-selective neurons, the randomly initialized networks were examined.
+% 节点数目的开方为标准差
+For the untrained AlexNet, the weights and biases of each convolutional layer were initialized from a Gaussian distribution or a uniform distribution with a zero mean and the standard deviation set to the square root of one over the number of units in the previous layer.
+This was done to balance the strength of the input signals across the layers, 
+and this approach follows previous research on efficient network initialization processes~\cite{lecun2012efficient}.
+
+\subsection{Stimulus dataset}
+Seven types of visual stimuli from six datasets were used.
+(1) A low-level feature-controlled stimulus set~\cite{stigliani2015temporal} was selected and modified from publicly available images in human fMRI study~\cite{stigliani2015temporal} (\url{http://vpnl.stanford.edu/fLoc})
+and was used to find units that responded selectively to face images.
+Specifically, 260 images were prepared for each class (face, hand, horn, flower, chair, and scrambled face).
+Then, 200 images were randomly sampled from each class and used for face unit selection.
+Among the 60 remaining images in each class, 40 images were used for the training of the SVM, 
+and the other 20 images used for testing.
+Each item was overlaid on a group of phase-scrambled background images.
+This was designed to reduce inter-class differences across various low-level properties,
+in this case, luminance, contrast, size, position, and the degree of intra-/inter-class image similarity.
+% 2
+To validate the face-selective response to novel face stimulus set, we used (2) 16 face images used in Tsao et al.~\cite{tsao2006cortical,freiwald2010functional} provide by D.Tsao group from personal communication,
+% 3
+(3) 50 face images from open access VGGFace2 dataset used in Cao et al.~\cite{cao2018vggface2} (\url{https://github.com/ox-vgg/vgg_face2});
+% 4
+(4) 50 face images artificially generated by the FaceGen simulator (singular inversions; FaceGen Modeller Pro) in color and grayscale (\url{https://facegen.com}).
+% 5
+(5) To investigate the invariance of face-selective units to face images of various sizes, position, and rotation angle of the faces and other objects in the similarity-controlled stimulus set~\cite{stigliani2015temporal}.
+% 6
+(6) Viewpoint dataset: This set was used to find units that invariantly responded to face images of different viewpoints.
+This dataset consists of five angle-based viewpoint classes ($ -90\degree $, $ -45\degree $, $ 0\degree $, $ 45\degree $, $ 90\degree $) with 10 different faces obtained from the publicly available Point'04 dataset (\url{http://crowley-coutaz.fr/Head%20Pose%	20Image%20Database.html}) used in Gourier et al~\cite{gourier2004estimating}.
+% 7
+To investigate the possibility of units selective to various objects, we used a publicly available ImageNet dataset~\cite{ILSVRC15} (\url{https://www.image-net.org/download}).
+For copyright reasons, the images in ~\Cref{fig:emergence}a, ~\Cref{fig:effect}a, and ~\Cref{fig:image_net}a,d are not the actual images used in our experiments.
+The original images are replaced with images with similar contents for display purposes.
+Alternative images used in this study are purchased from \url{https://www.shutterstock.com} with a standard image license, which includes rights to publish in e-publication and printed in physical form as part of a copy of magazines, newspapers, and books.
+For all datasets, the image size of the input to AlexNet was fixed at $ 227 \times 227 $ pixels.
+
+\subsection{Analysis of response of the network units}
+In our model, a unit refers to a unit component at each position of the channel in an activation map of the network.
+We defined this unit in a convolutional network as a simplified model of a biological unit (a single neuron or a group of neurons that generates a tuned activity), considering that the dynamics of a single neuron in biological brains can be estimated from its receptive filed,
+which behaves as a spatiotemporal filter at a local cortical position retinotopically matching the external visual space.
+Based on a previous study~\cite{grossman2019convergent}, face-selective units were defined as units that had significantly higher mean responses to face images than to images in any non-face class ($ P \textless 0.001 $, two-sided rank-sum test).
+To estimate the normalized response, the responses to each unit was $ z $-scored using the average and the standard deviation of responses to stimulus images.
+To quantify the degree of tuning, an FSI of a single unit was defined as in previous experimental research~\cite{aparicio2016neurophysiological}
+\begin{equation}\label{eq:fsi}
+	FSI = \frac{(\overline{R}_\textrm{face} - \overline{R}_\textrm{non-face})}
+	{\sqrt{(\sigma^2_\textrm{face} + \sigma^2_\textrm{non-face}) / 2}}
+\end{equation}
+where $ \overline{R}_\textrm{face} $ is the average response to face images 
+and $ \overline{R}_\textrm{non-face} $ is the average response to all non-face images.
+An FSI of 0 indicates equal responses to face and non-face objects.
+
+Among the face-selective units found, a face viewpoint-invariant unit was defined as a unit for which the response was not significantly different (one-way ANOVA, $ P \textgreater 0.05 $, Bonferroni adjustment $ n = 5 $) among all viewpoint classes.
+Similar to the face-selective units, the viewpoint-specific units were determined by the mean response of the preferred viewpoint class being significantly higher than that for any other viewpoint (one-way ANOVA, $ P \textless 0.05 $, Bonferroni adjustment $ n = 5 $).
+We defined mirror-symmetric tuning as the condition that arises when a viewpoint-specific face-selective unit has a symmetric shape of the tuning curve (one-way ANOVA, $ P \textless 0.05 $, Bonferroni adjustment $ n = 5 $; i.e., a unit shows peak responses at $ -45\degree $ and $ 45\degree $ or $ -90\degree $ and $ 90\degree $).
+The invariance index of a single unit was defined as the inverse of the standard deviation of the average responses for images within each viewpoint class.
+The same analysis was also performed for the stimulus set that added the face class to ILSVRC2010.
+
+\subsection{Face vs. non-face detection task for the network}
+A face vs. non-face detection task was established to investigate whether face-selective units could perform basic face perception.
+To determine if this was possible, an SVM was trained with network responses to images and was then made to predict whether a class of unseen images was or was not a face.
+To avoid the double-dipping issue~\cite{kriegeskorte2009circular} we undertook the training and testing of the SVM using distinct sets of images, 
+where 260 images were prepared for each class, 
+and 200 image were then randomly sampled from those images and used for face unit selection.
+Among the 60 remaining images in each class, 40 images were used for the training of the SVM, 
+and the other 20 images were used for testing.
+The label of the training set was then changed to a binary class: face or non-face.
+For each trial, the SVM was trained with the relationship between the fifth layer's response to the training set and the new training label.
+After a training session, the model predicted the test label using the network response to the test set.
+Furthermore, to test whether the responses of face-selective units could detect faces varied in different ways, 
+we trained an SVM with network responses for center-view face images ($ N = 40 $) and non-face images $ N = 40 $.
+The model then predicted test labels using the responses of face-selective units to new test sets which consisted of a face and non-face images with different types of variation, in this case, different sizes, positions, and rotation angles.
+
+\subsection{Preferred input feature (receptive field) analysis} \label{sec:preferred}
+To visualize the preferred input feature of target units, the receptive field was estimated by the RC method~\cite{bonin2011local} with multiple iterations.
+The initial stimulus set was generated as 2500 random local 2D Gaussian filters.
+Such stimuli were weighted by the corresponding responses and were added as an initial preferred feature image.
+Then, to detect the preferred feature more accurately, we calculated the PFI iteratively;
+the PFI of the next iteration was calculated by a new stimulus set consisting of the summation of the current PFI and 2500 random local 2D Gaussian filters (\Cref{fig:preferred}a).
+We repeated 100 iterations and obtained the final PFI.
+
+% b
+To obtain the preferred feature images of target units, we used a generative adversarial network (X-Dream)~\cite{dosovitskiy2016generating}.
+X-Dream consists of a generative adversarial network (GAN) with a genetic algorithm as the optimization algorithm of the responses.
+We used a GAN~\cite{dosovitskiy2016generating} pre-trained with natural images (ILSVRC 2012).
+The response optimization algorithm~\cite{ponce2019evolving} finds the optimal image code that maximizes the response of the target unit.
+In this algorithm, a single image code consists of 1000 initial values randomly sampled from a zero-centered Gaussian distribution with a standard deviation of 0.5.
+In each iteration, 50 images codes are randomly generated, and the five image codes with the highest optimization score are preserved for the next iteration while the other 45 codes are recombined through a pairwise-randomization step before the next iteration.
+Then, individual values of an image code are randomly mutated with a probability of 0.01;
+i.e., each value is replaced with a random number drawn from a zero-centered Gaussian with a standard deviation of 0.5.
+The preferred feature image of a target unit is achieved after 100 iterations.
+
+\subsection{Trained network model}
+To investigate the effect of training on a face image set,
+we prepared the following three different stimulus sets:
+(1) face-reduced ImageNet: images with those including a face excluded (ILSVRC 2010; 500 classes),
+(2) the original ImageNet (1,000 classes), 
+and (3) the original ImageNet with added face images used in the current study (1,001 classes).
+The network was trained with each of these image sets using a stochastic gradient descent algorithm.
+Detailed training parameters were adapted from Krizhevsky et al., 2012:
+batch size = 128,
+momentum = 0.9,
+weight decay = 0.0005,
+training epoch = 90, 
+learning rate = 0.01,
+learning rate decay = 10 times for every 30 epochs.
+
+\subsection{Statistics}
+All sample sizes, exact $ P $ values, and statistical methods are indicated in the corresponding text, figure legends and tables.
+A rank-sum test was used for all analyses, 
+except for the number of face units across convolutional groups (Kolmogorov-Smirnov test),
+the face detection task (Kolmogorov-Smirnov test),
+the detection of viewpoint-invariant and -specific units (one-way ANOVA with Bonferroni adjustment)
+and a connectivity analysis (one-way ANOVA with Bonferroni adjustment).
+The devisor of all Bonferroni adjustments was five viewpoint group ($ n = 5 $).
+All statistical tests used to determine statistical significance were two-sided, except for the chance level of FSI (one-sided, ~\Cref{fig:emergence}f),
+response to controlled face images and novel faces (~\Cref{fig:emergence}g,h),
+chance level of the face-configuration index (one-sided, ~\Cref{fig:preferred}e,f),
+response to controlled gazania images (~\Cref{fig:image_net}b),
+intra-class image similarity (Supplementary Fig.S1g),
+the effective range of image correlation (Supplementary Fig.S5f),
+average weight between Conv4 and Conv5 (Supplementary Figs.S8c,d,and S9b)
+and the number of viewpoint invariant units (Supplementary Fig.S9h).
+All error bars and shaded areas indicate the standard deviation, 
+except for response to PFIs (standard error; ~\Cref{fig:preferred}a,b),
+connectivity analysis (standard error; Supplementary Figs.S8c,d,S9b,d,f,h),
+viewpoint invariance index (standard error; Supplementary Fig.S8g).
+Box plots in ~\Cref{fig:emergence}e-h, ~\Cref{fig:preferred}e,f, ~\Cref{fig:effect}b-d and ~\Cref{fig:image_net}b, and in Supplementary Figs.
+1d-h, 2h, 3, 7b, c, and 9d, h indicate the inter-quartile range (IQR between Q1 and Q3) of the dataset,
+the horizontal line depicts the median and the whiskers correspond to the rest of the distribution (Q1-1.5*IQR, Q3+1.5*IQR).
+In Supplementary Table 2 and 3, we included the effect size alongside all $ P $ values for each statistical test:
+the rank-biserial correlation value~\cite{cureton1956rank} for the rank-sum test, 
+and Cohen's~\cite{cohen2013statistical} for ANOVA test, the dissimilarity value~\cite{vermeesch2013multi} for Kolmogorov-Smirnov test, respectively.
 
@@
 
-\section{Experiments} \label{sec:experiments}
+\section{Experiments}
 Here we indicate the experiments and validity of our proposed BTN with three steps. 
@@
 
-\section{Discussion}
-\label{sec:discussion}
-
-Using fMRI, the current study revealed the cortical organization underlying different music genres.
-As the genre-label model did not assume any acoustic properties, we used genre-weight maps to reflect music genre information in general.
-% FBS (Feature-Brain Similarity)
-Thus, it was important to obtain similar weight patterns between the genre-label model and the FBS map based on the MTF model.
-The FBS map shows how the spectro-temporal modulation of each cortical voxel corresponds to the reference spectro-temporal modulation profile for each music genre.
-Thus, it is likely that the weight values in the bilateral STG for the genre-label model were determined by the degree to which each STG voxel's spectro-temporal modulation property resembles that of the music stimuli.
-
-Among the multiple subregions in STG, music genres were represented more clearly in both HS and LSTG than in the other subregions.
-% 音区定位
-Previous studies on frequency-selective (i.e., tonotopic) maps of the human STG have indicated that the primary auditory cortex (A1) is located around the posterior part of HG and HS accompanied by a gradient of low- to high-frequency selectivity from the anterior to posterior direction~\cite{ahveninen2016intracortical,leaver2016functional}.
-While cochlear features correspond to positions in the frequency axis and may therefore reflect tonotopic properties, the MTF model further captures the modulation property around each position on the frequency axis.
-% MTF 优于 耳蜗模型
-Santoro et al.~\cite{santoro2014encoding} showed that the MTF model outperformed the cochlear model in terms of predicting STG activation in response to natural sound stimuli~\cite{santoro2014encoding}, which is consistent with the current results.
-% norman2015distinct 音乐和说话的不同皮层通路
-LSTG has been reported to represent different sound categories such as the sound of guitar versus.
-voice of a cat~\cite{staeren2009sound}, and it exhibits human speech-selective activation~\cite{norman2015distinct}.
-The MTF model captures detailed spectro-temporal modulation properties both in human speech~\cite{elliott2009the} and in musical instruments~\cite{patil2012music}, which may explain the more general acoustic features that can encompass the feature space of simple categorical models such as genre-label or voice models.
-To summarize, the spectro-temporal modulations obtained in our study seem to reflect the general processing of auditory stimuli in the bilateral STG.
-
-Several studies have reported that perceived music genres can be decoded from brain activity.
-Ghaemmaghami and Sebe~\cite{ghaemmaghami2016brain} used magnetoencephalogram and electroencephalogram datasets to classify musical stimuli as either pop or rock using SVM.
-Further, Casey~\cite{casey2017music} and Sengupta et al.~\cite{sengupta2018spatial} used fMRI data with five distinct music genres, followed by activity-based multi-class classification using SVM.
-However, these studies did not provide answers to how cortical representations of music genres contribute to genre classification.
-Collectively, the present findings demonstrate the underlying mechanisms of such activity-based genre classification.
-
-We investigated classification accuracy using five models (cochlear, MTF, MIRT, MFCC, and voice).
-% Mel-Frequency Cepstral Coefficient / MIRtoolbox
-Both the MFCC and the MIRT models were developed in the field of computational science and have been employed previously in studies of music-induced brain activity~\cite{alluri2012large,gucclu2016brains,toiviainen2014capturing}.
-The cochlear model has been employed to test cortical activation in the spectral domain~\cite{de2017hierarchical};
-however, it cannot capture the dynamic temporal modulation of spectra.
-The MTF model was constructed based on the physiological properties of neurons in the auditory cortex~\cite{chi2005multiresolution} and is used widely in neuroscience research into auditory perception~\cite{norman2015distinct,patil2012music,santoro2014encoding,santoro2017reconstructing}.
-Therefore, it is likely that the MTF model is more biologically plausible for addressing the auditory processing of music genres.
-Our current findings are consistent with this view, because, of all the models, the MTF model showed the highest correlation coefficients between the FBS maps and genre-weight maps.
-
-% 能捕获快节奏
-One might argue that the fMRI signal change is too slow to capture the rapid acoustic features of music stimuli and that this could affect the model performance with up-tempo (e.g.,metal) and slow-tempo (e.g., classical) music genres.
-However, the MTF model includes temporal modulations of frequency (from 2.8 to 64.0 Hz) and the estimated model weights show signals in high temporal modulation rates suggesting that this model can capture the fine-scale musical information necessary to distinguish relatively up-tempo music genres (e.g., metal and hip-hop).
-Indeed, the difference in decoding accuracy in not explained by the difference in tempo, given that both classical and hip-hop music showed higher decoding accuracies.
-
-% 使用行为实验补充 没有主动听的问题
-In the MRI experiments in this study, participants listened passively to music stimuli and did not carry out any genre classification tasks during scanning.
-It could be argued that we did not confirm that the participants listened attentively to the stimuli and that we overlooked the brain regions activated for top-down decision-making on music genre classification.
-To address this, we conducted behavioral experiments of genre classification for MRI participants and confirmed that there were significant correlations between the confusion matrices based on brain activation and behavior.
-These findings suggested that passive listening to music stimuli captured enough brain information for use in behavioral music genre classification.
-
-In this study, we adopted a small-N design (five participants).
-The small number of subjects is compensated for by the large number of samples for each participant (i.e., three hours).
-The small-N design has attracted substantial attention in recent studies combining fMRI data and machine learning~\cite{smith2018small}.
-Instead, of group-level statistical analyses, as are often used in conventional neuroimaging, we performed subject-wise analyses.
-The correspondence of genre representation among participants was confirmed using Person's correlation of confusion matrices for both activity-based decoding and behavior-based analyses.
-In contrast, cortical organization differed across participants.
-% SD 标准差
-In contrast, cortical organization much larger $ SD $ of prediction accuracy than the other anatomical ROI (genre-label model: left HS, $ SD = 0.085 $; mean $ SD $ across other ROIs = 0.026), indicating that the left HS is the most sensitive region to the individual variability of music genre representation.
-
-% 语言的影响
-It is worth considering whether linguistic factors could explain genre-specific organization because most classical and jazz pieces employed in the current study were instrumental (i.e., without human voice), whereas other genres included the human voice.
-Previous studies have reported voice-selective and non-voice-selective cortical areas around STG~\cite{kell2018task,leaver2010cortical,norman2015distinct}.
-However, our study demonstrated that such linguistic factors do not explain genre-specific patterns.
-The genre-label model in our study predicted brain activity even after regressing out voice-related features.
-In addition, we also showed that classical and jazz music were not confused with each other and that some music genres containing voice stimuli were not confused with each other (e.g., hip-hop and country music).
-Thus, it is likely that genre-specific activation patterns in the bilateral STG reflected detailed spectro-temporal modulation even within nonvoice music pieces.
-
-% 结果不完美的原因
-Although we have shown that FBS maps and genre-weight maps largely corresponded, the correspondence is not perfect.
-There are several possible reasons for such imperfection.
-% 1. 容易受噪声影响
-First, the FBS maps and genre-weight maps were susceptible to the noise of brain activity.
-The upper limit of prediction accuracy also affects the accuracy of both FBS maps and genre-weight maps.
-% 2. MTF模型本身不是最好->深度网络
-Second, the MTF might not be the best model.
-Indeed, an acoustic model might exist that captures more detailed characteristics of music genres.
-% 3. 其他非声音特征
-Third, some nonacoustic features (such as the participants' preference, knowledge, and experience related to music) may play important roles in producing the genre-specific cortical organization.
-% 音乐类别的神经基础 
-Further research is therefore required to clarify the detailed neural basis of music categorization.
-
-\section{CONCLUSION}
+\section{Conclusion}\label{sec13}
 Inspired by the visual processing mechanisms found in the human brain, our study presents a brain-like tracking model suited to the problem of visual object tracking. 
@@
 
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-
-\section*{Acknowledgment}
-This work was partially supported by the National Key R$\&$D Program of China (No.
-2018YFB1308604), Hunan Science and Technology Innovation Project (No.
-2017XK2102) and National Natural Science Foundation of China (No.61976086, No.61672215, U1613209).
-Haidong Wang and Zhiyong Li are co-first authors, they contributed equally to this work.
-Haidong Wang and Zhiyong Li are the corresponding authors.
-
-\bibliographystyle{IEEEtran}
-\bibliography{reference}
-
-%\appendices
-%\section{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-
-%\section{}
-%Appendix two text goes here.
-
-% use section* for acknowledgment
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-%\begin{IEEEbiography}{Michael Shell}
-%Biography text here.
-%\end{IEEEbiography}
-
-% if you will not have a photo at all:
-%\begin{IEEEbiographynophoto}{John Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-%
-%\begin{IEEEbiographynophoto}{Jane Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Authors/HaidongWang.eps}}]{Haidong Wang}
-	 received the B.E.
-degree in Computer Science and Technology from Hunan University Of Technology and Business, Changsha, China, in 2014, and the M.Sc.
-degree in Computer Technology from the University of Chinese Academy of Sciences (UCAS), Beijing, 	China, in 2017.
-At present, he is currently pursuing the Ph.D.
-degree in Hunan University, Changsha, China.
-His current research interests include machine learning,  multi-object tracking and reinforcement learning.
-\end{IEEEbiography}
-
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Authors/ZhiyongLi.eps}}]{Zhiyong Li}
-%	received the MSc degree in System Engineering from National University of Defense Technology, Changsha, China, in 1996 and PhD degree in Control Theory and Control Engineering from Hunan University, Changsha, China, in 2004.
-%	Since 2004, he joined the College of Computer Science and Electronic Engineering of Hunan University. 
-%	Now, he is a Full Professor with Hunan University, member of IEEE, China Computer Federation (CCF) and Chinese Association for Artificial Intelligence (CAAI). 
-%	His research interests include Intelligent Perception and Autonomous Moving Body, Machine Learning and Industrial Big Data, Intelligent Optimization Algorithms with Applications.
-He has published more than 100 papers in international journals and conferences.
-%\end{IEEEbiography}
-%
-%
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Authors/XuanHe.eps}}]{Xuan He}
-%	received her B.S.
-and M.S.
-degree from Hunan Normal University (HNU), China, in 2016 and 2020.
-She is currently pursuing the Ph.D.
-degree in Computer science and technology with Hunan  University.
-Her research interests include object detection and recognition, machine learning.
-%\end{IEEEbiography}
-%
-%
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Authors/KeNai.eps}}]{Ke Nai}
-%	received the Ph.D.
-degree in Computer Science and Technology from Hunan University, Changsha, China, in 2019.
-Currently, he is working as a Postdoctoral Researcher at Hunan University.
-His current research interests include visual tracking, face recognition, computer vision, pattern recognition and machine learning.
-He has published several papers in IEEE-TIP, Information Sciences, Knowledge Based Systems, Neural Computing and Applications, ICIP2019 and so on.
-%\end{IEEEbiography}
-%
-%
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Authors/MingWen.eps}}]{Ming Wen}
-%	 received his M.S.
-degree and Ph.D.
-degree from Hunan University in 2006 and 2010, respectively.
-He has been a senior engineer at State Grid Hunan Electric Power Company Limited Economical \& Technical Research Institute.
-His research interests include energy internet demand forecasting, electricity price, smart grid, renewable energy accommodation and power system planning.
-%\end{IEEEbiography}
-
-% that's all folks
+\backmatter
+
+\bmhead{Supplementary information}
+
+If your article has accompanying supplementary file/s please state so here.
+
+Authors reporting data from electrophoretic gels and blots should supply the full unprocessed scans for key as part of their Supplementary information.
+This may be requested by the editorial team/s if it is missing.
+
+Please refer to Journal-level guidance for any specific requirements.
+
+\bmhead{Acknowledgments}
+
+Acknowledgments are not compulsory. Where included they should be brief. Grant or contribution numbers may be acknowledged.
+
+Please refer to Journal-level guidance for any specific requirements.
+
+\section*{Declarations}
+
+Some journals require declarations to be submitted in a standardised format.
+Please check the Instructions for Authors of the journal to which you are submitting to see if you need to complete this section.
+If yes, your manuscript must contain the following sections under the heading `Declarations':
+
+\begin{itemize}
+\item Funding
+\item Conflict of interest/Competing interests (check journal-specific guidelines for which heading to use)
+\item Ethics approval 
+\item Consent to participate
+\item Consent for publication
+\item Availability of data and materials
+\item Code availability 
+\item Authors' contributions
+\end{itemize}
+
+\noindent
+If any of the sections are not relevant to your manuscript, please include the heading and write `Not applicable' for that section.
+
+%%===================================================%%
+%% For presentation purpose, we have included        %%
+%% \bigskip command. please ignore this.             %%
+%%===================================================%%
+\bigskip
+\begin{flushleft}%
+Editorial Policies for:
+
+\bigskip\noindent
+Springer journals and proceedings: \url{https://www.springer.com/gp/editorial-policies}
+
+\bigskip\noindent
+Nature Portfolio journals: \url{https://www.nature.com/nature-research/editorial-policies}
+
+\bigskip\noindent
+\textit{Scientific Reports}: \url{https://www.nature.com/srep/journal-policies/editorial-policies}
+
+\bigskip\noindent
+BMC journals: \url{https://www.biomedcentral.com/getpublished/editorial-policies}
+\end{flushleft}
+
+\begin{appendices}
+
+\section{Section title of first appendix}\label{secA1}
+
+An appendix contains supplementary information that is not an essential part of the text itself but which may be helpful in providing a more comprehensive understanding of the research problem or it is information that is too cumbersome to be included in the body of the paper.
+
+%%=============================================%%
+%% For submissions to Nature Portfolio Journals %%
+%% please use the heading ``Extended Data''.   %%
+%%=============================================%%
+
+%%=============================================================%%
+%% Sample for another appendix section			       %%
+%%=============================================================%%
+
+%% \section{Example of another appendix section}\label{secA2}%
+%% Appendices may be used for helpful, supporting or essential material that would otherwise 
+%% clutter, break up or be distracting to the text. Appendices can consist of sections, figures, 
+%% tables and equations etc.
+
+\end{appendices}
+
+%%===========================================================================================%%
+%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
+%% system, please include the references within the manuscript file itself. You may do this  %%
+%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
+%% file, and delete the associated \verb+\bibliography+ commands.                            %%
+%%===========================================================================================%%
+
+\bibliography{sn-bibliography}% common bib file
+%% if required, the content of .bbl file can be included here once bbl is generated
+%%\input sn-article.bbl
+
+%% Default %%
+%%\input sn-sample-bib.tex%
+
 \end{document}
-
-% C#:  https://www.monodevelop.com/download/#fndtn-download-lin-ubuntu

### 2023-06-05 visual/face/latex/sn-bibliography.tex
init

--- 2023-06-05 visual/face/latex/sn-article.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                                                 %%
-%% Please do not use \input{...} to include other tex files.       %%
-%% Submit your LaTeX manuscript as one .tex document.              %%
-%%                                                                 %%
-%% All additional figures and files should be attached             %%
-%% separately and not embedded in the \TeX\ document itself.       %%
-%%                                                                 %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing
-
-%%=======================================================%%
-%% to print line numbers in the margin use lineno option %%
-%%=======================================================%%
-
-%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
-
-%%======================================================%%
-%% to compile with pdflatex/xelatex use pdflatex option %%
-%%======================================================%%
-
-%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
-
-%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
-\documentclass[sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
-%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
-%%\documentclass[sn-vancouver]{sn-jnl}% Vancouver Reference Style
-%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style
-%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
-%%\documentclass[sn-standardnature]{sn-jnl}% Standard Nature Portfolio Reference Style
-%%\documentclass[default]{sn-jnl}% Default
-%%\documentclass[default,iicol]{sn-jnl}% Default with double column layout
-
-%%%% Standard Packages
-%%<additional latex packages if required can be included here>
-%%%%
-
-%%%%%=============================================================================%%%%
-%%%%  Remarks: This template is provided to aid authors with the preparation
-%%%%  of original research articles intended for submission to journals published 
-%%%%  by Springer Nature. The guidance has been prepared in partnership with 
-%%%%  production teams to conform to Springer Nature technical requirements. 
-%%%%  Editorial and presentation requirements differ among journal portfolios and 
-%%%%  research disciplines. You may find sections in this template are irrelevant 
-%%%%  to your work and are empowered to omit any such section if allowed by the 
-%%%%  journal you intend to submit to. The submission guidelines and policies 
-%%%%  of the journal take precedence. A detailed User Manual is available in the 
-%%%%  template package for technical guidance.
-%%%%%=============================================================================%%%%
-
-\jyear{2021}%
-
-%% as per the requirement new theorem styles can be included as shown below
-\theoremstyle{thmstyleone}%
-\newtheorem{theorem}{Theorem}%  meant for continuous numbers
-%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
-%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
-\newtheorem{proposition}[theorem]{Proposition}% 
-%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
-
-\theoremstyle{thmstyletwo}%
-\newtheorem{example}{Example}%
-\newtheorem{remark}{Remark}%
-
-\theoremstyle{thmstylethree}%
-\newtheorem{definition}{Definition}%
-
-\raggedbottom
-%%\unnumbered% uncomment this for unnumbered level heads
-
+%% 代码没有生成 fig_5_a-f_1.pdf, fig_1_d.pdf ？
+%% Copyright 2007-2019 Elsevier Ltd
+%% 
+%% This file is part of the 'Elsarticle Bundle'.
+%% ---------------------------------------------
+%% 
+%% It may be distributed under the conditions of the LaTeX Project Public
+%% License, either version 1.2 of this license or (at your option) any
+%% later version.  The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.2 or later is part of all distributions of LaTeX
+%% version 1999/12/01 or later.
+%% 
+%% The list of all files belonging to the 'Elsarticle Bundle' is
+%% given in the file `manifest.txt'.
+%%
+
+%% Template article for Elsevier's document class `elsarticle'
+%% with numbered style bibliographic references
+%% SP 2008/03/01
+%%
+%% 
+%%
+%% $Id: elsarticle-template-num.tex 168 2019-02-25 07:15:41Z apu.v $
+%%
+%%
+%\documentclass[preprint,12pt]{elsarticle}
+%\documentclass[final,1p,times,twocolumn]{elsarticle} 
+\documentclass[final,3p,times,twocolumn]{elsarticle}
+%% Use the option review to obtain double line spacing
+%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+%% \documentclass[final,1p,times]{elsarticle}
+% \documentclass[final,1p,times,twocolumn]{elsarticle}
+%% \documentclass[final,3p,times]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
+%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+%% For including figures, graphicx.sty has been loaded in
+%% elsarticle.cls. If you prefer to use the old commands
+%% please give \usepackage{epsfig}
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
+%% The amsthm package provides extended theorem environments
+%% \usepackage{amsthm}
+
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers.
+%% \usepackage{lineno}
+
+\graphicspath{{image/}}
 \usepackage{float}
@@
  % 设置超链接跳转
-%\usepackage[colorlinks,
-%linkcolor=blue,
-%anchorcolor=blue,
-%citecolor=blue]{hyperref} 
+\usepackage[colorlinks,
+            linkcolor=blue,
+            anchorcolor=blue,
+            citecolor=blue]{hyperref} 
 \usepackage{amsmath}
@@
 
+\journal{Neurocomputing}
+
 \begin{document}
 
-\title[Article Title]{Article Title}
-
-%%=============================================================%%
-%% Prefix	-> \pfx{Dr}
-%% GivenName	-> \fnm{Joergen W.}
-%% Particle	-> \spfx{van der} -> surname prefix
-%% FamilyName	-> \sur{Ploeg}
-%% Suffix	-> \sfx{IV}
-%% NatureName	-> \tanm{Poet Laureate} -> Title after name
-%% Degrees	-> \dgr{MSc, PhD}
-%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate} 
-%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
-%%=============================================================%%
-
-\author*[1,2]{\fnm{Haidong} \sur{Wang}}\email{wanghaidong@hutb.edu.cn}
-
-\author[2,3]{\fnm{Second} \sur{Author}}\email{iiauthor@gmail.com}
-\equalcont{These authors contributed equally to this work.}
-
-\author[1,2]{\fnm{Third} \sur{Author}}\email{iiiauthor@gmail.com}
-\equalcont{These authors contributed equally to this work.}
-
-\affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}
-
-\affil[2]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{10587}, \state{State}, \country{Country}}}
-
-\affil[3]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{610101}, \state{State}, \country{Country}}}
-
-%%==================================%%
-%% sample for unstructured abstract %%
-%%==================================%%
-
-\abstract{Inspired by neuroanatomy, deep neural networks (DNNs) have recently developed from shallow network structures to exceedingly deep structures, providing excellent recognition performance.
+\begin{frontmatter}
+
+%% Title, authors and addresses
+
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for theassociated footnote;
+%% use the fnref command within \author or \address for footnotes;
+%% use the fntext command for theassociated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for theassociated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%% \title{Title\tnoteref{label1}}
+%% \tnotetext[label1]{}
+%% \author{Name\corref{cor1}\fnref{label2}}
+%% \ead{email address}
+%% \ead[url]{home page}
+%% \fntext[label2]{}
+%% \cortext[cor1]{}
+%% \address{Address\fnref{label3}}
+%% \fntext[label3]{}
+
+% Brain-like Auditory Network
+\title{BAN: Neuroanatomical Aligning in Face Detection between \\Deep Neural Network and Human Brain}
+
+%% use optional labels to link authors explicitly to addresses:
+ \author[label1]{Haidong Wang}
+ \ead{haidong@hnu.edu.cn}
+ \author[label1]{Zhiyong Li\corref{cor1}}
+ \ead{zhiyong.li@hnu.edu.cn}
+ \author[label1]{Ke Nai}
+ \ead{naike\_hnu@hnu.edu.cn}
+ \author[label1]{Jin Yuan}
+ \ead{yuanjin@hnu.edu.cn}
+ \author[label2]{Shutao Li}
+ \ead{shutao\_li@hnu.edu.cn}
+ \author[label3]{Xianghua Li}
+ \ead{493630379@qq.com}
+ \address[label1]{College of Computer Science and Electronic Engineering, Hunan University, Changsha, China}
+ \address[label2]{College of Electrical and Information Engineering, Hunan University, Changsha, China}
+ \address[label3]{State Grid Hunan Electric Power Company Limited Economical and Technical Research Institute, Changsha, China}
+\cortext[cor1]{Corresponding authors.}
+
+%\author{}
+%
+%\address{}
+
+\begin{abstract}
+Inspired by neuroanatomy, deep neural networks (DNNs) have recently developed from shallow network structures to exceedingly deep structures, providing excellent recognition performance.
 However, standard DNNs usually do not easily connect with brain areas on account of their excessive network depth and absent biological constraints, such as recurrent connections. 
@@
 In summary, this research builds a BTN, a brain-like and recurrent DNN, as the first model of the cortical pathway of smooth pursuit.
+\end{abstract}
+
+\begin{keyword}
+%% keywords here, in the form: keyword \sep keyword
+
+%% PACS codes here, in the form: \PACS code \sep code
+
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+Visual object tracking \sep deep neural network \sep neuroscience \sep smooth pursuit
+
+\end{keyword}
+
+\end{frontmatter}
+
+%% \linenumbers
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=6.7in]{figs/introduction.pdf}
+	\caption{
+		\textbf{
+		Collaborative design between a DNN and neuroanatomy with a BTS.} 
+		Through the quantitative brain-like score, we refer to the human brain and utilize acquired knowledge to enlighten the design of the BTN. 
+		The BTN includes four regions that are mapped into the 		primary visual cortex (V1), 
+		the middle temporal and medial superior temporal areas (MT/MST), the frontal eye field (FEF) and the brainstem/cerebellum. 
+		CONV\textsubscript{V1} is the classical convolutional layer and performs preprocessing to reduce the data size.
+		The DFN\textsubscript{MT/MST} is dynamic filter network, and the RNN\textsubscript{FEF} is recurrent, as depicted in Section~\ref{sec:cornet_s_def} for details.
+		The the upper-right image corresponds to the tracking activation and bounding box in the brain-aligned models, 
+		while lower-right image represents the cortical activation and eye gaze position with the stimulus in the far left,
+		which demonstrates the relationship between computer vision tracking performance and brain tracking response with the BTS, as depicted in Section~\ref{sec:results1}.
 	}
-
-%%================================%%
-%% Sample for structured abstract %%
-%%================================%%
-
-% \abstract{\textbf{Purpose:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
-The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
-As a guide the abstract should not exceed 200 words.
-Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
-% 
-% \textbf{Methods:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
-The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
-As a guide the abstract should not exceed 200 words.
-Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
-% 
-% \textbf{Results:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
-The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
-As a guide the abstract should not exceed 200 words.
-Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
-% 
-% \textbf{Conclusion:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
-The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
-As a guide the abstract should not exceed 200 words.
-Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.}
-
-\keywords{keyword1, Keyword2, Keyword3, Keyword4}
-
-%%\pacs[JEL Classification]{D8, H51}
-
-%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}
-
-\maketitle
-
-\section{Introduction}\label{sec1}
-
+	\label{fig:introduction}
+\end{figure*}
+
+\section{Introduction}
 % /data3/dong/data/brain/auditory/Music_Genre_Classification_Pytorch-master/report.pdf, 1. Music
@@
 
-\section{Results}\label{sec2}
+% 原论文主要说明发现的现象
+\section{Results}
 
@@
 
-\section{Discussion}\label{sec12}
-
+\section{Discussion}
 We showed that a biologically inspired DNN develops face-selective units without training, solely from statistical variations of the feedforward projections.
@@
 These findings may provide insight into the origin of innate cognitive functions in both biological and artificial neural networks.
+
+% todo
 
@@
 
-\section{Conclusion}\label{sec13}
+\section{CONCLUSION}
 Inspired by the visual processing mechanisms found in the human brain, our study presents a brain-like tracking model suited to the problem of visual object tracking. 
@@
 
-\backmatter
-
-\bmhead{Supplementary information}
-
-If your article has accompanying supplementary file/s please state so here.
-
-Authors reporting data from electrophoretic gels and blots should supply the full unprocessed scans for key as part of their Supplementary information.
-This may be requested by the editorial team/s if it is missing.
-
-Please refer to Journal-level guidance for any specific requirements.
-
-\bmhead{Acknowledgments}
-
-Acknowledgments are not compulsory. Where included they should be brief. Grant or contribution numbers may be acknowledged.
-
-Please refer to Journal-level guidance for any specific requirements.
-
-\section*{Declarations}
-
-Some journals require declarations to be submitted in a standardised format.
-Please check the Instructions for Authors of the journal to which you are submitting to see if you need to complete this section.
-If yes, your manuscript must contain the following sections under the heading `Declarations':
-
-\begin{itemize}
-\item Funding
-\item Conflict of interest/Competing interests (check journal-specific guidelines for which heading to use)
-\item Ethics approval 
-\item Consent to participate
-\item Consent for publication
-\item Availability of data and materials
-\item Code availability 
-\item Authors' contributions
-\end{itemize}
-
-\noindent
-If any of the sections are not relevant to your manuscript, please include the heading and write `Not applicable' for that section.
-
-%%===================================================%%
-%% For presentation purpose, we have included        %%
-%% \bigskip command. please ignore this.             %%
-%%===================================================%%
-\bigskip
-\begin{flushleft}%
-Editorial Policies for:
-
-\bigskip\noindent
-Springer journals and proceedings: \url{https://www.springer.com/gp/editorial-policies}
-
-\bigskip\noindent
-Nature Portfolio journals: \url{https://www.nature.com/nature-research/editorial-policies}
-
-\bigskip\noindent
-\textit{Scientific Reports}: \url{https://www.nature.com/srep/journal-policies/editorial-policies}
-
-\bigskip\noindent
-BMC journals: \url{https://www.biomedcentral.com/getpublished/editorial-policies}
-\end{flushleft}
-
-\begin{appendices}
-
-\section{Section title of first appendix}\label{secA1}
-
-An appendix contains supplementary information that is not an essential part of the text itself but which may be helpful in providing a more comprehensive understanding of the research problem or it is information that is too cumbersome to be included in the body of the paper.
-
-%%=============================================%%
-%% For submissions to Nature Portfolio Journals %%
-%% please use the heading ``Extended Data''.   %%
-%%=============================================%%
-
-%%=============================================================%%
-%% Sample for another appendix section			       %%
-%%=============================================================%%
-
-%% \section{Example of another appendix section}\label{secA2}%
-%% Appendices may be used for helpful, supporting or essential material that would otherwise 
-%% clutter, break up or be distracting to the text. Appendices can consist of sections, figures, 
-%% tables and equations etc.
-
-\end{appendices}
-
-%%===========================================================================================%%
-%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
-%% system, please include the references within the manuscript file itself. You may do this  %%
-%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
-%% file, and delete the associated \verb+\bibliography+ commands.                            %%
-%%===========================================================================================%%
-
-\bibliography{sn-bibliography}% common bib file
-%% if required, the content of .bbl file can be included here once bbl is generated
-%%\input sn-article.bbl
-
-%% Default %%
-%%\input sn-sample-bib.tex%
-
+\section*{Acknowledgements}This work was partially supported by National Key Research and Development Program of China (No.2018YFB1308604), National Natural Science Foundation of China (No.61976086,62106071), Hunan Innovation Technology Investment Project (No.2019GK5061), and Special Project of Foshan Science and Technology Innovation Team (No. FS0AA-KJ919-4402-0069).
+\label{}
+
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+%% \appendix
+
+%% \section{}
+%% \label{}
+
+%% If you have bibdatabase file and want bibtex to generate the
+%% bibitems, please use
+%%
+%%  \bibliographystyle{elsarticle-num} 
+%%  \bibliography{<your bibdatabase>}
+
+%% else use the following coding to input the bibitems directly in the
+%% TeX file.
+
+\bibliographystyle{elsarticle-num} 
+\bibliography{references}
+%
+%\begin{thebibliography}{00}
+%
+%%% \bibitem{label}
+%%% Text of bibliographic item
+%
+%\bibitem{}
+%
+%\end{thebibliography}
 \end{document}
+\endinput
+%%
+%% End of file `elsarticle-template-num.tex'.

### 2023-06-05 visual/nsfc/visual.tex
init

%!TEX program = xelatex 
% 告诉 texstudio， 无论默认编译器什么设置， 本 tex 文档都采用 xelatex 编译
% 参考：https://github.com/YimianDai/iNSFC

% 问题：参考文献为问号
% 解决：配置bibtex
% D:/matlab/latex/bin/win32/bibtex.exe

% 神经代码：F1205

% 科研处：http://kyc.hutb.edu.cn/show_content.php?id=5559

\documentclass[a4paper,zihao=-4]{article}
\usepackage[UTF8,punct,linespread=1.56]{ctex}
% \documentclass[a4paper,cs4size,UTF8,punct,linespread=1.56]{ctexart}
\pagestyle{empty} % 第二页以后页码空白
\usepackage[a4paper, left = 3.2cm, right = 3.2cm, top = 2.54cm, bottom = 2.54cm]{geometry}

% 解决下划线不换行
\usepackage{ulem}
\usepackage{CJKulem}

\usepackage{xcolor}
% \usepackage[citebordercolor = white]{hyperref}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{times}
\usepackage[subrefformat=parens,labelformat=parens]{subfig} %
\usepackage{booktabs} % for \toprule \midrule \bottomrule \cmidrule
\usepackage{cleveref}
\crefformat{table}{表~#2#1#3}
\crefformat{figure}{图~#2#1#3}
\crefformat{equation}{式~（#2#1#3）}
\usepackage{enumitem}
% \setenumerate[1]{itemsep = 0pt, parsep = 0pt, topsep = 2bp}
\setlist[enumerate]{itemsep = 0pt, parsep = 0pt, topsep = 2bp}
% \setitemize[1]{itemsep = 0pt, parsep = 0pt, topsep = 2bp}
\setlist[itemize]{itemsep = 0pt, parsep = 0pt, topsep = 2bp}
\usepackage{fontspec}
\setmainfont{Times New Roman}
% \usepackage{minted}   % For syntax highlighting
% \usemintedstyle{friendly}
\usepackage{setspace} 
\usepackage{caption}
\DeclareCaptionFont{capfont}{\kaishu\zihao{-4}\selectfont} % Caption font
\DeclareCaptionFont{subfont}{\kaishu\zihao{5}\selectfont} % Sub-caption font
\captionsetup{font = capfont}
\captionsetup[subfigure]{font = subfont}
\captionsetup[figure]{labelsep=space} % 空格 space；点 period；冒号 colon
\captionsetup[table]{labelsep=space}  % 空格 space；点 period；冒号 colon
\usepackage[square,numbers,sort&compress]{natbib}   % For Reference
\newcommand{\citess}[1]{\textsuperscript{\cite{#1}}}
\setlength{\bibsep}{1pt plus 0.3ex}
\usepackage{titlesec}
\titleformat{\subsubsection}[block]{\hspace{3em}}{\thesubsubsection}{1em}{}

% 使用.sty文件(insfc.sty)来单独存放常用格式设置，可避免每次书写.tex文档时重复书写类似导言
\usepackage{insfc}

\graphicspath{{images/}}   % 设置图片所存放的目录

\begin{document}

\kaishu

% Decrease space above and below equations
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}

%%%%%%%%% TITLE %%%%%%%%%
% \title{报告正文 \vspace{-3.4ex}}
% \title{报告正文}
% \maketitle
\begin{center}
	{\kaishu \zihao{2} \textbf{报告正文} \vspace{-3ex}}
\end{center}

\thispagestyle{empty} 　　　% 首页页码空白

%%%%%%%%% Your Content %%%%%%%%%
%{\kaishu \zihao{4}参照以下提纲撰写，要求内容翔实、清晰，层次分明，标题突出。}\alert{请勿删除或改动下述提纲标题及括号中的文字。\vspace{9bp}}

\NsfcChapter{（一）立项依据与研究内容}{（建议8000字以内）：}

\NsfcSection{1}{项目的立项依据}{（研究意义、国内外研究现状及发展动态分析，需结合科学研究发展趋势来论述科学意义；或结合国民经济和社会发展中迫切需要解决的关键科技问题来论述其应用前景。附主要参考文献目录）；}

\textcolor{NsfcBlue}{\subsection{研究意义}}
%\NsfcSection{研究意义}
近年来，人工智能技术发展突飞猛进，并以不可阻挡之势影响着社会和人们的生活。
许多国家和地区都将人工智能的发展作为提高国家实力、增强核心竞争力和建设现代化强国的核心所在。
例如，2020 年 3 月，中共中央政治局常委会提出将人工智能作为新型基础设施建设七大板块中的重要一项，以便更好地推动中国经济的转型和升级。
2021 年 3 月，美国国家人工智能安全委员会发布了《人工智能国家安全委员会最终报告》，提出推动人工智能以及相关技术的研究和应用，以解决国家安全和国防需求~\cite{schmidt2021national}。
而计算机视觉作为人工智能最重要的领域之一，正在成为科学研究和产业落地的重要方向。

基于深度神经网络的计算机视觉模型已经取得了巨大的进步~\cite{ILSVRC15}，然而随之而来的是越来越复杂的模型和可解释性的缺失，导致单目标跟踪算法难以扩展到多目标场景，并严重制约了模型的理解与实际应用。
尽管更深的深度神经网络确实能提高跟踪的精度，但这并不能提高神经网络模型和人脑的相似性~\cite{rajalingham2018large}。
深度学习发展初期部分人工神经网络模块可以映射到大脑皮层视觉通路的相应区域，然而随着模型的发展，比如 GoogleNet~\cite{szegedy2015going} 或 Inception-v4~\cite{szegedy2017inception}中，人工神经网络中众多复杂模块与大脑皮层中少量的视觉区域之间的关系越来越弱。
为了在模型中更准确地捕捉大脑皮层的处理模式，提高模型的可解释性和降低模型复杂性，仅仅基于传统视觉数据集进行模型架构搜索似乎不再是可行的解决方案。

在目标识别领域，深度模型在构建具有神经可解释的模型方面取得了一些成就~\cite{RN687}，
出现了一些设计类脑深度神经网络架构用于图像识别的工作~\cite{RN1115, RN688}。
其中的神经元能部分解释为什么人类大脑视觉皮层中的神经细胞对图像有特定的激活~\cite{RN1127,RN1144,RN1145,RN1535,RN1146,RN1100}。
这些模型也部分预测了灵长类图像分类的行为和评估~\cite{RN730,RN1139}，提高模型可解释性的同时降低了模型复杂度。
同时这些优秀的类脑模型能预测在人类大脑皮层通路中产生的激活模式~\cite{RN968}，为脑机接口的实现提供了很好的机会。

同时，随着人工智能的蓬勃发展，以图像分类、视觉目标跟踪、目标检测等任务为代表的计算机视觉领域也获得了广泛的关注并在理论研究和实际应用方面取得了巨大的进展。
作为人工智能与计算机视觉领域最重要的问题之一，视觉感知在智能驾驶系统、服务机器人和无人机等方面有着十分重要的应用。
随着深度学习和传统机器学习相关理论的发展与完善，封闭固定环境下的视觉感知已经达到了实际应用所需的性能要求。
一些面向封闭环境的视觉感知系统已经被用于现实生活中以保证人们的生命财产安全，比如家庭智能监控系统等。
与封闭环境下的视觉感知相比，开放环境下的视觉感知具有更为重要的应用价值和社会需求。
例如，对于智能驾驶系统来说，视觉感知功能是其完成智能决策所必不可少的组成部分。
一个稳定且可靠的智能驾驶系统必须在开放环境中准确地感知到智能车周边的不同目标（如车辆、行人等）以便做出合理的决策来规避潜在的交通风险，进而保证智能车的行车安全。
然而，开放环境下的视觉感知是一个非常具有挑战性的任务并且依然存在着诸多技术难点和挑战，这极大地限制了各类视觉感知方法的感知性能和在实际工程中的推广与使用~\cite{RN308}。
因此，深入研究面向开放环境的鲁棒视觉感知方法具有非常重要的理论研究意义和实际应用价值。
针对开放环境下的视觉感知任务，已有许多机器学习方法~\cite{smeulders2013visual}和深度网络模型\cite{li2018deep}被研究以进一步提高感知性能。
但是由于某些技术困难与挑战，这些方法无法获得理想的感知精度来完成从封闭环境到开放环境的有效跨越，也不能被真正地用于解决各种实际问题。
具体来说，开放环境下的感知主要存在以下几个方面的难点和挑战：

1）\textbf{视觉感知中的模型可解释性问题}。
随着深度学习在实际视觉场景中中使用的越来越多，日益复杂的深度模型时间复杂度高、训练和推理速度慢，无法用于实际场景。
%
一个完整的视觉感知系统主要包括目标识别和目标跟踪两个基础任务，其中目标识别主要用于提取区分不同目标的表征，目标跟踪则主要负责在视频序列中确定目标位置。
因此，为了追求更好的感知性能，主流的感知方法往往会学习到高度复杂的视觉感知模型。
以目前十分流行的目标的特征提取模型包括 vgg19~\cite{simonyan2014very}、resnet~\cite{he2016deep}、googlenet~\cite{szegedy2015going}等。
高度复杂的特征提取模型会极大增加模型的训练时间和推理时间，从而降低视觉感知方法的应用能力。
例如，在智能驾驶系统中，高度复杂的视觉感知模型将极大地降低感知方法的适应性，从而造成视觉感知方法不能在复杂的交通场景中准确地感知到智能车周围的重要目标以规避交通风险。
机器学习中的奥卡姆剃刀原则（Occam’s Razor）指出~\cite{ml_zhou}：在所有可以选择的模型当中，能够很好地解释已知数据并且十分简单才是最好的模型。
同时，凭借经验设计深度网络模型导致模型的可解释性能力差，极大的限制了视觉感知模型在现实场景中的推广和应用。
因此，如何降低视觉感知模型复杂度和提升模型的可解释性，以提高复杂场景下的感知适应性是开放环境下视觉感知的一个重大挑战。

2）\textbf{环境和目标动态变化}。
在动态开放环境下，目标自身会发生十分复杂的外观变化，这极大地增加了跟踪方法取得理想性能的难度。
目前主流的 OTB 数据集\cite{wu2013online}和每年举办的 VOT（Visual Object Tracking）\cite{kristan2019seventh}目标跟踪竞赛都把目标的外观变化分为多种类型，如：运动模糊、目标形变、光照变化、平面旋转等。值得一提的是，目标在某个时刻可能同时发生多种类型的外观变化，这将直接导致目标出现非常复杂的外观变化，进而限制跟踪方法在开放环境下的跟踪准确性。
能否成功地应对目标复杂的外观变化将决定跟踪方法的跟踪性能和在实际问题中的应用前景。
以刑事侦查中所依靠的天眼系统为例，如果目标在跟踪过程中所出现的复杂外观变化能够被有效地捕获，那么天眼系统将顺利地完成跟踪任务以确保社会安全，反之则系统可能在某一时刻跟丢目标，后果将十分严重。
综上所述，如何捕获目标所出现的复杂外观变化以提高跟踪准确性是开放环境下目标跟踪的又一个重大挑战。

3）\textbf{单一模态感知信息不足问题}。
在视觉感知过程中，场景中不仅有视觉信息，而且还会包含其他模态的信息。
因此，理想的感知模型必须综合考虑各种模态的输入信息以应对复杂场景下鲁棒性问题。
然而，目前主流的视觉感知方法依然不具备良好的多模态融合感知鲁棒性，实验室条件下的模型迁移到真实场景时经常会出现感知能力不足的问题，进而导致应用失败的结果。
对于ADAS系统（Advanced Driving Assistance System，高级驾驶辅助系统）和天眼系统等应用系统来说，能否综合利用其他模态的信息也在很大程度上决定着这些系统的性能和应用前景。
所以理想情况下能融合其他模型的信息，将在一定程度上提高模型的感知能力。
因此，如何解决单一模态感知信息不足的问题以保证跟踪鲁棒性也开放环境下感知的一个重大挑战。

针对上述挑战，本项目从模型的可解释性和精简压缩、环境和目标动态变化、单一模态信息感知能力不足等方面展开研究，
基于大脑皮层解剖对齐思想，解决开放环境下目标跟踪所面临的多个关键性科学问题，实现开放场景下的鲁棒视觉感知。
具体的研究工作包括：

（1）拟提出基于腹侧流解剖对齐的类脑精细化识别模型，主要解决由于跟踪模型复杂度过高和解释能力不足所引起的跟踪适应性问题；

（2）拟提出基于腹侧流和背侧流融合的类脑视觉跟踪模型，重点解决目标所出现的复杂外观变化以提高开放场景下的跟踪准确性；

（3）拟提出基于大脑皮层解剖对齐和全局工作空间的多模态融合模型，主要解决视觉感知过程中单一模态信息感知能力不足的问题以提高开放场景下的跟踪鲁棒性。
值得一提的是，由于上述三个工作分别从图像识别、目标跟踪和多模态融合角度出发以解决关键科学问题，因此工作（1）可以作为（2）的基础，同时（1）和（2）可以直接嵌入到工作（3）中以保证研究的整体性和统一性。
项目基于前期关于注意力机制\cite{nai2018robust,li2018visual}、类脑跟踪~\cite{nai2019multi,li2020reliable}、多任务学习等方法的研究基础，结合神经科学、多模态融合和全局工作空间等相关方法和理论，
拟提出基于腹侧流解剖对齐的类脑精细化识别模型、基于腹侧流和背侧流融合的类脑视觉跟踪模型、基于大脑皮层解剖对齐和全局工作空间的多模态融合模型，
解决开放场景下视觉感知任务中的可解释性、环境和目标动态变化挑战、单一模态信息感知能力不足等重要问题，
提高感知方法的视觉感知性能，实现开放环境下的类脑鲁棒视觉感知方法。
本课题具有十分重要的理论研究意义和实际应用价值，相关研究成果将为视觉感知的发展提供重要参考，并促进视觉感知方法在不同领域中的现实应用。

\textcolor{NsfcBlue}{\subsection{国内外研究现状及发展动态分析}}
\subsubsection{类脑目标识别研究现状}
% 参考：https://cloud.tencent.com/developer/article/1626780
视觉感知是人工智能领域最重要和最有挑战性的任务之一，具备十分重要的科学价值和应用价值。
近年来，许多视觉感知算法被提出以便在开放环境下取得理想的感知性能。
总的来说，视觉感知方法的基础任务包括两个：目标识别算法和目标跟踪算法。
而类脑识别方法作为一个新兴的方法，有解决模型可解释问题的潜力。

Kamitani等~\cite{horikawa2017generic}提出的基于深度学习的神经解码方法，研究了各种视觉特征与大脑视觉皮层各个脑区之间的对应关系，分析了计算机视觉模型和人脑视觉之间的联系和差异。
视觉编码模型~\cite{RN1519}要求通过模拟大脑视觉系统信息处理过程，预测不同外部图像刺激下的视觉皮层响应。
视觉信息解码模型~\cite{decoding_fMRI}能够根据视觉皮层响应预测响应自然图像刺激的内容，如图像目标语义类别、场景内容等。

张铁林等~\cite{zhang2018brain}提出的脉冲神经网络更新方法同时考虑了神经元的四个特性，包括神经元膜电位总是趋于稳态，神经元存在兴奋型和抑制型两类，神经元突触拥有短时可塑性，神经元之间存在逆向通路用于信号的反响传播，利用这四种特性，就可以使用简单的脉冲神经网络网络结构获得较好的图像分类结果，该研究既能保证脉冲神经网络仿生特性不减少，又能大幅提高图像分类准确率。
Naselaris等人\cite{st2018feature}提出的基于深度特征加权的神经编码模型，该研究基于群体感受野和多层特征加权思想构建了一个可解释的神经编码模型，相较于传统的编码模型，该方法效果更好，可解释性也更好。

% 
但由于学习得到的识别模型具有很高的复杂度，这些方法的识别速度和可解释性都会受到很大的影响。
由上可知，模型参数量更少和模型结构具有更好的解释性可以取得比其他方法更优的识别性能，具有更好地应用前景。
然而，在寻求更好的识别结果的同时，这些方法往往学习到高度复杂的识别模型。
当使用深度特征时，该类方法的模型复杂度将变得不可接受。
高度复杂的识别模型严重降低了识别方法对复杂场景的适应性。
因此，提出有效方法降低跟踪模型复杂度以提高开放场景下的识别适应性具有重要意义。

\subsubsection{视觉目标跟踪研究现状}

Zhongming Liu等~\cite{wen2018neural}提出的基于深度学习的神经编解码研究，该研究从动态视频刺激入手研究人脑对动态场景的编码和解码能力。采用 AlexNet 为基础深度学习网络，将视频刺激在 AlexNet 中的各层表征与大脑视觉皮层各个脑区建立关系，得出初级视觉皮层与神经网络的浅层特征相关性较高，而高级视觉皮层与神经网络深层次特征相关性较高的结论。
Horikawa等~\cite{horikawa2020neural}等证明利用动态视频诱发情绪在神经表征上是高维的、分类的，并且分布在跨模式的大脑区域中。
Shrestha等\cite{shrestha2018slayer}利用概率的方法解决了脉冲信号不可求导的问题，从而大幅提高了脉冲神经网络用于图像分类的准确率，还创新性地将脉冲神经网络用于动态图像识别、人体动作识别和音频识别，获得了非常好的实验效果。

通常使用人工合成刺激来研究人眼凝视，比如研究眼跳采用改变目标位置时眼睛注视的形式，而研究平滑跟踪则使用线性或者正弦运动的点。
使用人工合成数据最大的优势是拥有定义良好的属性和明显特征，特定的特征简化了眼球跟踪和血氧水平依赖信号的分析的过程。通过仅仅沿着一个独立的特征位置，可以进行理想的刺激调制，能更加精确地建立起特定脑区之间激活的联系。
但这些优势所牺牲的是人工合成数据并不能代表人类正常的视觉，实际有效的视觉输入会更加复杂，并且动态开放的环境中平滑跟踪不会单独出现，而是和眼跳和注视的序列混在一起。
因此，在单一背景上的人工合成刺激忽略了可能的背景信息、拥挤效应和全部眼睛运动规划流程的影响。
另外一个缺点是长时间的跟踪单一背景下的人工合成刺激会导致人注意力维持的降低。

特别是日常生活中，在动态背景上进行平滑跟踪，并行处理互相冲突的信息通常是必要的，这种情况下可能在不同方向上包含多个移动的目标。
值得注意的是从猴子的研究中得出结论：V5 不仅在平滑跟踪中，而且即使在视网膜上冲突时不同刺激之间的相互作用中也发挥重要的作用~\cite{neural_sp}。
然而，在自然条件下处理平滑跟踪眼睛运动所引起的动态视觉输入时必须非常小心。
然而即使是对于非常大且多样的数据集，最近计算机视觉领域所取得的进步已经开始能够自动理解动态开放的场景。
相比于人工合成的刺激，当使用不受限的动态自然刺激，在实验中如何利用运动眼睛的显示指令（比如：“跟踪这个点”、“当目标出现时进行眼跳”等），将凝视轨迹分成不同眼睛运动成分仍然很有挑战。
手动标注“真实数据”被认为是眼睛运动成分分类的黄金标准，对于每一秒的凝视信号，只有注视和眼跳能在4 到15 秒的时间内到达场景的任何地方~\cite{gold_standard}。
比如，StudyForrest 数据集中提供了大约30 小时的fMRI 和同步的凝视记录~\cite{gaze_forrest}。
因此，StudyForrest 数据集同时记录了视觉和非视觉线索相关的脑部激活，可以用来更好的进行眼睛运动成分的分类。

% 参考：https://blog.csdn.net/weixin_43741711/article/details/106071445
\subsubsection{多模态融合研究现状}

由于环境的复杂性，单一视觉数据所提供的信息已经不能满足机器认知能力的需求，与人类利用视觉、听觉、触觉等多种感官信息来感知世界类似，机器也需要模拟人类联觉来提升认知水平。
为了确保感知方法的鲁棒性，必须设计有效的方法解决视觉感知单一模态不足的问题。
其他模态的数据可以是音频、文本等描述同一对象的多媒体数据。
常见的信息融合方式有物理层融合、特征层融合、决策层融合几个类型。
物理层融合指在传感器层级对采集到的数据进行融合处理，即多传感器信息融合，在工业生产场景中最常见的信息融合方法。
特征层融合指在特征抽取和表达的层级对信息进行融合，例如对不同摄像头采集到的图像数据采用相同的特征表达形式，进而进行相应的叠加计算。
决策层融合指对不同模态的感知模型所输出的结果进行融合，这种融合方式对传感器性能和种类要求相对不高，但具有较大的信息损耗。

% 类脑其他模态(音频)
AVLnet\cite{rouditchenko2020avlnet}和PolyViT\cite{likhosherstov2021polyvit}融合了图像、视频和音频的的特征。
Jing Huang~\cite{huang2013audio}等使用深度信念网络进行视听语音识别，并使用来自音频和视觉特征的深度学习来进行噪声鲁棒语音识别。
CLIP~\cite{radford2021learning}可以有效地从自然语言监督中学习视觉概念。
Gota\cite{reed2022generalist}实现了多模型、多任务、多具象的多面手智能体。

% 全局工作空间
全局工作空间理论的核心主张是，心智状态在全局工作空间内广播时具有意识，额叶与顶叶区域的神经网络在全局工作空间中扮演着中心枢纽般的角色。
当局部处理系统（例如感觉区域）被点火时，其中的活动会暂时性地具有对工作空间的“可移动性”\cite{dehaene2001towards}。
对全局工作空间理论的实验证据支持包括，将意识与点火的神经元特征信号，或长程信息共享的神经元特征信号相关联的研究~\cite{dehaene2011experimental,mashour2020conscious,demertzi2019human,van2018threshold}。
在外界刺激发生约200-300ms之后，对应于有意识状态或无意识状态的试次，前部皮层区域的神经活动具有差异，这种差异被认为是“点火”的神经元特征信号。
这类实验包括“无报告范式”实验\cite{sergent2021bifurcation}（另见\cite{sergent2005timing}）。
这种研究最近已推广到解码领域。
例如，刺激后约300ms的神经活动模式能被用来预测主观报告，而且这种方法可在不同感知模态间泛化\cite{sanchez2020decoding}。
有意识或无意识的内容的长程信息传递特征已经使用一系列方法进行了鉴定\cite{mashour2020conscious,gaillard2009converging}。
意识知觉的第一个标志是双侧前额叶和顶叶强烈的放电活动。
意识知觉的第二个标志是正向慢波（P3波），有意识的知觉起始于270毫秒左右，在430毫秒时左右额叶和前扣带回中出现P3a波，580毫秒时活动又回到后侧的视觉区的P3b波（回归波）。
% 回归波也许是维持视觉表征的记忆（一瞬间的意识不能保存）
意识知觉的第三个标志是在刺激呈现大约300毫秒的时间里，$ \gamma $ 波大幅增加。
意识知觉的第四个标志是跨越整个皮质的巨大同步信号。
这些意识知觉的标志需要新的工具来理解这些复杂的模式，比如深度学习。

%
为了获得满意的融合性能，基于多模态融合的感知方法需要满足两个基本要求：
首先，多模态融合方法必须学习具有多样性的特征提取器以确保最终的特征提取器能够应对复杂多变的感知场景；
其次，所有特征提取器必须以合理的方式进行融合以保证融合特征能够对环境进行全面系统的感知。
然而，现存的基于多模态融合的感知方法无法很好的满足上述两个基本要求，这严重地限制了感知的鲁棒性和准确性。
由上可知，多样的类脑特征提取器和合理的融合策略是类脑多模态融合方法取得理想感知性能的关键，
前者保证感知方法可以成功应对感知过程中多变的场景，
后者则能确保感知方法能有效利用各种模态信息的。
设计高效的类脑多模态融合感知方法来消除单一模态感知能力不足的问题和对提高开放环境下感知的鲁棒性具有重要意义。

% 参考文献放这里
\begin{spacing}{1.3} % 行距
	\zihao{5} \songti   
	\bibliographystyle{gbt7714-nsfc}
	\bibliography{D:/BaiduSyncdisk/work/paper/doctor,ref}  
	\vspace{11bp}
\end{spacing}

\NsfcSection{2}{项目的研究内容、研究目标，以及拟解决的关键科学问题}{（此部分为重点阐述内容）；}

% 实现意图的判断，危险的规避
% 面向开放场景的鲁棒类脑视觉感知方法研究
% 机理、模型、应用
% 基于大脑皮层解剖对齐的类脑鲁棒视觉感知方法研究
% 科研处
\textcolor{NsfcBlue}{\subsection{研究目标}}
本项目以开放环境下的视觉感知所面临的\textbf{模型可解释低}、\textbf{环境和目标动态变化}和\textbf{单一模态信息不足等挑战出发}，
从解剖对齐的\textbf{类脑模型设计}、\textbf{运动感知}和\textbf{多模态融合框架设计}等方面展开研究，
聚焦深度学习、类脑模型、目标识别、视觉跟踪和多模态融合等相关理论与方法，
\textbf{重点突破基于大脑皮层解剖对齐的类脑精细化识别模型}、\textbf{基于大脑解剖对齐的类脑跟踪模型}、\textbf{基于大脑皮层解剖对齐的多模态融合模型等关键技术}，
研发面向开放环境的类脑鲁棒视觉感知算法，并利用\textbf{标准视频和神经记录数据集}、\textbf{ADAS高级智能驾驶辅助系统}和\textbf{真实智能车平台}相结合的实验手段进行算法验证与测试，
提高开放环境下的感知适应性、准确性和鲁棒性，
设计具有良好性能的视觉感知系统，推动类脑感知在实际问题中的具体应用，为实现开放环境下的类脑鲁棒视觉感知提供新技术和新方法。
图~\ref{fig:research}~展示了本项目的技术挑战、研究内容和关键科学问题。

% 字多
\begin{figure*}[htb!]
	\centering  
	{\includegraphics[width=1.0\textwidth]{"images/research"}
	}
	\caption{ 本项目整体研究思路与关系}
	\label{fig:research}
\end{figure*}

\textcolor{NsfcBlue}{\subsection{研究内容}}

\subsubsection{基于大脑解剖对齐的类脑精细化识别模型}
本项目针对开放环境下视觉感知所存在的模型可解释性问题，从类脑模型设计和精细化识别的角度出发，拟提出基于大脑解剖对齐的类脑精细化识别模型以限制跟踪模型复杂度，提升跟踪方法在开放环境下的可解释性和适应性。

% 机理、模型、应用
\begin{itemize}
	\item 掌握大脑识别机理方面的理论与方法，深入研究皮层识别脑区和类脑模块（例如：卷积神经网络和循环神经网络等）的识别模型对识别鲁棒性和可解释性的影响，了解类脑模型方法在各类计算机视觉任务中的具体应用；
	\item 将大脑解剖对齐的模型设计思想引入到类脑精细化识别模型当中，设计基于大脑结构约束的类脑识别模型，研究高效的目标识别算法以正确地感知视觉目标；
	\item 研究类脑模型各层的激活和大脑皮层对应脑区激活之间的相似性，设计相似性度量标准全量衡量中间层激活和人类识别行为选择，判断所提出模型的有效性和鲁棒性；
\end{itemize}

\subsubsection{基于腹侧流和背侧流融合的的类脑跟踪模型}
本项目针对目标在开放环境下所出现的复杂外观变化，从腹侧流识别和背侧流运动感知相互融合的角度出发，拟提出基于腹侧流和背侧流融合的类脑跟踪模型以有效地捕获目标所出现的复杂外观变化，提高视觉目标跟踪方法的可解释性、鲁棒性和准确性。

\begin{itemize}
	\item 研究循环等结构对人类和深度网络在视觉跟踪中的作用机理，分析腹侧流和背侧流在人类视觉目标跟踪中发挥的作用，以及不同结构和深度特征在不同跟踪场景下的跟踪性能；
	\item 利用腹侧流和背侧流的解剖结构和作用机理，设计基于解剖对齐的类脑鲁棒跟踪模型，并衡量类脑深度模型和大脑皮层在激活相应和跟踪行为输出之间的相似性；
	\item 在上述基础之上，研究类脑跟踪模型对腹侧流和背侧流相互作用的理解，提高跟踪的可解释性和准确性；
\end{itemize}

\subsubsection{基于大脑皮层解剖对齐的多模态融合感知模型}
本项目针对真实场景视觉感知过程中所出现的信息不足等问题，从感知框架的角度出发，拟提出基于大脑皮层解剖对齐的的多模态融合感知方法以解决特征不足的问题，提高感知模型在开放环境下的鲁棒性。

\begin{itemize}
	\item 研究和分析全局工作空间在类脑多模态融合感知模型中的应用，分析模型对感知性能的影响，以应对模型信息不足问题，提高模型在开放场景下的鲁棒性；
	\item 设计大脑皮层解剖对齐的类脑音频感知模型和音视频特征融合模型；
	\item 研究与探索类脑多模态融合感知方法在意图判断等方面的应用，进一步提高类脑感知方法在复杂场景下的鲁棒性；
\end{itemize}

综上所述，本项目旨在从模型可解释性、目标动态变化和融合框架设计等角度展开研究以设计具有鲁棒性的类脑视觉感知方法。
考虑到视觉感知系统中目标跟踪需要提取鲁棒的识别特征，所以研究内容一是研究内容二的基础。
同时其他模态的特征可以作为动态视频特征的一个补充，所以研究内容第二点又可以嵌入到研究内容第三点以保证项目研究的完整性。
因此，本项目的研究工作具有系统性和整体性。

\textcolor{NsfcBlue}{\subsection{拟解决的关键科学问题}}

本项目以开放环境下的视觉感知为研究对象，旨在设计鲁棒的类脑感知方法以获得更好的跟踪精度，拟解决如下关键科学问题：

\subsubsection{图像刺激下皮层激活信息的精细化编解码模型}
面向开放环境的目标识别方法需要具有良好的识别适应性以应对复杂多变的实际场景。
然而，为了获得更好的识别性能，主流的识别方法（如：深度学习方法）往往会学习到高度复杂的识别模型。
高度复杂的跟踪模型不仅计算代价大，而且深度模型的“黑盒”效应导致模型的可解释性低。
因此，如何对皮层激活的视觉信息进行精细化编解码，
如何对识别模型进行类脑设计和相似性度量，
以提高识别模型的可解释性和适应性是提高本项目拟解决的关键科学问题之一，也是提升开放环境下的识别性能所必须要解决的困难。

\subsubsection{时间序列皮层激活信息解码策略}
面向开放环境的视觉目标跟踪方法需要具有良好的跟踪适应性以应对复杂多变的跟踪场景。
然而，为了获得更好的跟踪性能，主流的跟踪方法（如深度学习方法）往往会学习到高度复杂的跟踪模型。
高度复杂的跟踪模型不仅计算代价大，而且模型的可解释性差。
同时大脑的皮层激活的时间序列特征提取相比于静态的激活信息解码更具有挑战性。
因此，如何对高度复杂的跟踪模型进行精简以提高模型的跟踪可解释性和适应性是提高本项目拟解决的关键科学问题之一，也是提升开放环境下的跟踪性能所必须要解决的困难。

%目标在开放环境下不可避免地会出现光照变化、平面旋转、剧烈形变和运动模糊等多种外观变化，进而产生十分复杂的外观变化。
%复杂的外观变化大大地增加了跟踪方法成功跟踪目标的难度，降低了跟踪方法开放环境下的跟踪准确性。
%研究表明，单个视觉特征往往不能有效地捕获目标所出现的复杂外观变化。
%考虑到不同的视觉能够从不同的角度对目标进行表示，融合多种视觉特征便成为应对目标复杂外观变化的一种可行方案。
%因此，如何设计具有强表示能力的多特征融合以捕获目标复杂的外观变化也是本项目拟解决的关键科学问题。

\subsubsection{提出多模态融合类脑处理策略}
开放场景下智能感知拥有丰富的输入信息，包括视觉、听觉等，仅使用视觉信息可能导致不能有效利用其他模态的信息。
而一个鲁棒的视觉感知系统系统必须具有良好的鲁棒性来适应各种场景。
因此，本项目以视觉和听觉融合的角度出发，以探索听觉解码策略并设计听觉皮层解剖对齐的类脑听觉模型为基础，考虑单一模态感知能力不足的问题。
如何设计具有强鲁棒性的多模态融合的类脑感知框架以消除单一模态感知信息不足的问题是本项目拟解决的又一关键科学问题。

% TODO
\NsfcSection{3}{拟采取的研究方案及可行性分析}{（包括研究方法、技术路线、实验手段、关键技术等说明）；}

\textcolor{NsfcBlue}{\subsection{研究方法与技术路线}}
该课题主要包括三个阶段：类脑图像识别的设计分析和建模、类脑跟踪的机理研究和仿真、类脑感知融合探索和研究。
本项目结合理论研究与实际应用，针对开放环境下的目标跟踪所面临的感知可解释性问题、环境和目标动态变化、单一模态感知信息不足等挑战，
采用计算机视觉、深度学习、神经科学、类脑模型、全局工作空间理论、多模态融合等方法、技术与理论，考虑公开视据集、ADAS智能驾驶辅助系统和真实智能车平台相结合的验证与测试方法，
研究基于腹侧流解剖对齐的类脑精细化识别模型、基于腹侧流和背侧流融合的类脑视觉跟踪模型和基于大脑解剖对齐和全局工作空间的多模态融合模型，提高开放环境下的跟踪性能。

以开放环境下的视觉感知为研究对象，本项目的研究工作分为相关问题分析、模型算法设计和方法验证测试三个层面（图~\ref{fig:route}~为技术路线）：

（1）相关问题分析：利用当前主流的视觉感知系统和公开视视频和神经激活数据集，深入分析模型可解释性问题、目标动态变化问题和视觉感知信息不足等挑战对视觉感知算法性能和鲁棒性的影响。
此外，结合计算机视觉、深度学习、神经科学等相关理论方法与申请人前期关于视觉感知课题所做的研究工作，从类脑精细化识别、基于背侧流和腹侧流融合的跟踪、类脑多模态融合框架设计等方面展开具体的研究工作。
具体来说，从跟踪模型精简与压缩的角度研究跟踪适应性问题的解决方法、从特征融合的角度研究目标复杂的外观变化的解决方法、从跟踪框架设计的角度研究模型漂移问题的解决方法。

（2）模型算法设计：基于对关键性科学问题的详细分析与申请人在视觉感知、深度学习、神经科学、类脑模型、类脑相似性度量、多模态融合等方面的相关工作，设计鲁棒的类脑感知方法解决（1）中的科学问题以获得更好的感知效果。
其中，提出类脑精细化识别模型、类脑跟踪模型、类脑听觉感知模型解决模型可解释性问题，提出基于腹侧流和背侧流融合的类脑视觉跟踪模型捕获环境和目标动态变化的挑战，提出基于大脑皮层解剖对齐和全局工作空间的多模态融合模型应对单一模态感知信息不足的问题。

（3）方法验证测试：为有效地评估（2）中所设计的视觉感知方法，采用标准数据集、项目申请人参加研发的 ADAS 高级智能驾驶辅助系统与真实智能车平台进行测试和验证，分析智能感知算法的感知性能、优势和不足，增强感知算法在实际应用中的可行性。

综上所述，本项目基于\underline{大脑解剖对齐原理}，重点研究开放环境下的\underline{视觉感知}，
以\underline{模型可解释性}、\underline{环境和目标动态变化}、\underline{单一模态感知信息不足问题}等科学问题为驱动，
采用“\underline{\textbf{相关问题分析->模型算法设计->方法验证测试}}”的技术路线，研究“{基于腹侧流解剖对齐的类脑精细化识别模型}、{基于腹侧流和背侧流融合的类脑视觉跟踪模型}、{基于大脑皮层解剖对齐和全局工作空间的多模态融合模型}”三个方面的相关理论与关键技术。

\begin{figure*}[htb!]
	\centering  
	{\includegraphics[width=1.0\textwidth]{"images/route"}
	}
	\caption{本项目整体研究思路与关系}
	\label{fig:route}
\end{figure*}

\textcolor{NsfcBlue}{\subsection{关键技术}}

\subsubsection{基于腹侧流解剖对齐的类脑精细化识别模型}

\textbf{1）类脑识别模型构建}

该研究设计的目标是在视觉深度神经网络（Deep Neural Networks，DNN）模型和大脑中的平滑跟踪通路之间获得高度的相似性，
同时遵循两个准则来设计类脑网络：

(1) \textbf{结构}：在性能相差不多的模型架构中，一般更加倾向于使用类脑模型，因为它模型复杂度低、更容易理解并且可以满足大脑的解剖约束。
使用深度神经网络是因为它们的神经元是数据处理的基本单元，并且深度神经网络中的所有神经激活都可以清晰地映射到大脑皮层激活。
除此之外，由于大脑皮层中广泛存在的循环连接，类脑视觉模型自然会考虑使用循环连接。
同时背侧和腹侧通路的激活也具有时间属性，因此也假定类脑模型会为时间序列生成激活响应。

(2) \textbf{功能}: 
在类脑模型中，满足神经解剖学约束的中间层激活响应和最终输出行为会有更准确的结果，
这使得设计的类脑模型能够更好地预测视觉皮层的激活和人的行为响应，
能同时满足计算机视觉目标跟踪预测和神经科学平滑跟踪预测的需求。

% 结构
图~\ref{fig:recognition_ch}~所示为基于大脑皮层解剖对齐的类脑跟踪模型技术架构。
根据大脑皮层视觉中腹侧流通路的研究，涉及目标识别的通路主要包括初级视觉皮层V1、纹外皮层 V2 和 V4、颞枕皮层 TEO、下颞皮层 IT，其中下颞皮层时目标识别的主要区域。
参照腹侧流通路的解剖结构，利用卷积和循环结构，构建大脑对齐的深度模型，可以设计相对应的类脑图像识别网络，并获得输入图像在深度网络中的激活响应，研究图像识别功能在大脑皮层和深度神经网络中表现的激活相似性。
\begin{figure*}[htb!]
	\centering  
	{\includegraphics[width=1.0\textwidth]{"images/recognition_ch"}
	}
	\caption{ 基于大脑皮层解剖对齐的类脑跟踪模型的架构图}
	\label{fig:recognition_ch}
\end{figure*}

% 响应的编解码
大脑视觉信息的处理过程是一个高度非线性变化，可以采用两阶段的线性化编码方式。
如图~\ref{fig:encoding_model}所示，首先通过非线性变换实现自然图像空间到图像特征空间的映射，然后通过线性变换，完成图像特征空间（比如循环神经网络）到体素响应空间（下颞皮层）的映射。
\begin{figure*}[htb!]
	\centering  
	{\includegraphics[width=1.0\textwidth]{"images/encoding_model"}
	}
	\caption{ 两阶段非线性视觉编码模型原理图}
	\label{fig:encoding_model}
\end{figure*}

\textbf{2）大脑数据分析}

在被试观看图像的过程中，采集被试的 fMRI 原始数据，然后使用 Statistical Parametric Mapping (SPM) 对原始数据进行三维重构、配准、头动校正等预处理操作，得到被试在观看不同图像刺激时对应的感兴趣视觉区域体素随时间变化的血氧水平依赖响应时间信号，反映了大脑对相应图像刺激的神经活动。
通常通过解卷积的方式得到血氧水平依赖响应信号的幅值，作为图像刺激对应的大脑视觉皮层体素的响应值。
一幅图像刺激对应的成千上万个体素的响应值组成了大脑视觉皮层对这一幅图像刺激的神经响应情况。
按照这种方式，可以得到每幅图像刺激对应的大脑视觉皮层体素响应向量，从而组成了最终的 fMRI 数据集。
另外，通常会选择多个被试进行相同的实验并采集和处理数据，从而包含多套被试的 fMRI 数据，用于后续验证计算模型在不同被试数据上的鲁棒性。
考虑到 fMRI 实验设计、数据采集及预处理等过程较为相似，本研究更加侧重通过预处理后的 fMRI 数据，针对自然图像刺激下的视觉信息解析任务设计符合视觉皮层信息表征特点的深度神经网络计算模型，分析和验证人类视觉信息处理机制和特征表达方式，探究深度神经网络与人类视觉信息处理的关系。
自然图像刺激下的 fMRI 视觉信息解析领域存在若干公开的 fMRI 实验数据库，这些数据被很多研究团队使用并公开发表大量相关研究工作，具有很高的可信度。
因此，本研究考虑到与前人实验结果进行比较，拟使用公开 fMRI 数据集进行类脑模型构建、验证、对比和分析。

\textbf{3）解码精度衡量}

% 解码
视觉分类模型首先在 fMRI 数据训练集上训练视觉皮层 fMRI 体素响应到图像场景语义类别的映射，然后，能够根据测试集中新的视觉皮层 fMRI 体素响应预测被试所观看图像刺激的场景语义类别。
通常视觉皮层中体素数量较多，即视觉皮层区域 fMRI 体素响应向量维度较高，且 fMRI 数据集规模较小，直接进行模型训练容易导致过拟合。
因此，在视觉皮层大量体素响应输入模型之前，通常从视觉区域中的大量体素中挑选一些重要的体素，降低用于后续视觉分类模型构建的输入维度，从而提高分类模型的准确性和鲁棒性。

拟采用基于体素激活的方法，将每个体素看作独立变量进行分析，通过对比每个体素与基线的激活响应程度，使用神经影像数据处理软件 SPM，根据一般线性模型(General Linear Model, GLM)，计算表征体素激活程度的系数，给每个体素进行打分。
最后按照得分从高到低的顺序选择一定数量的体素，也可以选择高于某个设定阈值的体素。

% 行为输出
同时进行进行神经度量和行为度量，利用类脑识别分数进行深度神经网络和大脑的对比，并利用设计并训练好的类脑模型，确定识别的图像模式分别在深度网络和大脑皮层中的位置，寻找图像识别的类别信息在深度网络中的表征模式与大脑中的激活特征之间的映射关系。

\subsubsection{基于背侧流解剖对齐的类脑平滑跟踪模型}

% 基于背侧流的类脑视觉跟踪模型

参照人类大脑皮层中背侧流通路进行类脑跟踪的机理研究和仿真，通过量化的大脑相似性分数，并利用所获得的皮层解剖知识来启发类脑跟踪模型的设计。

\textbf{1）类脑平滑跟踪模型设计}

如图~\ref{fig:tracking_ch}~所示，类脑跟踪模型包括映射到人脑的四个区域：初级视觉皮层，中颞和上颞内侧区、额叶视区和脑干/小脑。
初级视觉皮层使用经典的卷积层进行建模，执行预处理以减少数据大小。
中颞区和上颞内侧区使用动态滤波器网络进行建模，额叶视区使用循环神经网络进行建模。
对于最开始的输入刺激，神经网络的输出表示大脑对齐模型中的深度神经网络的激活响应和边界框，而大脑皮层在跟踪时的表示是大脑皮层的激活和眼睛注视的位置，同时类脑跟踪模型显示了计算机视觉跟踪性能与大脑跟踪响应之间的相似性关系。

为了比较模型，通过检查深度神经网络中各层的激活来构建到皮层的映射，以便能够很好地理解特定大脑皮层区域中的激活，理想情况下，这种大脑皮层激活不需要多余参数的类脑模型所预测得到，将会降低传统深度跟踪模型的冗余度。
因此类脑跟踪模型由卷积层、动态滤波网络、长短时记忆网络和全连接层四个神经网络模块组成，它们类比于大脑平滑跟踪皮层通路中的初级视觉皮层、中颞区和上颞内侧区、额叶视区、脑干/小脑，其中脑干/小脑是运动预测器，将额叶视区的输出转换为相应的运动响应。
这种明确的大脑分区思想是设计类脑跟踪模型重要的一步，并且致力于寻找更通用的网络结构。
整个模型包括在皮层区域没有差异的神经网络，以及各种改进类脑跟踪模型的连接。
并在此基础上对比激活和行为之间的相似性。

% 需要用jpg图像
\begin{figure*}[htb!]
	\centering  
	{\includegraphics[width=1.0\textwidth]{"images/tracking_ch"}
	}
	\caption{基于大脑皮层解剖对齐的类脑跟踪模型的架构图}
	\label{fig:tracking_ch}
\end{figure*}

\textbf{2）大脑数据分析}

本研究拟使用 SPM12 工具进行核磁共振数据的分析。
首先对每个 fMRI 记录利用标准的处理流程进行预处理。
包括对每个会话的平均图像进行功能性数据对齐，并将对齐后的数据与大脑解剖的 T1 扫描进行配准，
然后将其正则化到 MNI 模板，再重采样到 $3 \times 3 \times 3$立方毫米的体素中。
最终，在脉冲的半峰全宽上使用 8 毫米高斯核进行平滑。

在 StudyForrest 数据集的记录中，将整部电影刺激分割成 8 个不同的视频片段，每个大约 15 分钟，在扫描仪中分别展示给每个受试。
在第一阶段的个体分析中，
为了建模整个《阿甘正传》电影，将 8 个记录会话组合到一个设计矩阵中，每一行表示一个电影片段。
在设计矩阵的每个会话中，从同一受试观察不同的电影片段的凝视中回归出一个平滑跟踪回归变量、一个眼跳回归变量和一个电影运动回归变量。
为了考虑受试之间血液动力学响应开始时刻和宽度的变化，沿着时间和离散度梯度方向使用标准血液动力学响应函数（Hemodynamic Response Function，HRF）。
除了以上三个回归变量，还使用了从预处理重对齐步骤中得到的六个头部运动分量作为用于校正的干扰因素回归变量。

为了和扫描仪重复时间相一致，眼动和运动回归变量建模成有 2 秒间隔的事件序列，因此每个事件都被表示成两个扫描之间变化的回归变量。
每个事件的幅值都根据 2 秒时间窗口内对应的眼动或运动数目进行调整，当和整体均值相同时对应的值为 0。
在回归变量建模中，如果没有创建两个之间的强烈的正相关或者负相关，就不可能同时建模注视和平滑跟踪。
为了使注视和平滑跟踪相互依赖更加清晰，可以考虑受试开始跟踪一个目标。
然后随着注视幅值的减少，平滑跟踪回归变量的幅值就会成比例增加。

对每个受试数据独立地应用广义线性模型后，使用每个回归变量血液动力学响应函数的幅值部分（为了计算和平滑跟踪相关的感兴趣部分进行对比，该处理过程横跨了对应 8 个电影片段的 8 个记录会话）。
这些对比包括眼动和运动主要响应的对比、平滑跟踪和眼跳之间的对比，以及眼动和运动的对比。
最后，在第二阶段受试之间核磁共振分析中，对有效受试的第一阶段对比结果进行单样本 $t$ 检验。

\textbf{3）平滑跟踪皮层神经预测性}

皮层神经预测性是指在源系统中（比如深度神经网络）评估给定输入图像 $X$，预测在目标系统（比如视觉区域 V1 和 MT/MST）中的激活响应。
作为输入，该度量方法的评估过程为：刺激 $\times$ 神经网络 = 激活响应，这里的神经网络可以是深度人工神经网络，也可以是灵长类的大脑皮层。
并且源神经网络（深度人工神经网络）可以使用线性变换映射到目标神经网络（灵长类皮层网络）：
\begin{equation}
	y = Xw + \epsilon \mbox{，}
\end{equation}
这里 $w$ 表示线性回归的权重，$\epsilon$ 表示皮层记录的噪声。

此外还展示了类脑跟踪网络中最具预测性的网络层和特定的模型区域。

这些关系被拟合为从深度神经网络到大脑皮层的映射，并用这个映射关系来预测人的大脑皮层对视频帧的响应。
由于大脑的激活响应数据维度远远大于神经网络模型激活数据的维度，所以利用主成分分析（Principal Component Analysis, PCA）将大脑激活维度压缩到指定的维度来进行程序运行加速和相关性分析，
并利用来自 MT/MST 的激活来进行拟合。 
最终使用皮尔逊相关系数 $s_r$ 来衡量最终人工神经网络模型和视觉运动皮层的神经相似性分数，如下所示：
\begin{equation}
	s_r=\frac{\sum_{i=1}^{n} (y_i-\bar{y}) (y_i^\prime - \bar{y}^\prime) }{\sqrt{\sum_{i=1}^{n} (y_i - \bar{y})^2 (y_i^\prime - \bar{y}^\prime)^2 }}\mbox{，}
\end{equation}
其中 $y^\prime$ 是人工神经网络模型特定层的激活，$y$ 是人类大脑皮层特定区域的激活，$n$ 是深度神经网络中对应的特征维度，$\bar{y}$ 和 $\bar{y}^\prime$ 是所有神经响应值的中位数（使用中位数是因为响应通常是非正态分布）。

\subsubsection{基于腹侧流和背侧流融合的类脑视觉跟踪模型}
% 腹侧/背侧融合
% todo

类脑跟踪网络的处理流程如图~\ref{fig:tracking_pipeline} 所示，在平滑跟踪中发挥特定作用的大脑皮层区域用矩形框表示。
对于给定的输入帧 $F_t$ 和注意力参数 $a_t$，模仿空间注意力的中央凹从 $F_t$ 中选择包含目标的局部区域视图 $f_t$。
此外，在考虑外观特征 $\alpha_t$ 的基础上，使用包括初级视觉皮层 V1 的背侧和腹侧通路的外观选择器，获得跟踪目标更加精细的特征 $m_t$，并在 LSTM 中更新隐藏状态 $h_t$。
并将 FEF 的输出 $o_t$ 和背侧流输出 $d_t$ 合并输入到脑干/小脑模块中进行解码，
来预测下一帧的空间注意力 $a_{t+1}$ 、外观注意力 $\alpha_{t +1}$、眼位校正信号 $\Delta p$，甚至眼球运动信号 $\Delta p_t$。
所有黑色箭头表示信息在同一个时间步内流动，而灰色箭头代表不同时间步之间的连接。

\begin{figure*}[htb!]
	\centering  
	{\includegraphics[width=1.0\textwidth]{"images/tracking_pipeline"}
	}
	\caption{类脑视觉目标跟踪的网络架构}
	\label{fig:tracking_pipeline}
\end{figure*}

\textbf{BTN 架构}

% 处理流程
首先简要介绍 BTN 的处理流程，如图~\ref{fig:tracking_pipeline} 所示，在平滑跟踪中发挥特定作用的大脑皮层区域用矩形框表示。
对于给定的输入帧 $F_t$ 和注意力参数 $a_t$，模仿空间注意力的中央凹从 $F_t$ 中选择包含目标的局部区域视图 $f_t$。
此外，在考虑外观特征 $\alpha_t$ 的基础上，使用包括初级视觉皮层 V1 的背侧和腹侧通路的外观选择器，获得跟踪目标更加精细的特征 $m_t$，并在 LSTM 中更新隐藏状态 $h_t$。
并将 FEF 的输出 $o_t$ 和背侧流输出 $d_t$ 合并输入到脑干/小脑模块中进行解码，
来预测下一帧的空间注意力 $a_{t+1}$ 、外观注意力 $\alpha_{t +1}$、眼位校正信号 $\Delta p$，甚至眼球运动信号 $\Delta p_t$。
所有黑色箭头表示信息在同一个时间步内流动，而灰色箭头代表不同时间步之间的连接。
下面详细介绍类脑跟踪架构的每个模块。

\textbf{视网膜和背侧/腹侧通路}

视网膜上的空间选择器为当前帧 $F_t$ 选择中央凹视图 $f_t$，它的输出被输入到两条相互连接的腹侧/背侧通路。
腹侧通路识别被跟踪的目标，而背侧通路学习被跟踪目标的运动特征。
腹侧/背侧通路中的外观注意力由当前帧自下而上的中心凹视图信息 $f_t$ 和前一帧自上而下的外观注意力信息 $\alpha_{t+1}$ 所驱动。
然而，中央凹的空间注意力只依赖于空间注意力信息 $a_{t+1}$，
在这种情况下，自下而上的信息仅具有局部影响并依赖于某个位置的显著性输入，
但自上而下的信息将全局特征结合到局部分析中。

(1) \textbf{视网膜}: 
在类脑模型的处理流程中，根据空间注意力机制进行建模。
对于输入帧 $F_t \in R^{W \times H}$ 形成矩阵 $M_t^x \in R^{w \times W}$ 和 $M_t^y \in R^{h \times H}$，
矩阵中的每一行都包含一个高斯分布。
高斯分布的位置和宽度决定了输入帧的哪些部分被选为视网膜中的中央凹视图 $f_t$。
因此，中央凹视图 $f_t \in R^{h \times w}$ 可以表示为：
\begin{equation}
	f_t = M_t^y F_t (M_t^x)^T \mbox{，}
\end{equation}
用连续矩阵行的分布中心、步长和方差来表示注意力。
与循环注意力跟踪类似，只有步长和分布中心是通过 LSTM 预测的，而方差依赖于步长。
该操作在估计较小的方差时避免了过度的偏差，有助于提高学习的速度。
此外，中央凹 $f_t$ 的大小依赖于具体的实验分析。

(2) \textbf{腹侧通路}: 
腹侧通路（包括初级视觉皮层 V1）将中央凹视图 $f_t$ 转换为固定维度的外观表征向量 $v_t$，其中包括被跟踪目标的空间特征和外观特征，
具体地网络结构依赖于具体的实验分析。
在本章的腹侧通路架构中，使用卷积神经网络实现初级视觉皮层 V1，这是腹侧通路和背侧通路共享的模块。
然而，通常使用若干个卷积层和最大池化层来实现模仿人类初级视觉皮层 V1。
在这以后，处理流程分为背侧通路和腹侧通路。
最后，通过卷积神经网络提取被跟踪目标的特征 $v_t$，以实现腹侧通路功能。

(3) \textbf{背侧通路}: 
背侧通路（包括 V1 和 MT/MST）用于提取运动特征，将显著目标 $d_t$ 和中央凹视图中的背景进行分割。
使用动态滤波网络建模背侧通路（MT/MST），用于处理中央凹视图前景和背景之间的空间关系。
FC$(\cdot)$ 表示全连接层，
所以 MT/MST 中基于外观表示 $\alpha_t$ 动态预测卷积滤波器 $\phi_t$ 为：
\begin{equation}
	\left\{ \phi _t ^i \right\}_{i=1}^N = \text{FC}(\alpha_t) \mbox{，}
\end{equation}
V1 输出的的特征经过具有 $N$ 个卷积层的非线性滤波器，
然后，将其输出传递给卷积核大小为 $1 \times 1$ 的卷积和 Sigmoid 激活函数，将特征转换为二维掩码 $d_t$。
$d_t$ 中的每一点都表示被所跟踪目标占据的概率。

背侧通路的位置图是基于腹侧通路抽取的目标表示，这模拟了视觉系统中的噪声抑制机制。
因为在当前帧没有跟踪目标的表征时，LSTM 中的目标表征不会被覆盖，所以使用这种机制可以处理遮挡和漂移的情况。
因此，腹侧和背侧通路的输出可以被整合为：
\begin{equation}
	m_t = \text{FC}(conc(v_t \odot d_t)) \mbox{，}
\end{equation}
其中 $\odot$ 表示通过特征掩码执行显著目标提取的哈达玛积，
$conc$ 表示将矩阵的所有行连接成向量的连接运算符。

\textbf{额叶视区}

所提出的类脑跟踪方法性能取决于估计下一帧中目标外观和位置的能力。
因此，它在很大程度上依赖于跟踪目标状态的预测。
而 LSTM 可以利用时空和外观特征，使所提出的模型能够处理遮挡和漂移的情况，例如跟踪目标被其他干扰物遮挡的情况。

如图~\ref{fig:tracking_pipeline} 所示，将 LSTM 模块命名为 FEF，利用输出误差来预测眼球运动。
在平滑跟踪中，FEF 区域接受来自腹侧/背侧流的输出 $m_t$，
精调后的目标表征 $m_t$ 用于更新 FEF 中的隐藏状态 $h_t$，
并在 FEF 中存在类似的预测动作。
当模型训练过程中，被跟踪目标和眼球运动之间的延迟减少时，输出误差趋向于零。
因此，LSTM 需要即使在没有图像输入的情况下依然能够推断眼球的运动。
\begin{equation} \label{equ:c2:LSTM}
h_t, o_t = \text{LSTM}(h_{t-1}, m_t) \mbox{。}
\end{equation}

\textbf{脑干和小脑}

脑干和小脑一起（包括脑桥核、绒球、小脑蚓体和前庭核）使用全连接层进行建模，
然后利用背侧流的输出 $d_t$ 和额叶视区的输出 $o_t$ 来估计注意力 $a_{t+1}$ 和外观 $\alpha_{t+1}$，
最后通过动眼神经生成眼球运动信号 $\Delta p_t$。
\begin{equation} \label{equ:c2:FC}
\Delta p_t, \Delta a_{t+1}, \alpha_{t+1} = \text{FC}(conc(d_t), o_t) \mbox{，}
\end{equation}
\begin{equation} \label{equ:c2:attention}
a_{t+1} = a_t + tanh(c) \Delta a_{t+1} \mbox{，}
\end{equation}
其中 $c$ 是一个可训练参数，用较小的值进行初始化以限制训练期间模型更新的大小。
方程~\ref{equ:c2:LSTM} 到 ~\ref{equ:c2:attention} 描述信息更新的过程。
通过累积注意力变化来计算眼睛注视的位置，
学习空间注意力来估计下一帧中被跟踪目标的位置，并预测在时间 $t$ 相对于注意力的注视位置 $p_t$。
\begin{equation}
p_t = a_t + \Delta p_t \mbox{。}
\end{equation}

此外，参考脑干和小脑都可以利用反向动力学控制器进行建模的发现和想法，
基于动力学的平滑跟踪模型，这里假设反向动力学控制器是完美的，因此眼球的运动信号可以表示为：
\begin{equation}
\Delta p_t = \Delta p \mbox{，}
\end{equation}
其中 $\Delta p$ 是眼球运动的低通滤波器。
基于这个假设，在该研究中不需要实现反向动力学控制器。

\textbf{2）平稳跟踪样本的提取}

实验中每个凝视样本都包含一个四元组：时间、显示器坐标系下的横坐标 $x$ 和纵坐标 $y$、眼跟踪质量的置信度估计。
因为数据集使用的是单眼跟踪，所以置信度为 1 表示好的眼跟踪，而 0 表示跟踪丢失。
经数据检查后发现在所有受试中跟踪丢失的比例一般在 $1.2\%$ 和 $16.7\%$ 之间，而受试 5 和受试 20 跟踪丢失特别明显，丢失比例分别是 $86.7\%$ 和 $39.0\%$，所以将他们的数据从分析中剔除。
%
对余下的凝视样本利用一种比较有代表性的基于密度的聚类算法 MOSP 进行分类以得到平稳跟踪样本。
该算法在手动标注的公共数据集上和几个最新的眼动检测算法相比有很好的分类性能。
MOSP 算法的另一个优势是在程序中使用了简单且容易理解的门限值，这样保证在使用过程中比较容易进行调整，而不像一些深度学习方法的超参数调整困难。
这一步 MOSP 取得较高的平滑跟踪检测精度（比如较低的误检）对后续的分析非常重要。

MOSP 算法包括两个步骤，第一步负责眼跳检测，先将眼跳剔除，第二步负责区分注视和平滑跟踪。
眼跳检测算法使用一个高速度门限值和一个低速度门限值。
眼跳检测器使用高速门限值进行初始化，然后往门限值两端进行扩展，直到小于低速门限值。
使用大于输入样本之间噪声的高速门限值使算法对噪声更加鲁棒。
MOSP 算法的第二步是进一步处理眼跳间的间隔，通过给几乎可以确定是注视的样本赋予一个注视的标签。
余下的样本就标记为平滑跟踪的候选结果，并在所有受试中进行处理。
然后，只有当凝视样本密度大于某个门限值时才使用基于密度的聚类算法 DBSCAN 进行聚类。
基于密度的聚类算法能很好地检测出平滑跟踪是因为平滑跟踪的的两个属性。
% 
首先，只有在给定时间内刺激出现运动时，平滑跟踪才会出现；并且视频刺激中每一帧移动的目标数目较少。
%
第二个特点是移动的目标能吸引受试的注意力（特别是在电影中），并且它们经常会被超过一个受试所跟踪。
平滑跟踪的这两个属性使算法能够把真实的平滑跟踪从漂移和类平滑跟踪中区分开来，这对于 fMRI 实验中的平稳跟踪样本的提取特别重要。
即使一些凝视样本被错误的标记成候选平滑跟踪，只要在当前时间的相同区域其他受试没有相同的模式，那么它也不会被标记成平滑跟踪，通过这些机制提高算法的鲁棒性对识别与处理平滑跟踪相关的大脑区域特别重要。

由于原始的 MOSP 算法是针对 GazeCom 数据集进行设计和优化的，在本实验中对一些参数与进行了调整。
因为增加凝视轨迹的数目会提高平滑跟踪检测算法的精度，所以同时使用了不在核磁共振扫描仪里的记录（获取难度较小，且相比于扫描仪记录有更少的噪声）和在扫描仪里的记录。
尽管刺激大小不同，对不在扫描仪里的记录使用单位观测角中所包含的像素数来进行按比例缩放；
所以使用两个数据集进行平滑跟踪片段检测会有更高的置信度。

\textbf{3）评价指标：类脑跟踪分数}

这一部分介绍了衡量深度神经网络模型与人类大脑皮层之间的相似性的类脑跟踪分数 BTS。
BTS 是在特定实验数据集上测试的指标，包括眼动行为预测性和皮层神经预测性两个指标。

为了获得关于大脑相似性的量化指标，提出了类脑跟踪分数，用于评估跟踪模型类脑预测能力的指标：
(a) 对于 StudyForrest 数据集的每个输入视频帧，预测人眼跟踪目标时的平均人眼运动；
(b) 在 StudyForrest 数据集上预测人类视觉区域 MT/MST 中大脑皮层位置对每个输入视频帧的平均激活响应。

%所有眼动的娇娇
为了在统一指标上评估类脑跟踪网络，该指标计算了眼动行为预测性指标和皮层神经皮层预测性指标的平均值。

\textbf{眼动行为预测性}

眼动行为度量的目的是衡量对于特定任务深度神经网络输出与人眼行为输出之间的相似性。
在人眼目标跟踪中，被试者的注意力是一个与人瞳孔有关的圆形范围。
因此，将模型呈现的行为模式（眼睛注视的位置和瞳孔的大小）建模为圆形，并且它不同于视觉目标跟踪中的长方形边界框。
同时，由于该工作不仅仅是为了提高计算机的跟踪性能，更主要目的是实现类人的智能；
如果类脑跟踪网络获得了更好的行为相似性，就可以很好地预测眼睛注视的位置和范围。
否则会导致深度神经网络获得了完美的边界框拟合，却无法获得良好的人眼行为预测效果。

使用的 12 个视频序列是在自然背景下有一个显著的目标在移动，每个视频序列大约 20 秒，并利用眼动仪记录下受试的注视范围来表示跟踪显著目标，
并使用 12 个图像序列中的 149 张图像的受试眼球运动和深度神经网络预测来分析和评估所提出的模型的眼动行为预测性能。
总共的 149 帧图像中，每一帧都作为深度神经网络的输入，用于预测眼睛的注视范围。
然后通过每一帧中眼睛注意力的范围来衡量这种眼动行为预测性。

目标跟踪深度神经网络的输出结果是所跟踪目标的边界框，而受试的注意力是一个包含中心坐标 $x$、$y$ 和半径的圆形范围。
因此将眼动预测性或行为评分建模为实际眼睛注意的圆形范围 $S_{roi}^a$ 与深度神经网络预测边界框 $S_{roi}^b$ 之间的交并比（Intersection over Union，IoU），
并将所有帧序列中的整体行为指标~$s_b$ 作为眼动预测分数：
\begin{equation}
	s_b=\frac{area(S_{roi}^a \cap S_{roi}^b) }  { area(S_{roi}^a \cup S_{roi}^b) } \mbox{。}
\end{equation}

为了全面衡量类脑跟踪网络的类脑性能，拟同时考虑 IoU 行为度量和 MT/MST 皮层度量。
下面给出的 BTS $s_{t}$ 是两个分数的平均值 ：
\begin{equation} \label{equ:score_btn}
	s_{t} = \frac{s_b + s_r}{2}\mbox{。}
\end{equation}
考虑到归一化可能会惩罚方差较小的分数，而应该平等对待两个分数对类脑跟踪分数的重要性程度，因此类脑跟踪分数的设计没有在各个分数大小上进行归一化。

同时时在类脑跟踪模型的基础之上分析模型的动态响应和大脑皮层对运动的响应之间的相似性或相关性。
并加入第一个研究的类脑图像识别模型，类比于大脑皮层中腹侧流和背侧流之间的相互连接和影响，进一步提高视觉皮层的建模精度，以便更好地适应真实和复杂的动态场景，提高类脑模型的跟踪精度和类脑的真实性。

% 基于全局工作空间理论
\subsubsection{基于大脑皮层解剖对齐和全局工作空间的多模态融合模型}
\begin{figure*}[htb!]
	\centering  
	{\includegraphics[width=1.0\textwidth]{"images/auditory_ch"}
	}
	\caption{基于大脑皮层解剖对齐的类脑音频识别模型和多模态融合架构图}
	\label{fig:auditory}
\end{figure*}

在之前工作的基础之上，考虑大脑中其他模态的信息和视觉信息的相互作用，类比于人类感知中的“通感”。
考虑在人所接收的所有感知信息中，听觉信息是仅次于视觉信息的第二大感知源，两者占人所有感知信息的百分之九十以上，所以在建模类脑的多模态感知时主要考虑人类的听觉。
听觉识别通路主要包括初级听觉皮层A1、带状区Belt、伞状区PB、中颞/下颞区，并利用卷积神经网络和循环网络为基本结构，模拟人脑处理模式，构建大脑对齐的类脑模型，进行激活和行为之间的对比，包括大脑激活和神经网络激活之间的相似性、网络预测的音频类别和人类动作选择之间的相似性。

同时由于听觉识别的核心区域中颞/下颞区和第一阶段中的目标识别的下颞核心区有重叠部位，为视觉和听觉的融合处理提供了神经解剖基础，可以进一步在图像识别模型和音频识别模型的基础之上设计视觉/听觉融合模块，进行高层特征级别融合，有望进一步提高处理复杂环境输入的能力和提升类脑模型的预测能力。
% 《意识与脑》
% ~\cite{dehaene2001towards}
根据全局工作空间理论，在边缘区域，知觉是平行进行的：编码光线和声音的神经元可以同时被激活，而且不会互相干扰。
专业化的模块位于外围，适用于各种任务，比如：目标识别、检测、分割、语音识别、运动等，每个模块通过模块相关的隐藏空间连接到位于中心位置的全局工作空间。
通过以循环一致性目标进行训练，工作空间学会了以几乎无监督的方式在任意两个模块的隐空间表征中进行切换。
然而，在更高级的皮质体系中，它们会相互抑制，使得这些区域只允许存在激活神经元的单一整合状态，即单个“想法”。

在进行类脑模型的研究过程中，期待逐步建立一套科学合理的类脑评价指标用于评价所设计的类脑深度神经网络模型和人脑大脑处理信息的相似程度，在类脑图像识别中表现为图像分类和人进行图片识别时选择的相似性，在类脑跟踪中表现为深度神经网络输出的定位框和以人眼中央凹为中心的注意力范围，在感知融合中表现为在融合其他类型信息的复杂条件下模型的预测输出和人行为的相似性。该指标不仅衡量和模型的预测输出和人类行为之间的相似性，而且还衡量模型面对相同的输入刺激，各个中间层的激活响应和人类大脑皮层各个区域的激活（血液动力学响应或者脑电信号等）之间的相似性或相关性，实现从模型结构、皮层激活响应、人类行为等方面进行综合的类脑相似性解释。

\textcolor{NsfcBlue}{\subsection{实验手段}}
本项目主要采用标准数据集、ADAS高级智能驾驶辅助系统和真实智能车平台相结合的实验方法，分析拟提出的跟踪方法在开放环境下的跟踪性能。
实验主要包括基于标准数据集的验证、基于ADAS系统的测试和基于真实智能车平台的测试等三个方面。

\subsubsection{基于标准数据集的验证}
当前已有许多具有大规模的标准数据集被发布以推动视觉感知的发展，例如 ImageNet、OTB、VOT 等。
这些数据集都是在复杂多变的场景下所采集到的，十分具有挑战性。
以权威的 OTB 和 VOT 为例，OTB数据集由100个视频所组成，包含了58000多帧图片，视频集捕获了复杂场景下的行人、车辆、动物等多种目标，VOT数据主要用于一年一度的视觉目标跟踪竞赛，该数据集每年都会被重新标注和更新来提高数据集的准确性和竞赛难度，目前主要包括60个具有高难度的视频。
本项目申请人所在的实验室拥有由多台服务器和 PC 机所组成的计算平台，该计算平台上安装了Pytorch、Keras 和 Tensflow 等深度学习框架，下载了 ImageNet、OTB、VOT 等计算机视觉数据集，并配置了不同数据集的测试程序。
值得一提的是，由于不同数据集采用不同的性能指标以评估跟踪算法的结果，因此测试程序可以有效地验证跟踪算法在不同数据集上的跟踪精度。
通过在大规模的标准数据集进行综合性实验能够可靠地验证拟提出的视觉感知算法在开放环境下的跟踪性能。

同时使用《阿甘正传》电影作为动态开放自然环境的一种近似，原始数据集StudyForrest 包含受试观看电影时的核磁共振记录。
原始的《阿甘正传》电影包含的实际的 7 个电影片段。
这7 个部分连接起来并重新分割为8 个视频刺激段，每个视频段对应一个核磁共振记录。
时间戳参照《阿甘正传》2002年发行的DVD，PAL制式，DE103519SV， 每秒25帧，并按照“HH:MM:SS.FRAME”的格式给出。
该数据集包含15个受试，使用飞利浦Achieva dStream 核磁共振扫描仪记录下他们在观看好莱坞电影《阿甘正传》时的脑部激活数据和眼睛凝视数据，另外15 位不在核磁共振扫描仪中记录的受试仅仅记录下他们的凝视数据，这些不在核磁共振扫描仪中记录的数据仅仅用于提高平稳跟踪事件的检测精度。
使用液晶投影仪进行电影刺激的播放，受试在配有前反射镜的核磁共振扫描仪中进行电影的观看，并记录下观看电影时的脑部激活情况。凝视数据使用高频眼球跟踪仪EyeLink 1000 进行记录，在记录核磁共振扫描数据时，配有长焦镜头并以1000 次每秒的速度进行采样。
使用7 特斯拉的高精度核磁共振扫描仪，重复时间为 2 秒，体素大小为3 $\times$ 3 $\times$ 3立方毫米获取核磁共振记录。
此外，还获得了一套综合的辅助数据（弥散张量成像、磁敏感加权图像、血管造影）以及用于评估技术和生理噪声成分的测量数据。

\subsubsection{基于ADAS高级智能驾驶辅助系统的测试}
项目申请人在攻读博士学位期间作为团队的骨干成员参与了ADAS高级智能驾驶辅助系统的研发工作，主要负责环境感知模块的主要功能与相关算法的设计。
具体来说，ADAS 系统中的环境感知模块主要包括行人与车辆检测与跟踪、交通标志检测与跟踪和车道线检测等任务。
图~\ref{fig:adas}~展示了与本项目研究相关的行人与车辆检测与跟踪和交通标志检测与跟踪的定性结果。
因此，可以将本项目拟提出的目标跟踪算法移植到 ADAS 系统中，通过利用 ADAS 系统平台测试跟踪方法的性能。

\begin{figure*}[htb!]
	\centering  
	{\includegraphics[width=1.0\textwidth]{"images/adas"}
	}
	\caption{ADAS 系统中行人与车辆和交通标志检测与跟踪结果}
	\label{fig:adas}
\end{figure*}

\subsubsection{基于真实智能车平台的测试}
本项目申请人所在的团队与长沙智能驾驶研究院存在合作关系，具有智能车一台。
智能车平台上装有摄像头、激光雷达、毫米波雷达和组合导航等多个传感设备。
图~\ref{fig:car}~展示了智能车平台和团队成员进行实车测试的情况。
因此，本项目具有在真实智能车平台上进行实车测试的条件，将来有可能利用该智能车平台验证本项目拟提出的类脑感知算法在开放环境下的感知性能。

\begin{figure*}[htb!]
	\centering  
	{\includegraphics[width=1.0\textwidth]{"images/car"}
	}
	\caption{真实无人车平台和在线测试视频}
	\label{fig:car}
\end{figure*}

\textcolor{NsfcBlue}{\subsection{可行性分析}}
（1）\textbf{研究目标明确，技术路线清晰}。
本项目主要研究基于大脑皮层解剖对齐的类脑感知方法。
具体来说，以视觉感知所存在的模型可解释性、环境和目标动态变化和单一模态感知信息不足等问题为驱动，
基于“相关问题分析——模型算法设计——方法验证测试”的技术路线，利用深度学习、计算机视觉、神经科学、全局工作空间理论和多模态融合等方法与理论，
拟提出基于腹侧流解剖对齐的类脑精细化识别模型、基于腹侧流和背侧流融合的类脑视觉跟踪模型和基于大脑皮层解剖对齐和全局工作空间的多模态融合模型以提高开放环境下的视觉感知的适应性、准确性和鲁棒性，进而提高开放环境下的感知性能。

（2）\textbf{项目申请人具有一定的研究基础}。
如上所述，关于该课题三个阶段已有一定的研究基础，包括基本的类脑图像识别模型和评价指标，可以要在此基础上基于已有的人脸识别刺激数据和对应的多模型神经成像数据，利用人脸识别任务分析类脑模型和深度神经网络对相同图像刺激所产生的激活之间的相似性或关联关系，以及进一步分析负责人脸识别区的梭状回和负责目标识别区的下颞回之间的联系和区别。
本课题组已设计和测试类脑跟踪中背侧通路的建模和仿真，建立初步的运动感知模型，定量化验证中颞区和上颞内侧区和动态滤波网络激活的相似性，并在公开数据集上进行了仿真和验证，可以在此基础上加入图像识别的腹侧流模型，进一步研究背侧流和腹侧流共同作用下动态环境的建模和仿真。
类脑感知融合研究中已对类脑听觉皮层模型进行了初步建模，在音乐流派分类数据集合对应的核磁共振数据集上进行了响应分析，需要在此基础上分析深度模型激活和大脑皮层激活之间的相似性，并加入第一阶段腹侧流通路的建模，以进一步提高类脑模型的鲁棒性，提升模型的激活和行为的预测精度。
%
上述研究工作为本项目关于基于腹侧流解剖对齐的类脑精细化识别模型、基于腹侧流和背侧流融合的类脑视觉跟踪模型和基于大脑皮层解剖对齐和全局工作空间的多模态融合模型的研究奠定了良好的基础。
另外，项目申请人在攻读博士学位期间对类脑视觉感知进行了长期深入的研究，获取了大量主流跟踪方法的源代码，并且关注目标跟踪领域的最新发展趋势，这些也为研究工作的展开提供了巨大的帮助。

（3）\textbf{具有有效的实验方法和理想的实验平台}。
本项目主要利用标准数据集、ADAS高级智能驾驶辅助系统和真实无人车平台相结合的实验方法。
目前，项目组已收集了ImageNet、OTB、VOT 和 StudyForrest 等多个大规模标准数据集，并且为每个数据集配置了相应的测试程序以评估测试感知方法的性能。
项目申请人在攻读博士学位期间作为团队骨干成员参加了 ADAS 系统的研发工作，并且主要负责环境感知模块的功能与算法的设计。
因此，所研发的 ADAS 高级智能驾驶辅助系统能够用来进一步测试视觉感知方法的感知精度。
此外，申请人所在团队与长沙智能驾驶研究院存在合作，具有无人车平台，具备进行实车测试的可能。
项目申请人所在的湖南大学嵌入式与网络计算省重点实验室拥有由多台服务器和PC机所组成的强大计算平台，其中服务器配有多块 GeForce RTX 2080Ti 型号（共计 44GB 显存）、128G内存，这些是本项目研究工作开展与完成所必不可少的硬件条件。

\NsfcSection{4}{本项目的特色与创新之处；}{}

该类脑研究是可解释深度神经网络的一个很好地解决方案，设计大脑皮层对齐的类脑模型不仅可以设计出符合生物学解剖规律的深度神经网络，利用神经科学的原理来解释所设计的深度网络模型，有望解决深度神经网络“黑盒”的问题，还可以精简模型的层数，减少模型冗余，有利于工程化部署，加快计算机视觉算法的产业化落地。
同时利用设计并训练好的类脑深度神经网络探索脑机接口的应用和人产生视觉概念乃至意识的神经相关物，利用已经比较成熟的高性能计算机和深度学习算法，解决神经科学实验条件受限的不足，解决深度学习领域模型的复杂度越来越高、可解释性越来越差的问题。
本项目的特色与创新之处由主要包括如下几个方面：

\begin{itemize}
	\item 从模型可解释角度出发，将基于大脑皮层对齐的思想引入到类脑感知模型的设计之中，拟提出基于腹侧流解剖对齐的类脑精细化识别模型、基于腹侧流和背侧流融合的类脑跟踪模型、基于感知通路的类脑音频感知模型。
	这些模型不仅能够具有良好的识别性，而且能够利用大脑的生物学约束来限制模型的复杂度（即模型参数数目）以提高开放环境下的跟踪适应性；
	\item 研究类脑模型各层的激活和大脑皮层对应脑区激活之间的相似性，设计相似性度量标准全量衡量中间层激活和人类识别行为选择，判断所提出模型的有效性和鲁棒性；
	\item 从多模态融合框架设计的角度出发，拟提出基于大脑皮层解剖对齐和全局工作空间的多模态融合的感知方法。
	该方法基于全局工作空间将其他模态的信息融入视觉信息当中，强化视觉感知特征，可以有效地解决单一视觉感知信息不足的问题，提高开放环境下的感知的鲁棒性。
	\item 本项目具有明确的工程应用背景，相关科学问题能在重要工程领域得到应用，研究基础得到了实际工程验证，关键技术服务于工程关键技术领域突破，有利于推动人工智能产业科技进步。
\end{itemize}

\NsfcSection{5}{年度研究计划及预期研究结果}{（包括拟组织的重要学术交流活动、国际合作与交流计划等）。}

\textcolor{NsfcBlue}{\subsection{年度研究计划}}

（1）2023年1月-2023年12月

调研国际顶级会议与期刊中关于类脑视觉感知问题的最新研究工作与进展，把握领域前沿的研究趋势和热点，完善项目的主要目标整体规划，确定项目的具体工作；
针对视觉感知模型复杂度过高和可解释性不足所引起的感知适应性的问题，掌握模型类脑设计的主流方法，深入研究神经解剖对齐的类脑模型方法的特点与优势，将基于生物学约束引入到类脑模型中以构建相应的目标模型，训练合适的深度神经网络以对目标进行感知；
掌握基于类脑结构的卷积网络和循环神经网络的生物学连接意义，探索其在目标识别和视觉跟踪中的作用，尝试发现类脑模型和生物学机理之间更多的相关性。
撰写学术论文2\textasciitilde3篇，专利1\textasciitilde2个；

（2）2024年1月-2024年12月

了解主流的多模态融合和特征融合方法在开放环境下的感知性能、优势与不足；
研究不同模态信息的特性、优势和适应的感知场景，采用全局工作空间理论和多模态融合以建模目标外观，设计高效的多模态融合方法以设计目标模型；
在上述基础上，研究场景的多源信息（如深度信息，声音信息等），提出多模态信息融合方法以融合目标不同模态的特征；
撰写学术论文2\textasciitilde3篇，专利1\textasciitilde2个；

（3）2025年1月-2025年12月

深入分析不同跟多模态融合框架应对单一模态感知不足问题的鲁棒性，
研究全局共组空间理论的特点与性质，
设计基于全局工作空间理论的多模态融合方法，
提出基于多模态融合的类脑场景感知方法以消除单一模态感知能力不足的问题；
研究全局工作空间理论在感知理解、多模态融合、意识形成等方面的启发作用，以及尝试发现类脑感知模型中可能出现的意识相关物；
完善实验平台，验证和测试所提出的类脑感知方法的感知性能；
撰写学术论文2\textasciitilde3篇，软件著作权1\textasciitilde2个；
总结项目研究成果与相关研究资料，完成项目验收工作。

\textcolor{NsfcBlue}{\subsection{拟组织的重要学术交流活动、国际合作与交流计划}}

（1）参加1~2次人工智能和计算机视觉领域的顶级学术会议，如AAAI、CVPR、ICCV、ECCV和NIPS等；与相关领域的权威学者和学术团队进行学术问题的探讨与交流，掌握本领域的最新前沿研究方向和热点问题；

（2）参加1~2次国内计算机视觉和人工智能领域的重要学术会议，如中国模式识别与计算机视觉大会（PRCV）、CCF人工智能会议等；与国内本领域的专家与学术团队进行相关问题的讨论与交流，获取研究的新方向和新思路；

（3）计划在项目研究前期进行一次短期境外、国外访学，邀请国外研究专家（UC-Berkeley深度学习研究组、日本奈良先端科技研究院/东京大学视觉计算研究组）来华进行研讨与讲学，交流研究成果、研究方法和心得；

\textcolor{NsfcBlue}{\subsection{预期研究成果}}
（1）开发面向开放环境的类脑鲁棒视觉感知系统，该系统可以在复杂场景下达到理想的视觉感知适应性、准确性与鲁棒性；

（2）发表本领域SCI/EI高水平学术论文6\textasciitilde8篇，其中CCF A类/CCF B类/IEEE Transaction/SCI一区/SCI二区论文4\textasciitilde6篇，本领域其他高水平论文2\textasciitilde3篇；

（3）基于以上学术成果，申请相关专利2\textasciitilde3项与软件著作权1\textasciitilde2项；

（4）培养硕士研究生2\textasciitilde3名；

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\NsfcChapter{（二）研究基础与工作条件}{}

\NsfcSection{1}{研究基础}{（与本项目相关的研究工作积累和已取得的研究工作成绩）；}

本项目申请人近年来研究了应用基于大脑解剖对齐的类脑建模方法、深度学习、神经科学、计算机视觉和多模态融合等方法以解决开放环境下的视觉感知的问题，相关研究工作已经发表于《ACM Transactions on Multimedia Computing Communications and Applications》（CCF B 类）、《Neurocomputing》（SCI 2区）、《Image and Vision Computing》（SCI 3区）、《Computer Vision and Image Understanding》（CCF B类）等国际著名期刊之上，具备了较好的研究基础。
这些研究工作为本项目研究的开展和深入奠定了理论基础和积累了宝贵经验。
另外，申请人还作为骨干成员参加了与相关工程项目的研发工作，这进一步为本项目的完成提供了实践基础。
具体来说，与本项目相关的研究基础主要包括如几个方面：

（1）视觉感知。本项目申请人在湖南大学攻读博士学位期间依托湖南大学嵌入式与网络计算湖南省重点实验室、国家超算（长沙）中心长期从事目标跟踪方面的相关研究，作为骨干参与了多项国家自然科学基金和高校企业合作的产学研项目，发表了多篇以目标跟踪为主题的高水平学术论文，具有相当丰富的学术研究与工程项目经验。
特别地，申请人作为主要参与人随团队完成了ADAS高级智能驾驶辅助系统的研发工作，主要负责了系统中环境感知模型的相关功能与算法的设计。
ADAS系统的环境感知模块包含了多个与目标跟踪有紧密联系的功能，这为本课题的研究工作提供了较好的工程基础。
另外，项目申请人完成了以目标跟踪为主题的博士学位论文，开发了一个具有良好跟踪性能且非常实的目标跟踪系统，提出了基于非局部注意力、类脑跟踪方法和基于多任务学习的感知方法以提高视觉感知的准确性和鲁棒性。
本项目是申请人博士期间所做研究的延续，也是对先前工作的进一步深化与扩展，这说明申请人具备了十分坚实的研究基础。

（2）基于神经解剖的类脑跟踪方法。
本项目申请人前期对基于大脑解剖的类脑跟踪模型建模方法进行了初步的研究，提出了类脑跟踪方法以学习具有和人类大脑皮层类似的跟踪模型，并在相同刺激下大脑皮层中发现了相似的激活模式，研究成果发表于《Neurocomputing》。
本项目旨在设计基于大脑皮层解剖对齐的跟踪模型并尝试基于类脑模型中发现和大脑皮层类似的激活，找到运动意识的物质基础。
因此，前期的研究工作为本项目的工作提供了研究基础。

（2）非局部注意力机制。
本项目申请人应用非局部注意力机制解决视觉感知任务，提出了基于非局部注意力机制的跟踪方法，研究成果发表于《Image and Vision Computing》和《Computer
Vision and Image Understanding》等国际期刊之上。
本项目旨在将大脑皮层解剖对齐和注意力的思想引入到类脑识别模型中以降低跟踪模型的复杂度，提高感知方法在开放环境下的适应性。
因此，前期研究工作为本项目的研究提供了重要的理论基础。

（3）多模态融合方法。
本项目申请人深入分析于研究了多模态融合和多任务学习方法，提出了联合检测和跟踪的的融合方法以有效地融合多种视觉形态来完成视觉感知任务，相关研究成果已经发表在《ACM Transactions on Multimedia
Computing Communications and Applications》期刊之上。
本项目旨在研究基于神经解剖对齐的多模态融合模型以捕获场景中中复杂的特征。
因此，前期相关研究工作对本项目具有重要的指导意义。

\NsfcSection{2}{工作条件}{（包括已具备的实验条件，尚缺少的实验条件和拟解决的途径，包括利用国家实验室、国家重点实验室和部门重点实验室等研究基地的计划与落实情况）；}

%项目依托单位为湖南工商大学，拥有“移动商务智能湖南省重点实验室”、“湖南省移动电子商务2011 协同创新中心”等，已具备良好的工作环境和实验条件。

项目依托单位为湖南工商大学，拥有“湘江实验室”、“数字经济时代的资源环境管理理论与应用国家基础科学中心”、“统计学习与智能计算湖南省重点实验室”、“生态环境大数据与智能决策技术湖南省工程研究中心”、“长沙人工智能社会实验室”等，已具备良好的工作环境和实验条件。
另外项目申请团队可访问湖南大学信息科学与工程学院、湖南大学嵌入式与网络计算实验室和超级计算与云计算研究所的计算资源，且可获得数据挖掘、人工智能、数据融合、神经科学、算法设计等各个方向的学术力量支持。

湖南大学嵌入式与网络计算实验室是信息科学与工程学院的三个省重点实验室之一，主要研究方向是智能感知、大数据计算、信息网络和嵌入式计算等，目前实验室包括教师28名、博士后3名、博士研究生20多名、硕士研究生100多名，近五年完成和主持多项国家自然科学基金重点项目、国家自然科学基金面上项目、国家“973”，“863”及重大科技支撑计划、高校与企业合作的产学研项目等。
实验室拥有由多台Dell服务器和PC机所构成的强大计算平台（图17（a）），其中服务器配有Core i9-9820X（3.30GHz）处理器、128G内存、多块GeForce RTX 2080Ti型号显卡（共计显存33G），PC机配有Core i7处理器、16G内存、显卡GTX730（显存2G）。该计算平台上配置了Keras、Tensflow和Caffe等深度学习框架，安装了Visual Studio、Matlab、Python等正版实验软件，除了需要对计算平台中的内存和显卡进行升级并且购买一些采集数据集的设备以外，不需要购买大型实验设备，具备完成本项目研究所需要的基本实验条件。

湖南大学国家级超级计算长沙中心（图~\ref{fig:compution_resource}（b）），在实验环境、科研基础及国际交流合作方面已具备良好的研究条件。
该中心是继天津和深圳之后，目前科技部正式批准建立的第三家国家级超级计算中心，工程总投资8.6 亿。中心采用“天河1A-HN”计算核心，一期工程主机为CPU 和GPU 异构结构，运算速度为每秒1372 万亿次，其中CPU 峰值性能为302 万亿次、GPU 峰值性能为1070 万亿次、总的计算核心超过3万，内存总容量为106TB、存储容量为1.5PB、系统综合功耗为1.212MW，建筑面积近3 万平方米。
超级计算机主机部分由国防科大负责研制、软件部分由国防科大和湖南大学共同负责，机器已于2011 年6 月上线运行。
现由湖南大学组建专门团队负责全面的运营管理，国防科大提供技术运营支撑。
一方面，国家超级计算长沙中心能够为本项目提供超强计算能力的实验平台；
另一方面，项目组已搭建了一个小规模的CPU+GPU工作站，该系统由 6 个计算节点组成，其中单纯多核CPU 计算节点共4 个，CPU+FPGA 计算节点共1 个，CPU+GPU 计算节点共1 个。
该平台为相关并行算法的研究提供了一个实验验证平台。

此外，申请人所在团队与长沙智能驾驶研究院建立了合作关系，具有无人车一辆，这也为本项目进行实车测试提供了可能。

\begin{figure*}[htb!]
	\centering  
	{\includegraphics[width=1.0\textwidth]{"images/compution_resource"}
	}
	\caption{本项目的计算资源}
	\label{fig:compution_resource}
\end{figure*}

\NsfcSection{3}{正在承担的与本项目相关的科研项目情况}{（申请人和项目组主要参与者正在承担的与本项目相关的科研项目情况，包括国家自然科学基金的项目和国家其他科技计划项目，要注明项目的名称和编号、经费来源、起止年月、与本项目的关系及负责的内容等）；}

无

\NsfcSection{4}{完成国家自然科学基金项目情况}{（对申请人负责的前一个已结题科学基金项目（项目名称及批准号）完成情况、后续研究进展及与本申请项目的关系加以详细说明。另附该已结题项目研究工作总结摘要（限500字）和相关成果的详细目录）。}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

无

\NsfcChapter{（三）其他需要说明的问题}{}

\NsfcSection{1}{}{申请人同年申请不同类型的国家自然科学基金项目情况（列明同年申请的其他项目的项目类型、项目名称信息，并说明与本项目之间的区别与联系）。}

无

\NsfcSection{2}{}{具有高级专业技术职务（职称）的申请人或者主要参与者是否存在同年申请或者参与申请国家自然科学基金项目的单位不一致的情况；如存在上述情况，列明所涉及人员的姓名，申请或参与申请的其他项目的项目类型、项目名称、单位名称、上述人员在该项目中是申请人还是参与者，并说明单位不一致原因。}

无

\NsfcSection{3}{}{具有高级专业技术职务（职称）的申请人或者主要参与者是否存在与正在承担的国家自然科学基金项目的单位不一致的情况；如存在上述情况，列明所涉及人员的姓名，正在承担项目的批准号、项目类型、项目名称、单位名称、起止年月，并说明单位不一致原因。}

无

\NsfcSection{4}{}{其他。}

\end{document}

### 2023-06-05 auditory/classification/data_manager.py

@@ -1,0 +1,65 @@
+import os
+import numpy as np
+from torch.utils.data import Dataset, DataLoader
+
+class GTZANDataset(Dataset):
+    def __init__(self, x, y):
+        self.x = x
+        self.y = y
+
+    def __getitem__(self, index):
+        return self.x[index], self.y[index]
+
+    def __len__(self):
+        return self.x.shape[0]
+
+
+# Function to get genre index for the give file
+def get_label(file_name, hparams):
+    genre = file_name.split('.')[0]
+    genre = genre.split('_')[-1]  # added for fMRI music
+    label = hparams.genres.index(genre)
+    return label
+
+
+def load_dataset(set_name, hparams):
+    x = []
+    y = []
+
+    dataset_path = os.path.join(hparams.feature_path, set_name)
+    for root,dirs,files in os.walk(dataset_path):
+        for file in files:
+            data = np.load(os.path.join(root,file))
+            label = get_label(file, hparams)  # 根据文件名得到音乐流派的真实标签
+            x.append(data)
+            y.append(label)
+            # 需要记录下测试的顺序，以便 模型输入的音频 和 fMRI中使用的刺激 对应上
+            with open(os.path.join(hparams.data_path, 'run_dataset', set_name + "_order_in_DNN.txt"), 'a') as f:
+                f.writelines(file + "\n")
+
+    x = np.stack(x)
+    y = np.stack(y)
+
+    return x,y
+
+
+def get_dataloader(hparams):
+    x_train, y_train = load_dataset('train', hparams)
+    x_valid, y_valid = load_dataset('valid', hparams)
+    x_test, y_test = load_dataset('test', hparams)
+
+    mean = np.mean(x_train)
+    std = np.std(x_train)
+    x_train = (x_train - mean)/std
+    x_valid = (x_valid - mean)/std
+    x_test = (x_test - mean)/std
+
+    train_set = GTZANDataset(x_train, y_train)
+    vaild_set = GTZANDataset(x_valid, y_valid)
+    test_set = GTZANDataset(x_test, y_test)
+
+    train_loader = DataLoader(train_set, batch_size=hparams.batch_size, shuffle=True, drop_last=False, num_workers=hparams.workers)
+    valid_loader = DataLoader(vaild_set, batch_size=hparams.batch_size, shuffle=False, drop_last=False, num_workers=hparams.workers)
[…]

### 2023-06-05 auditory/classification/prepare_fMRI_music.py

@@ -1,0 +1,293 @@
+# 根据 fMRI 实验的数据划分音频的训练集和测试集（测试集和验证集一样），
+import librosa
+import numpy as np
+import os
+import random
+import shutil
+from hparams import hparams
+
+# 读取.mat文件
+import scipy.io as scio
+
+import shutil
+
+from hparams import hparams
+
+
+
+# 解压.tar.gz文件到当前文件夹
+def extract_tar_files(tar_file):
+    cur_dir, tar_file_name = os.path.split(tar_file);
+    # tar_file_name = tar_file.split('/')[-1]
+    des_dir = os.path.join(cur_dir, tar_file_name.split('.')[0])
+    # 如果存在文件夹，则删除
+    if os.path.exists(des_dir):
+        shutil.rmtree(des_dir)  # 删除任意文件夹，可以不为空
+        os.mkdir(des_dir)
+    else:
+        os.mkdir(des_dir)
+
+    import tarfile
+    f = tarfile.open(tar_file)
+    names = f.getnames()
+    for name in names:
+        f.extract(name, path=cur_dir)
+    return 0
+
+
+def get_genre(hparams):
+    return hparams.genres
+
+def load_list(list_name, hparams):
+    with open(os.path.join(hparams.dataset_path, list_name)) as f:
+        file_names = f.read().splitlines()
+
+    return file_names
+
+def get_item(hparams, genre):
+    return librosa.util.find_files(hparams.dataset_path + '/' + str(genre))
+
+
+def readfile(file_name, hparams):
+    y, sr = librosa.load(file_name, hparams.sample_rate)
+    return y, sr
+
+
+def change_pitch_and_speed(data):
+    y_pitch_speed = data.copy()
+    # you can change low and high here
+    length_change = np.random.uniform(low=0.8, high=1)
+    speed_fac = 1.0 / length_change
+    tmp = np.interp(np.arange(0, len(y_pitch_speed), speed_fac), np.arange(0, len(y_pitch_speed)), y_pitch_speed)
+    minlen = min(y_pitch_speed.shape[0], tmp.shape[0])
+    y_pitch_speed *= 0
+    y_pitch_speed[0:minlen] = tmp[0:minlen]
+    return y_pitch_speed
+
+
+def change_pitch(data, sr):
+    y_pitch = data.copy()
+    bins_per_octave = 12
+    pitch_pm = 2
+    pitch_change = pitch_pm * 2 * (np.random.uniform())
[…]

### 2023-06-05 auditory/classification/src/CNN2D/model/custom_RCNN.py

@@ -1,0 +1,61 @@
+import torch
+torch.manual_seed(123)
+import torch.nn as nn
+
+class RCNN(nn.Module):
+    def __init__(self, hparams):
+        super(RCNN, self).__init__()
+
+        self._extractor = nn.Sequential(
+            nn.Conv2d(in_channels=1, out_channels=64, kernel_size=3, stride=1, padding=1),
+            nn.BatchNorm2d(64),
+            nn.ReLU(),
+            nn.MaxPool2d(kernel_size=2),
+
+            nn.Conv2d(in_channels=64, out_channels=128, kernel_size=3, stride=1, padding=1),
+            nn.BatchNorm2d(128),
+            nn.ReLU(),
+            nn.MaxPool2d(kernel_size=2),
+
+            nn.Conv2d(in_channels=128, out_channels=256, kernel_size=3, stride=1, padding=1),
+            nn.BatchNorm2d(256),
+            nn.ReLU(),
+            nn.MaxPool2d(kernel_size=4),
+
+            nn.Conv2d(in_channels=256, out_channels=512, kernel_size=3, stride=1, padding=1),
+            nn.BatchNorm2d(512),
+            nn.ReLU(),
+            nn.MaxPool2d(kernel_size=8)
+        )
+
+        self._rnnModule = nn.Sequential(
+                 nn.GRU(512, 512, batch_first=False,bidirectional=True),
+                #nn.LSTM(512, 512, batch_first=False, bidirectional=True),
+                )
+
+        self._classifier = nn.Sequential(nn.Linear(in_features=1024, out_features=512),
+                                         nn.ReLU(),
+                                         nn.Dropout(),
+                                         nn.Linear(in_features=512, out_features=256),
+                                         nn.ReLU(),
+                                         nn.Dropout(),
+                                         nn.Linear(in_features=256, out_features=len(hparams.genres)))
+        self.apply(self._init_weights)
+
+    def forward(self, x):
+        x = torch.unsqueeze(x,1)  # b*128*128 -> b*1*128*128
+        x = self._extractor(x)    # -> b * 512*1*1
+        x = x.permute(3,0,1,2)    # -> 1*128*512*1
+        x = x.view(x.size(0), x.size(1), -1)  # -> 1*128*512
+
+        x, hn = self._rnnModule(x)   # .flatten_parameters()  # -> 1*128*1024, 2*128*512
[…]

### 2023-06-05 auditory/init.m

@@ -1,0 +1,79 @@
+% clear; clc;
+% 可以改变的配置
+%% 路径配置
+% 获得工程的路径
+
+raw_url = 'D:\data\neuro\music_genre';  % 本地原始音频和fMRI文件的存放目录
+% work_dir = tempdir;
+work_dir = 'D:\buffer';  % 工作目录
+if ~exist(work_dir, 'dir'); mkdir(work_dir); end
+
+% fMRI原始数据放置的目录
+fMRI_dir = fullfile(work_dir, 'data', 'brain', 'auditory', 'music_genre_fMRI', 'preprocess', 'ds003720-download');
+if ~exist(fMRI_dir, 'dir'); mkdir(fMRI_dir); end
+fMRI_raw_path = fullfile(raw_url, 'ds003720-download.zip');
+
+proj_dir = mfilename("fullpath");
+for i = 1 : 3; proj_dir = fileparts(proj_dir); end
+
+% if ~exist(fullfile(proj_dir, 'utils','spr_1_0', ['repadd.' mexext]), 'file')
+%     run(fullfile(proj_dir, 'utils', "spr_1_0", "mex_compile.m"));
+% end
+
+% https://bicr.atr.jp//cbi/sparse_estimation/sato/VBSR.html
+% 稀疏估计工具箱
+% addpath(fullfile(proj_dir, 'utils', "spr_1_0"));
+
+% 保存论文所需图片的目录
+figs_dir = fullfile(fileparts(mfilename("fullpath")), 'latex', 'figs');
+
+
+% 大脑解码工具箱
+cur_dir = pwd;
+brain_decoder_toolbox_dir = fullfile(matlabroot, 'software', 'matlab_utils', 'BrainDecoderToolbox2-0.9.17/');
+cd(brain_decoder_toolbox_dir);
+run('setpath.m');
+cd(cur_dir);
+
+
+workDir = fullfile(proj_dir, 'data', 'brain', 'auditory') ;
+dataDir = fullfile(workDir, 'data');       % 包含大脑和图像特征数据的目录
+resultsDir = fullfile(workDir, 'results'); % 保存分析结果的目录
+lockDir = fullfile(workDir, 'tmp');        % 保存文件锁（正在分析的过程）的目录
+
+setupdir(dataDir);
+setupdir(resultsDir);
+setupdir(lockDir);
+%% 数据设置
+
[…]

### 2023-06-05 auditory/latex/authors/convert_gray.m

@@ -1,0 +1,6 @@
+H=imread('HaidongWang.jpg');
+gray=rgb2gray(H);
+imwrite(gray,'HaidongWang_gray.bmp');
+imshow('HaidongWang_gray.bmp');
+
+% https://cloudconvert.com/bmp-to-eps

### 2023-06-05 auditory/latex/figs/music_traffic_wordcloud_chinese.m

@@ -1,0 +1,46 @@
+
+rng(32);
+
+% https://www.iotword.com/2032.html
+Word = {'空调声';
+    '手提钻';
+    '儿童玩耍声';
+    '狗叫声';
+    '钻孔声';
+    '街道音乐';
+    '枪声';
+    '警笛声';
+    '引擎空转声';
+    '汽车鸣笛声'};
+Count = [11;23;13;44;55;10;9;88;71;69];
+tbl = table(Word, Count);
+
+numWords = size(tbl,1);
+colors = rand(numWords, 3);  
+
+figure
+wordcloud(tbl, 'Word', 'Count', 'Color', colors);
+title("Sonnets Word Cloud")
+
+
+%%
+rng(2323);
+Word = {'空调声';
+    '手提钻';
+    '儿童玩耍声';
+    '狗叫声';
+    '钻孔声';
+    '街道音乐';
+    '枪声';
+    '汽车鸣笛声';
+    '警笛声';
+    '引擎空转声'};
+Count = [11;23;13;44;55;10;9;88;71;69];
+tbl = table(Word, Count);
+
+numWords = size(tbl,1);
+colors = rand(numWords, 3);  
+
+figure
+wordcloud(tbl, 'Word', 'Count', 'Color', colors);
+title("Sonnets Word Cloud")

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/CalcPredAcc_TopVoxels.m

@@ -1,0 +1,30 @@
+function CalcPredAcc_TopVoxels(ID, Method)
+% Select top voxels from training dataset prediction accuracy 
+% Novel task, using CogFacotor model
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+
+SaveDir = [pwd '/SampleResult/'];
+
+Ntop = 1000;
+%Å@Select top voxels using traing dataset 
+load([SaveDir 'RidgeRepFit_' Method '_' ID '.mat'], 'rResult');
+[baval baind] = max(rResult.mccs);
+tccs = [];
+for rr = 1:50
+    CCS = rResult.CCS{rr};
+    tccs = [tccs,  CCS(:,baind)];
+end
+ccs = nanmean(tccs,2);
+
+[val ind] = sort(ccs,'descend');
+
+load([SaveDir 'RidgeResult_' Method '_' ID '_NewTask_All.mat'], 'Result'); 
+mccs = mean(Result.ccs(ind(1:Ntop)));
+
+display(['Mean accuracy of top ' num2str(Ntop) ' voxels is ' num2str(mccs) ])
+
+
+

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/Cluster_NeuroSynth.m

@@ -1,0 +1,91 @@
+function Cluster_NeuroSynth(ID, Cluster, NeuroSynthDir)
+%Reverse infernce of cognitive factors related to each PC 
+%
+%Input:
+% ID... subject ID (e.g., 'sub-01')
+% Cluster...Target cluster number
+% NeuroSynthDir...Directory where reference images in NeuroSynth were saved
+%
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+switch Cluster
+    case 1
+        TargetTask = 1:36; 
+    case 2
+        TargetTask = 37:49;
+    case 3
+        TargetTask = 50:64;
+    case 4
+        TargetTask = 65:77;
+    case 5
+        TargetTask = 78:86;
+    case 6
+        TargetTask = 87:103;
+end
+
+% Load group cluster weight data
+InputFile = [SaveDir 'GroupCluster_' ID '_Cluster' num2str(Cluster) '.nii'];
+V = MRIread(InputFile);
+vol = V.vol;
+vol = permute(vol,[2,1,3]);
+tdata =  reshape(vol,prod(size(vol)),1);
+
+% Load registration matrix from  MNI152 space to EPI space
+load([DataDir 'reg_mni152_' ID '.mat'],'R');
+
+% Load neurosynth terms
+load([DataDir 'NeuroSynthTerms.mat'],'sTerm');
+
+% Load reference EPI data
+Targ = MRIread([DataDir 'target_' ID '.nii']);
+
+% Load target voxels in the cerebral cortex
+load([DataDir 'VsetInfo_' ID '.mat'],'vset_info');
+ROI = vset_info.IDs;
+vset = ROI(1);
+voxelSetForm = [DataDir 'vset_' ID '/vset_%03d.mat'];
+load(sprintf(voxelSetForm,vset),'tvoxels');
+
+tdata = tdata(tvoxels);
+tdata(find(tdata<0)) = 0;
+
+% Correlation with Neurosynth database
+CorrData = [];
+for mm = 1:length(sTerm)
+    disp(['processing NeuroSynth database No. ' num2str(mm)])
+    tTerm = char(sTerm(mm));
+    tTerm(strfind(tTerm,' ')) = '_';
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/Cluster_Visualize_raw.m

@@ -1,0 +1,124 @@
+function Cluster_Visualize_raw
+%
+% Hierarchical clustering analysis and visualization, 
+% using brain response data
+%
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+gtResp = [];
+for ii  = 1:6
+    ID = ['sub-0' num2str(ii)];
+
+    % Load response data (Matrix of Time points * Voxels)
+    load([DataDir 'RespData_' ID '.mat']);
+    respTrn_ROI = RespData.respTrn;
+
+    % Correction for bold time delay
+    RespTrn = cat(3,circshift(respTrn_ROI,-1), circshift(respTrn_ROI,-2), circshift(respTrn_ROI,-3));
+    RespTrn = squeeze(mean(RespTrn,3));
+    
+    % Load stimulus information (Matrix of Time points * features)
+    load([DataDir 'Stim_TaskType_' ID '.mat']);
+    stimTrn = StimData.stimTrn;
+
+    StimTrn = [];
+    for ii = 1:size(stimTrn,1)
+        if ~isempty(find(stimTrn(ii,:)))
+            StimTrn(ii) = find(stimTrn(ii,:));
+        else
+            StimTrn(ii) = 0; 
+        end
+    end
+    
+    % Average for each task type
+    tResp = [];
+    NTask = 8;
+    for tt = 1:103
+        tdata = RespTrn( find(StimTrn==tt) , :);
+        ttdata = reshape(tdata,size(tdata,1)/NTask,NTask,size(tdata,2));
+        tResp = cat(1,tResp,nanmean(ttdata , 1) );
+    end
+    ttResp = tResp;
+    tResp = squeeze( nanmean(ttResp,2) );
+    gtResp = [gtResp,tResp];
+end
+
+% Load task names
+load([DataDir 'TaskList.mat'],'TaskList');
+
+% Hierarchical clustering analysis with dissimilarity matrix
+X = pdist(gtResp,'correlation');
+Y = linkage(X, 'average');
+fig = figure;
+[T H outperm] = dendrogram(Y,0);
+permtask = TaskList(outperm);
+set(gca,'XTickLabel',permtask,'FontSize',10);
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/GroupWeight.m

@@ -1,0 +1,98 @@
+function GroupWeight( Method )
+%
+%Select the best regularization parameter used in the principal component
+%analysis and hierarchical clustering analysis
+%
+%Input:
+% Method... 'TaskType'
+%
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+DummyID = 'sub-01';
+% Load target voxels in the cerebral cortex
+load([DataDir 'VsetInfo_' DummyID '.mat'],'vset_info');
+ROI = vset_info.IDs;
+vset = ROI(1);
+voxelSetForm = [DataDir 'vset_' DummyID '/vset_%03d.mat'];
+load(sprintf(voxelSetForm,vset),'tvoxels');
+
+% Load stimulus information (Matrix of Time points * features)
+load([DataDir 'Stim_' Method '_' DummyID '.mat']);
+stimTrn = StimData.stimTrn;
+
+% Normalization of Training Stimuli feature values
+mu = nanmean(stimTrn);
+sigma = nanstd(stimTrn);
+stimTrn = bsxfun(@minus, stimTrn, mu);
+stimTrn = bsxfun(@rdivide, stimTrn,sigma);
+
+% NAN to zero
+stimTrn(isnan(stimTrn))=0;
+
+% Make delayed stimulus matrix
+stimTrn = cat(2, circshift(stimTrn,1), circshift(stimTrn,2), circshift(stimTrn,3));
+
+% Load result of repetitive ridge to search for the best parameter
+repN = 50;
+tmccs = zeros(1,18);
+for ii = 1:6
+    ID = ['sub-0' num2str(ii)];    
+    load([SaveDir 'RidgeRepFit_' Method '_' ID '.mat'], 'rResult');
+    tmccs = tmccs + rResult.mccs;
+end
+tmccs = tmccs / 6;
+%@Select the best regularization parameter for 6 participants
+[baccs, baind] = max(tmccs);
+best_a = rResult.as(baind);
+
+
+tresp = [];
+svoxels = [];
+for ii = 1:6
+    ID = ['sub-0' num2str(ii)];    
+    load([SaveDir 'RidgeRepFit_' Method '_' ID '.mat'], 'rResult');
+    tccs = zeros(size(rResult.CCS{1}(:,1)));
+    for nn = 1:repN
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/MTFset/MakeCochleogram.m

@@ -1,0 +1,112 @@
+function [Coch, LogScale] =  MakeCochleogram(filename, Dir, Params, ImageSwitch)
+%Coch...Cohleogram N (frequency bands) * T (Time) matrix 
+%LogScale... Frequency bin between each freq. band
+%
+%filename ... wave format
+%Params...STRFparams
+%ImageSwitch... if 1, show spectrogram image
+%
+%Requirement: gammatonegram (https://www.ee.columbia.edu/~dpwe/resources/matlab/gammatonegram/)
+
+if ~exist('ImageSwitch')
+    ImageSwitch = 1;
+end
+
+
+Nchannel = Params.Nchannel;
+LowestFreq = Params.LowestFreq;
+HighestFreq = Params.HighestFreq;
+
+
+[Data, Fs] = audioread([Dir filename]);
+
+% Transform to monaural
+if size(Data,2) > 1
+	Data(:,2) = []; 
+end
+
+% Resampling to 2*HighestFreq 
+rsData = resample(Data,2*HighestFreq,Fs);
+rsFs = 2*HighestFreq;
+ 
+if Params.cNorm
+    %Normalization to mean 0, sd 1
+    rsData = zscore(rsData);
+end
+
+% Gammatone gram
+% Note that output CentFreq array is in the reverse order (CentFreq(1) i the
+% Highest frequency), but Coch matrix rows are in the normal order.
+[Coch,CentFreq] = gammatonegram(rsData,rsFs,Params.WinSize,Params.HopSize,Nchannel,LowestFreq,HighestFreq,0);
+
+% Order reverse
+CentFreq = flipud(CentFreq);
+LogCentFreq = log2(CentFreq);
+
+% Log scaling of amplitude (Decibel)
+if Params.LogSwitch
+    Coch = 20*log10(Coch);
+end
+
+% Resample data with EqualSpacing
+if Params.EqualSpacing == 1
+    bin = ( log2(HighestFreq) - log2(LowestFreq) ) / Nchannel;
+    LogCf = [(log2(LowestFreq)+bin/2) :bin: (log2(HighestFreq)-bin/2 )]';
+    Cf = 2 .^ LogCf; 
+
+    xx = [log2(LowestFreq):0.001:log2(HighestFreq)]';
+    Idx = knnsearch(xx,LogCf); 
+    nLogCf = xx(Idx);
+    
+    nCoch = zeros(size(Coch));
+    for tt = 1:size(Coch,2)       
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/MTFset/MakeMTFmodel.m

@@ -1,0 +1,185 @@
+
+function [STRFu, STRFuq, STRFd, STRFdq] = MakeMTFmodel(Params, LogScale, ImageSwitch)
+% MTF Model based on Chi et al. (2005)
+% if ImageSwitch = 1, show STRF filter figures.
+if ~exist('ImageSwitch')
+    ImageSwitch = 1;
+end
+
+
+os = Params.os;
+ot = Params.ot;
+ps = Params.ps;
+pt = Params.pt;
+FreqSpan = Params.FreqSpan;
+TimeSpan = Params.TimeSpan;
+
+OctaveFreqSpan = 2^FreqSpan;
+%x is Log. Frequency (octave)
+x = [-OctaveFreqSpan:0.01:OctaveFreqSpan];
+
+
+xx = os*x;
+hs = os * (1 - xx.^2 ) .* exp(-xx.^2 /  2); %Gamma function
+hhs = imag(hilbert(hs)); %Hilbert transform
+
+
+%point close to 0
+CFpoint = knnsearch(x',0);
+NScaledPoints = floor(max(x)/LogScale);
+
+%down sampling to (Cochleogram) Log-scaled Frequency
+sx = [];
+shs = [];
+shhs = [];
+FreqPlot=[];
+for kk = 1:(NScaledPoints * 2 + 1)
+   FreqPlot(kk) = LogScale * ( kk - NScaledPoints - 1);
+   ScaledPoints = knnsearch(x', LogScale * ( kk - NScaledPoints - 1 ) ); 
+   sx(kk) = x(ScaledPoints);
+   shs(kk) = hs(ScaledPoints);
+   shhs(kk) = hhs(ScaledPoints);   
+end
+
+t = [0:0.001:TimeSpan];
+tt = ot*t;
+
+%To make the STRF onset later and avoid aliasing
+tt = [zeros(1,1500) , tt];
+t = [0:0.001:(TimeSpan + 1.5)];
+
+ht = ot* tt .^ 2 .* exp( -3.5 * tt ) .* sin(2*pi.*tt);
+hht = imag(hilbert(ht)); % Hilbert transform
+
+
+HopSize = Params.HopSize;
+NScaledPoints = floor(max(t)/HopSize);
+st = [];
+sht = [];
+shht = [];
+TimePlot=[];
+for kk = 1:NScaledPoints
+    TimePlot(kk) = HopSize * ( kk - 1);
+    ScaledPoints = knnsearch(t', HopSize * ( kk - 1 ));
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/MakeFeatureSpace_NeuroSynth.m

@@ -1,0 +1,28 @@
+function MakeFeatureSpace_NeuroSynth(ID)
+%
+%Obtain cognitive factor features
+%
+%Input:
+% ID... subject ID (e.g., 'subject-01')
+%
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+% Load CTM
+load([SaveDir 'CTM_' ID '.mat'],'CTM');
+
+% Load stimulus information (Matrix of Time points * features)
+Method = 'TaskType';
+load([DataDir 'Stim_' Method '_' ID '.mat']);
+stimTrn = StimData.stimTrn;
+stimVal = StimData.stimVal;
+
+% Transform into the cognitive factor space
+StimData.stimTrn = stimTrn*CTM;
+StimData.stimVal = stimVal*CTM;
+
+save([DataDir 'Stim_CogFactor_' ID '.mat'],'StimData', '-v7.3');

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/PC2Cluster.m

@@ -1,0 +1,103 @@
+function PC2Cluster
+%
+% Calculation of the relative contribution of the top PCs to the largest clusters
+%
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+
+Method = 'TaskType';
+rng(1234,'twister')
+RepN = 1000;
+
+% Load label weight for each PC
+load([ SaveDir 'GroupPCA_Result.mat']);
+coeff = pcaResult.coeff;
+TargPC = 1:4;
+TargCluster = 1:6;
+coeff = coeff(:,TargPC);
+
+tCon = [];
+pCon = [];
+for Cluster =  TargCluster
+
+    switch Cluster
+        case 1
+            TargetTask = 1:36; 
+        case 2
+            TargetTask = 37:49;
+        case 3
+            TargetTask = 50:64;
+        case 4
+            TargetTask = 65:77;
+        case 5
+            TargetTask = 78:86;
+        case 6
+            TargetTask = 87:103;
+    end
+    
+    % Load task sets in the target cluster
+    load([SaveDir 'ClusteringResult.mat'],'dResult');
+    TargetTask = dResult.PermInd(TargetTask);
+
+    % Relative contribution of top PCs to the target cluster
+    Con = coeff(TargetTask,:);
+    mCon = mean(Con,1);
+
+    % Statistical testing (sign test)
+    for PC = TargPC
+        pCon(Cluster,PC) = signtest(Con(:,PC));
+    end   
+    tCon= [tCon;mCon];
+end
+
+
+Ps = reshape(pCon,prod(size(pCon)),1);
+Ps = Ps';
+%FDR correction
+Q = 0.05; %default Q value
+[PXsorted PXind] = sort(Ps, 'ascend');
+NBox = length(TargPC)*length(TargCluster);
+FDRthr = Q*[1:NBox]/NBox;
+Diff = PXsorted - FDRthr;
+thrInd = PXind(max(find(Diff<0)));
+Thr = Ps(thrInd);
+NS = find(Ps >= Thr);
+nsCon = ones(size(pCon));
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/PlotDecoding_Shuffle.m

@@ -1,0 +1,120 @@
+function PlotDecoding_Shuffle(ID, Method)
+%
+%Plotting of decoding result using novel tasks,
+%Shuflling CTM for 1000 times
+%
+%Input:
+% ID... subject ID (e.g., 'sub-01')
+% Method... 'CogFactor'
+%
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+% Load stimulus information (Matrix of Time points * features)
+DummyMethod = 'TaskType';
+load([DataDir 'Stim_' DummyMethod '_' ID '.mat']);
+stimTrn = StimData.stimTrn;
+stimVal = StimData.stimVal;
+
+% Get label index at each time bin
+mstim = [];
+for tt = 1:size(stimVal,1)
+    if ~isempty(find(stimVal(tt,:)))
+        mstim(tt) = find(stimVal(tt,:));
+    else
+        mstim(tt) = 0; 
+    end
+end
+
+% Exclude no task time point (feedback time point)
+Label_vec = mstim;
+for tt = 1:length(Label_vec)
+    if tt > length(Label_vec)
+        break;   
+    elseif Label_vec(tt) == 0
+        Label_vec(tt) = [];
+        tt = tt -1;
+    end
+end
+
+% Load decoding result
+load([SaveDir 'RidgeDecResult_' Method '_' ID '_NewTask_All.mat'], 'Result');
+pstim = Result.pstim;
+
+% Load cognitive transform matrix
+load([SaveDir 'CTM_' ID '.mat'],'CTM');
+
+
+% Randomize CTM
+RepN = 1000;       
+rng(1234,'twister')
+rAcc = []; 
+rTaskScore = [];
+for rr = 1:RepN
+    % Randomize task order
+    if mod(rr,10) ==0
+        display([' Resampling n = ' num2str(rr) ])
+    end
+    
+    for ii = 1:103
+        Rn = randperm(prod(size(CTM))); 
+        rCTM = reshape(CTM,length(Rn),1);
+        rCTM = rCTM(Rn);
+        rCTM = reshape(rCTM, size(CTM));    
+        rTaskVec = rCTM(ii,:);
+        for tt = 1:size(pstim,1)
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/RidgePart_CerebCortex_NewTask_All.m

@@ -1,0 +1,69 @@
+function RidgePart_CerebCortex_NewTask_All(ID,Method)
+%
+%Concatenation of ridge regression analyses of subgroups 
+%using novel tasks 
+%
+%Input:
+% ID... subject ID (e.g., 'sub-01')
+% Method... 'CogFactor'
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+% Load original response data
+DummyMethod = 'TaskType';
+load([SaveDir 'RidgeResult_' DummyMethod '_' ID '.mat'], 'Result');
+oriresp = Result.resp;
+
+% Load the regression results of five subgroups
+tresp = [];
+tpresp = [];
+for Rep = 1:5
+    load([SaveDir  'RidgeResult_' Method '_' ID '_NewTask' num2str(Rep) '.mat'], 'Result');
+    tresp = [tresp; Result.resp];
+    tpresp = [tpresp; Result.presp];
+end
+
+% Load target time points
+load([SaveDir 'NewTask_Target.mat'],'Targ');
+TargetTimeVal = Targ.TargetTimeVal;
+
+% Concatenate time points of five subgroups
+NewTime = [];
+for rr = 1:5
+    NewTime = [NewTime; TargetTimeVal{rr}];
+end
+[uniqueNT ia ic] = unique(NewTime);
+
+% Concatenate predited responses of five subgroups
+ctpresp = [];
+for tt = 1:length(uniqueNT)
+    DoubledTime = find(NewTime == uniqueNT(tt));
+    ctpresp(min(NewTime(DoubledTime)),:) = nanmean(tpresp(DoubledTime,:),1);
+end
+
+% Calculate prediction performance
+ccs = mvncorr(ctpresp, oriresp);
+
+Result.ccs = ccs;  
+Result.mean_ccs = nanmean(ccs);
+Result.resp = oriresp;
+Result.presp = ctpresp;
+
+% Mapping from 1d Data to 3d .nii data 
+RefEPI = [DataDir 'target_' ID '.nii'];
+Y = zeros(prod(Result.datasize),1);
+for ii=1:length(Result.tvoxels)
+    Y(Result.tvoxels(ii))= ccs(ii);
+end
+vol = reshape(Y,Result.datasize);
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/RidgePart_CerebCortex_NewTask_All_Shuffle.m

@@ -1,0 +1,123 @@
+function RidgePart_CerebCortex_NewTask_All_Shuffle(ID,Method)
+%
+%Shuffling ananalyis, it randomly shuffles feature matrix 1000 times in element-wise
+%manner and produce a null distribution of mean prediction accuracy. Using
+%novel tasks.
+%
+%Input: 
+% ID... subject ID
+% Method... 'CogFactor'
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+% Load target voxels in the cerebral cortex
+load([DataDir 'VsetInfo_' ID '.mat'],'vset_info');
+ROI = vset_info.IDs;
+vset = ROI(1);
+voxelSetForm = [DataDir 'vset_' ID '/vset_%03d.mat'];
+load(sprintf(voxelSetForm,vset),'tvoxels');
+
+% Load stimulus information (Matrix of Time points * features)
+load([DataDir 'Stim_' Method '_' ID '.mat']);
+stimTrn = StimData.stimTrn;
+stimVal = StimData.stimVal;
+
+% Normalization of Training Stimuli feature values
+mu = nanmean(stimTrn);
+sigma = nanstd(stimTrn);
+% Normalization of Validation Stimuli based on the Training norm value
+stimVal = bsxfun(@minus, stimVal, mu);
+stimVal = bsxfun(@rdivide, stimVal,sigma);
+% NAN to zero
+stimVal(isnan(stimVal))=0;
+% Make delayed stimulus matrix
+stimVal = cat(2, circshift(stimVal,1), circshift(stimVal,2), circshift(stimVal,3));  
+
+% Load target time points
+load([SaveDir 'NewTask_Target.mat'],'Targ');
+TargetTimeVal = Targ.TargetTimeVal;
+
+% Concatenate time points of five subgroups
+NewTime = [];
+for rr = 1:5
+    NewTime = [NewTime; TargetTimeVal{rr}];
+end
+[uniqueNT ia ic] = unique(NewTime);
+
+
+AllResult= [];
+for Rep = 1:5
+    load([SaveDir  'RidgeResult_' Method '_' ID '_NewTask' num2str(Rep) '.mat'], 'Result');
+    AllResult{Rep} = Result;
+end
+
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/Ridge_CerebCortex.m

@@ -1,0 +1,119 @@
+function Ridge_CerebCortex(ID, Method)
+%
+%Ridge regression analysis
+%
+%Input:
+% ID... subject ID (e.g., 'sub-01')
+% Method... 'TaskType'
+%
+
+disp(['Performing Ridge regression for ' ID])
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+% Load target voxels in the cerebral cortex
+load([DataDir 'VsetInfo_' ID '.mat'],'vset_info');
+ROI = vset_info.IDs;
+vset = ROI(1);
+voxelSetForm = [DataDir 'vset_' ID '/vset_%03d.mat'];
+load(sprintf(voxelSetForm,vset),'tvoxels');
+datasize = [96 96 72];
+
+% Load response data (Matrix of Time points * Voxels)
+load([DataDir 'RespData_' ID '.mat']);
+respTrn_ROI = RespData.respTrn;
+respVal_ROI = RespData.respVal;
+
+% Load stimulus information (Matrix of Time points * features)
+load([DataDir 'Stim_' Method '_' ID '.mat']);
+stimTrn = StimData.stimTrn;
+stimVal = StimData.stimVal;
+
+% Normalization of Training Stimuli feature values
+mu = nanmean(stimTrn);
+sigma = nanstd(stimTrn);
+stimTrn = bsxfun(@minus, stimTrn, mu);
+stimTrn = bsxfun(@rdivide, stimTrn,sigma);
+
+% Normalization of test stimuli based on the Training norm value
+stimVal = bsxfun(@minus, stimVal, mu);
+stimVal = bsxfun(@rdivide, stimVal,sigma);
+
+% NAN to zero
+stimTrn(isnan(stimTrn))=0;
+stimVal(isnan(stimVal))=0;
+
+% Make delayed stimulus matrix
+stimTrn = cat(2, circshift(stimTrn,1), circshift(stimTrn,2), circshift(stimTrn,3));
+stimVal = cat(2, circshift(stimVal,1), circshift(stimVal,2), circshift(stimVal,3));
+
+% 10 fold cross validation
+ssinds = getResampInd10fold(size(respTrn_ROI,1));
+Abase = 100;
+as = Abase*(2.^(0:17));
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/Ridge_CerebCortex_NewTask_Dec.m

@@ -1,0 +1,26 @@
+function Ridge_CerebCortex_NewTask_Dec(ID, Method)
+%
+%Decoding analysis by ridge regression , using novel tasks
+%
+%Input:
+% ID... subject ID (e.g., 'sub-01')
+% Method... 'CogFactor'
+%
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+SaveDir = [pwd '/SampleResult/'];
+
+load([SaveDir 'NewTask_Target_Dec.mat'],'Targ');
+
+TargetTimeTrn = Targ.TargetTimeTrn;
+TargetTimeVal = Targ.TargetTimeVal;
+
+% Perform ridge regression for each of the five subgroups
+for rr = 1:5
+    RidgePart_CerebCortex_NewTask_Dec(ID,Method, TargetTimeTrn{rr},TargetTimeVal{rr},rr)
+end
+RidgePart_CerebCortex_NewTask_Dec_All(ID, Method);
+% Plot decoding result
+PlotDecoding(ID, Method)

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/Ridge_CerebCortex_RepFit.m

@@ -1,0 +1,87 @@
+function Ridge_CerebCortex_RepFit(ID, Method)
+%
+%Determine the best regularization parameter
+%by performing ridge regression repN (e.g., 50) times
+%within the training dataset
+%
+%Input:
+% ID... subject ID (e.g., 'sub-01')
+% Method... 'TaskType' or 'CogFactor'
+%
+
+% Random seed
+rng(1234,'twister')
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+% Load target voxels in the cerebral cortex
+load([DataDir 'VsetInfo_' ID '.mat'],'vset_info');
+ROI = vset_info.IDs;
+vset = ROI(1);
+voxelSetForm = [DataDir 'vset_' ID '/vset_%03d.mat'];
+load(sprintf(voxelSetForm,vset),'tvoxels');
+datasize = [96 96 72];
+
+% Load response data (Matrix of Time points * Voxels)
+load([DataDir 'RespData_' ID '.mat']);
+respTrn_ROI = RespData.respTrn;
+
+% Load stimulus information (Matrix of Time points * features)
+load([DataDir 'Stim_' Method '_' ID '.mat']);
+stimTrn = StimData.stimTrn;
+
+% Normalization of Training Stimuli feature values
+mu = nanmean(stimTrn);
+sigma = nanstd(stimTrn);
+stimTrn = bsxfun(@minus, stimTrn, mu);
+stimTrn = bsxfun(@rdivide, stimTrn,sigma);
+
+% NAN to zero
+stimTrn(isnan(stimTrn))=0;
+
+% Make delayed stimulus matrix
+stimTrn = cat(2, circshift(stimTrn,1), circshift(stimTrn,2), circshift(stimTrn,3));
+
+% Calculate best as from 18 candidate, for repN times
+repN = 50;
+SSinds = getResampInd_repN(size(respTrn_ROI,1), repN);
+Abase = 100;
+as = Abase*(2.^(0:17));
+ttccs = zeros(1,length(as));
+CCS = [];
+for nn = 1:repN
+    % Get random part
+    ssinds = SSinds{nn};
+    % Model fitting
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/Ridge_FDRcorr_NewTask.m

@@ -1,0 +1,81 @@
+function Ridge_FDRcorr_NewTask(ID, Method)
+%
+%FDR correction for multiple comparison (Benjamini & Hochberg, 1995)
+%Using novel tasks
+%
+%Input:
+% ID... subject ID (e.g., 'sub-01')
+% Method... 'CogFactor'
+%
+
+% Random seed
+rng(1234,'twister')
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+% Load target voxels in the cerebral cortex
+load([DataDir 'VsetInfo_' ID '.mat'],'vset_info');
+ROI = vset_info.IDs;
+vset = ROI(1);
+voxelSetForm = [DataDir 'vset_' ID '/vset_%03d.mat'];
+load(sprintf(voxelSetForm,vset),'tvoxels');
+datasize = [96 96 72];
+
+load([SaveDir 'RidgeResult_' Method '_' ID '_NewTask_All.mat'], 'Result');
+ccs = Result.ccs;
+
+% Default Q value
+Q = 0.05; 
+% Make random correlation coefficient histogram
+for ii = 1:length(ccs)
+	A = normrnd(0,1,size(Result.resp,1),1);
+	B = normrnd(0,1,size(Result.resp,1),1);
+	rccs(ii) = corr2(A,B);
+end
+
+% Calculate P values in each voxel
+PX = [];
+for ii = 1:length(ccs)
+	x = find(rccs>ccs(ii));
+	px = length(x)/length(ccs);
+	PX(ii) = px;
+end
+
+% FDR correction
+[PXsorted PXind] = sort(PX, 'ascend');
+FDRthr = Q*[1:length(ccs)]/length(ccs);
+Diff = PXsorted - FDRthr;
+thrInd = PXind(max(find(Diff<0)));
+thrP = PX(thrInd);
+thrCCs = ccs(thrInd);
+disp(['Threshold ccs = ' num2str(thrCCs)])
+
+% New ccs above threshold
+ccs(find(ccs < thrCCs)) = 0;
+
+
+% Mapping from 1d Data to 3d .nii data 
+RefEPI = [DataDir 'target_' ID '.nii'];
+Y = zeros(prod(datasize),1);
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/Ridge_FDRcorr_NewTask_WithReg.m

@@ -1,0 +1,81 @@
+function Ridge_FDRcorr_NewTask_WithReg(ID, Method)
+%
+%FDR correction for multiple comparison (Benjamini & Hochberg, 1995)
+%Using novel tasks, with sensorimotor regressors
+%
+%Input:
+% ID... subject ID (e.g., 'sub-01')
+% Method... 'CogFactor'
+%
+
+% Random seed
+rng(1234,'twister')
+
+if ~exist('SampleData')
+   error('Error. \nNo SampleData Folder.')    
+end
+
+SaveDir = [pwd '/SampleResult/'];
+DataDir = [pwd '/SampleData/'];
+
+% Load target voxels in the cerebral cortex
+load([DataDir 'VsetInfo_' ID '.mat'],'vset_info');
+ROI = vset_info.IDs;
+vset = ROI(1);
+voxelSetForm = [DataDir 'vset_' ID '/vset_%03d.mat'];
+load(sprintf(voxelSetForm,vset),'tvoxels');
+datasize = [96 96 72];
+
+load([SaveDir 'RidgeResult_WithReg_' Method '_' ID '_NewTask_All.mat'], 'Result');
+ccs = Result.ccs;
+
+% Default Q value
+Q = 0.05; 
+% Make random correlation coefficient histogram
+for ii = 1:length(ccs)
+	A = normrnd(0,1,size(Result.resp,1),1);
+	B = normrnd(0,1,size(Result.resp,1),1);
+	rccs(ii) = corr2(A,B);
+end
+
+% Calculate P values in each voxel
+PX = [];
+for ii = 1:length(ccs)
+	x = find(rccs>ccs(ii));
+	px = length(x)/length(ccs);
+	PX(ii) = px;
+end
+
+% FDR correction
+[PXsorted PXind] = sort(PX, 'ascend');
+FDRthr = Q*[1:length(ccs)]/length(ccs);
+Diff = PXsorted - FDRthr;
+thrInd = PXind(max(find(Diff<0)));
+thrP = PX(thrInd);
+thrCCs = ccs(thrInd);
+disp(['Threshold ccs = ' num2str(thrCCs)])
+
+% New ccs above threshold
+ccs(find(ccs < thrCCs)) = 0;
+
+
+% Mapping from 1d Data to 3d .nii data 
+RefEPI = [DataDir 'target_' ID '.nii'];
[…]

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/getResampInd.m

@@ -1,0 +1,27 @@
+function ssinds = getResampInd(samplenum, divsample)
+
+if ~exist('divsample', 'var')
+    divnum = 50;
+else
+    divnum = samplenum/divsample;
+end
+
+% get cross validation samples
+cvFrac = 0.1;
+randSeed = 1234;
+rand('twister',randSeed);
+randn('state',randSeed);
+
+zs=floor(samplenum/divnum);
+zr = reshape(1:zs*divnum, zs, divnum);
+
+ssinds = [];
+for ii=1:10
+  a=randperm(divnum);
+  regInd = zr(:,a(1:round(divnum*cvFrac)));
+  regInd = regInd(:)';
+  trnInd = setdiff(1:samplenum, [regInd]);
+  ssinds(ii).regInd = regInd;
+  ssinds(ii).trnInd = trnInd;
+end
+

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/getResampInd_repN.m

@@ -1,0 +1,32 @@
+function SSinds = getResampInd_repN(samplenum, repN , divsample)
+
+if ~exist('divsample', 'var')
+    divnum = 50;
+else
+    divnum = samplenum/divsample;
+end
+
+% get cross validation samples
+cvFrac = 0.2;
+randSeed = 1234;
+rand('twister',randSeed);
+randn('state',randSeed);
+
+zs=floor(samplenum/divnum);
+zr = reshape(1:zs*divnum, zs, divnum);
+
+for nn = 1:repN
+
+    ssinds = [];
+    for ii=1:10
+      a=randperm(divnum);
+      regInd = zr(:,a(1:round(divnum*cvFrac)));
+      regInd = regInd(:)';
+      trnInd = setdiff(1:samplenum, [regInd]);
+      ssinds(ii).regInd = regInd;
+      ssinds(ii).trnInd = trnInd;
+    end
+
+    SSinds{nn} = ssinds;
+
+end

### 2023-06-05 auditory/music_genre_fMRI/over_100_task/main.m

@@ -1,0 +1,97 @@
+% Analysis of behavioral data (Supplementary Figure 10)
+BehavAnalysis;
+
+%%
+% 当使用最小二乘法计算线性回归模型参数的时候，如果数据集合矩阵（也叫做设计矩阵(design matrix)）X，
+% 存在多重共线性，那么最小二乘法对输入变量中的噪声非常的敏感，其解会极为不稳定。
+% 为了解决这个问题，就有了脊回归（Ridge Regression ）
+% Ridge regression using Task-type and Cognitive-factor models:
+ID = 'sub-01'; % or 'sub-02', …, 'sub-06'
+addpath('../../../utils/freesurfer');  % Ridge_CerebCortex需要'MRIread'函数
+Ridge_CerebCortex(ID, 'TaskType');
+Ridge_FDRcorr(ID, 'TaskType');
+
+% Determining the best parameter for group PCA/HCA
+Method = 'TaskType';
+Ridge_CerebCortex_RepFit(ID, Method);
+ 
+% Get group ridge weight
+GroupWeight('TaskType');
+
+% Visualization of the hierarchical clustering analysis (Figure 2, 已经它上面的树状图)
+load('./SampleResult/GroupRidgeWeight.mat','w');
+Cluster_Visualize(w);
+
+% 层次化模型； Hierarchical model
+MakeHCAbase
+Ridge_CerebCortex_HCAModel(ID, 'TaskType');
+Ridge_FDRcorr(ID, 'HCA');
+
+% PCA可视化； Visualization of the principal component analysis (Figure 3a, b, S2, S3)
+load('./SampleResult/GroupRidgeWeight.mat','w');
+PCAvisualize_RGB(w);  % Figure 3a
+TargPC = 2;
+voxelID = SelectTargVoxelByPCA(ID, TargPC); % Select target voxel based on PCA result (e.g., TargPC = 2)
+PCAvisualize_PosNeg(w, ID, voxelID); % Top voxel of target PC (TargPC, e.g., 1,2,…) is used
+% For the visualization of IPL voxels, use voxel ID = 32850, 32824, and 29651.
+
+% Downloading of reference Neurosynth database is based on the instruction of following link:
+% https://github.com/neurosynth/neurosynth
+% Save the Neurosynth database in the “NSDir”.
+% 下载数据链接：https://github.com/neurosynth/neurosynth-data/archive/refs/tags/0.5.tar.gz
+% 怎么解析出需要的.nii.gz文件？
+
[…]

### 2023-06-05 auditory/music_genre_fMRI/preprocess/PreprocessRegex.m

@@ -1,0 +1,95 @@
+% function PreprocessRegex.m
+% 对所有的受试数据进行处理（暂时还没有GLM处理的过程）
+%
+% 对所有受试者的视频段1到8进行预处理
+% This function finds all the directories in the provided regular expression
+% and preprocesses the data for runIds from 1 to 8
+%
+% input:
+%   regex   -   dir regex
+%
+% ex. PreprocessRegex('/mnt/scratch/ioannis/studyforrest_preprocessed/sub-*/')
+% 
+% 在 Matlab 命令行中运行：
+% PreprocessRegex('/data3/dong/brain/auditory/music_genre_fMRI/preprocess/ds003720-download/sub-*/')
+
+function PreprocessRegex(regex)
+    
+    dirs = glob(regex);  % dirs = {dirs{2:5,1}}' % for debug
+
+    runIds = 1:18;
+    % test data
+%     runIds = 18 : -1 : 1;
+
+    for dir=dirs'
+        % prepare data
+        dst_dir = fullfile(dir{1}, 'func');
+        
+        % 重置测试镜像文件
+%         copyfile('/data3/whd/data/neuro/music_genre/ds003720-download_bak/sub-001/func/sub-001_task-Training_run-01_bold.nii', ...
+%             dst_dir);
+        
+%         if exist(dst_dir, 'dir')
+%            rmdir(dst_dir, 's'); 
+%         end
+%         path_names = strsplit(dir{1}, '/');
+%         cur_subject = path_names(end-1);
+%         src_dir = fullfile(raw_data_dir, cur_subject, 'ses-movie', 'func');
+%         copyfile(src_dir{1}, dst_dir);
+%         extract_all_file(dst_dir);
+        
+        for runId = runIds
+            fprintf('Processing run %d from %s\n', runId, dir{1});
+            Preprocess(dir{1}, runId);  
+%             spm_model(dir{1}, runId);
+        end
+    end
+end
+
+
+%% 
+% SPM12: spm_coreg (v7320)                           00:22:35 - 22/03/2022
+% ========================================================================
+% 22-Mar-2022 00:22:35 - Failed  'Coregister: Estimate'
+% Error using spm_vol>spm_vol_hdr (line 80)
+% File "/data3/dong/brain/auditory/music_genre_fMRI/preprocess/ds003720-download/sub-002/anat/sub-001_T1w.nii" does not exist.
[…]

### 2023-06-05 auditory/utils/helperAudioPreprocess.m

@@ -1,0 +1,24 @@
+function [predictor,response,segmentsPerFile] = helperAudioPreprocess(ads, overlap)
+% 支持函数 helperAudioPreprocess 将 audioDatastore 对象和 log mel 频谱图之间的重叠百分比作为输入，
+% 并返回适合输入到 VGGish 网络的预测变量和响应矩阵。
+
+numFiles = numel(ads.Files);
+
+% Extract predictors and responses for each file
+for ii = 1:numFiles
+    [audioIn,info] = read(ads);
+
+    fs = info.SampleRate;
+    features = vggishPreprocess(audioIn,fs,OverlapPercentage=overlap); 
+    numSpectrograms = size(features,4);
+
+    predictor{ii} = features;
+    response{ii} = repelem(info.Label,numSpectrograms);
+    segmentsPerFile(ii) = numSpectrograms;
+
+end
+
+% Concatenate predictors and responses into arrays
+predictor = cat(4,predictor{:});
+response = cat(2,response{:});
+end

### 2023-06-05 auditory/utils/helperPlotMaps.m

@@ -1,0 +1,20 @@
+% 支持函数 helperPlotMap 生成输入图像和指定的可解释性图的图。
+function helperPlotMaps(img,YPred,YTrue,maps,mapNames,viewingAngle,mapClass)
+nexttile
+surf(img,EdgeColor="none")
+view(viewingAngle)
+title({"True: "+ string(YTrue), "Predicted: " + string(YPred)}, ...
+    interpreter="none")
+colormap parula
+
+numMaps = length(maps);
+for i = 1:numMaps
+    map = maps{i};
+    mapName = mapNames(i);
+
+    nexttile
+    surf(map,EdgeColor="none")
+    view(viewingAngle)
+    title(mapName,mapClass,interpreter="none")
+end
+end

### 2023-06-05 consciousness/attention_schema/Experiment_1.py

@@ -1,0 +1,1100 @@
+#First we import some libraries
+#Json for loading and saving the model (optional)
+import json
+#Pandas for saving datasets
+import pandas as pd
+#matplotlib for rendering
+import matplotlib.pyplot as plt
+#numpy for handeling matrix operations
+import numpy as np
+#time, to, well... keep track of time
+import time
+#iPython display for making sure we can render the frames
+from IPython import display
+#seaborn for rendering
+import seaborn
+#pympler to find memory leaks
+# from pympler import muppy, summary, refbrowser
+# import objgraph
+#Keras is a deep learning libarary
+import tensorflow as tf
+print(tf.__version__)
+from tensorflow.keras.models import model_from_json
+from tensorflow.keras.models import Sequential
+from tensorflow.keras.layers import Dense
+from tensorflow.keras.optimizers import SGD
+
+import tf_agents
+from tf_agents.environments import py_environment
+from tf_agents.environments import tf_environment
+from tf_agents.environments import tf_py_environment
+from tf_agents.environments import utils
+from tf_agents.specs import array_spec
+from tf_agents.environments import wrappers
+from tf_agents.environments import suite_gym
+from tf_agents.trajectories import time_step as ts
+from tf_agents.agents.dqn import dqn_agent
+from tf_agents.agents.reinforce import reinforce_agent
+from tf_agents.networks import actor_distribution_network
+from tf_agents.drivers import dynamic_step_driver
+from tf_agents.networks import q_network
+from tf_agents.replay_buffers import tf_uniform_replay_buffer
+from tf_agents.utils import nest_utils
+
+import PIL.Image
+import copy
+from os import path, mkdir, chdir
+
+# gpu = tf.config.experimental.list_physical_devices('GPU')
+# tf.config.experimental.set_memory_growth(gpu[0], True)
+
+import os
+from datetime import datetime
+import math
+import pprint
+
+#Setup for memory profiling
+import sys
+# from memory_profiler import profile
+# %load_ext memory_profiler
+#Setup matplotlib so that it runs nicely in iPython
+# %matplotlib inline
+#setting up seaborn
+seaborn.set()
+
+print("The 'ball' is a leaf that drifts downward, randomly moving lateraly as well as descending. Attention starts on the ball at the beginning of each trial.")
+
+
+#%% Hyperparameters
+
+# How many trials back to store in each observation
+LOOK_BACK = 10
+
[…]

### 2023-06-05 consciousness/global_workspace_network/gwn/classifier.py

@@ -1,0 +1,769 @@
+# classifier.py
+# author: Cong Bao
+
+from __future__ import division
+from __future__ import print_function
+from __future__ import absolute_import
+
+import gc
+import os
+import re
+import json
+import random
+import collections
+
+import emoji
+import numpy as np
+import tensorflow as tf
+
+import gwn.model as model
+
+
+
+class Flag(object):
+    """
+    Running flags.
+
+    Properties:
+    + data_path: str, path of data file
+    + ckpt_path: str, path of checkpoint file
+    + output_dir: str, directory of output files
+    + model_name: str, name of model
+    + do_train: bool, whether to do train or not
+    + do_valid: bool, whether to do validation or not
+    + do_test: bool, whether to do test or not
+    + train_ids: list, indexes of train examples
+    + valid_ids: list, indexes of validation examples
+    + test_ids: list, indexes of test examples
+    + padding: bool, whether to pad sequence or not
+    + augment: bool, whether to augment data or not
+    + balance: bool, whether to do over-sampling or not
+    + learning_rate: float, learning rate
+    + sample_step: int, step of sampling
+    + n_train_epoch: int, number of epochs to train
+    + n_warmup_step: int, number of warm up steps
+    + train_batch_size: int, batch size for training
+    + valid_batch_size: int, batch size for validation
+    + test_batch_size: int, batch size for testing
+    + save_summary_steps: int, number of steps to save summary
+    + save_checkpoints_steps: int, number of steps to save checkpoint
+    + keep_checkpoint_max: int, number of checkpoint files to keep
+    + log_step_count_steps: int, number of steps to record log messages
+    """
+
+    def __init__(self):
+        self.data_path = None
+        self.ckpt_path = None
+        self.output_dir = 'output/'
+        self.model_name = 'gwn'
+        self.do_train = True
+        self.do_valid = True
+        self.do_test = True
+        self.train_ids = None
+        self.valid_ids = None
+        self.test_ids = None
+        self.padding = True
+        self.augment = True
+        self.balance = True
+        self.learning_rate = 1e-3
+        self.sample_step = 1
+        self.n_train_epoch = 30
+        self.n_warmup_step = 5
+        self.train_batch_size = 64
+        self.valid_batch_size = 16
+        self.test_batch_size = 16
+        self.save_summary_steps = 5
+        self.save_checkpoints_steps = 5
+        self.keep_checkpoint_max = None
+        self.log_step_count_steps = 1
+
+
+
[…]

### 2023-06-05 consciousness/global_workspace_network/gwn/model.py

@@ -1,0 +1,570 @@
+# model.py
+# author: Cong Bao
+
+from __future__ import division
+from __future__ import print_function
+from __future__ import absolute_import
+
+import six
+import copy
+import json
+import math
+
+import numpy as np
+import tensorflow as tf
+
+
+
+class GWNConfig(object):
+    """
+    Configuration for GWN model.
+
+    Properties:
+    + gws_size: int, size of global workspace (rnn cell)
+    + proj_size: int, size of final projection
+    + inter_size: int, size of intermediate layer
+    + hidden_size: int, size of mapping and attention heads
+    + n_head: int, number of attention heads
+    + self_atten: bool, whether apply self-attention or not
+    + atten_type: str, name of scoring function
+    + map_activ: str, name of activation function in mapping
+    + proj_activ: str, name of activation function in projection
+    + inter_activ: str, name of activation function in intermediate layer
+    + drop_rate: float, rate of dropout
+    """
+
+    def __init__(self):
+        self.gws_size = 64
+        self.proj_size = 64
+        self.inter_size = 128
+        self.hidden_size = 32
+        self.n_head = 4
+        self.self_atten = True
+        self.atten_type = 'scaled_dot_product'
+        self.map_activ = 'gelu'
+        self.proj_activ = 'tanh'
+        self.inter_activ = 'gelu'
+        self.drop_rate = 0.1
+
+
+
+class MappingPretrain(object):
+    """
+    Pretrain the mapping component.
+
+    Arguments:
+    + inputs: list, a list of input tensors for different modalities
+    + config: object, an instance of `GWNConfig`
+    + is_training: bool, whether is training or not
+
+    Properties:
+    + mapped_inputs: tensor (B, M, S, H), tensor after mapping
+    + loss: tensor (), loss of the pretrain model
+    """
+
+    def __init__(self, inputs, config, is_training):
+
+        config = copy.deepcopy(config)
+        if not is_training:
+            config.drop_rate = 0.0
+
+        with tf.variable_scope('gwn_model'):
+            with tf.variable_scope('mapping'):
+                self.mapped_inputs = mapping(
+                    input_list=inputs,
+                    units=config.hidden_size,
+                    activ=get_activ_fn(config.map_activ),
+                    dropout=config.drop_rate
[…]

### 2023-06-05 evolution/bioinfo/primatesdemo.m

@@ -1,0 +1,114 @@
+%% 为人科物种建立系统发育树
+% 此示例说明如何从人科类群（也称为猩猩科）的线粒体DNA(mtDNA)序列构建系统发育树。
+% 这个家庭包括大猩猩、黑猩猩、猩猩和人类。
+
+% 参考：https://ww2.mathworks.cn/help/bioinfo/ug/building-a-phylogenetic-tree-for-the-hominidae-species.html
+% 需要加载数据文件：mitochondria.mat、primates.mat、sequences.mdb
+data_dir = fullfile(matlabroot, 'examples', 'bioinfo');
+addpath(data_dir);
+
+%% 介绍
+% 线粒体 D环 是动物 DNA 中突变最快的序列区域之一，因此常用于比较密切相关的生物。
+% 现代人的起源是一个备受争议的问题，已通过使用 mtDNA 序列得到解决。
+% 人类 mtDNA 的有限遗传变异性已根据最近的共同遗传祖先得到解释，
+% 因此暗示所有现代人口的 mtDNA 可能起源于生活在非洲不到 200,000 年的单个女性。
+
+%% 从 GenBank® 中检索序列数据
+% 此示例使用为具有以下 GenBank 登录号的不同人科物种分离的线粒体 D 环序列。
+
+%        物种描述                  GenBank登录号
+data = {'German_Neanderthal'      'AF011222';  % 德国尼安德特人
+        'Russian_Neanderthal'     'AF254446';  % 俄罗斯尼安德特人
+        'European_Human'          'X90314'  ;  % 欧洲人
+        'Mountain_Gorilla_Rwanda' 'AF089820';  % 卢旺达山地大猩猩
+        'Chimp_Troglodytes'       'AF176766';  % 黑猩猩穴居人
+        'Puti_Orangutan'          'AF451972';  % 菩提猩猩
+        'Jari_Orangutan'          'AF451964';  % ?
+        'Western_Lowland_Gorilla' 'AY079510';  % 西非低地大猩猩
+        'Eastern_Lowland_Gorilla' 'AF050738';  % 东非低地大猩猩
+        'Chimp_Schweinfurthii'    'AF176722';  % 黑猩猩Schweinfurthii ?
+        'Chimp_Vellerosus'        'AF315498';
+        'Chimp_Verus'             'AF176731';
+       };
+   
+%%
+% 可以使用循环内的函数 |getgenbankfor| 从 NCBI 数据库中检索序列并将它们加载到 MATLAB® 中。
+%
[…]

### 2023-06-05 evolution/bioinfo/wholegenomedemo.m

@@ -1,0 +1,335 @@
+%% Comparing Whole Genomes
+% This example shows how to compare whole genomes for organisms, which
+% allows you to compare the organisms at a very different resolution
+% relative to single gene comparisons. Instead of just focusing on the
+% differences between homologous genes you can gain insight into the
+% large-scale features of genomic evolution.
+
+% 参考：Comparing Whole Genomes的例子
+% https://ww2.mathworks.cn/help/bioinfo/ug/comparing-whole-genomes.html
+% 需要引用数据"chlamydia.mat"和"sequences.mdb"
+
+
+%%
+% This example uses two strains of Chlamydia, Chlamydia trachomatis and
+% Chlamydophila pneumoniae. These are closely related bacteria that cause
+% different, though both very common, diseases in humans. Whole genomes are
+% available in the GenBank(R) database for both organisms. 
+
+
+%% Retrieving the Genomes
+% You can download these genomes using the |getgenbank| function. First,
+% download the Chlamydia trachomatis genome. Notice that the genome is
+% circular and just over one million bp in length. These sequences are
+% quite large so may take a while to download.
+%
+%   seqtrachomatis = getgenbank('NC_000117');
+
+%%
+% Next, download Chlamydophila pneumoniae. This genome is also circular and
+% a little longer at 1.2 Mbp.
+%
+%   seqpneumoniae = getgenbank('NC_002179');
+
+%%
+% For your convenience, previously downloaded sequences are included in a
+% MAT-file. Note that data in public repositories is frequently curated and 
+% updated. Hence, the results of this example might be slightly different
+% when you use up-to-date datasets.
+
+data_dir = fullfile(matlabroot, 'examples', 'bioinfo', 'data');
+load(fullfile(data_dir, 'chlamydia.mat'), 'seqtrachomatis', 'seqpneumoniae')
+
+%% 
+% A very simple approach for comparing the two genomes is to perform
+% pairwise alignment between all genes in the genomes. Given that these are
+% bacterial genomes, a simple approach would be to compare all ORFs in the
+% two genomes. However, the GenBank data includes more information about
+% the genes in the sequences. This is stored in the CDS field of the data
+% structure. Chlamydia trachomatis has 895 coding regions, while
[…]

### 2023-06-05 memory/Pinsky_Rinzel_CA3/Pinsky_Rinzel_Fig2.code.py

@@ -1,0 +1,215 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# In[12]:
+# Pinsky-Rinzel(PR)模型的放电行为.PR模型能够模拟癫痫样式放电和正常放电,
+# 癫痫样式的行为由29Hz的高频簇放电模拟,6Hz的低频放电模拟正常的神经元放电
+
+
+import numpy as np
+import scipy as sp
+from scipy.integrate import odeint, solve_ivp
+import matplotlib.pyplot as plt
+from peaks import *
+
+
+# In[13]:
+
+
+#Constants
+Gna = 30
+Gkdr = 15
+Gkca = 15
+Gkahp = 0.8
+Gca = 10
+Gl = 0.1
+Gc = 1.425
+Gnmda = 1.75
+Vna = 60 #Paper says 60, DB says 55 - DB has actually used 60.
+Vk = -75
+Vca = 80
+Vl = -60
+p = 0.5
+
+#Ca taken from modelDB (=Cad)
+Ca = 0.21664282 
+Cm = 3
+
+#Is and Id-diff values of them are given in the modelDB code.
+Isapp = -0.5
+Idapp = 0.0
+
+
+# In[14]:
+
+
+#Alpha and Beta functions and Chi
+#Heaviside Step function - Not used in the code
+def alphaM(Vs):
+    return (0.32*(-46.9 - Vs)/(np.exp((-46.9 - Vs)/4.0) - 1.0))
+
+def betaM(Vs):
+    return (0.28*(Vs + 19.9)/(np.exp((Vs + 19.9)/5.0) - 1.0))
+
+def Minf(Vs):
+    return (alphaM(Vs)/(alphaM(Vs) + betaM(Vs)))
+
+def alphaN(Vs):
+    return ((0.016*(-24.9 - Vs))/(np.exp((-24.9 - Vs)/5.0) - 1.0))
+
+def betaN(Vs):
+    return (0.25*np.exp(-1.0 - 0.025*Vs))
+
+def alphaH(Vs):
+    return (0.125*np.exp((-43.0-Vs)/18.0))
+
+def betaH(Vs):
+    return (4.0/(1.0 + np.exp((-20.0-Vs)/5.0)))
+
+def alphaS(Vd):
+    return (1.6/(1.0 + np.exp(-0.072*(Vd - 5.0))))
+
+def betaS(Vd):
[…]

### 2023-06-05 memory/spatial_memory_pipeline/src/classify_units.py

@@ -1,0 +1,305 @@
+# Copyright 2022 DeepMind Technologies Limited
+#
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+#      http://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+"""Classify units according to measureas used for biological cells."""
+import numpy as np
+
+from . import scores
+
+
+def _make_intervals(x):
+  """Given [0, 1, 2], return [-0.5, 0.5, 1.5, 2.5]."""
+  d = np.diff(x)
+  return np.concatenate([
+      [x[0] - d[0] / 2.0],  # first interval's left bound
+      x[:-1] + d / 2.0,  # interval separations
+      [x[-1] + d[-1] / 2.0]  # last interval's right bound
+  ])
+
+
+def _rotate_distances(distances, hd):
+  """Rotate allocentric distances to egocentric according to head direction.
+
+  Args:
+    distances: Array of shape [B, n_angles].`n_angles` the number of angles in
+      the rat's distance sensor. The values are the distances to the closest
+      wall for each world (allocentric) angle. The angles they correspond to are
+      supposed to be equispaced at 2 * pi / `n_angles` rad of each other.
+    hd: Array of shape [B]. For each distance, the corresponding allocentric
+      head direction, in radians.
+
+  Returns:
+    Array of same shape as `distances`, each row shifted (rotated) to make
+    the distances egocentric.
+  Raises:
+    ValueError: The dimensions of `distances` and/or `hd` are not as expected.
+  """
+  hd = hd.squeeze()  # it comes with trailing dimension typically
+  if hd.ndim != 1:
+    raise ValueError("Head direction should be a vector.")
+  if distances.ndim != 2:
+    raise ValueError("Distances should be a 2-D array.")
+  if hd.shape[0] != distances.shape[0]:
+    raise ValueError("Head direction should have same batch size as distances.")
+  n_angles = distances.shape[1]
[…]

### 2023-06-05 society/justice/voi_ai_study_1_analysis.R

@@ -1,0 +1,419 @@
+# Copyright 2022 DeepMind Technologies Limited.
+#
+#
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+# https://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+# Load packages ----------------------------------------------------------------
+
+suppressPackageStartupMessages(library(ggeffects))
+suppressPackageStartupMessages(library(ggplot2))
+suppressPackageStartupMessages(library(irr))
+suppressPackageStartupMessages(library(rms))
+suppressPackageStartupMessages(library(tidyverse))
+
+# Define utility functions -----------------------------------------------------
+
+source('voi_ai_utils.R')
+
+# Read and process data --------------------------------------------------------
+
+# Read study data.
+raw_study_data <- read.csv('voi_ai_study_1_data.csv')
+
+# Prepare data for analysis.
+study_df <- raw_study_data %>%
+  # Cast variables to correct types.
+  mutate(
+    Participant = as.factor(Participant),
+    Condition = as.factor(Condition),
+    Passed_Comp_Test = as.logical(Passed_Comp_Test),
+    Position = as.factor(Position),
+    Chose_Prioritarian = as.integer(Chose_Prioritarian),
+    Repeat = as.integer(Repeat),
+    Motiv_To_Change = as.logical(Motiv_To_Change),
+    Motiv_To_Maximize = as.logical(Motiv_To_Maximize),
+    Motiv_To_Prioritize = as.logical(Motiv_To_Prioritize),
+    Risk = as.integer(Risk),
+    Pol_A = as.integer(Pol_A),
+    Pol_B = as.integer(Pol_B),
+    Fairness_Reasoning = as.integer(Fairness_Reasoning),
[…]

### 2023-06-05 society/justice/voi_ai_study_3_analysis.R

@@ -1,0 +1,369 @@
+# Copyright 2022 DeepMind Technologies Limited.
+#
+#
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+# https://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+# Load packages ----------------------------------------------------------------
+
+suppressPackageStartupMessages(library(ggeffects))
+suppressPackageStartupMessages(library(ggplot2))
+suppressPackageStartupMessages(library(irr))
+suppressPackageStartupMessages(library(rms))
+suppressPackageStartupMessages(library(tidyverse))
+
+# Define utility functions -----------------------------------------------------
+
+source('voi_ai_utils.R')
+
+# Read and process data --------------------------------------------------------
+
+# Read study data.
+raw_study_data <- read.csv('voi_ai_study_3_data.csv')
+
+# Prepare data for analysis.
+study_df <- raw_study_data %>%
+  # Cast variables to correct types.
+  mutate(
+    Participant = as.factor(Participant),
+    Condition = as.factor(Condition),
+    Passed_Comp_Test = as.logical(Passed_Comp_Test),
+    Saw_Correct_Harvest = as.logical(Saw_Correct_Harvest),
+    Position = as.factor(Position),
+    Chose_Prioritarian = as.integer(Chose_Prioritarian),
+    Repeat = as.integer(Repeat),
+    Motiv_To_Change = as.logical(Motiv_To_Change),
+    Motiv_To_Maximize = as.logical(Motiv_To_Maximize),
+    Motiv_To_Prioritize = as.logical(Motiv_To_Prioritize),
+    Risk = as.integer(Risk),
+    Pol_A = as.integer(Pol_A),
[…]

### 2023-06-05 society/justice/voi_ai_study_4_analysis.R

@@ -1,0 +1,268 @@
+# Copyright 2022 DeepMind Technologies Limited.
+#
+#
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+# https://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+# Load packages ----------------------------------------------------------------
+
+suppressPackageStartupMessages(library(irr))
+suppressPackageStartupMessages(library(rms))
+suppressPackageStartupMessages(library(tidyverse))
+
+# Define utility functions -----------------------------------------------------
+
+source('voi_ai_utils.R')
+
+# Read and process data --------------------------------------------------------
+
+# Read study data.
+raw_study_data <- read.csv('voi_ai_study_4_data.csv')
+
+# Prepare data for analysis.
+study_df <- raw_study_data %>%
+  # Cast variables to correct types.
+  mutate(
+    Participant = as.factor(Participant),
+    Condition = as.factor(Condition),
+    Passed_Comp_Test = as.logical(Passed_Comp_Test),
+    Position = as.factor(Position),
+    Chose_Prioritarian = as.integer(Chose_Prioritarian),
+    Repeat = as.integer(Repeat),
+    Motiv_To_Change = as.logical(Motiv_To_Change),
+    Motiv_To_Maximize = as.logical(Motiv_To_Maximize),
+    Motiv_To_Prioritize = as.logical(Motiv_To_Prioritize),
+    Risk = as.integer(Risk),
+    Pol_A = as.integer(Pol_A),
+    Pol_B = as.integer(Pol_B),
+    Fairness_Reasoning = as.integer(Fairness_Reasoning),
+  ) %>%
+  # Filter out participants who failed the comprehension test.
+  filter(Passed_Comp_Test)
+
[…]

### 2023-06-05 society/justice/voi_ai_study_5_analysis.R

@@ -1,0 +1,268 @@
+# Copyright 2022 DeepMind Technologies Limited.
+#
+#
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+# https://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+# Load packages ----------------------------------------------------------------
+
+suppressPackageStartupMessages(library(irr))
+suppressPackageStartupMessages(library(rms))
+suppressPackageStartupMessages(library(tidyverse))
+
+# Define utility functions -----------------------------------------------------
+
+source('voi_ai_utils.R')
+
+# Read and process data --------------------------------------------------------
+
+# Read study data.
+raw_study_data <- read.csv('voi_ai_study_5_data.csv')
+
+# Prepare data for analysis.
+study_df <- raw_study_data %>%
+  # Cast variables to correct types.
+  mutate(
+    Participant = as.factor(Participant),
+    Condition = as.factor(Condition),
+    Passed_Comp_Test = as.logical(Passed_Comp_Test),
+    Position = as.factor(Position),
+    Chose_Prioritarian = as.integer(Chose_Prioritarian),
+    Repeat = as.integer(Repeat),
+    Motiv_To_Change = as.logical(Motiv_To_Change),
+    Motiv_To_Maximize = as.logical(Motiv_To_Maximize),
+    Motiv_To_Prioritize = as.logical(Motiv_To_Prioritize),
+    Risk = as.integer(Risk),
+    Pol_A = as.integer(Pol_A),
+    Pol_B = as.integer(Pol_B),
+    Fairness_Reasoning = as.integer(Fairness_Reasoning),
+  ) %>%
+  # Filter out participants who failed the comprehension test.
+  filter(Passed_Comp_Test)
+
[…]

### 2023-06-05 utils/matlab_utils/AppendArff.m

@@ -1,0 +1,48 @@
+% function AppendArff:
+%
+% Loads the given ARFF file appends the provided attribute and saves the data
+% the original file
+%
+% input:
+%   arffFile    - file to load the data from
+%   attData     - attribute data
+%   attName     - attribute name
+%   attType     - attribute type (Integer or Numeric accepted for now)
+%   extraId     - extension to add to the name before file extension
+
+function AppendArff(arffFile, attData, attName, attType, extraId)
+    if (nargin<5)
+        extraId = '';
+    end
+    % initially load data
+    [data, metadata, attributes, relation] = LoadArff(arffFile);
+
+    % check if attribute already exists
+    for i=1:size(attributes,1)
+        if (strcmpi(attributes{i,1}, attName))
+            error(['Attributes "' attName '" already exists in file ' arffFile]);
+        end
+    end
+
+    % check for data and attribute values
+    assert(size(data,1)==size(attData,1), 'Attribute data and arff data should be of the same length');
+
+    % set data
+    appData = zeros(size(data,1), size(data,2)+1);
+    appData(:,1:end-1) = data;
+    appData(:,end) = attData;
+
+    % append attribute
+    index = size(attributes,1)+1;
+    attributes{index,1} = attName;
+    attributes{index,2} = attType;
+
+    [dir, name, ext] = fileparts(arffFile);
+    outArffFile = [name extraId ext];
+    if (~isempty(dir))
+        outArffFile = [dir '/' outArffFile];
+    end
+
+    % save to the same file
+    SaveArff(outArffFile, appData, metadata, attributes, relation);
+end    

### 2023-06-05 utils/matlab_utils/IsOctave.m

@@ -1,0 +1,12 @@
+%
+% Return: true if the environment is Octave.
+%
+function retval = IsOctave
+  persistent cacheval;  % speeds up repeated calls
+
+  if isempty (cacheval)
+    cacheval = (exist ("OCTAVE_VERSION", "builtin") > 0);
+  end
+
+  retval = cacheval;
+end

### 2023-06-05 utils/matlab_utils/SaveArff.m

@@ -1,0 +1,127 @@
+% SaveArff.m
+%
+% Function to save ARFF data to file.
+% 
+% input:
+%   arffFile    - name of the file to save data
+%   data        - data to write in arff file
+%   metadata    - metadata struct in
+%   attributes  - nx2 cell array holding the attribute names
+%   relation    - relation described in the file
+%   comments    - (optional) nx1 cell array containing one comment line per cell
+
+function SaveArff(arffFile, data, metadata, attributes, relation, comments)
+    if (nargin < 6)
+        comments = {};
+    end
+    % check input
+    assert(isfield(metadata,'width_px'), 'metadata should contain "width_px" field');
+    assert(isfield(metadata,'height_px'), 'metadata should contain "height_px" field');
+    assert(isfield(metadata,'width_mm'), 'metadata should contain "width_mm" field');
+    assert(isfield(metadata,'height_mm'), 'metadata should contain "height_mm" field');
+    assert(isfield(metadata,'distance_mm'), 'metadata should contain "distance_mm" field');
+    assert(size(relation,2)>0, 'relation should not be empty');
+    assert(size(attributes,1)==size(data,2), 'attribute number should be the same with data');
+
+    % start writing
+    fid = fopen(arffFile, 'w+');
+
+    % write relation
+    fprintf(fid, '@RELATION %s\n\n', relation);
+
+    % write metadata
+    fprintf(fid, '%%@METADATA width_px %d\n', metadata.width_px);
+    fprintf(fid, '%%@METADATA height_px %d\n', metadata.height_px);
+    fprintf(fid, '%%@METADATA width_mm %.2f\n', metadata.width_mm);
+    fprintf(fid, '%%@METADATA height_mm %.2f\n', metadata.height_mm);
+    fprintf(fid, '%%@METADATA distance_mm %.2f\n\n', metadata.distance_mm);
+
+    % write metadata extras. Those are data that vary between experiments
+    for i=1:size(metadata.extra,1)
+        fprintf(fid, '%%@METADATA %s %s\n', metadata.extra{i,1}, metadata.extra{i,2});
+    end
+    % print an empty line
+    fprintf(fid, '\n');
+
+    % write attributes and get their type
+    % 1 = integer
+    % 2 = numeric
+    % -1 = other
+    numAtts = size(attributes,1);
+    attType = -1*ones(numAtts,1);
+    numMaps = cell(numAtts,1);
+    for i=1:numAtts
[…]

### 2023-06-05 visual/dorsal/auto.m

@@ -1,0 +1,67 @@
+
+%% 环境初始化
+run('./config.m');
+proj_dir = fileparts( mfilename('fullpath') );
+
+%% 视频数据处理
+
+%% 视觉跟踪测试
+track_forrest_cmd = [python2_path, ' ', ...
+    fullfile(proj_dir, 'scripts', 'demo_btn_forrest.py')];
+disp(track_forrest_cmd);
+[~, track_out] = system(track_forrest_cmd);
+% 使用命令行运行Python脚本和Pycharm运行Python有区别
+% 当前工作路径应修改为工程主目录，而不是脚本所在的目录。
+
+
+%% 处理眼动数据
+gaze_analysis_dir = fullfile(proj_dir, 'gaze', 'analysis');
+addpath(gaze_analysis_dir);
+
+% 将“研究阿甘”的眼动数据转换为Arff格式
+% Studyforrest2ArffRegex(... 
+%     fullfile(data_home_dir, '*', '*', '*', '*movie*events.tsv'), ...
+%     fullfile(data_home_dir, '*', '*', '*', '*eyegaze_physio.tsv'), ...
+%     fullfile(proj_dir, 'result' ,'gaze_data') ...
+% );
+
+% 平稳跟踪检测
+% utils/sp_tools/run_detection.py
+
+% 回归出平稳跟踪、注视和运动
+sp_sacc_motion_analysis_dir = fullfile(gaze_analysis_dir, 'sp_saccade_motion_analysis');
+addpath(sp_sacc_motion_analysis_dir);
+% ComputeRegressorsAll.m
+
+
+%% 处理核磁共振数据
+
+% 对所有受试者视频段1到8进行预处理
+% PreprocessRegex('/data2/whd/workspace/data/neuro/software/ds000113/sub-*/')
+PreprocessRegex(fullfile(data_home_dir, 'sub-*/'));
+
+
+% 一阶段分析（个体层次）
+% run_1stLevelAnalysis.m
+
+% 不同眼动类型之间对比分析
+% run_ContrastAnalysis.m
+
+% 二阶段（不同受试者之间）分析并可视化
+score_dir = fullfile(proj_dir, 'score');
+addpath(score_dir);
+% analysis_fMRI.m
+
+%% 视觉跟踪和平稳跟踪之间的相似度分数
+
+% 获得和平稳跟踪相关脑区的镜像数据
+% get_image_data.m
+
[…]

### 2023-06-05 visual/dorsal/gaze/analysis/Studyforrest2ArffRegex.m

@@ -1,0 +1,58 @@
+% function Studyforrest2ArffRegex:
+% gets as inputs regular expressions to gaze and events files. 
+% The execution of this function is around 3 times faster in matlab
+%
+% input:
+%   eventsFiles - regex to events files
+%   gazeFiles   - regex to gaze files
+%   outputDir   - directory to save results (.arff)
+%
+% ex. fMRI results
+% Studyforrest2ArffRegex('/path/to/studyforrest/*/*/*/*movie*events.tsv', '/path/to/studyforrest/*/*/*/*eyegaze_physio.tsv', '/path/to/results');
+%
+% Studyforrest2ArffRegex('/data2/whd/workspace/data/neuro/software/ds000113/sub-01/ses-movie/func/sub-01_ses-movie_task-movie_run-1_events.tsv', '/data2/whd/workspace/data/neuro/software/ds000113/sub-01/ses-movie/func/sub-01_ses-movie_task-movie_run-1_recording-eyegaze_physio.tsv', '/data2/whd/workspace/sot/hart/result/gaze_data');
+% Studyforrest2ArffRegex('/data2/whd/workspace/data/neuro/software/ds000113/*/*/*/*movie*events.tsv', '/data2/whd/workspace/data/neuro/software/ds000113/*/*/*/*eyegaze_physio.tsv', '/data2/whd/workspace/sot/hart/result/gaze_data');
+
+function Studyforrest2ArffRegex(eventFiles, gazeFiles, outputDir)
+    % set metadata for fMRI and lab experiments
+    metadataFmri.width_px = 1280;
+    metadataFmri.height_px = 546;
+    metadataFmri.width_mm = 265;
+    metadataFmri.height_mm = 113;
+    metadataFmri.distance_mm = 630;
+    metadataFmri.extra = {};
+
+    metadataLab.width_px = 1280;
+    metadataLab.height_px = 546;
+    metadataLab.width_mm = 522;
+    metadataLab.height_mm = 223;
+    metadataLab.distance_mm = 850;
+    metadataLab.extra = {};
+
+    eventFilelist = glob(eventFiles);
+    gazeFilelist = glob(gazeFiles);
+
+    assert(size(eventFilelist,1)==size(gazeFilelist,1), 'Provided regular expressions returned different number of files');
+
+    % Subjects 1 to 20 were recorded in the scanner. Subjects 21 to 36 were recorded in the lab
+    for fileId=1:size(eventFilelist,1)
[…]

### 2023-06-05 visual/dorsal/gaze/analysis/sp_saccade_motion_analysis/run_1stLevelAnalysis.m

@@ -1,0 +1,24 @@
+% replace 1stLevelAnalysis.sh
+% 运行一阶段分析（个体层次）
+subjects = dir('/data2/whd/workspace/data/neuro/software/ds000113');  % 12
+preprocDir="/data2/whd/workspace/data/neuro/software/ds000113/";
+analysisBaseDir="/data2/whd/workspace/sot/hart/gaze/analysis/sp_saccade_motion_analysis/sp_sacc_motion_analysis/";
+% if exist(analysisBaseDir, 'dir')
+%     rmdir(analysisBaseDir, 's');
+% end
+% mkdir(analysisBaseDir);
+
+% 对每个受试者的目录分别进行处理
+for i = 1 : length(subjects)
+    if strcmpi(subjects(i).name, '.') == 1 || strcmpi(subjects(i).name, '..') == 1
+        continue;
+    end
+    subDir = fullfile(preprocDir, subjects(i).name, 'ses-movie', 'func');
+    initsDir = 'regressors';  % 回归变量（平滑跟踪、扫视）目录（由ComputeRegressorAll.m计算获得，每一行：开始时间、持续时间、sp值）
+    analysisDir = fullfile(analysisBaseDir, subjects(i).name);
+    sub_name = subjects(i).name;
+    Create1stLevelMat(char(analysisDir), char(subDir), initsDir, sub_name(5:6));
+end
+% Create1stLevelMat('/data2/whd/workspace/sot/hart/gaze/analysis/sp_saccade_motion_analysis/sp_sacc_motion_analysis/sub-01', ...
+%  '/data2/whd/workspace/data/neuro/software/ds000113/sub-01/ses-movie/func', ...
+%   'regressors', '01');

### 2023-06-05 visual/dorsal/gaze/analysis/sp_saccade_motion_analysis/run_ContrastAnalysis.m

@@ -1,0 +1,14 @@
+%% 不同眼动类型之间对比分析
+run('../init_env.m');
+
+analysisBaseDir = '/data2/whd/workspace/sot/hart/gaze/analysis/sp_saccade_motion_analysis/sp_sacc_motion_analysis/';
+
+subjects = dir(analysisBaseDir);
+
+for i = 1 : length(subjects)
+    if strcmpi(subjects(i).name, '.') == 1 || strcmpi(subjects(i).name, '..') == 1
+        continue;
+    end
+    sub_dir = fullfile(subjects(i).folder, subjects(i).name);
+    ContrastAnalysis(sub_dir);
+end

### 2023-06-05 visual/dorsal/gaze/extract_all_file.m

@@ -1,0 +1,49 @@
+% nohup matlab -nodesktop -nosplash -r extract_all_file > extract_all_file.log &
+function r = extract_all_file(data_home_dir)
+% clc,close,clear
+
+% diary('extract_all_file.log');
+% diary on;
+
+% cur_dir = fileparts( mfilename('fullpath') );
+% eval(sprintf('cd %s', cur_dir));
+% addpath(cur_dir);
+
+% run('../config.m');
+% addpath('../utils/');
+
+% only extract the files in specified directory by overwriting this
+% variable.
+% data_home_dir = '/data2/whd/workspace/data/neuro/software/ds000113/sub-01/ses-movie/'; % sub-03
+
+%% 
+% sub-01/ses-forrestgump/func
+% the processed data is copied from '/data2/whd/workspace/data/neuro/ds000113-download/'
+% data_home_dir = '/data2/whd/workspace/data/neuro/software/ds000113/';
+% all_files = RangTraversal(data_home_dir);
+
+% extract file to current directory
+i = 0;
+FileData = {};
+
+all_files = RangTraversal(data_home_dir); % 获取所有文件
+len_File = size(all_files); % 获取文件列表长度
+
+for i = 1:len_File
+    cur_file = all_files{i};
+    dot = max(find(cur_file == '.'));
+    suffix = cur_file(dot:dot+2);
+	% 后缀为.gz文件
+	if strcmp(suffix, '.gz') == 1
+        disp(cur_file);
+        [cur_file_path, cur_file_name] = fileparts(cur_file);
+        
+        gunzip(cur_file, cur_file_path);
+        
+		i = i+1;
+	end
+end
+
+% diary off;
+
+end

### 2023-06-05 visual/dorsal/hart/model/attention_ops.py

@@ -1,0 +1,495 @@
+# -*- coding:utf-8 -*-
+########################################################################################
+# 
+# Hierarchical Attentive Recurrent Tracking
+# Copyright (C) 2017  Adam R. Kosiorek, Oxford Robotics Institute, University of Oxford
+# email:   adamk@robots.ox.ac.uk
+# webpage: http://ori.ox.ac.uk
+# 
+# This program is free software; you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation; either version 3 of the License, or
+# (at your option) any later version.
+# 
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+# You should have received a copy of the GNU General Public License
+# along with this program. If not, see <http://www.gnu.org/licenses/>.
+# 
+########################################################################################
+
+import numpy as np
+import tensorflow as tf
+# from tensorflow.contrib.rnn.python.ops.core_rnn_cell_impl import LSTMCell
+from tensorflow.contrib.rnn.python.ops.lstm_ops import LSTMBlockCell
+# from tensorflow.python.ops.rnn_cell_impl import _RNNCell as RNNCell
+from tensorflow.python.ops.rnn_cell_impl import RNNCell
+from tensorflow.python.util import nest
+
+from hart.model import tensor_ops
+from hart.model.nn import DynamicFilterModel
+from hart.model.rnn import ZoneoutWrapper, IdentityLSTMCell
+from neurocity.component.layer import AffineLayer, ConvLayer
+from neurocity.tensor_ops import convert_shape
+
+
+def gaussian_mask(params, R, C):
+    """Define a mask of size RxC given by one 1-D Gaussian per row.
+
+    u, s and d must be 1-dimensional vectors"""
+    u, s, d = (params[..., i] for i in xrange(3))
+
+    for i in (u, s, d):
+        assert len(u.get_shape()) == 1, i
+
+    batch_size = tf.to_int32(tf.shape(u)[0])
+
+    R = tf.range(tf.to_int32(R))
+    C = tf.range(tf.to_int32(C))
[…]

### 2023-06-05 visual/dorsal/predictivePursuit/gen_pursuit_eye_velocity.m

@@ -1,0 +1,205 @@
+% 预测性平滑跟踪实验的主脚本。Main script to run the predictive smooth pursuit experiment
+% 作者：王海东
+% 基于 : Hirak J Kashyap, UC Irvine
+% Based on FORCE learning code by David Sussillo (Neuron 2009)
+% output: pursuit_fig.jpg
+disp('Clearing workspace');
+clear;
+
+rng(0);          % 为了实验复现（任何种子都可以）For reproducibility -- any seed is fine
+% target = "ramp";
+target = "sine"; % 是否运行预测性正弦指数，或者初始ramp指数。whether to run the predicitve "sine" exp. or initiation "ramp"exp.
+numTrials = 10;  % 实验的尝试次数。trials of the experiment
+feedback = 1;    % RNN的输出反馈（考虑反馈）。 Output feedback to the RNN 0/1
+N = 500;         % RNN中神经元的个数。 Number of neurons in RNN
+p = 1.0;         % 初始权重分布宽度的倒数。 1/width of initial weight distribution
+dt = 0.001;
+dtt = dt * 100;
+step = 16;                % 一个仿真步中dt的单位。 Units of dt in a simulation step
+% 神经系统具有分叉、混沌和奇怪吸引子动力学行为。
+% 混沌神经网络模型是在Hopfield神经网络中引入一个具有混沌特性的负反馈项。
+% 循环网络的权重初始化：均值为0，标注差为1.5的高斯分布，导致一种自发地混沌行为。
+g = 1.5;                  % g大于1表示是一个混沌网络。 g greater than 1 leads to chaotic networks.
+wf = 2.0*(rand(N,1)-0.5); % 反馈权重(500*1)。 Feedback weights
+delay = 80/step;          % 生物物理学 输入延迟的长度(5)。 Length of biophysical input delay 
+learn_every = delay;
+
+blank_starts = [25, 15, 15];
+blank_ends =   [25, 20, 25];
+
+% 绘制三种遮挡情况的图
+figure;
+for i = 1 : size(blank_starts, 2)
+    if target == "sine"
+        nsecs = 25;        % 实验时间（秒） Experiment time in seconds
+        blankStart = blank_starts(i); % 空白周期的开始时间（以逗号分隔）。 start time(s) of blank period(s) separated by comma(s)
+        blankEnd = blank_ends(i);   % end time(s) of blank period(s) separated by comma(s)
[…]

### 2023-06-05 visual/dorsal/predictivePursuit/get_RS.m

@@ -1,0 +1,44 @@
+% 绘制视网膜滑动(Retinal Slip)
+% Author : Hirak J Kashyap, UC Irvine
+% 之前需要运行 main_sp_predict.m
+% output: rs_fig.jpg
+clear;
+speed=0.7;
+findOptLatency = 1;
+target = "sine";
+accmean = [];
+accsd = [];
+tLatencymean = [];
+tLatencysd = [];
+vel500sd = [];
+
+filename = strcat("pursuit_",target,"_",num2str(speed),".mat");
+load(filename, 'zt_t', 'nsecs', 'simtime', 'step', 'ft', 'numTrials', 'amp', 'blankStart', 'blankEnd', 'delay', 'mask', 'startStim');
+
+rs = zeros(size(zt_t));
+
+for iTrial = 1:size(zt_t,3)
+    rs(:,:,iTrial) = zt_t(:,:,iTrial)-ft;
+end
+
+%rs = rs/size(zt_t,3);
+
+colorVec = hsv(numTrials);
+figure;
+set(gca,'XTick', [simtime(1):1/step:simtime(end)]*step);
+plot(simtime*step, ft, '--', 'linewidth', 1, 'color', 'black');  % 1*1526, 虚线：函数目标 function target 
+ylim([-1 1]);
+hold on;
+% for i = 1:size(rs,3)
+%     plot(simtime*step, rs(:,:,i), 'linewidth', 2, 'color', colorVec(i,:));
+% end
+plot(simtime*step, mean(rs,3), 'linewidth', 2, 'color', 'black');  % 1*1526*10，10次尝试做平均
+xlabel('Time (s)');
+ylabel('RS/Target velocity (deg/s)')
+
+%% Save figure to local file
+% rs_fig = gca;
+% conf
+% output_file_name = fullfile(latex_home,  'imgs', 'rs_fig');  % latex image path
+% print(output_file_name, '-djpeg', '-f1', '-r600');
+% print -f1 -r600 -djpeg imgs/rs_fig;

### 2023-06-05 visual/dorsal/score/basic_usage.py

@@ -1,0 +1,27 @@
+import brainscore
+import os
+import pickle
+
+filename = 'dicarlo.MajajHong2015.public'
+# filename = 'dicarlo.Majaj2015'
+
+saved_filename = os.path.join('data', filename)
+# if os.path.exists(saved_filename) == False:
+#     os.mkdir('data')
+
+if os.path.exists(saved_filename) == False:
+    data = brainscore.get_assembly(filename)
+    with open(saved_filename, 'wb') as f:
+        pickle.dump(data, f, protocol=pickle.HIGHEST_PROTOCOL)
+else:
+    with open(saved_filename, 'rb') as f:
+        data = pickle.load(f)
+
+
+from brainscore.metrics.rdm import RDM
+metric = RDM()
+score = metric(assembly1=data, assembly2=data)  # np.corrcoef
+# > Score(aggregation: 2)>
+# > array([1., 0.])
+# > Coordinates:
+# >   * aggregation    'center' 'error'

### 2023-06-05 visual/dorsal/score/get_GLM_intensity.m

@@ -1,0 +1,88 @@
+%% 从GLM得到的脑区中得到强度值
+
+%%
+addpath('utils');
+proj_home = fileparts( fileparts( mfilename('fullpath') ) );
+res_dir = fullfile(proj_home, 'result');
+addpath(fullfile(proj_home, 'utils/', 'spm12/'));
+
+%% Load Image Data
+image_filename = '/data2/whd/workspace/sot/hart/gaze/analysis/sp_saccade_motion_analysis/sp_sacc_motion_analysis/sub-01/spmT_0001.nii';
+
+[imageFileName, M, DIM, TF, df, mni, intensity] ...
+    = get_image_file(image_filename);
+mni = mni{1};
+intensity = intensity{1};
+
+%% Load Brain Area Data
+X = load('data/TDdatabase');
+wholeMaskMNIAll = X.wholeMaskMNIAll;
+
+
+%% Filter with brain area
+V1_mask = wholeMaskMNIAll.brodmann_area_17;
+MT_mask = wholeMaskMNIAll.brodmann_area_21;
+FEF_mask = wholeMaskMNIAll.brodmann_area_8;
+
+% pcshow(pointCloud(V1_mask))
+% pcshow(pointCloud(mni))
+
+
+V1_intensity = zeros(1, length(V1_mask));
+MT_intensity = zeros(1, length(MT_mask));
+FEF_intensity = zeros(1, length(FEF_mask));
+V1_idx = 0;
+MT_idx = 0;
+FEF_idx = 0;
+for j = 1 : length(V1_mask)
+    for i = 1 : length(mni)
+        cur_mni = mni(i, :);
+        if sum(cur_mni == V1_mask(j, :)) == 3  % coordinate match
+            V1_idx = V1_idx + 1;
+            V1_intensity(V1_idx) = intensity(i);
+            break;
+        end
+    end
+    disp(j)
+end
+V1_intensity = V1_intensity(1:V1_idx);  % crop 
+
+for j = 1 : length(MT_mask)
+    for i = 1 : length(mni)
+        cur_mni = mni(i, :);
+        if sum(cur_mni == MT_mask(j, :)) == 3
+            MT_idx = MT_idx + 1;
+            MT_intensity(MT_idx) = intensity(i);
+            break;
+        end
+    end
+    disp(j);
+end
+MT_intensity = MT_intensity(1:MT_idx);
+
+for j = 1 : length(FEF_mask)
+    for i = 1 : length(mni)
[…]

### 2023-06-05 visual/dorsal/score/track_score.m

@@ -1,0 +1,229 @@
+%%
+% 分别加载script/demo_btn_forrest_batch.py得到的深度模块vt得到的激活特征 和score/get_priori_intensity_par.m处理得到的大脑激活强度信息
+
+clc; clear;
+
+feature_dim = 1000;
+gaze_radius_scale = 8;  % 半径缩小的倍数
+
+cur_dir = fileparts( mfilename('fullpath') );
+% project_home_dir = fileparts(cur_dir);
+
+run('../config.m');
+% addpath(fullfile(project_home_dir, 'utils', 'matlab_utils'));
+
+
+%% LSTM feature
+seg_dir = fullfile(proj_home_dir, 'data', 'seg/');
+segs = dir(seg_dir);
+segs = segs(cellfun(@valid_dir_name, {segs.name}));
+segs_name = cellfun(@(x) str2double(x), {segs.name});  % 对cell数组中的名字字段都转换成int，以便进行排序
+[blah, order] = sort(segs_name);
+segs = segs(order);  % 对cell数组按照排序好的名字字段进行重新调整行顺序
+
+vt_feature_accum = cell(length(segs), 1);
+MT_intensity_accum = cell(length(segs), 1);
+iou = 0;
+for i = 1 : length(segs)
+    cur_seg_dir = fullfile(segs(i).folder, segs(i).name);
+    img_num = numel(dir(fullfile(cur_seg_dir, '*.png')));  % 获得当前跟踪序列的图片数
+    vt_feature = importdata(fullfile(cur_seg_dir, 'feature',  ...
+        sprintf('frame-1-%02d_vt_feature', img_num) ) );  % 每个跟踪序列都少了一张图片的vt特征？
+    vt_feature_accum{i} = vt_feature;
+    
+    intensity_dir = fullfile(cur_seg_dir, 'intensity');
+    MT_idx = 0;
+    cur_MT_intensity = [];
+    for j = 2 : size(vt_feature, 1)+1
+        MT_idx = MT_idx+1;
+        cur_MT_intensity(MT_idx, :) = importdata(fullfile(intensity_dir, ...
+            sprintf('sub-01_frame-%d_MT_intensity.txt', j)));
+    end
+    MT_intensity_accum{i} = cur_MT_intensity;
+    
+    %% 计算目标跟踪框和凝视范围的交兵比
+    % 加载目标跟踪框的结果
[…]

### 2023-06-05 visual/dorsal/score/utils/row_index.m

@@ -1,0 +1,13 @@
+% 在A中查找item
+% 如果不存在，idx=0；
+% 如果存在曾返回对应A中的索引idx
+function idx = row_index(A, item)
+idx = 0;
+for i = 1 : size(A, 1)
+    if sum(A(i, :) == item) == size(A, 2)
+        idx = i;
+        return;
+    end
+end
+
+end

### 2023-06-05 visual/dorsal/scripts/demo_btn_forrest.py

@@ -1,0 +1,165 @@
+# -*- coding:utf-8 -*-
+# 中文注释报错：SyntaxError: Non-ASCII character '\xe8'
+# %%
+# --img_dir=/data2/whd/workspace/sot/data/hart/training/image_02/ --label_dir=/data2/whd/workspace/sot/data/hart/training/label_02/ --is_debug True
+
+import matplotlib
+matplotlib.use('TkAgg')  # TkAgg, Agg
+
+import os
+
+import sys
+# pycharm运行py文件会自动将当前运行py文件的工程目录加载到sys.path中，不加这个命令行运行会报错：ImportError: No module named hart.data
+sys.path.append("/data2/whd/workspace/sot/hart")
+script_dir = os.path.split(os.path.realpath(__file__))[0]
+proj_dir = os.path.split(script_dir)[0]
+
+os.chdir('../')  # 加上这个命令行运行报错？ IOError: [Errno 2] No such file or directory: 'result/activation/LSTM'
+
+# print(os.getcwd())
+# sys.path.append('neurocity')
+# sys.path.append('neurocity/component')
+
+import numpy as np
+import tensorflow as tf
+from scipy.misc import imread, imresize  # ImportError: cannot import name imread  -> install pillow
+
+
+from hart.data import disp
+from hart.data.kitti.tools import get_data
+from hart.model import util
+from hart.model.attention_ops import FixedStdAttention
+from hart.model.eval_tools import log_norm, log_ratios, log_values, make_expr_logger
+from hart.model.tracker import HierarchicalAttentiveRecurrentTracker as HART
+from hart.model.nn import AlexNetModel, IsTrainingLayer
+from hart.train_tools import TrainSchedule, minimize_clipped
+
+
+import matplotlib.pyplot as plt
+# % matplotlib
+# inline
+
+os.environ["CUDA_VISIBLE_DEVICES"] = "3"
+
+
+# %%
+
+def load_imgs(img_dir):
+    imgs_list = []
+    for file in os.listdir(img_dir):
+        if file.endswith(".jpg") or file.endswith(".png"):
+            imgs_list.append(file)
+    img_paths = sorted(imgs_list)
+    imgs = np.empty([len(img_paths), 1] + list(img_size), dtype=np.float32)
+    for i, img_path in enumerate(img_paths):
+        img_path = os.path.join(img_dir, img_path)
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/first_level_gppi/gPPI_first_level_same_voi_lgn.m

@@ -1,0 +1,87 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% first-level gPPI analysis for left and right LGN seed regions
+%-----------------------------------------------------------------------
+
+project_path = 'your_project_path'; % please customize to your project path
+cd(project_path);
+
+% project path should contain study folders that contain the individual
+% first-level subject folders that contain a folder called "SPEM" that
+% contain a folder called "nonparametric" with the first-level data
+% e. g. a first-level path could look like this:
+% C:\Data\study_1\subject_33\SPEM\nonparametric
+
+
+study_dir = list_vp_names(project_path);
+
+% same start voxel for every participant
+% -24, -26, -4;22, -26, 0
+
+for j = 1:numel(study_dir)
+
+study_path = [project_path filesep study_dir{j}];
+subjects = list_vp_names(study_path);
+
+voxel_names = { 'LGNl4' 'LGNr4'};
+voxel_mni = [-24, -26, -4;22, -26, 0];
+
+% Add the path to the gPPI toolbox. 
+
+addpath 'C:/spm';
+spms(8);
+spmpath=fileparts(which('spm.m'));
+addpath([spmpath filesep 'toolbox']);
+addpath([spmpath filesep 'toolbox' filesep 'PPPI']);
+spm('defaults','fmri')
+
+for k = 1:numel(subjects)
+    
+    sb_name = subjects{k};
+        disp(sb_name)
+        disp('analyzing')
+    
+workdir= [study_path filesep subjects{k}];
+cd(workdir);
+
+first_level_dir = [workdir filesep 'SPEM' filesep 'nonparametric'];
+
+cd(first_level_dir);
+
+% create sphere around voxel of interest
+
+for i = 1:numel(voxel_names)
+
+cd(first_level_dir);
+create_sphere_image('SPM.mat',voxel_mni(i,:),voxel_names(i),4);
+
+% Set up the control param structure P which determines the run
+cd(workdir);
+
+P.subject=subjects{k};
+P.directory=[workdir filesep 'SPEM' filesep 'nonparametric'];
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_FEFlin_gain4.m

@@ -1,0 +1,81 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in left FEF and pursuit gain for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.89
+0.92
+0.84
+0.95
+0.75
+0.87
+0.84
+0.87
+0.86
+0.41
+0.96
+0.79
+0.77
+0.9
+0.47
+0.94
+0.88
+0.89
+0.96
+0.75
+0.89
+0.84
+0.84
+0.83
+0.89
+0.93
+0.87
+0.99
+1.03
+0.88
+0.85
+0.85
+0.94
+0.94
+0.95
+0.91
+0.9
+0.92
+0.85
+0.89
+0.85
+0.79
+                                                  ];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_04';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_FEFlin_rmse4.m

@@ -1,0 +1,81 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in left FEF and RMSE for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [93.86
+97.81
+106.93
+101.25
+93.08
+100.93
+100.91
+103.09
+96.19
+68.7
+105.19
+106.79
+86.54
+56.92
+140.32
+69.54
+57.67
+69.38
+67.49
+78.38
+46.57
+57.56
+136.25
+44.21
+58.46
+42.54
+90.16
+96.19
+51.58
+71.38
+44.24
+67.31
+57.36
+61.8
+65.93
+88.24
+60.1
+52.77
+53.96
+54.2
+57.05
+52.52
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'rmse_04';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_FEFlin_sacfreq4.m

@@ -1,0 +1,81 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in left FEF and saccadic frequency for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [1.52
+0.62
+0.41
+0.56
+0.97
+1.49
+1.05
+0.86
+1.21
+2.28
+0.71
+1.56
+1.33
+1.19
+2.57
+1.36
+0.95
+0.37
+1.42
+1.24
+2.47
+1.64
+2.19
+2.26
+1.86
+1.38
+1.21
+1.54
+0.35
+1.81
+1.07
+2.1
+1.59
+2.19
+0.88
+1.95
+0.3
+0.67
+1.12
+0.36
+1.63
+1.73
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'sacfreq_04';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_LGNl_gain4.m

@@ -1,0 +1,81 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in left LGN and pursuit gain for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.89
+0.92
+0.84
+0.95
+0.75
+0.87
+0.84
+0.87
+0.86
+0.41
+0.96
+0.79
+0.77
+0.9
+0.47
+0.94
+0.88
+0.89
+0.96
+0.75
+0.89
+0.84
+0.84
+0.83
+0.89
+0.93
+0.87
+0.99
+1.03
+0.88
+0.85
+0.85
+0.94
+0.94
+0.95
+0.91
+0.9
+0.92
+0.85
+0.89
+0.85
+0.79
+                                                  ];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_04';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_LGNl_rmse4.m

@@ -1,0 +1,82 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in left LGN and RMSE for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [93.86
+97.81
+106.93
+101.25
+93.08
+100.93
+100.91
+103.09
+96.19
+68.7
+105.19
+106.79
+86.54
+56.92
+140.32
+69.54
+57.67
+69.38
+67.49
+78.38
+46.57
+57.56
+136.25
+44.21
+58.46
+42.54
+90.16
+96.19
+51.58
+71.38
+44.24
+67.31
+57.36
+61.8
+65.93
+88.24
+60.1
+52.77
+53.96
+54.2
+57.05
+52.52
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_LGNr_gain2.m

@@ -1,0 +1,81 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in right LGN and pursuit gain for .2 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .2_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.94
+0.98
+0.9
+1.01
+0.88
+1.02
+0.91
+0.92
+1
+0.76
+1.03
+0.89
+0.93
+0.89
+0.67
+0.99
+0.92
+0.93
+1
+0.86
+0.9
+0.89
+0.93
+0.91
+0.93
+0.96
+0.87
+1.04
+1.01
+0.95
+0.93
+0.92
+0.98
+1
+1.01
+0.92
+0.97
+1.03
+0.96
+0.95
+1
+0.89];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_LGNr_gain4.m

@@ -1,0 +1,82 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in right LGN and pursuit gain for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.89
+0.92
+0.84
+0.95
+0.75
+0.87
+0.84
+0.87
+0.86
+0.41
+0.96
+0.79
+0.77
+0.9
+0.47
+0.94
+0.88
+0.89
+0.96
+0.75
+0.89
+0.84
+0.84
+0.83
+0.89
+0.93
+0.87
+0.99
+1.03
+0.88
+0.85
+0.85
+0.94
+0.94
+0.95
+0.91
+0.9
+0.92
+0.85
+0.89
+0.85
+0.79
+                                                  ];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_04';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_LGNr_rmse2.m

@@ -1,0 +1,82 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in right LGN and RMSE for .2 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .2_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [54.53
+51.87
+67.85
+65.76
+56.23
+56.22
+54.09
+81
+53.38
+32.1
+63.32
+68.13
+45.08
+42.93
+108.08
+45.3
+40.35
+44.86
+45.08
+63.26
+25.87
+54.82
+81.51
+32.62
+40.88
+26.38
+70.88
+102.62
+33.75
+63.83
+29.81
+81.44
+35.91
+39.66
+33.23
+47.78
+33.01
+15.22
+28.68
+24.43
+27.3
+25.15];
+
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_LGNr_sacfreq2.m

@@ -1,0 +1,82 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in right LGN and saccadic frequency for .2 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .2_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.51
+0.31
+0.03
+0.25
+0.2
+0.8
+0.37
+0.37
+0.54
+0.61
+0.47
+0.34
+0.35
+0.5
+1.47
+0.33
+0.21
+0.06
+0.45
+0.74
+1.42
+0.76
+1.4
+1.03
+0.99
+0.75
+0.35
+1.01
+0.12
+0.88
+0.37
+0.78
+0.39
+0.94
+0.59
+0.1
+0.04
+0.24
+0.16
+0.05
+0.49
+0.21
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'sacfreq_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_PARlin_rmse4.m

@@ -1,0 +1,82 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in left PPC and RMSE for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [93.86
+97.81
+106.93
+101.25
+93.08
+100.93
+100.91
+103.09
+96.19
+68.7
+105.19
+106.79
+86.54
+56.92
+140.32
+69.54
+57.67
+69.38
+67.49
+78.38
+46.57
+57.56
+136.25
+44.21
+58.46
+42.54
+90.16
+96.19
+51.58
+71.38
+44.24
+67.31
+57.36
+61.8
+65.93
+88.24
+60.1
+52.77
+53.96
+54.2
+57.05
+52.52
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'rmse_04';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_PARlin_sacfreq4.m

@@ -1,0 +1,82 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in left PPC and saccadic frequency for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [1.52
+0.62
+0.41
+0.56
+0.97
+1.49
+1.05
+0.86
+1.21
+2.28
+0.71
+1.56
+1.33
+1.19
+2.57
+1.36
+0.95
+0.37
+1.42
+1.24
+2.47
+1.64
+2.19
+2.26
+1.86
+1.38
+1.21
+1.54
+0.35
+1.81
+1.07
+2.1
+1.59
+2.19
+0.88
+1.95
+0.3
+0.67
+1.12
+0.36
+1.63
+1.73
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'sacfreq_04';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_PARrin_gain4.m

@@ -1,0 +1,82 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in right PPC and pursuit gain for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.89
+0.92
+0.84
+0.95
+0.75
+0.87
+0.84
+0.87
+0.86
+0.41
+0.96
+0.79
+0.77
+0.9
+0.47
+0.94
+0.88
+0.89
+0.96
+0.75
+0.89
+0.84
+0.84
+0.83
+0.89
+0.93
+0.87
+0.99
+1.03
+0.88
+0.85
+0.85
+0.94
+0.94
+0.95
+0.91
+0.9
+0.92
+0.85
+0.89
+0.85
+0.79
+                                                  ];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_04';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_PARrin_sacfreq2.m

@@ -1,0 +1,82 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in right PPC and saccadic frequency for .2 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .2_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.51
+0.31
+0.03
+0.25
+0.2
+0.8
+0.37
+0.37
+0.54
+0.61
+0.47
+0.34
+0.35
+0.5
+1.47
+0.33
+0.21
+0.06
+0.45
+0.74
+1.42
+0.76
+1.4
+1.03
+0.99
+0.75
+0.35
+1.01
+0.12
+0.88
+0.37
+0.78
+0.39
+0.94
+0.59
+0.1
+0.04
+0.24
+0.16
+0.05
+0.49
+0.21
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'sacfreq_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_V1lin_gain2.m

@@ -1,0 +1,81 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in left V1 and pursuit gain for .2 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .2_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.94
+0.98
+0.9
+1.01
+0.88
+1.02
+0.91
+0.92
+1
+0.76
+1.03
+0.89
+0.93
+0.89
+0.67
+0.99
+0.92
+0.93
+1
+0.86
+0.9
+0.89
+0.93
+0.91
+0.93
+0.96
+0.87
+1.04
+1.01
+0.95
+0.93
+0.92
+0.98
+1
+1.01
+0.92
+0.97
+1.03
+0.96
+0.95
+1
+0.89];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_V1lin_rmse4.m

@@ -1,0 +1,82 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in left V1 and RMSE for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [93.86
+97.81
+106.93
+101.25
+93.08
+100.93
+100.91
+103.09
+96.19
+68.7
+105.19
+106.79
+86.54
+56.92
+140.32
+69.54
+57.67
+69.38
+67.49
+78.38
+46.57
+57.56
+136.25
+44.21
+58.46
+42.54
+90.16
+96.19
+51.58
+71.38
+44.24
+67.31
+57.36
+61.8
+65.93
+88.24
+60.1
+52.77
+53.96
+54.2
+57.05
+52.52
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_V1lin_sacfreq2.m

@@ -1,0 +1,82 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in left V1 and saccadic frequency for .2 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .2_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.51
+0.31
+0.03
+0.25
+0.2
+0.8
+0.37
+0.37
+0.54
+0.61
+0.47
+0.34
+0.35
+0.5
+1.47
+0.33
+0.21
+0.06
+0.45
+0.74
+1.42
+0.76
+1.4
+1.03
+0.99
+0.75
+0.35
+1.01
+0.12
+0.88
+0.37
+0.78
+0.39
+0.94
+0.59
+0.1
+0.04
+0.24
+0.16
+0.05
+0.49
+0.21
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'sacfreq_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_V5lin_rmse4.m

@@ -1,0 +1,81 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in left V5 and RMSE for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [93.86
+97.81
+106.93
+101.25
+93.08
+100.93
+100.91
+103.09
+96.19
+68.7
+105.19
+106.79
+86.54
+56.92
+140.32
+69.54
+57.67
+69.38
+67.49
+78.38
+46.57
+57.56
+136.25
+44.21
+58.46
+42.54
+90.16
+96.19
+51.58
+71.38
+44.24
+67.31
+57.36
+61.8
+65.93
+88.24
+60.1
+52.77
+53.96
+54.2
+57.05
+52.52
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_V5rin_gain4.m

@@ -1,0 +1,81 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in right V5 and pursuit gain for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.89
+0.92
+0.84
+0.95
+0.75
+0.87
+0.84
+0.87
+0.86
+0.41
+0.96
+0.79
+0.77
+0.9
+0.47
+0.94
+0.88
+0.89
+0.96
+0.75
+0.89
+0.84
+0.84
+0.83
+0.89
+0.93
+0.87
+0.99
+1.03
+0.88
+0.85
+0.85
+0.94
+0.94
+0.95
+0.91
+0.9
+0.92
+0.85
+0.89
+0.85
+0.79
+                                                  ];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_04';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_V5rin_rmse2.m

@@ -1,0 +1,81 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in right V5 and RMSE for .2 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .2_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [54.53
+51.87
+67.85
+65.76
+56.23
+56.22
+54.09
+81
+53.38
+32.1
+63.32
+68.13
+45.08
+42.93
+108.08
+45.3
+40.35
+44.86
+45.08
+63.26
+25.87
+54.82
+81.51
+32.62
+40.88
+26.38
+70.88
+102.62
+33.75
+63.83
+29.81
+81.44
+35.91
+39.66
+33.23
+47.78
+33.01
+15.22
+28.68
+24.43
+27.3
+25.15];
+
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_V5rin_sacfreq2.m

@@ -1,0 +1,81 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in right V5 and saccadic frequency for .2 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .2_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.51
+0.31
+0.03
+0.25
+0.2
+0.8
+0.37
+0.37
+0.54
+0.61
+0.47
+0.34
+0.35
+0.5
+1.47
+0.33
+0.21
+0.06
+0.45
+0.74
+1.42
+0.76
+1.4
+1.03
+0.99
+0.75
+0.35
+1.01
+0.12
+0.88
+0.37
+0.78
+0.39
+0.94
+0.59
+0.1
+0.04
+0.24
+0.16
+0.05
+0.49
+0.21
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'sacfreq_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_regression/spem_connect_second_level_multi_regr_gPPI_V5rin_sacfreq4.m

@@ -1,0 +1,81 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression: gPPI starting in right V5 and saccadic frequency for .4 Hz smooth pursuit 
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_PPI_SPEM .4_minus_none contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [1.52
+0.62
+0.41
+0.56
+0.97
+1.49
+1.05
+0.86
+1.21
+2.28
+0.71
+1.56
+1.33
+1.19
+2.57
+1.36
+0.95
+0.37
+1.42
+1.24
+2.47
+1.64
+2.19
+2.26
+1.86
+1.38
+1.21
+1.54
+0.35
+1.81
+1.07
+2.1
+1.59
+2.19
+0.88
+1.95
+0.3
+0.67
+1.12
+0.36
+1.63
+1.73
+];
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'sacfreq_04';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_ttest/gPPI_second_level_ind_vois_fef_left.m

@@ -1,0 +1,145 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second level analysis of gppi for left FEF as a seed region
+%-----------------------------------------------------------------------
+
+
+% for the script so run smoothly first level PPI names should be saved along the following hierarchy:
+% data_path    <- directory where first level data is saved, contains folders
+%                 for each study: 
+% study_dir    <- contain one folder for each participant with a 
+%                 unique name ('subject_name', e.g. 'subject_33'),
+%                 contains folder called:
+% SPEM         <- contains folder called:
+% gPPI         <- contains separate folders for each seed region: 
+% voi_dir      <- named ("PPI_" name of seed region), e. g. "PPI_V5lin",
+%                 contains first-level images that are named like this: 
+% image_name  <-  (contrast name "_" subject_name ".img")
+%                 for each participant, 8 contrasts exist, named like this: 
+%                   con_PPI_none_minus_SPEM .2
+%                   con_PPI_none_minus_SPEM .4
+%                   con_PPI_none_minus_SPEM .2_SPEM .4
+%                   con_PPI_SPEM .2_minus_SPEM .4
+%                   con_PPI_SPEM .2_minus_none
+%                   con_PPI_SPEM .2_SPEM .4_minus_none
+%                   con_PPI_SPEM .4_minus_none
+%                   con_PPI_SPEM .4_minus_SPEM .2
+
+% example of a first-level path:
+% C:\data\study_1\subject_33\SPEM\gPPI\PPI_V5lin\con_PPI_none_minus_SPEM.2_subject_33.img
+
+
+% your project path should contain folders for each seed region, e. g.
+% "V5lin_without_critical" that contain the following subfolders (one for each contrast): 
+%                   con_PPI_none_minus_SPEM .2
+%                   con_PPI_none_minus_SPEM .4
+%                   con_PPI_none_minus_SPEM .2_SPEM .4
+%                   con_PPI_SPEM .2_minus_SPEM .4
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_ttest/gPPI_second_level_ind_vois_fef_right.m

@@ -1,0 +1,143 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second level analysis of gppi for right FEF as a seed region
+%-----------------------------------------------------------------------
+
+
+% for the script so run smoothly first level PPI names should be saved along the following hierarchy:
+% data_path    <- directory where first level data is saved, contains folders
+%                 for each study: 
+% study_dir    <- contain one folder for each participant with a 
+%                 unique name ('subject_name', e.g. 'subject_33'),
+%                 contains folder called:
+% SPEM         <- contains folder called:
+% gPPI         <- contains separate folders for each seed region: 
+% voi_dir      <- named ("PPI_" name of seed region), e. g. "PPI_V5lin",
+%                 contains first-level images that are named like this: 
+% image_name  <-  (contrast name "_" subject_name ".img")
+%                 for each participant, 8 contrasts exist, named like this: 
+%                   con_PPI_none_minus_SPEM .2
+%                   con_PPI_none_minus_SPEM .4
+%                   con_PPI_none_minus_SPEM .2_SPEM .4
+%                   con_PPI_SPEM .2_minus_SPEM .4
+%                   con_PPI_SPEM .2_minus_none
+%                   con_PPI_SPEM .2_SPEM .4_minus_none
+%                   con_PPI_SPEM .4_minus_none
+%                   con_PPI_SPEM .4_minus_SPEM .2
+
+% example of a first-level path:
+% C:\data\study_1\subject_33\SPEM\gPPI\PPI_V5lin\con_PPI_none_minus_SPEM.2_subject_33.img
+
+
+% your project path should contain folders for each seed region, e. g.
+% "V5lin_without_critical" that contain the following subfolders (one for each contrast): 
+%                   con_PPI_none_minus_SPEM .2
+%                   con_PPI_none_minus_SPEM .4
+%                   con_PPI_none_minus_SPEM .2_SPEM .4
+%                   con_PPI_SPEM .2_minus_SPEM .4
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_ppi_ttest/gPPI_second_level_ind_vois_v5_right.m

@@ -1,0 +1,146 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second level analysis of gppi for right V5 as a seed region
+%-----------------------------------------------------------------------
+
+
+% for the script so run smoothly first level PPI names should be saved along the following hierarchy:
+% data_path    <- directory where first level data is saved, contains folders
+%                 for each study: 
+% study_dir    <- contain one folder for each participant with a 
+%                 unique name ('subject_name', e.g. 'subject_33'),
+%                 contains folder called:
+% SPEM         <- contains folder called:
+% gPPI         <- contains separate folders for each seed region: 
+% voi_dir      <- named ("PPI_" name of seed region), e. g. "PPI_V5lin",
+%                 contains first-level images that are named like this: 
+% image_name  <-  (contrast name "_" subject_name ".img")
+%                 for each participant, 8 contrasts exist, named like this: 
+%                   con_PPI_none_minus_SPEM .2
+%                   con_PPI_none_minus_SPEM .4
+%                   con_PPI_none_minus_SPEM .2_SPEM .4
+%                   con_PPI_SPEM .2_minus_SPEM .4
+%                   con_PPI_SPEM .2_minus_none
+%                   con_PPI_SPEM .2_SPEM .4_minus_none
+%                   con_PPI_SPEM .4_minus_none
+%                   con_PPI_SPEM .4_minus_SPEM .2
+
+% example of a first-level path:
+% C:\data\study_1\subject_33\SPEM\gPPI\PPI_V5lin\con_PPI_none_minus_SPEM.2_subject_33.img
+
+
+% your project path should contain folders for each seed region, e. g.
+% "V5lin_without_critical" that contain the following subfolders (one for each contrast): 
+%                   con_PPI_none_minus_SPEM .2
+%                   con_PPI_none_minus_SPEM .4
+%                   con_PPI_none_minus_SPEM .2_SPEM .4
+%                   con_PPI_SPEM .2_minus_SPEM .4
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_task_regression/spem_connect_second_level_multi_regr_gain4.m

@@ -1,0 +1,86 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression analysis: .4 Hz smooth pursuit and corresponding
+% pursuit gain values
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_0002 contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+%%
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+%%
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [0.89
+0.92
+0.84
+0.95
+0.75
+0.87
+0.84
+0.87
+0.86
+0.41
+0.96
+0.79
+0.77
+0.9
+0.47
+0.94
+0.88
+0.89
+0.96
+0.75
+0.89
+0.84
+0.84
+0.83
+0.89
+0.93
+0.87
+0.99
+1.03
+0.88
+0.85
+0.85
+0.94
+0.94
+0.95
+0.91
+-0.19
+0.9
+0.92
+0.85
+0.89
+0.85
+0.79
+                                                  ];
+%%
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'gain_04';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_task_regression/spem_connect_second_level_multi_regr_rmse2.m

@@ -1,0 +1,87 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level regression analysis: .2 Hz smooth pursuit and corresponding
+% RMSE values
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_0001 contrast paths
+                                                                                        % double-check: order has to be the same as in matlabbatch{1}.spm.stats.factorial_design.cov.c;
+%%
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.mcov = struct('c', {}, 'cname', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.des.mreg.incint = 1;
+%%
+matlabbatch{1}.spm.stats.factorial_design.cov.c = [54.53
+51.87
+67.85
+65.76
+56.23
+56.22
+54.09
+81
+53.38
+32.1
+63.32
+68.13
+45.08
+42.93
+108.08
+45.3
+40.35
+44.86
+45.08
+63.26
+25.87
+54.82
+81.51
+32.62
+40.88
+26.38
+70.88
+102.62
+33.75
+63.83
+29.81
+81.44
+35.91
+39.66
+33.23
+47.78
+120.56
+33.01
+15.22
+28.68
+24.43
+27.3
+25.15
+
+                                                    ];
+%%
+matlabbatch{1}.spm.stats.factorial_design.cov.cname = 'rmse_02';
+matlabbatch{1}.spm.stats.factorial_design.cov.iCFI = 1;
+matlabbatch{1}.spm.stats.factorial_design.cov.iCC = 1;
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
[…]

### 2023-06-05 visual/dorsal/spem/Analysis/second_level_task_ttest/spem_connect_second_level_.2_minus_none.m

@@ -1,0 +1,36 @@
+%-----------------------------------------------------------------------
+% Script by Rebekka Schröder (rebekka.schroeder@uni-bonn.de) to analyse
+% data for smooth pursuit connectivity study
+
+% second-level t-test between .2 Hz smooth pursuit and fixation
+%-----------------------------------------------------------------------
+matlabbatch{1}.spm.stats.factorial_design.dir = {'your_results_path'};                % please customize to your individual results path
+%%
+matlabbatch{1}.spm.stats.factorial_design.des.t1.scans = {'your_first_level_vector'}; % please customize to your vector of first level con_0001 contrast paths
+                                                        
+%%
+matlabbatch{1}.spm.stats.factorial_design.cov = struct('c', {}, 'cname', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.multi_cov = struct('files', {}, 'iCFI', {}, 'iCC', {});
+matlabbatch{1}.spm.stats.factorial_design.masking.tm.tm_none = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.im = 1;
+matlabbatch{1}.spm.stats.factorial_design.masking.em = {''};
+matlabbatch{1}.spm.stats.factorial_design.globalc.g_omit = 1;
+matlabbatch{1}.spm.stats.factorial_design.globalm.gmsca.gmsca_no = 1;
+matlabbatch{1}.spm.stats.factorial_design.globalm.glonorm = 1;
+
+%%
+matlabbatch{2}.spm.stats.fmri_est.spmmat(1) = cfg_dep('Factorial design specification: SPM.mat File', substruct('.','val', '{}',{1}, '.','val', '{}',{1}, '.','val', '{}',{1}), substruct('.','spmmat'));
+matlabbatch{2}.spm.stats.fmri_est.write_residuals = 0;
+matlabbatch{2}.spm.stats.fmri_est.method.Classical = 1;
+
+
+%% run batch
+spm('defaults', 'FMRI');
+spm_jobman('run', matlabbatch, '');
+
+%% save batch
+
+cd(char(matlabbatch{1}.spm.stats.factorial_design.dir))
+batch_name = ['con_0001' '.mat'];
+save (batch_name, 'matlabbatch');
+

### 2023-06-05 visual/dorsal/study/matplotlib_demo.py

@@ -1,0 +1,29 @@
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib import animation
+import matplotlib
+
+
+#%%
+fig = plt.figure()
+ax = plt.axes(xlim=(0, 2), ylim=(-2, 2))
+line, = ax.plot([], [], lw=2)
+
+
+def init():
+    line.setdata([], [])
+    return line,
+
+
+def animate(i):
+    x = np.linspace(0, 2, 1000)
+    y = np.sin(2 * np.pi * (x - 0.01 * i))
+    line.setdata(x, y)
+    return line,
+
+
+anim = animation.FuncAnimation(fig, animate, init_func=init, frames=200,
+                               interval=20, blit=True)
+anim.save('../result/study/sin.gif', fps=75, writer='imagemagick')
+plt.show()

### 2023-06-05 visual/emotion/code/sub/perform_clustering_analysis.m

@@ -1,0 +1,237 @@
+function perform_clustering_analysis(p,encRes)
+%
+% - This code is written for performing clustering analysis
+%   based on encoding accuracy
+%
+% called from emotion2020_analysis_BATCH
+%
+
+%% settings
+testSubjectTypes = {p.sbjID{:},'randctrl'};
+
+nclust_all = [50,27,15]; % numbers of kmeans clustering
+nTopSampleProp = 5; % percentage of assigning samples
+cvth = 0.124; % threshold for voxel selection
+selectVoxProp = 100; % proportion of voxels used for voxel selection
+
+nSample = 2181;
+nRand = 100000; % # of shuffling computations
+
+
+cat = load([p.featdir,'category.mat']);
+dim = load([p.featdir,'dimension.mat']);
+
+
+%% perform kmeans clustering
+for sbjitr = 1:length(testSubjectTypes)
+    testSubjectType = testSubjectTypes{sbjitr};
+    
+    suffix_full = [testSubjectType,'/',p.suffix_enc,'/'];
+    
+    for nclitr = randsample(1:length(nclust_all),length(nclust_all))%1:length(nclust_all)
+        nclust = nclust_all(nclitr);
+        
+        
+        saveFname = sprintf('%s/kmeans_clustering/%s/kmeans_%dclust_top%d_res.mat',p.savdir,suffix_full,nclust,nTopSampleProp);
+        saveFnameChk = sprintf('%s/kmeans_clustering/%s/kmeans_%dclust_top%d_log.txt',p.logdir,suffix_full,nclust,nTopSampleProp);
+        setdir(fileparts(saveFname));
+        setdir(fileparts(saveFnameChk));
+        
+        if exist(saveFnameChk,'file')
+            fprintf('%s\n',saveFname)
+        else
+            fprintf('Start:%s\n',saveFnameChk)
+            tmp = [];
+            save(saveFnameChk,'tmp','-ascii')
+            
+            % subject
+            switch testSubjectType
+                case 'randctrl'
+                    
+                    % prepare scores
+                    catScore = cat.L.feat;
+                    dimScore = dim.L.feat-5;
+                    cat2734Score = cat.L.feat(:,[1:11,13,15:17,19:20,22:25,27:32]);
+                    
+                    % remove duplicates
+                    catScore(p.dupidx,:) = [];
+                    dimScore(p.dupidx,:) = [];
+                    cat2734Score(p.dupidx,:) = [];
+                    
[…]

### 2023-06-05 visual/emotion/code/sub/prepare_roidata.m

@@ -1,0 +1,98 @@
+function prepare_roidata(rootPath)
+%  
+% This script was written for preparing preprocessed MRI data for cowen &
+% keltner movie clip presentation data, which were pre-processed by the fmriprep. 
+% The data was devided into individual ROIs.
+% 
+% 
+% call prepare_roidata_individual.m
+% called from emotion2020_analysis_BATCH.m
+% 
+% Required libraries:
+% BrainDecoderToolbox2
+% 
+% 
+% Note: this script tentatively requires ~80GB memory for data preprocessing
+% 
+% written by Tomoyasu Horikawa horikawa-t@atr.jp 2020/03/11
+% 
+
+%% initialize
+% general info.
+if ~exist('rootPath','var')
+    rootPath = './'; 
+end
+fileName = 'prepare_roidata';
+
+% add path to code
+addpath(genpath([rootPath,'code/']));
+
+% set paths to directories/data
+p.savdir = setdir(sprintf('%s/res/%s/',rootPath,fileName));
+p.logdir = setdir(sprintf('%s/log/%s/',rootPath,fileName));
+p.fmridir = setdir(sprintf('%s/data/fmri/',rootPath));
+p.miscdir = setdir(sprintf('%s/data/fmri/misc/',rootPath));
+p.roiInfPath = [p.miscdir,'roiInf.mat'];
+
+%% subject info. {sbjID, nSession}
+dataList = {
+    {'Subject1',5}
+    {'Subject2',7}
+    {'Subject3',6}
+    {'Subject4',5}
+    {'Subject5',5}
+    };
+nSbj = length(dataList);
+
+%% Set ROI information
+p.roiDescrip = {};
+p.roiName = {};
+p.exRoiName = {};
+
+% load prepared roiInf
+load(p.roiInfPath,'roiInf');
+
+% add individual ROIs for hcp360, 13 individual, and 10 subcortical ROIs
+p.roiDescrip = {p.roiDescrip{:},roiInf.hcp360.roiDescrip{:},roiInf.individual.roiDescrip{:},roiInf.subcortex.roiDescrip{:}}';
+p.roiName = {p.roiName{:},roiInf.hcp360.roiName{:},roiInf.individual.roiName{:},roiInf.subcortex.roiName{:}}';
[…]

### 2023-06-05 visual/face/Run_PFI.m

@@ -1,0 +1,255 @@
+%% Preferred feature images of face-selective units in untrained networks (Fig.2, Fig.S4) 
+
+%% Preferred feature images (PFI) (Fig 2c)
+Cell_PFI = cell(numCLS-1,2);
+if Sim == 0                                                                % 1 : Fast version of PFI simulation. The saved PFI would be displayed.
+    load('Data_PFI_XDream_ClsUnit.mat','PFI_XDream_mat')
+    load('Data_PFI_RevCorr_ClsUnit.mat','PFI_RevCorr_mat')
+
+    for cc = 1:numCLS-1
+        for ii = 1:2
+            switch ii
+                case 1
+                    Cell_PFI{cc,1} = PFI_XDream_mat{cc};
+                case 2
+                    Cell_PFI{cc,2} = PFI_RevCorr_mat{cc};
+            end
+        end
+    end
+elseif Sim == 1                                                            % 2 : Actual calculation process would be run. It takes around 30 minutes.
+    net_rand = Cell_Net{1,1,1}; IND_face = Cell_Idx{1,1,1,length(layerArray)};
+        
+    %% Reverse correlation (Fig 2a)
+    % Stimulus parameters
+    N_image = 2500;         % Number of stimulus images
+    iteration = 100;         % Number of iteration
+    img_size = 227;         % Image size
+    dot_size = 5;           % Size of 2D Gaussian filter
+    
+    % Generate 2D Gaussian filters
+    [pos_xx,pos_yy] = meshgrid(linspace(1+dot_size,img_size-dot_size,sqrt(N_image)),linspace(1+dot_size,img_size-dot_size,sqrt(N_image)));
+    pos_xy_list = pos_xx(:) + 1i*pos_yy(:);
+    [xx_field,yy_field] = meshgrid(1:img_size,1:img_size); xy_field = xx_field + 1i*yy_field;
+    
+    img_list = zeros(img_size,img_size,3,length(pos_xy_list));
+    count = 1;
+    for pp = 1:length(pos_xy_list)
+        pos_tmp = pos_xy_list(pp);
+        img_tmp = repmat(exp(-(abs(xy_field-pos_tmp).^2)/2/dot_size.^2)*0.5,1,1,3);
+        img_list(:,:,:,count) = -img_tmp;
+        count = count + 1;
+    end
[…]

### 2023-06-05 visual/face/Run_Unit.m

@@ -1,0 +1,326 @@
+%% Spontaneous emergence of face-selectivity in untrained networks (Fig.1, Fig.S1-3)
+
+%% DNN with randomly initialized weights (Fig 1b)
+net_rand = Cell_Net{vv,1,1};                                                                                 % untrained AlexNet
+layers_ind = [2,10,14];                                                                                     % target layers: conv1~5
+vis_N = 3;                                                                                                  % number of filters to visualize
+
+h = figure('units','normalized','outerposition',[0 0.5 0.5 0.5]); colormap(gray)
+sgtitle('Result 1 : DNN with randomly initialized weights (Fig 1b)')
+for ii = 1:length(layers_ind)
+    filter_pre = net.Layers(layers_ind(ii)).Weights; ...
+        sztmp = size(filter_pre,4); indtmpp=randi(sztmp, [1, vis_N]);                                        % load pre-trained filter
+    filter_perm = net_rand.Layers(layers_ind(ii)).Weights; ...
+        sztmp_r = size(filter_perm,4); indtmpp_r=randi(sztmp_r, [1, vis_N]);                                 % load permutedre filter
+    for jj = 1:length(indtmpp)
+        ax=subplot(3,7,7*(ii-1)+jj);
+        tmp = squeeze(filter_pre(:,:,1,indtmpp(jj))); 
+        imagesc(squeeze(filter_pre(:,:,1,indtmpp(jj)))); axis image off;                                    % plot pre-trained filter
+        if jj == 2; title(['Pretrained Conv',num2str(2*ii-1),' filters']); end
+        ax=subplot(3,7,7*(ii-1)+jj+4);
+        tmp = squeeze(filter_perm(:,:,1,indtmpp_r(jj))); 
[…]

### 2023-06-05 visual/face/Subfunctions/fun_FindNeuron.m

@@ -1,0 +1,36 @@
+function [cell_idx] = fun_FindNeuron(act_rand,num_cell,numCLS,numIMG,pThr,indClass)
+
+act_reshape = reshape(act_rand, num_cell, numCLS*numIMG);  % 每张图对应一个43264向量; 细胞数43264 * （类别数6 * 每一类200张图像）
+act_3D = zeros(num_cell, numCLS, numIMG);  % 43264 * 6 * 200
+
+for cc = 1:numCLS
+    act_3D(:, cc, :) = act_reshape(:, (cc-1)*numIMG+1 : cc*numIMG);  % 每次 43264*200
+end
+
+pref_class = zeros(num_cell, 1);  % 每一个细胞偏好的类别: 43264*1
+sel_p_val = zeros(num_cell, 1);   % 每一个细胞所对应的 p 值: 43264*1
+
+% parfor
+for cc = 1 : num_cell  % parfor
+    mean_FR = [];  % 对特定位置200张图片激活的平均（Face Response）
+    for cls = 1 : numCLS
+        mean_FR = [mean_FR, mean(act_reshape(cc, (cls-1)*numIMG+1 : cls*numIMG))];  % 每个类别所有200张图片对应一个mean_FR（对200张图像该位置的激活求平均）
+    end
+    
+    [~,sort_ind] = sort(mean_FR, 'descend');  % 当前细胞位置，对6个类别的平均激活进行降序排列(当然位置激活最大的类别id为偏好类别id)
+    pref_class(cc) = sort_ind(1);             % 选取6个类别中激活最大的类别作为当前细胞位置偏好的类别
+    
+    resp1 = act_reshape(cc, (sort_ind(1)-1)*numIMG+1:numIMG*sort_ind(1) );  % 偏好类别图像(200 张)在当前位置cc的激活resp1 (1*200)
+    pval_temp = [];
+    for ee = 2:numCLS
+        resp2 = act_reshape(cc, (sort_ind(ee)-1)*numIMG+1:numIMG*sort_ind(ee));  % 除了偏好类别的其他类别图像(每个200张) 激活(resp2) 1*200
+        pval_temp(ee-1) = ranksum(resp1, resp2);  % 相对于偏好类别 的p值
+    end
+    sel_p_val(cc) = max(pval_temp);  % 当前位置选是该类别选择单元的p值 <- 1*5
+end
+
[…]

### 2023-06-05 visual/face/Subfunctions/fun_Initializeweight.m

@@ -1,0 +1,47 @@
+function [net_test, lim, Weights, Biases] = fun_Initializeweight(net, ver, stdfac)
+% 随机初始化 AlexNet 的 5 个卷积层（其他层不做处理）
+
+net_test = net;
+net_tmp = net_test.saveobj;  % saveobj: 修改对象的保存过程
+
+rand_layers_ind = [2, 6, 10, 12 14];        % 5 个卷积层
+Weights = cell(1, length(rand_layers_ind));
+Biases = cell(1, length(rand_layers_ind));
+for ind_tl = 1:length(rand_layers_ind)
+    % ind_tl = 1;
+    % LOI = layers_set{ind_tl};
+    targetlayer_ind = rand_layers_ind(ind_tl);
+    weight_conv = net.Layers(targetlayer_ind, 1).Weights;  % 当前卷积层的权重
+    bias_conv = net.Layers(targetlayer_ind, 1).Bias;       % 当前卷积层的偏置
+    
+    fan_in = size(weight_conv,1) * size(weight_conv,2) * size(weight_conv,3);  % 11*11*3
+    
+    % (11*11*3*96,  1*1*96 ), 
+    % (5*5*48*256,  1*1*256), 
+    % (3*3*256*384, 1*1*384), 
+    % (3*3*192*384, 1*1*384), 
+    % (3*3*192*256, 1*1*256)
+    if ver == 1 
+        lim(ind_tl) = sqrt(2/fan_in);
+        % 在初始化阶段让前向传播过程每层方差保持不变,权重从 N(0, 1/fan_in) 的高斯分布采样 (Efficient
+        % BackProp )
+        Wtmp = stdfac*randn(size(weight_conv))*sqrt(1/fan_in); % 正态分布（randn） LeCun initializaation
+        Btmp = randn(size(bias_conv));
+    elseif ver == 2  
+        lim(ind_tl) = sqrt(3/fan_in);
+        Wtmp = stdfac*(rand(size(weight_conv))-0.5)*2*sqrt(3/fan_in); % 均匀分布（rand） Lecun uniform initializaation
+        Btmp = randn(size(bias_conv));
+    end
+
+    %% 改变网络参数 change network parameters
+    weight_conv_randomize = single(1*Wtmp);
+    bias_conv_randomize = single(0*Btmp);
+    
+    Weights{ind_tl} = weight_conv_randomize;
+    Biases{ind_tl} = bias_conv_randomize;
+    
[…]

### 2023-06-05 visual/face/Subfunctions/save_fig.m

@@ -1,0 +1,28 @@
+% 被 export_fig 工具箱代替
+function save_fig(h, filename)  
+% 将当前绘制的图像保存到latex的figs目录下（以pdf的格式），
+% 参考：https://baijiahao.baidu.com/s?id=1704887660228490516&wfr=spider&for=pc
+
+% h = figure;%% -----程序中的figure；plot(1:10);
+% 自动提取图片的尺寸和范围；
+% set(gcf,'Units','inches');
+% screenposition = get(gcf,'Position');
+% set(gcf,...    
+%     'PaperPosition',[0 0 screenposition(3:4)],...    
+%     'PaperSize',[screenposition(3:4)]);
+% save figure as pdfprint -dpdf -painters figure1
+
+set(h, 'Units', 'Inches');
+pos = get(h, 'Position');
+set(h, 'PaperPositionMode','Auto', ...
+    'PaperUnits','Inches','PaperSize',[pos(3), pos(4)])
+
+set(gca, 'LooseInset', [0,0,0,0]);
+
+
+% 保存图片为pdf格式，分辨率设置为600
+print(h, filename, '-dpdf','-r600')
+close(h)
+
+end
+

### 2023-06-05 visual/face/analysis_network.m

@@ -1,0 +1,209 @@
+%% Demo code ver. 11/01/2021
+%==================================================================================================================================================
+% Face Detection in Untrained Deep Neural Networks
+% Seungdae Baek, Min Song, Jaeson Jang, Gwangsu Kim & Se-Bum Paik*
+%
+% *Contact: sbpaik@kaist.ac.kr
+%
+% Prerequirement 
+% 1) MATLAB 2019b or later version is recommended.
+% 2) Install deeplearning toolbox. 
+% 3) Please download 
+% 'Data.zip'(https://zenodo.org/record/5637812/files/Stimulus.zip?download=1), 
+% 'Stimulus.zip'(https://zenodo.org/record/5637812/files/Data.zip?download=1) from below link
+%
+%      - [Data URL] : https://doi.org/10.5281/zenodo.5637812
+%
+%    and unzip these files in the same directory
+
+% 输出结果和论文图片
+% Below results for untrained AlexNet will be shown.
+% Result 1) Run_Unit: Spontaneous emergence of face-selectivity in untrained networks (Fig.1, Fig.S1-3)
+% Result 2) Run_PFI: Preferred feature images of face-selective units in untrained networks (Fig.2, Fig.S4) 
+% Result 3) Run_SVM: Detection of face images using the response of face units in untrained networks (Fig.3, Fig.S11-12) 
+% Result 4) Run_Trained: Effect of training on face-selectivity in untrained networks (Fig.4) 
+% Result 5) Run_Invariance: Invariant characteristics of face-selective units in untrained networks (Fig.S5) 
+% Result 6) Run_View: Viewpoint invariance of face-selective units in untrained networks (Fig.S8) 
+%==================================================================================================================================================
+close all;
+% clc;clear;
+seed = 1; rng(seed)                                                       % fixed random seed for regenerating same result
+
+%% 添加数据路径
+cur_fullpath = mfilename('fullpath');
[…]

### 2023-06-05 visual/face/brain_like/face_rep_spm12_batch.m

@@ -1,0 +1,218 @@
+% This batch script analyses the Face fMRI dataset available from the SPM
+% website:
+%   http://www.fil.ion.ucl.ac.uk/spm/data/face_rep/
+% as described in the SPM manual:
+%   http://www.fil.ion.ucl.ac.uk/spm/doc/spm12_manual.pdf#Chap:data:faces
+%__________________________________________________________________________
+% Copyright (C) 2014-2015 Wellcome Trust Centre for Neuroimaging
+
+% Guillaume Flandin
+% $Id: face_rep_spm12_batch.m 17 2015-03-06 11:24:19Z guillaume $
+
+% Directory containing Face data
+%--------------------------------------------------------------------------
+data_path = fullfile(pwd, 'face_rep');
+if ~exist(data_path, 'dir')
+    fprintf('%-40s:', 'Downloading Face dataset...');
+    urlwrite('http://www.fil.ion.ucl.ac.uk/spm/download/data/face_rep/face_rep.zip','face_rep.zip');
+    unzip(fullfile(data_path,'face_rep.zip'));
+    fprintf(' %30s\n', '...done');
+end
+% if isempty(data_path), data_path = pwd; end
+
+
+% Initialise SPM
+%--------------------------------------------------------------------------
+addpath(fullfile( matlabroot, 'utils', 'spm12'));
+spm('Defaults', 'fMRI');
+spm_jobman('initcfg');
+% spm_get_defaults('cmdline',true);
+
+% Change working directory (useful for PostScript (.ps) files only)
+%--------------------------------------------------------------------------
+%clear matlabbatch
+%matlabbatch{1}.cfg_basicio.file_dir.dir_ops.cfg_cd.dir = cellstr(data_path);
+%spm_jobman('run',matlabbatch);
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% SPATIAL PREPROCESSING
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+clear matlabbatch
+
+% Select functional and structural scans
+%--------------------------------------------------------------------------
[…]

### 2023-06-05 visual/face/brain_like/feature/generate_face_50d_face_space.m

@@ -1,0 +1,305 @@
+clear;
+close all;
+np=58;
+%average landmark positions
+num=[121.806288847908,229.889015478914;151.286063798839,230.244392948549;96.9762721414530,268.811706229708;126.082174632477,255.378619098425;136.628240443922,258.498193119184;147.500590221395,255.616343057027;175.167365832797,268.703420074134;149.162698240004,283.515571732374;123.538280860057,283.316751573451;68.1223209799350,174.389736397628;89.5754388449790,164.858402153764;110.268696032633,174.488501303010;89.8781571865340,179.183272770824;161.307257313939,175.359874499624;181.813299584059,164.838678471877;202.866545164355,175.165858125379;182.140017612159,179.250403922976;37.2889496008500,174.214955878691;37.9882581259887,217.141483517378;42.9458744015501,251.690279240828;53.7942018028700,285.314477372387;72.5210877639865,309.097312425385;97.0028979035317,327.539870958972;135.127605488986,336.243020689102;176.981866139239,325.822823999902;202.714867599183,302.539766536478;220.761516144183,268.730917906374;227.961952847210,232.607443144093;230.356046372917,195.934450238339;229.205962906583,173.558749224018;55.1319801212780,153.353000466879;73.4758699336921,140.468343364377;107.076066898949,142.783258542434;115.681635529347,153.400151939173;155.109774792031,154.447963969138;162.153604365859,143.702212834141;196.701567479335,139.788342216138;213.371727261171,151.368028200814;122.523606016498,179.623545382894;120.582553926553,201.319111577588;108.727301662662,212.896011179715;108.514840116632,235.869529114779;163.807620086345,236.021210625970;163.347043727620,212.256324039636;151.643144468853,201.260520103444;149.845049242458,179.446383934843;133.943822035310,64.9056148841150;132.732087943732,0.547862879376879;13.3968709894577,79.2182903299707;250.905009489888,75.1883021887648;14.8865167751942,174.071020402470;250.475757121916,173.006157131873;65.4983220386920,15.1824219870093;200.014732690810,15.7607608655378;67.0278704601246,85.7804071884441;200.5862040
[…]

### 2023-06-05 visual/object_decoding/analysis_CategoryIdentification.m

@@ -1,0 +1,150 @@
+% analysis_CategoryIdentification    运行目标类别识别
+
+%% 目录设置
+cur_dir = fileparts(mfilename('fullpath'));
+run(fullfile(cur_dir, 'init.m'));
+
+
+%% 初始化设置 
+
+% 数据设置
+% subjectList  : List of subject IDs [cell array]
+% featureList  : List of image features [cell array]
+% roiList      : List of RoiList [cell array]
+
+subjectList = {'Subject1', 'Subject2', 'Subject3', 'Subject4', 'Subject5'};
+featureList = {'cnn1', 'cnn2', 'cnn3', 'cnn4', ...
+               'cnn5', 'cnn6', 'cnn7', 'cnn8', ...
+               'hmax1', 'hmax2', 'hmax3', 'gist', 'sift'};
+roiList     = {'V1', 'V2', 'V3', 'V4', 'FFA', 'LOC', 'PPA', 'LVC', 'HVC',  'VC'};
+
+% 图像特征数据
+imageFeatureFile = 'ImageFeatures.mat';
+
+
+%% 文件名设置
+predResultFile = fullfile(resultsDir, 'FeaturePrediction.mat');
+resultFile = fullfile(resultsDir, 'CategoryIdentification.mat');
+
+
+%% 分析主程序
+
+fprintf('%s started\n', mfilename);
+
+
+%% 初始化
+
+addpath(genpath('./lib'));
+
+if ~exist(resultsDir, 'dir'), mkdir(resultsDir); end;
+
+
+%% 加载数据
+
+% 加载图像特征
+fprintf('Loading image feature data...\n');
+
+[feat.dataSet, feat.metaData] = load_data(fullfile(dataDir, imageFeatureFile));
+
+%% 创建分析参数矩阵 (analysisParam)
+% 5个受试 * 10个roi * 13个特征层
+analysisParam = uint16(zeros(length(subjectList) * length(roiList) * length(featureList), 3)); 
+
+c = 1;
+for iSbj = 1:length(subjectList)
+for iRoi = 1:length(roiList)
+for iFeat = 1:length(featureList)
+    analysisParam(c, :) = [ iSbj, iRoi, iFeat ];
+    c =  c + 1;
+end
+end
+end
+
+
+%% 分析循环
+featpred = load(predResultFile);
+
+results = [];
+for n = 1:size(analysisParam, 1)
+
+    %% 初始化
+
+    % 在当前分析中获得数据索引
[…]

### 2023-06-05 visual/reconstruction/3_reconstruct_natural_image_different_combinations_of_CNN_layers.py

@@ -1,0 +1,186 @@
+'''
+Reconstruct natural images from CNN features decoded from the brain with different combinations of CNN layers.
+
+- ROI: VC
+- Layers: different combinations of CNN layers
+- Reconstruction algorithm: Without DGN + LBFGS
+'''
+
+
+import os
+import pickle
+from datetime import datetime
+from itertools import product
+
+import caffe
+import numpy as np
+import PIL.Image
+import scipy.io as sio
+
+from icnn.icnn_lbfgs import reconstruct_image  # Without DGN
+from icnn.utils import clip_extreme_value, estimate_cnn_feat_std, normalise_img
+
+
+# Settings ###################################################################
+
+# GPU usage settings
+caffe.set_mode_gpu()
+caffe.set_device(0)
+
+# Decoded features settings
+decoded_features_dir = './data/decodedfeatures'
+decode_feature_filename = lambda net, layer, subject, roi, image_type, image_label: os.path.join(decoded_features_dir, image_type, net, layer, subject, roi,
+                                                                                                 '%s-%s-%s-%s-%s-%s.mat' % (image_type, net, layer, subject, roi, image_label))
+
+# Data settings
+results_dir = './results'
+
+subjects_list = ['S1', 'S2', 'S3']
+
+rois_list = ['VC']
+
+network = 'VGG19'
+
+# DNN layer combinations
+layers_sets = {'layers-1to1' : ['conv1_1', 'conv1_2'],
+               'layers-1to3' : ['conv1_1', 'conv1_2', 'conv2_1', 'conv2_2',
+                                'conv3_1', 'conv3_2', 'conv3_3', 'conv3_4'],
+               'layers-1to5' : ['conv1_1', 'conv1_2', 'conv2_1', 'conv2_2',
+                                'conv3_1', 'conv3_2', 'conv3_3', 'conv3_4',
+                                'conv4_1', 'conv4_2', 'conv4_3', 'conv4_4',
+                                'conv5_1', 'conv5_2', 'conv5_3', 'conv5_4'],
+               'layers-1to7' : ['conv1_1', 'conv1_2', 'conv2_1', 'conv2_2',
+                                'conv3_1', 'conv3_2', 'conv3_3', 'conv3_4',
+                                'conv4_1', 'conv4_2', 'conv4_3', 'conv4_4',
+                                'conv5_1', 'conv5_2', 'conv5_3', 'conv5_4',
+                                'fc6', 'fc7']}
[…]

### 2023-06-05 visual/reconstruction/5_reconstruct_shape_image_different_ROI.py

@@ -1,0 +1,172 @@
+'''
+Reconstruct colored artificial shapes from CNN features decoded from multiple visual areas in the brain.
+
+- ROI: V1, V2, V3, V4, HVC, VC
+- Layers: all conv and fc layers
+- Reconstruction algorithm: Without DGN + LBFGS
+'''
+
+
+import os
+import pickle
+from datetime import datetime
+from itertools import product
+
+import caffe
+import numpy as np
+import PIL.Image
+import scipy.io as sio
+
+from icnn.icnn_lbfgs import reconstruct_image  # Without DGN
+from icnn.utils import clip_extreme_value, estimate_cnn_feat_std, normalise_img
+
+
+# Settings ###################################################################
+
+# GPU usage settings
+caffe.set_mode_gpu()
+caffe.set_device(0)
+
+# Decoded features settings
+decoded_features_dir = './data/decodedfeatures'
+decode_feature_filename = lambda net, layer, subject, roi, image_type, image_label: os.path.join(decoded_features_dir, image_type, net, layer, subject, roi,
+                                                                                                 '%s-%s-%s-%s-%s-%s.mat' % (image_type, net, layer, subject, roi, image_label))
+
+# Data settings
+results_dir = './results'
+
+subjects_list = ['S1', 'S2', 'S3']
+
+rois_list = ['V1', 'V2', 'V3', 'V4', 'HVC', 'VC']
+
+network = 'VGG19'
+
+# Images in figure 3A
+image_type = 'color_shape'
+image_label_list = ['Img0004',
+                    'Img0008',
+                    'Img0011']
+
+max_iteration = 200
+
+
+# Main #######################################################################
+
+# Initialize CNN -------------------------------------------------------------
+
+# Average image of ImageNet
+img_mean_file = './data/ilsvrc_2012_mean.npy'
+img_mean = np.load(img_mean_file)
+img_mean = np.float32([img_mean[0].mean(), img_mean[1].mean(), img_mean[2].mean()])
+
+# CNN model
+model_file = './net/VGG_ILSVRC_19_layers/VGG_ILSVRC_19_layers.caffemodel'
+prototxt_file = './net/VGG_ILSVRC_19_layers/VGG_ILSVRC_19_layers.prototxt'
+channel_swap = (2, 1, 0)
+net = caffe.Classifier(prototxt_file, model_file, mean=img_mean, channel_swap=channel_swap)
+h, w = net.blobs['data'].data.shape[-2:]
+net.blobs['data'].reshape(1, 3, h, w)
+
[…]

### 2023-06-05 visual/reconstruction/6_reconstruct_alphabet_image.py

@@ -1,0 +1,174 @@
+'''
+Reconstruct alphabetical letters shapes from CNN features decoded from the brain.
+
+- ROI: VC
+- Layers: all conv and fc layers
+- Reconstruction algorithm: Without DGN + LBFGS
+'''
+
+
+import os
+import pickle
+from datetime import datetime
+from itertools import product
+
+import caffe
+import numpy as np
+import PIL.Image
+import scipy.io as sio
+
+from icnn.icnn_lbfgs import reconstruct_image  # Without DGN
+from icnn.utils import clip_extreme_value, estimate_cnn_feat_std, normalise_img
+
+
+# Settings ###################################################################
+
+# GPU usage settings
+caffe.set_mode_gpu()
+caffe.set_device(0)
+
+# Decoded features settings
+decoded_features_dir = './data/decodedfeatures'
+decode_feature_filename = lambda net, layer, subject, roi, image_type, image_label: os.path.join(decoded_features_dir, image_type, net, layer, subject, roi,
+                                                                                                 '%s-%s-%s-%s-%s-%s.mat' % (image_type, net, layer, subject, roi, image_label))
+
+# Data settings
+results_dir = './results'
+
+subjects_list = ['S1', 'S2', 'S3']
+
+rois_list = ['VC']
+
+network = 'VGG19'
+
+# Images in figure 3A
+image_type = 'alphabet'
+image_label_list = ['Img0005',
+                    'Img0003',
+                    'Img0010',
+                    'Img0007',
+                    'Img0006']
+
+max_iteration = 200
+
+
+# Main #######################################################################
+
+# Initialize CNN -------------------------------------------------------------
+
+# Average image of ImageNet
+img_mean_file = './data/ilsvrc_2012_mean.npy'
+img_mean = np.load(img_mean_file)
+img_mean = np.float32([img_mean[0].mean(), img_mean[1].mean(), img_mean[2].mean()])
+
+# CNN model
+model_file = './net/VGG_ILSVRC_19_layers/VGG_ILSVRC_19_layers.caffemodel'
+prototxt_file = './net/VGG_ILSVRC_19_layers/VGG_ILSVRC_19_layers.prototxt'
+channel_swap = (2, 1, 0)
+net = caffe.Classifier(prototxt_file, model_file, mean=img_mean, channel_swap=channel_swap)
+h, w = net.blobs['data'].data.shape[-2:]
+net.blobs['data'].reshape(1, 3, h, w)
+
[…]

### 2023-06-05 visual/reconstruction/7_reconstruct_imagined_image.py

@@ -1,0 +1,179 @@
+'''
+Reconstruct imagined image from CNN features decoded from the brain.
+
+- ROI: VC
+- CNN: VGG19 with leaky ReLU layers and average pooling layers
+- Layers: all conv and fc layers
+- Reconstruction algorithm: Without DGN + LBFGS
+'''
+
+
+import os
+import pickle
+from datetime import datetime
+from itertools import product
+
+import caffe
+import numpy as np
+import PIL.Image
+import scipy.io as sio
+
+from icnn.icnn_lbfgs import reconstruct_image  # Without DGN
+from icnn.utils import clip_extreme_value, estimate_cnn_feat_std, normalise_img
+
+
+# Settings ###################################################################
+
+# GPU usage settings
+caffe.set_mode_gpu()
+caffe.set_device(0)
+
+# Decoded features settings
+decoded_features_dir = './data/decodedfeatures'
+decode_feature_filename = lambda net, layer, subject, roi, image_type, image_label: os.path.join(decoded_features_dir, image_type, net, layer, subject, roi,
+                                                                                                 '%s-%s-%s-%s-%s-%s.mat' % (image_type, net, layer, subject, roi, image_label))
+
+# Data settings
+results_dir = './results'
+
+subjects_list = ['S1', 'S2', 'S3']
+
+rois_list = ['VC']
+
+network = 'VGG19_leaky'
+
+# Images in figure 3A
+image_type = 'imagery'
+image_label_list = ['Img0001',
+                    'Img0005',
+                    'Img0009',
+                    'Img0008',
+                    'Img0003',
+                    'Img0010',
+                    'Img0021',
+                    'Img0022',
+                    'Img0020']
+
+max_iteration = 200
+
+
+# Main #######################################################################
+
+# Initialize CNN -------------------------------------------------------------
+
+# Average image of ImageNet
+img_mean_file = './data/ilsvrc_2012_mean.npy'
+img_mean = np.load(img_mean_file)
+img_mean = np.float32([img_mean[0].mean(), img_mean[1].mean(), img_mean[2].mean()])
+
+# CNN model
+model_file = './net/VGG_ILSVRC_19_layers/VGG_ILSVRC_19_layers.caffemodel'
+prototxt_file = './net/VGG_ILSVRC_19_layers/VGG_ILSVRC_19_layers_lrelu_avePool.prototxt'
+channel_swap = (2, 1, 0)
+net = caffe.Classifier(prototxt_file, model_file, mean=img_mean, channel_swap=channel_swap)
[…]

### 2023-06-25 auditory/latex/ban.tex
修复eps转pdf的异常
fix

@@
 
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=5.7in]{figs/pipeline.pdf}
-%	\caption{
-	%		\textbf{
-		%			The designed architecture in visual object tracking in humans.} 
-	%		The believable cortical areas implementing particular roles in smooth pursuit are indicated with rectangular modules.
-	%		The foveal view $f_t$ is obtained in the input frame $F_t$ with the spatial selector in the fovea. 
-	%		V1 and the ventral pathway learn the appearance representations $v_t$, 
-	%		and neurons in the dorsal pathway (including V1 and MT/MST) segment the salient object $d_t$ and background on the foveal view.
-	%		The refined representations $m_t$ are utilized to compute the working memory $h_t$.
-	%		Specifically, the FEF may be more important for initiating pursuit learning based on the target velocity,
-	%		and we combine FEF output $o_t$ and dorsal stream output $d_t$ into the next module. 
-	%		The cerebellum and brainstem together (including pontine nuclei (PN), flocculus, vermis and vestibular nuclei (VN)) are modeled by fully connected layers (FCs) to generate attention $a_{t+1}$, appearance $\alpha_{t+1}$, and eye position correction signals $\Delta p$,
-	%		even the final eye movement ($\Delta p_t$) via the oculomotor.
-	%		All black arrows indicate that information flows within one time-step, 
-	%		while the gray colored arrows represent the temporal connections.  
-	%	}
-%	\label{fig:pipeline}
-%\end{figure*}
+\begin{figure*}
+	\centering
+	\includegraphics[width=5.7in]{figs/pipeline.pdf}
+	\caption{
+	\textbf{
+	The designed architecture in auditory recognition for humans.}
+	The believable cortical areas implementing particular roles in auditory recognition are indicated with rectangular modules.
+	The auditory neural signal $f_t$ is obtained for input voice $F_t$ with hair cells in cochlea. 
+	In ventral pathway, A1 learn the auditory representations $v_t$, 
+	and neurons in the ventral "what" pathway (including V1, Belt, PB and T2/T3) extract auditory features on preprocessed neural signal $m_t$.
+	The input representations $m_t$ are utilized to compute temporal and rate codes $a_t$ via primary cortex A1.
+	Specifically, the Belt and PB may be more important for refining features based on the temporal and rate codes $a_t$,
+	and we feed PB output $p_t$ into the next module. 
+	The middle A1, Belt, PB and superior temporal cortex are recurrent.
+	The coder are modeled by fully connected layers (FCs) to generate auditory category.
+	All black arrows indicate that information flows within one time-step, 
+	while the gray colored arrows represent the temporal connections.
+	}
+	\label{fig:pipeline}
+\end{figure*}
 
 \subsubsection{Cochlear and MFCC features}
-For the mel-frequency cepstral coefficient (MFCC) model, the MIR toolbox was used to extract multiple music-related features from the dataset (Lartillot et al., 2008).
+Mel-frequency cepstral coefficient (MFCC) model is used to extract multiple music-related features from the dataset\cite{rabiner2010theory}.
 Consistent with a previous neuroimaging study on music (Alluri et al., 2012), we extracted the following 24 features: 
@@
 
+\subsection{Humans have specialized cortical neurons that encode pitch and harmonics}
+Pitch perception is crucial for perceiving speech and music and for recognizing auditory objects in a complex acoustic environment.
+Pitch is the percept that allows harmonically structured periodic sounds to be perceived and ordered on a musical scale.
+Pitch carries crucial linguistic information in tonal languages such as Chinese and prosodic information in European languages.
+We use pitch to identify a particular voice from a noisy background in a cocktail party.
+When listening to an orchestra, we hear the melody of the soloist over the background of accompanying instruments.
+
+An important phenomenon for understanding pitch is the perception of “missing fundamental,” also referred to as the residue pitch.
+When the harmonics of a fundamental frequency are played together, the pitch is perceived as the fundamental frequency even if the fundamental frequency is missing.
+For example, the harmonics of the fundamental frequency of 200 Hz are at 400, 600, 800 Hz, and so on.
+Playing the frequencies 400, 600, and 800 Hz together will generate a pitch perception of 200 Hz, even though a distinct frequency component of 200 Hz is not physically present in the sound.
+We encounter this phenomenon routinely when we listen to music over speakers that are too small to generate sounds at low frequencies.
+
+Many combinations of frequencies can give rise to a common fundamental frequency or pitch, making it a particularly valuable auditory cue.
+This is especially useful when pitch conveys behaviorally important information, as in the case of human speech or animal vocalizations.
+Sounds propagated through the environment can become spectrally degraded, losing high or low frequencies.
+While such spectral filtering distorts spectral information, the perception of the missing fundamental is robust despite the loss of some harmonic components.
+
+The ability to perceive pitch is not unique to humans; 
+birds, cats, and monkeys can also pick out pitch.
+Monkeys are capable of spectral pitch discrimination, melody recognition, and octave generalization, each of which requires the perception of pitch.
+Marmoset monkeys (Callithrix jacchus), a highly vocal New World primate species whose hearing range is similar to that of humans, exhibit human-like pitch perception.
+Marmosets are able to discriminate a missing fundamental in harmonic sounds with a precision as small as one semitone for the periodicity above 440 Hz.
+
+Given that both humans and some animals experience a pitch that generalizes across a variety of sounds with the same periodicity (including harmonic sounds with a missing fundamental), it is reasonable to expect that some neurons extract pitch from complex sounds.
+Xiaoqin Wang and his colleagues discovered a decade ago that a small region in the auditory cortex of marmoset monkeys contains “pitch-selective neurons.”
+These neurons are tuned to pure tones with a best frequency and respond to harmonic complexes with a fundamental frequency near its best frequency even when the harmonics lay outside the neuron’s excitatory-frequency response area (Figure 28–13A).
+
+A pitch-selective neuron responds to pitch-evoking sounds (eg, harmonic sounds, click trains) when the pitch is near the neuron’s preferred best frequency.
+Pitch-selective neurons increase their firing rates as the behavioral salience of pitch increases and prefer sounds with periodicity over aperiodic sounds.
+It is important to note that the pitch-selective neurons in marmoset monkeys, which extract and code for pitch embedded in harmonic sounds (a highly nonlinear computation), are distinctly different from neurons in subcortical areas or A1 that merely “reflect” information on pitch in their firing patterns.
+
+The region containing the pitch-selective neurons in marmoset monkeys is confined to the low-frequency border of A1, the rostral auditory cortex (area R), and lateral belt areas (Figure 28–13B).
+Human imaging studies have identified a restricted region at the lateral end of Heschl’s gyrus anterolateral to A1 that extracts pitch of harmonic complex sounds and is sensitive to changes in pitch salience.
+The location of this region mirrors the location of the pitch center in marmoset monkeys (Figure 28–13B).
+
+The core regions of auditory cortex in marmosets also contain a class of harmonic template neurons that respond weakly or not at all to pure tones or twotone combinations but respond strongly to particular combinations of multiple harmonics.
+The harmonic template neurons show stronger responses to harmonic sounds than inharmonic sounds and selectivity for particular harmonic structures.
+In contrast to the pitch-selective neurons that are localized within a small cortical region lateral to the low-frequency border between A1 and R and have best frequencies less than 1,000 Hz, the harmonic template neurons are distributed across A1 and R and have best frequencies ranging from approximately 1 kHz to approximately 32 kHz, a range that covers the entire hearing range of marmosets.
+
+Whereas in the periphery single auditory nerve fibers encode individual components of harmonic sounds, the properties of the harmonic template neurons reveal harmonically structured receptive fields for extracting harmonic patterns.
+The change in neural representation of harmonic sounds from auditory nerve fibers to the auditory cortex reflects a principle of neural coding in sensory systems.
+Neurons in sensory pathways transform the representation of physical features, such as the frequency of sounds in hearing or luminance of images in vision, into a representation of perceptual features, such as pitch in hearing or curvature in vision.
+Such features lead to the formation of auditory or visual percepts.
+The harmonic template neurons in the auditory cortex are key to processing sounds with harmonic structures such as animal vocalizations, human speech, and music.
+
 \section{CONCLUSION}
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Authors/HaidongWang.eps}}]{Haidong Wang}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./authors/HaidongWang}}]{Haidong Wang}
 	 received the B.E.

### 2023-12-28 auditory/circuit/docs/documentation_standalone.tex
添加听觉皮层回路模型

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb,amsmath,amsfonts}
\usepackage{hyperref}
\usepackage[a4paper, margin=.5in]{geometry}

%opening
\title{Documentation: A Unifying Mechanistic Model of Excitatory-Inhibitory Interactions in the Auditory Cortex}
\author{Youngmin Park}

\newcommand{\y}[1]{{\texttt{#1}}}

\begin{document}

\maketitle

%\begin{abstract}

%\end{abstract}

\section{Introduction}
The primary tools of this paper are Python (with numpy, scipy, matplotlib), XPPAUTO (XPPAUT or XPP for short) \cite{ermentrout2002simulating}, a Python binding for XPP, \y{Py\_XPPCALL} \cite{xppy}, and Brian2 \cite{Stimberg595710}. Please contact me with any questions about these programs: \y{ympark1988@gmail.com}\footnote{I used XPP extensively in my PhD, and XPP was created by and continues to be developed by Bard Ermentrout, my doctoral advisor. In addition, I am one of the primary contributors to \y{Py\_XPPCALL}.}.

I highly recommend using Ubuntu, since the most stable versions of XPP are currently on Ubuntu. At the time of writing, I have used Ubuntu 16.04 (Python 2.7.12, numpy 1.15.2, scipy 1.1.0, matplotlib 2.2.3), Ubuntu 18.04.2 (Python 2.7.15rc1, numpy 1.15.2, scipy 1.1.0, matplotlib 2.2.3), and XPPAUT version 8 to successfully run all code.

\section{Rate Models}

Rate models are implemented in XPPAUTO. In order to plot the simulations, I run XPPAUTO through the Python binding \y{Py\_XPPCALL}.

\subsection{XPPAUTO}
All rate models were implemented in \texttt{XPPAUTO} for convenience. XPP auto uses an almost plain-text file format for simulating ordinary differential equations (ODEs). There is extensive documentation on XPPAUTO on Bard's website:
\url{http://www.math.pitt.edu/~bard/xpp/help/xppodes.html}. The linked page provides full documentation of ode file syntax. XPPAUTO also comes with a graphical user interface (GUI), but this will not be needed for this documentation. The XPP .ode files for this project are located in the directory \url{https://github.com/geffenlab/park_geffen/rate_models/xpp}.

Let us take a look at one of the ode files, \texttt{cols3\_fs.ode}, which is the three-unit rate model for the forward suppression paradigm. The file begins with a function definition and a bunch of parameters:
\begin{verbatim}
f(x)=al*heav(x)*x*heav(1/al-x)+heav(x-1/al)
dan(x)=exp(-tl*x)
p al = 3

p wee=1.1,wep=2,wes=1
# either wpe=1.2, or wpp=1.8 to reduce SOM disinhibition activity.
p wpe=1.,wpp=2,wps=2

p wse=6,wss=0,wsp=0
p wee2=1,wpe2=1.25,wse2=.125
#p wee2=1,wpe2=1.5,wse2=.25

par tau1=1,tau2=1
par et=.7,pt=1,st=1
par pv_opto=0,som_opto=0

p q=1.3,tl=1
p taud1=150,taud2=10
p tde1=150,tde2=2
p lat=.65
\end{verbatim}
Comment lines are denoted by the pound symbol (\#). The function \texttt{f} is the firing-rate function, which corresponds to Equation (2) in the manuscript (There is a typo in the current manuscript. All simulations were run using the correct $f$ as shown in the code). The function is zero until $x=0$, at which point the function increases linearly with slope $\text{al}=3$ as a function of $x$, until the function reaches the value 1 (when $x=1/\text{al}$, at which point the function ``saturates'' at the value 1. The second function, which I named \y{dan}, is a decaying exponential with rate \y{tl}, which we will later use to modulate the square-wave inputs into the model. We use the same firing rate function for all models, which is a common choice in modeling studies \cite{natan2015complementary,yarden2017stimulus}.

The notation \texttt{p} and \texttt{par} both denote a line consisting of parameters. The first set of parameters:
\begin{verbatim}
p wee=1.1,wep=2,wes=1
p wpe=1.,wpp=2,wps=2

p wse=6,wss=0,wsp=0
p wee2=1,wpe2=1.25,wse2=.125
\end{verbatim}
are for recurrent excitation (\texttt{wee}), PV-to-Pyr inhibition (\texttt{wep}), SOM-to-Pyr inhibition (\texttt{wes}), Pyr-to-PV excitation (\texttt{wpe}), recurrent PV inhibition (\y{wpp}), SOM-to-PV inhibition (\y{wps}), Pyr-to-SOM excitation (\y{wse}), PV-to-SOM inhibition (\y{wsp}), and recurrent SOM inhibition (\y{wss}). The remaining terms are for the lateral weights. Lateral Pyr-to-Pyr (\y{wee2}), lateral Pyr-to-PV (\y{wpe2}), and lateral Pyr-to-SOM (\y{wse2}). These parameters appear in Equation 4, and in the unit equations on page 2.

The next set of parameters:
\begin{verbatim}
par tau1=1,tau2=1
par et=.7,pt=1,st=1
par pv_opto=0,som_opto=0
\end{verbatim}
Are time constants \y{tau1} and \y{tau2} are for the inhibitory populations, PV, and SOM, respectively. This rate model is written so that 1 time unit is 10ms, i.e., \y{tau1=1} means $\tau_1 = 10$ms \cite{tsodyks1997neural,natan2015complementary}. If needed, one could perform the necessary transformation in time so the model displays the correct time units by default.

The next line is for thresholds in the excitatory activity \y{et}, PV activity \y{pt}, and SOM activity \y{st}. These thresholds are minimum values beyond which the population activity can influence the postsynaptic population. Finally, the \y{pv\_opto} and \y{som\_opto} parameters set the level of optogenetic \textit{inactivation}, i.e., positive values of \y{pv\_opto} inactivation PVs, and likewise for \y{som\_opto}. In the paper I flip these numbers for readability.

Next up:
\begin{verbatim}
p q=1.3,tl=1
p taud1=150,taud2=10
p tde1=150,tde2=2
p lat=.65 
\end{verbatim}
\y{q} is the strength of the thalamic inputs into the model. \y{tl} is the decay time constant in the exponential function \y{dan}. The depression time constants are \y{taud1} and \y{taud2}, again in the same units, so $\tau_{D_1} = 1500$ms and $\tau_{D_2} = 100$ms. We can ignore \y{tde1,tde2} as they are not used in the code. The parameter \y{lat} determines the strength of lateral thalamic inputs.

The next chunk of code sets up the stimuli in the forward suppression paradigm.
\begin{verbatim}
par t0=10,dur=5,isi=2

t1on=t0
t1off=t1on+dur
t2on=t1off+isi
t2off=t2on+dur

t3on=t2off+isi
t3off=t3on+dur
t4on=t3off+isi
t4off=t4on+dur

t5on=t4off+isi
t5off=t5on+dur
t6on=t5off+isi
t6off=t6on+dur

t7on=t6off+isi
t7off=t7on+dur
t8on=t7off+isi
t8off=t8on+dur

# thalamic inputs with fast timescale depression
gt1(x)=heav(x-t1on)*heav(t1off-x)*dan(x-t1on)
gt2(x)=heav(x-t2on)*heav(t2off-x)*dan(x-t2on)
gt3(x)=heav(x-t3on)*heav(t3off-x)*dan(x-t3on)
gt4(x)=heav(x-t4on)*heav(t4off-x)*dan(x-t4on)

gt5(x)=heav(x-t5on)*heav(t5off-x)*dan(x-t5on)
gt6(x)=heav(x-t6on)*heav(t6off-x)*dan(x-t6on)
gt7(x)=heav(x-t7on)*heav(t7off-x)*dan(x-t7on)
gt8(x)=heav(x-t8on)*heav(t8off-x)*dan(x-t8on)

par mode=1
i1(x)=g1*q*if(mode-1)then(0)else(gt1(x))
i2(x)=g2*q*if(mode-2)then(gt2(x))else(gt1(x)+gt2(x))
i3(x)=g3*q*if(mode-3)then(0)else(gt1(x))
\end{verbatim}

The functions \y{gt1(x)} through \y{gt8(x)} represent 8 different stimuli with stimulus onset times of \y{t1on} through \y{t8on}, stimulus offset times of \y{t1off} through \y{t8off}. The \y{heav} functions are heaviside functions, and the multiplication of two of them as written forms a square pulse. This pulse is then modulated by the exponential decay function \y{dan}. For the forward suppression paradigm, we only need two stimuli, so we only use \y{gt1} and \y{gt2} for the rest of the code.

The \y{mode} parameter sets which unit receives the first input. If \y{mode=1}, then
\begin{verbatim}
i1(x)=g1*q*gt1(x)
i2(x)=g2*q*gt2(x)
i3(x)=0
\end{verbatim}
For more information on how the if statement works in XPP, see the bottom of \url{http://www.math.pitt.edu/~bard/xpp/help/xppodes.html}. If the \y{mode} parameter is set to \y{mode=2}, then
\begin{verbatim}
i1(x)=0
i2(x)=g2*q*(gt1(x)+gt2(x))
i3(x)=0
\end{verbatim}
and so on. The terms \y{g1} and \y{g2} are variables and satisfy the equations
\begin{verbatim}
g1'=(1-g1)/taud1-i1(y)/taud2
g2'=(1-g2)/taud1-i2(y)/taud2
g3'=(1-g3)/taud1-i3(y)/taud2
\end{verbatim}
where \y{y'=1} and all \y{g1,g2,g3} are initialized with a value of 1. The trivial ODE \y{y'=1} is needed for technical reasons related to XPP that isn't too important for now. Anyway, as \y{i1(y)} activates, it ``depletes'' vesicles and forces \y{g1} to decay on a fast timescale. With no other activation of \y{i1}, \y{g1} recovers slowly back to its original value of 1.

Now we finally reach the actual model equations:
\begin{verbatim}
u1'=-u1+f(wee*u1-(wep-damp*(1-g1))*p1-(wes+samp*(1-g1))*s1-et+i1(y)+i2(y)*lat+wee2*u2/1.5)
p1'=(-p1+f(wpe*u1-wpp*p1-wps*s1-pt +i1(y)+i2(y)*lat +wpe2*u2-pv_opto ))/tau1
s1'=(-s1+f(wse*u1-wsp*p1-wss*s1-st                  +wse2*u2-som_opto ))/tau2

u2'=-u2+f(wee*u2-(wep-damp*(1-g2))*p2-(wes+samp*(1-g2))*s2-et+(i1(y)+i3(y))*lat+i2(y)+wee2*(u1+u3)/2)
p2'=(-p2+f(wpe*u2-wpp*p2-wps*s2-pt +(i1(y)+i3(y))*lat+i2(y)+wpe2*(u1+u3)/2 -pv_opto ))/tau1
s2'=(-s2+f(wse*u2-wsp*p2-wss*s2-st                         +wse2*(u1+u3)/2 -som_opto ))/tau2

u3'=-u3+f(wee*u3-(wep-damp*(1-g3))*p3-(wes+samp*(1-g3))*s3-et+i2(y)*lat+i3(y)+wee2*u2/1.5)
p3'=(-p3+f(wpe*u3-wpp*p3-wps*s3-pt +i2(y)*lat+i3(y) +wpe2*u2-pv_opto ))/tau1
s3'=(-s3+f(wse*u3-wsp*p3-wss*s3-st                  +wse2*u2-som_opto ))/tau2
\end{verbatim}
These are the implemented versions of the 3 unit equations from the manuscript:
Th first or left unit satisfies
\begin{align*}
 \tau_u u_1' &= -u_1 + f( w_{ee} u_1 - (w_{ep}(t)-aD_1)p_1 - (w_{es}(t)+b F_1)s_1 + qI_1(t) + w_{ee}^* u_2),\\
 \tau_p p_1' &= -p_1 + f( w_{pe} u_1 - w_{pp}p_1 - w_{ps}s_1 + I_\text{Opt,PV} + qI_1(t) + w_{pe}^* u_2),\\
 \tau_s s_1' &= -s_1 + f( w_{se} u_1 - w_{sp}p_1 - w_{ss}s_1 + I_\text{Opt,SOM} + w_{se}^* u_2),
\end{align*}
where $I_1 = i_1(t) +i_2(t)\alpha$. The second, or center unit, satisfies
\begin{align*}
 \tau_u u_2' &= -u_2 + f( w_{ee} u_2 - (w_{ep}(t)-aD_2)p_2 - (w_{es}(t)+b F_2)s_2 + qI_2(t) + w_{ee}^* (u_1+u_3)/2),\\
 \tau_p p_2' &= -p_2 + f( w_{pe} u_2 - w_{pp}p_2 - w_{ps}s_2 + I_\text{Opt,PV} + qI_2(t) + w_{pe}^* (u_1+u_3)/2),\\
 \tau_s s_2' &= -s_2 + f( w_{se} u_2 - w_{sp}p_2 - w_{ss}s_2 + I_\text{Opt,SOM} + w_{se}^* u_2),
\end{align*}
where $I_2(t) = (i_1(t)+i_3(t))\alpha +i_2(t)$. Finally, the third, or right unit, satisfies
\begin{align*}
 \tau_u u_3' &= -u_3 + f( w_{ee} u_3 - (w_{ep}(t)-aD_3)p_3 - (w_{es}(t)+b F_3)s_3 + qI_3(t) + w_{ee}^* u_2),\\
 \tau_p p_3' &= -p_3 + f( w_{pe} u_3 - w_{pp}p_3 - w_{ps}s_3 + I_\text{Opt,PV} + qI_3(t) + w_{pe}^* u_2),\\
 \tau_s s_3' &= -s_3 + f( w_{se} u_3 - w_{sp}p_3 - w_{ss}s_3 + I_\text{Opt,SOM} + w_{se}^* u_2), 
\end{align*}
where $I_3 = i_2(t) +i_3(t)\alpha$.

The remaining lines are mostly related to using the XPPAUTO GUI. Choices that affect the integration are
\begin{verbatim}
@ bounds=100000
@ maxstor=1000000
@ total=200
@ dt=.1
\end{verbatim}
\y{bounds} is simply the maximum possible value of any solution before XPPAUTO gives up. \y{maxstor} sets the max storage XPPAUTO is allowed to take from memory. \y{total} is the total time of the simulation, and \y{dt} is the time step.

\subsection{Python Visualization}
These XPP ode files can be run using the XPP GUI, but we will run them using Python using \y{Py\_XPPCALL}. I have tried to include enough documentation to help users understand the basics \url{https://github.com/youngmp/Py_XPPCALL}. The Python files that run the XPP files are are located in \url{https://github.com/geffenlab/park_geffen/rate_models}. The Python file that reads the ODE file from the example above is called \y{cols3\_fs.py}. You should be able to run the python file directly.
\begin{verbatim}
$ python cols3_fs.py
\end{verbatim}
There will be lots of text that appears. These were mostly for debugging purposes and can be turned off by commenting the print statements in this file and in \y{xppcall.py}. After the script runs, a few plots should appear. I like to set up the plotting framework in the individual Python files before finalizing them in \y{generate\_figures.py}.

The \y{main} function calls all the relevant files. In brief, the loop runs three different stimulus patterns. The first stimulates the left unit then the center unit with 50ms tones and a 20ms inter-stimulus-interval. The second stimulates the center unit twice with the same time intervals. The third stimulates the right unit then the center unit with the same time intervals. This is a simple version of the forward suppression paradigm. These three sets of stimuli are repeated for PV inactivation and SOM inactivation. The max firing rate response is then recorded into a matrix and plotted.

Much of this logic appears in its final form in the function \y{r3\_s3\_fs\_full} in \y{generate\_figures.py}. The difference is that the function \y{r3\_s3\_fs\_full} includes the spiking model simulation and plots. I've tried to comment on most things... Let me know if you have any questions.

The remaining Python files for simulating the rate model, \y{cols3\_ssa} and \y{natan2015\_simple\_linear} have a similar construction. The \y{main} function in each script contains all the preliminary plotting/visualization code, which you can use to tinker and learn the ins and outs of the python/xpp interface. Seriously, play with those all you want.

The final version of the plotting functions appear in \y{generate\_figures.py}. Don't change those unless you're familiar with the code.

\section{Spiking Models}

\section{Generating Figures}

\y{generate\_figures.py} is the master plotting function for the paper. Most figure papers are generated here, except for a couple that were created in Inkscape. This file serves as a technical documentation of the code. In the main function, comments note which function belong to which figure.

\begin{thebibliography}{1}

\bibitem{ermentrout2002simulating}
Bard Ermentrout.
\newblock {\em Simulating, analyzing, and animating dynamical systems: a guide
  to XPPAUT for researchers and students}, volume~14.
\newblock Siam, 2002.

\bibitem{natan2015complementary}
Ryan~G Natan, John~J Briguglio, Laetitia Mwilambwe-Tshilobo, Sara~I Jones, Mark
  Aizenberg, Ethan~M Goldberg, and Maria~Neimark Geffen.
\newblock Complementary control of sensory adaptation by two types of cortical
  interneurons.
\newblock {\em Elife}, 4, 2015.

\bibitem{xppy}
Ilya Prokin and Youngmin Park.
\newblock Pyxppcall.
\newblock \url{https://github.com/iprokin/Py_XPPCALL}, 2017.

\bibitem{Stimberg595710}
Marcel Stimberg, Romain Brette, and Dan F.~M. Goodman.
\newblock Brian 2: an intuitive and efficient neural simulator.
\newblock {\em bioRxiv}, 2019.

\bibitem{tsodyks1997neural}
Misha~V Tsodyks and Henry Markram.
\newblock The neural code between neocortical pyramidal neurons depends on
  neurotransmitter release probability.
\newblock {\em Proceedings of the national academy of sciences},
  94(2):719--723, 1997.

\bibitem{yarden2017stimulus}
Tohar~S Yarden and Israel Nelken.
\newblock Stimulus-specific adaptation in a recurrent network model of primary
  auditory cortex.
\newblock {\em PLoS computational biology}, 13(3):e1005437, 2017.

\end{thebibliography}
\end{document}

### 2024-01-16 auditory/emergence/audioset.py
添加音乐感知浮现

@@ -1,0 +1,329 @@
+import os
+import pandas as pd
+import numpy as np
+import gzip
+
+from torchvision.datasets import VisionDataset
+from scipy.io import wavfile
+
+class AudioSet(VisionDataset):
+    def __init__(self, root, transform = None, target_transform = None, train=True):
+        super(AudioSet, self).__init__(root, transform=transform,
+                                            target_transform=target_transform)
+        self.train = train
+        if self.train:
+            df = pd.read_csv(os.path.join(root, 'balanced_train_segments.csv'), 
+                             skiprows=3, sep=', ', usecols=[0, 1, 3], header=None, quotechar='"', engine='python')
+            self._dir = os.path.join(root, 'train')
+            _file_names = [x[:11] for x in os.listdir(self._dir)]
+            df = df[df[0].isin(_file_names)]
+        else:
+            df = pd.read_csv(os.path.join(root, 'eval_segments.csv'), 
+                             skiprows=3, sep=', ', usecols=[0, 1, 3], header=None, quotechar='"', engine='python')
+            self._dir = os.path.join(root, 'valid')
+            _file_names = [x[:11] for x in os.listdir(self._dir)]
+            df = df[df[0].isin(_file_names)]
+            
+        _class_labels_indices = pd.read_csv(os.path.join(root, 'class_labels_indices.csv'))
+        _label2index = {}
+        for row in _class_labels_indices[['mid', 'index']].iterrows():
+            _label2index[row[1]['mid']] = row[1]['index']
+            
+        def convert(x):
+            s = x[1:-1]
+            labels = s.split(',')
+            return np.array([_label2index[l] for l in labels])
+        
+        df[3] = df[3].map(convert)
+        
+        self.sample_rate = 22050
+        self.paths = []
+        for x, y in zip(df[0].to_list(), df[1].to_list()):
+            self.paths.append('{yid}_{start:.3f}.wav.gz'.format(yid=x, start=y))
+
+        self.targets = df[3].to_list()
+        
+        _idx2class = {}
+        for row in _class_labels_indices[['index', 'display_name']].iterrows():
+            _idx2class[row[1]['index']] = row[1]['display_name']
+        self.idx2class = _idx2class
+        self.n_class = 527
+        
+    def loader(self, path):
+        with gzip.open(os.path.join(self._dir, path), "rb") as f:
+            _, x = wavfile.read(f)
+        if len(x.shape) > 1:
+            return np.copy(x[:, 0])
+        return np.copy(x)
+    
[…]

### 2024-06-11 auditory/latex/ban.tex
添加音乐感知浮现
fix

@@
 
+% 初级听觉皮层
 \subsubsection{Primary Auditory Cortex}
-Typical, input is a data matrix represented by a time-frequency representation. 
+Typical, the processed signals reach the primary auditory cortex located in the temporal lobe of the brain. 
+This area is critical for processing the basic characteristics of sound such as pitch and volume.
+The input is a data matrix represented by a time-frequency representation $ m_t $. 
 Typically there is a Mel-spectrogram.
 
-The spatial selector selects the foveal view $f_t$ for the current frame $F_t$,
-and its output is transmitted to two interconnected cortical pathways.
-The ventral pathway recognizes the tracked targets 
-and the dorsal pathway learns motion features in the field of view. 
-We present the dorsal pathway with the MT/MST that analyses motion features, as depicted in Figure~\ref{fig:pipeline};
+The auditory pathway selects view $f_t$ for the current frame $F_t$,
+and its output is transmitted to ventral "what" cortical pathways.
+The ventral pathway recognizes the heard sound in the field of sound. 
+We present the ventral pathway that extracts audio features, as depicted in Figure~\ref{fig:pipeline};
 and computes a foreground segmentation $d_t$ of the foveal view.
 
-(1) \textbf{Retina}: 
-The spatial attention mechanism in our model pipeline is modeled according to~\cite{RATM}. 
-An input frame $F_t \in R^{W \times H}$ forms matrices $M_t^x \in R^{w \times W}$ and $M_t^y \in R^{h \times H}$.
-A row of the matrix contains a gaussian distribution. 
-The position and width of the gaussian distribution determine which parts of the input frame are selected as the foveal view $f_t$ in the retina.
-Therefore, the foveal view $f_t \in R^{h \times w}$ can be denoted as
-\begin{equation}
-	f_t = M_t^y F_t (M_t^x)^T.
-\end{equation}
-We represent attention with the distributive center, the variance and the stride of the distributive center of continuous matrix rows.
-Unlike the study~\cite{hart}, only the stride and center are predicted through LSTM;
-however, variance only relies on stride.
-The operation avoids extravagant bias when estimating a smaller variance, contributing to a faster learning speed. 
-In addition, the utilized size of $f_t$ relies on the experimental analysis.
-
-(2) \textbf{Ventral Pathway}: 
 The ventral pathway converts the foveal view $f_t$ into a fixed dimension vector $v_t$ including spatial and appearance features of the tracked object. 
@@
 
-(3) \textbf{Dorsal Pathway}: 
 The dorsal pathway (MT/MST) is implemented as a DFN~\cite{brabandere2016dynamic} 
@@
 
-\subsubsection{Belt and PB}
-
-The proposed method depends on the ability to estimate the object appearance and position in the next frame; 
+% 带状区和伞状区
+\subsubsection{Belt and PB area}
+
+The Belt and Parabelt (PB) areas are significant regions within the auditory cortex, specifically associated with the processing of complex auditory information. 
+These areas are located around A1 and are involved in higher-order auditory processing.
+Here's an overview of their functions and significance:
+
+% Belt Area
+The Belt area is the first level of auditory cortex that surrounds A1.
+It receives direct projections from the core area and is considered a secondary auditory processing region.
+The Belt area is crucial for processing more complex features of sound than the core area. 
+It integrates information from the core area and provides a more sophisticated analysis of sound, such as complex sound patterns and where sounds are coming from in space.
+
+% Parabelt Area (PB):
+The Parabelt area is located adjacent to the Belt area and represents an even higher level of auditory processing.
+It receives inputs from the Belt area and has connections with various other brain regions, including those involved in memory, emotion, and multisensory integration.
+The Parabelt area is thought to play a key role in complex auditory scene analysis, such as distinguishing between different voices in a crowded room or understanding modulated sounds like music or speech.
+It is also involved in the integration of auditory information with other sensory modalities, contributing to our perception of a cohesive environment.
+
+The Belt and Parabelt regions highlight the hierarchical nature of auditory processing in the brain, where sounds are analyzed in increasingly complex and integrative stages. 
+This organization allows for the nuanced perception and interpretation of a wide range of sounds, essential for communication, environmental awareness, and interaction with the world.
+
+The proposed method depends on the ability to estimate the response in next frame; 
 and therefore, it heavily relies on state prediction. 
-The LSTM can utilize spatial-temporal and appearance features, 
-and enables the proposed model to handle occlusion and drifting target representations, such as a tracked target obscured by other distractors.
-
-The LSTM module, presented in Figure~\ref{fig:pipeline} and named the FEF, utilizes the output error to predict eye movement. 
+The recurrent module can utilize spatial-temporal features, 
+and enables the proposed model to handle temporal prediction.
+
+The recurrent module, presented in Figure~\ref{fig:pipeline} and named the Belt and PB. 
 Similar predictive actions exist when smooth pursuit is demonstrated in the FEF area that accepts the output of the dorsal stream~\cite{b11,b13,b14}. 
 The output error goes to zero when the delay between object and eye movement is decreased in model training; 
-thus, LSTM requires inferring eye motion without image input.
+thus, recurrent module requires inferring eye motion without image input.
 The refined representations $m_t$ are used to update the hidden state $h_t$ in the FEF. 
@@
 
-\subsubsection{Middle and Superior Temporal Cortex}
-
-Then we utilize the output $d_t$ and $o_t$ to estimate eye movement $\Delta p_t$, attention $a_{t+1}$ and appearance $\alpha_{t+1}$.
-\begin{equation} \label{FC}
-	\Delta p_t, \Delta a_{t+1}, \alpha_{t+1} = \text{FC}(conc(d_t), o_t),
-\end{equation}
-\begin{equation} \label{attention}
-	a_{t+1} = a_t + tanh(c) \Delta a_{t+1},
-\end{equation}
-where $c$ is a trainable coefficient initialized with a low parameter to restrict the update size during learning. 
-Equations (\ref{LSTM}) to (\ref{attention}) describe the information update. 
-We calculate the gaze position with an accumulation of attention variations. 
-Because spatial attention is learned to estimate the position of the tracked object in the next frame, as depicted in Section~\ref{sec:loss}, a gaze position $p_t$ relative to the attention at time $t$ is predicted.
-\begin{equation}
-	p_t = a_t + \Delta p_t.
-\end{equation}
-
-In addition, we refer to the discoveries and the idea~\cite{b9} that the brainstem and the cerebellum both instantiate an inverse dynamics controller (IDC)~\cite{purkinje_IDC}. 
-Like~\cite{b9}, we suppose that the IDC is perfect, and thus we can denote 
-\begin{equation}
-	\Delta p_t = \Delta p,
-\end{equation}
-where $\Delta p$ is the low pass filter of eye motion.
-Based on this hypothesis, we will not implement IDC in our study.
+% 中颞皮层和上颞皮层
+\subsubsection{Middle and Superior Temporal Cortex (T2/T3)}
+
+The middle temporal (MT or T2) and superior temporal (ST or T3) cortices are key regions in the brain involved in various aspects of sensory processing, including auditory recognition. 
+These areas, particularly located in the temporal lobe, play critical roles in interpreting and understanding complex auditory signals such as speech and music. 
+Here's an overview of their functions related to auditory recognition:
+
+While the middle temporal cortex is primarily recognized for its role in processing visual motion (hence also known as V5), it also interacts with auditory processing, particularly when it comes to the perception of motion or the integration of audio-visual information.
+In the context of auditory recognition, the MT cortex can be involved when there's a need to integrate visual cues with auditory signals, as seen in speech perception where lip-reading and auditory cues are combined.
+
+The superior temporal cortex, particularly the superior temporal gyrus (STG), is directly involved in auditory processing and is crucial for recognizing complex sounds, including speech and music.
+Within the STG, the primary auditory cortex (Heschl's gyrus) is the initial cortical area to receive auditory information. 
+The surrounding areas, including the planum temporale, are heavily involved in processing the higher-order aspects of sound, such as language comprehension.
+The posterior part of the superior temporal gyrus and the adjacent superior temporal sulcus (STS) are involved in processing the more complex attributes of sounds, like prosody and the emotional content of speech.
+The superior temporal cortex has extensive connections with other brain regions, facilitating its role in integrating auditory information with other sensory modalities and cognitive processes.
+
+In auditory recognition, these areas work together to decode and interpret sounds, enabling individuals to recognize and respond to various auditory stimuli effectively. 
+This includes distinguishing between different speech sounds, understanding spoken language, appreciating music, and recognizing environmental sounds, which are crucial for effective communication and interaction with the environment.
 
@@
 
-\subsubsection{Tracking Loss}
-To locate the tracked target, we design the tracking loss between the output of the BAN and the true label. 
-We refer to the study~\cite{UnitBox} and denote the tracking loss as the negative logarithm of their intersection over union (IoU) between predicted bounding box $p_t$ and ground truth $\hat{p}_t$:
+\subsubsection{Recognition Loss}
+To recognize music, we design the recognition loss between the output of BAN and the true label. 
+We refer to the study~\cite{UnitBox} and denote the recognition loss as the negative logarithm of their intersection over union (IoU) between predicted label $p_t$ and ground truth $\hat{p}_t$:
 \begin{equation}
@@
 To train the BAN better, we utilize three attention loss terms.
-The first item makes the intersection area between the predicted attention $a_t$ and the bounding box $p_t$ as large as possible. 
+The first item makes the similarity between predicted attention $a_t$ and the bounding box $p_t$ as same as possible. 
 The second item prevents obtaining a very large width, and the log functions are applied to maintain stability in the calculation. 
@@
 
+% 数据分析
 \section{Data Analysis} \label{sec:data_analysis}
@@
 
+% 类脑分数
 \section{BAS: Brain-like Auditory Score} \label{sec:bas}
@@
 \subsection{Datasets} \label{sec:datasets}
+
+% 刺激
 We use the GTZAN dataset which has been the most widely used in the music genre classification task.
 The dataset contains 30-second audio file including 10 different genres including reggae, classical, country, jazz, metal, pop, disco, hiphop, rock and blues.
+From the original music pieces, we randomly selected 54 music pieces (30 s, 22,050 Hz) from each music genre. 
+A total of 540 music pieces were thus used in the current study. 
+A 15 s music clip was randomly extracted from each music piece.
+We applied 2 s of fade-in and fade-out effects for each music clip. 
+All music clips were normalized for their root mean square.
+
+% fMRI
+The fMRI experiment consisted of 12 training runs and 6 test runs (18 runs in total). 
+Each run lasted 10 min and consisted of 40 music clips.
+A total of 480 music clips were used for the training runs, and the left-out 60 music clips were used for the test runs. 
+In each test run, a set of 10 music clips (150 s in total) was presented four times in the same order. 
+There was no repetition in the training runs.
+
+% 行为
+To compare brain activation patterns and behavioral performance, we utilized the subjects to participate in additional behavioral experiments. 
+These music clips were selected randomly from the 460 music pieces which were not used in the MRI experiment. 
+The subjects selected the music genre of the target music clip by filling in 1 of 10 cells on the answer sheet displayed on a laptop computer screen. 
+The music clips were presented through closed headphones. 
+Music clips were presented in the same order as in the MRI experiments. 
+Subjects were allowed to listen to each music clip only once.
 
@@
 	\footnotesize
-	\caption{Frame sequences 1-12 to construct our Tracking-Gump dataset.
-		These 12 short videos in which only one salient object appears in the video sequence are selected. 
-		This ensures that most of subjects will gaze at the object constantly.}
-
-	\label{tab:track_seg}
-
-	\begin{tabular}{p{1.0cm}<{\centering}p{0.9cm}<{\centering}p{1.6cm}<{\centering}p{1.5cm}<{\centering}p{0.7cm}<{\centering}}
+	\caption{Age, sex, and number of fMRI runs and samples for each participant.}
+
+	\label{tab:fMRI_runs}
+
+	\begin{tabular}{p{2.9cm}<{\centering}p{0.6cm}<{\centering}p{0.6cm}<{\centering}p{0.7cm}<{\centering}p{0.7cm}<{\centering}p{0.7cm}<{\centering}}
 		\toprule[1.5pt]
-		Segment ID & Video ID  & Start Frame    & End Frame  & TRs   \\ \midrule[1pt]
-		1     		  & 3 			   & 02:30.00 	   & 02:48.00  & 10  		  \\
-		2  	 		  & 4 			   & 14:50.00 	   & 15:14.00  & 13   		  \\
-		3   		  & 5 			   & 01:32.00 	   & 01:48.00  & 9   		  \\
-		4   		  & 5 			   & 05:02.00  	   & 05:20.00  & 10   		  \\
-		5   		  & 6 			   & 00:08.00 	   & 00:24.00  & 9   		  \\
-		6   		  & 6 			   & 06:56.00 	   & 07:10.02  & 8   		  \\
-		7   		  & 6 			   & 09:42.00  	   & 09:56.01  & 8   		  \\
-		8   		  & 6 			   & 12:26.00 	   & 12:44.00  & 12		      \\
-		9   		  & 7  			   & 06:44.00 	   & 07:06.00  & 12		      \\
-		10  		  & 7 			   & 07:26.00 	   & 08:28.00  & 32		      \\
-		11  		  & 7 			   & 08:30.00 	   & 08:52.00  & 12		      \\
-		12 			  & 7 			   & 10:40.00 	   & 11:10.00  & 16		      \\
+		 & sub-001  & sub-002    & sub-003  & sub-004 & sub-005  \\ \midrule[1pt]
+		Age     		  & 30 			   & 33 	   & 23  & 30  & 25		  \\
+		Sex     		  & M  & F 	   & M  & M  & F		  \\
+		Music experience (years)     		  & 12  & 15 	   & 4  & 12  & 10		  \\
+		Total fMRI runs     		  & 18  & 18 	   & 18  & 18  & 18		  \\
+		train samples (volumes) & 4800  & 4800 	   & 4800  & 4800  & 4800		  \\
+		test samples (volumes) & 600  & 600 	   & 600  & 600  & 600		  \\
 		\bottomrule[1.5pt]
@@
 we convert the preliminary step size of 4 to 1 
-and remove a pooling module to retain spatial features, as depicted in Figure~\ref{fig:structure_analysis}. 
+and remove a pooling module to retain spatial features, as depicted in Figure~\ref{fig:pipeline}. 
 In this way, the size of the obtained feature is $14 \times 14 \times 384$, and the size of the input foveal view is $56 \times 56$.
@@
 The starting sequence length is five and increases every twelve iterations.
+
+\subsection{BAN circuitry analysis}
+While we believe that BAN is a closer approximation to the anatomy of the ventral auditory stream than current state-of-the-art deep ANNs because we specifically limit the number of areas and include recurrence, it is still far from complete in many ways.
+From a neuroscientist's point of view, on top of the lack of biologically-plausible learning mechanisms (self-supervised or unsupervised), a better model of the ventral auditory pathway would include more anatomical and circuitry-level details, such as cochlea or medial geniculate nucleus.
+Similarly, adding a skip connection was not informed by cortical circuitry properties but rather proposed by He et al.\cite{he2016deep} as a means to alleviate the degradation problem in very deep architectures.
+But we note that not just any architectural choices work.
+We have tested hundreds of architectures before finding CORnet-S type of circuitries, as Depicted in Figure~\ref{fig:structure_analysis}.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\linewidth]{figs/structure_analysis}
+	\caption{
+		\textbf{
+			BAN circuitry analysis.  
+		}
+		Each row indicates how GTZAN top-1 and Brain-Score change with respect to the baseline model (in bold) when a particular hyperparameter is changed.
+	}
+	\label{fig:structure_analysis}
+\end{figure}
 
